### 2015-05-20 paper.tex
Copied text from thesis.

\documentclass[english]{short-notes}

\title{Hochschild cohomology of torus-equivariant D-modules}
\author{Clemens Koppensteiner}

\usepackage{math-gl}

\addbibresource{math.bib}

\let\stack\mathbf

\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}
\newcommand\catDModMon[2]{\catDMod{#1}^{#2-\mathup{mon}}}
\newcommand\catDModHolMon[2]{\catDModHol{#1}^{#2-\mathup{mon}}}

\newcommand\dR{\mathrm{dR}}
\newcommand{\renstar}{\blacktriangle}

\newcommand{\HCoh}{\operatorname{HH}^\cx}
\newcommand\ΓdR{Γ_{\mkern-4mu\dR}}

\newcommand\opalg[1]{#1^{\mathrm{op}}}

\renewcommand\B{\stack{B}}
\newcommand\mappingstack{\mathbfup{Maps}}
\newcommand\X{\mathbb{X}}

\newcommand\Γsub[1]{\Gamma_{\mkern-3mu#1}}

\newcommand\ls[1]{\mathbfcal{L} #1}
\newcommand\lsY[1]{\mathbfcal{L}_{\stack Y} #1}
\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
\newcommand\clsY[1]{\overline{\mathbfcal{L}}_{\stack Y} #1}
\newcommand\lsc[1]{\mathbfcal{L}^c #1}
\newcommand\lscY[1]{\mathbfcal{L}_{\stack Y}^c #1}

\newfontfamily\cyrillicfont[Script=Cyrillic]{XITS}
\newcommand\cyrmath[1]{\textit{\cyrillicfont #1}}

%\newcommand\schemels[1]{\mathcal{L}\mkern2.5mu #1}
%\newcommand\schemecls[1]{\overline{\mathcal{L}}\mkern2.5mu #1}
%\newcommand\schemelsc[1]{\mathcal{L}\mkern2.5mu^c #1}
\newcommand\schemels[2][]{\cyrmath{Л}\mkern1.5mu^{#1}#2}
\newcommand\schemelsY[2][]{\schemels[#1]{_{\stack Y}#2}}
\newcommand\schemecls[2][]{\overline{\cyrmath{Л}}\mkern1.5mu^{#1}#2}
\newcommand\schemeclsY[2][]{\schemecls[#1]{_{\stack Y}#2}}
\newcommand\schemelsc[2][]{\cyrmath{Л}\mkern1.5mu^{\if\relax\detokenize{#1}\relax\else#1,\fi c} #2}
\newcommand\schemelscY[2][]{\schemelsc[#1]{_{\stack Y}#2}}

\newcommand\schemei{\cyrmath{и}}
\newcommand\schemej{\cyrmath{й}}
\newcommand\schemeq{\cyrmath{к}}
\newcommand\schemeh{h'}
%\newcommand\schemep{\cyrmath{п}}
%\newcommand\schemei{\tilde{\imath}}
%\newcommand\schemej{\tilde{\jmath}}
%\newcommand\schemeq{\tilde{q}}
%\newcommand\schemeh{\tilde{h}}

\newcommand\Stab{\operatorname{Stab}}

\newcommand\goodstack{good}
\newcommand\Goodstack{Good}
\newcommand\goodness{goodness}

\newcommand\dualize{\mathbb D}

% Formatting of upper case roman numerals (in references).
\newcommand{\RomanNum}[1]{\textsc{\MakeLowercase{#1}}}

\begin{document}

\maketitle

\section{Introduction}

Given a manifold $X$ and a category of sheaves on $X$, microlocal geometry asks whether these sheaves can be localized not just on $X$ but also with respect to codirections, i.e.~on the cotangent space $T^*X$.
For example, for constructible sheaves this leads to the notion of microsupport discussed in detail in \cite{KashiwaraSchapira:1994:SheavesOnManifolds}.
More generally, given a category of sheaves on a space $X$, we can ask whether it is possible to localize them on some space that is strictly larger than $X$ itself.

Even more generally one can ask the following question: Given a $k$-linear category $\cat C$, can one find a space over which $\cat C$ localizes?
For co-complete compactly generated triangulated categories one answer is provided by \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
To each map from a graded-commutative ring $R$ to the center of $\cat C$ the authors associate the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves).

We are led to consider the universal algebra acting on the category with this construction, i.e.~the \emph{Hochschild cohomology} of $\cat C$.
For a complete (pre-triangulated) dg category $\cat C$ the Hochschild cohomology is the dg algebra of derived endomorphisms of the identity functor of $\cat C$:
\[
    \HCoh(\cat C)
    = \operatorname{\mathbf{R}Hom}(\id[\cat C], \id[\cat C])
    = \Hom_{\cat{Funct}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
\]
The ring $R = \bigoplus \operatorname{HH}^{2n}(\HCoh(\cat C)$ is commutative and hence one can define for each $A ∈ \cat C$ the support $\supp_R A$ as a subset of $\Spec R$.
Thus understanding the Hochschild cohomology of a dg category can be an important step to understanding the category itself.

This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme yields the singular support of coherent sheaves which already served as the motivation for the first part of this thesis.
More concretely, Arinkin and Gaitsgory used singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture \cite{ArinkinGaitsgory:2015:SingularSupport}.
By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.

A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
We will review the general setup and basic properties of D-modules on (QCA) stacks in Chapter~\ref{ch:d-mod:pre}.
The upshot is that we have an isomorphism of dg algebras
\begin{equation}
    \label{eq:intro:d-mod:d-mod-hcoh}
    \HCoh(\catDMod{\stack X}) \cong \Hom_{\catDMod{X×X}}(Δ_*ω_{\stack X}, Δ_*ω_{\stack X}),
\end{equation}
where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Lemma show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
However, if $\stack X$ is not an algebraic space (and hence $Δ$ is not proper) then the situation becomes more complicated.

By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod:d-mod-hcoh} as
\[
    \HCoh(\catDMod{\stack X}) \cong
    \opalg{\Hom_{\catDMod{X}}(k_{\stack X}, Δ^!Δ_!k_{\stack X})} =
    \opalg{\ΓdR(\stack X, Δ^!Δ_!k_{\stack X})}.
\]
It is now tempting to look at the Cartesian square
\[
    \begin{tikzcd}
        \ls \stack X \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
where
\[
    \ls \stack X = \stack X ×\limits_{\stack X × \stack X} \stack X
\]
is the (derived) loop space of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
Naively we could expect the existence of an isomorphism
\begin{equation}
    \label{eq:intro:d-mod:naive}
    \ΓdR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
    \ΓdR(\stack X, p_{2,!}p₁^! k_{\stack X}).
\end{equation}
Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\as1$ is an easy counter-example).

In Chapter~\ref{ch:d-mod:strategy} we will investigate how to quantify the cone of the morphism
\[
    p_{2,!}p₁^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
\]
and thus the failure of the naive isomorphism \eqref{eq:intro:d-mod:naive} to hold.
As an application, we will prove the following theorem, giving a class of stacks where \eqref{eq:intro:d-mod:naive} is indeed an isomorphism.

\begin{Thm}\label{thm:d-mod:main}
    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
    Then there is a canonical isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{X/G}\bigr)
        \cong
        \opalg{\ΓdR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)},
    \]
    where the algebra structure on $\ΓdR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
\end{Thm}

\section{Prerequisites}%
\label{ch:d-mod:pre}

We fix an algebraically closed base field $k$ of characteristic $0$.
All stacks in this thesis are assumed to be algebraic QCA stacks over $k$.
As we will summarize in Section~\ref{sec:d-mod:pre:d-mods}, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
In particular for any stack $\stack X$ we have:
\begin{itemize}
    \item The diagonal morphism $Δ\colon \stack X → \stack X × \stack X$ is schematic.
    \item There exists a scheme $Z$ with a smooth and surjective map $Z → \stack X$.
    \item $\stack X$ is quasi-compact.
    \item The automorphism groups of the geometric points of $\stack X$ are affine.
    \item The loop space (or inertia stack) $\ls \stack X = \stack X ×_{\stack X × \stack X} \stack X$ is of finite presentation over $\stack X$.
\end{itemize}
The first two conditions ensure that the stack is algebraic, the other three that it is quasi-compact with affine automorphism group (QCA).
For details on QCA stacks we refer to~\cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
Every quotient of a scheme of finite type over $k$ by an affine algebraic group is a QCA stack, and we will be mainly interested in these.

In order to correctly define categories of D-modules on stacks it is necessary to work with dg-categories.
We refer to \cite{Keller:2006:OnDGCategories} for an introduction to dg categories.
It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2014-draft:HigherAlgebra}, which can be done via the nerve construction \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}. %\cite[Section~1.3.1]{Lurie:2014-draft:HigherAlgebra}
We will switch between those two languages without explicitly mentioning the intervening constructions and apply results from \cite{Lurie:2014-draft:HigherAlgebra} to dg categories.
Fortunately, a superficial knowledge of dg/$∞$-categories should be sufficient for reading this thesis.

\subsection{D-modules on stacks}
\label{sec:d-mod:pre:d-mods}

We will be primarily concerned with D-modules on (quotient) stacks.
Unfortunately there is currently no comprehensive text available that covers all the basic constructions and properties of D-modules on stacks (or even the \emph{dg category} of D-modules on schemes).
Thus we collect all the relevant properties (without proof) in this section.
The upshot is that the familiar \enquote{six functors formalism} essentially works for holonomic D-modules and schematic morphisms of stacks.

The category of D-modules on a stack $\stack X$ can be either constructed via descent \cite{BeilinsonDrifeld:unpublished:Hitchin,DrinfeldGaitsgory:2013:FinitenessQuestions} or equivalently as ind-coherent sheaves on the de Rham space of $\stack X$ \cite{GaitsgoryRozenblyum:2014:CrystalsAndDModules}.
While the first construction is more \enquote{hands on}, the second construction is often more useful from a theoretical point of view.
It is explained in detail in the upcoming book \cite{GaitsgoryRozenblyum:prelim:StudyInDAG} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and most of the following assertions are taken from there.

For any morphism $f\colon \stack X → \stack Y$ the constructions yield a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and (after some work) a not necessarily continuous functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
If $p\colon \stack X → \pt$ is the structure map then we set
\[
    \ΓdR(\stack X,\, {-}) = p_*({-}) \colon \catDMod{\stack X} → \catVect.
\]
The functor $\ΓdR$ is representable by a D-module $k_{\stack X}$, i.e.
\[
    \ΓdR(\stack X,\, {-}) = \Hom_{\catDMod{\stack X}}(k_{\stack X},\, {-}).
\]
Again we note that $\ΓdR(\stack X,\, {-})$ is usually not continuous and hence the object $k_{\stack X}$ not compact.

Let $Δ\colon \stack X → \stack X × \stack X$ be the diagonal.
The category $\catDMod{\stack X}$ has a monoidal structure given by the tensor product
\[
    \sheaf F \otimes \sheaf G = Δ^!\bigl( \sheaf F \boxtimes \sheaf G \bigr).
\]
The unit for this monoidal structure is $ω_{\stack X} = p^! k$.

We will be mainly concerned with the subcategory of holonomic D-modules since they enjoy extended functoriality.
\begin{Def}
    A $D$-module $\sheaf F ∈ \catDMod{\stack X}$ is called \emph{holonomic} if $f^!\sheaf F$ is holonomic for any smooth morphism $f\colon Z → \stack X$ from a scheme $Z$.
    The full subcategory of holonomic D-modules will be denoted $\catDModHol{\stack X}$.
\end{Def}

The following assertions mostly follow from their corresponding counterparts for schemes.
We refer to \cite{Braverman:LecturesOnAlgebraicDmodules} for proofs in the case of non-smooth schemes.

\begin{Prop}
    Let $f\colon \stack X → \stack Y$ be a schematic morphism.
    Then $f^!$ and $f_*$ restrict to functors
    \[
        f^!\colon \catDModHol{\stack Y} → \catDModHol{\stack X}
        \quad\text{and}\quad
        f_*\colon \catDModHol{\stack X} → \catDModHol{\stack Y}.
    \]
\end{Prop}

The Verdier duality functor on schemes induces an involutive anti auto-equivalence
\[
    \dualize_{\stack X}\colon \catDModHol{\stack X}^\mathrm{op} → \catDModHol{\stack X}
\]
such that for each smooth morphism $Z → \stack X$ of relative dimension $d$ from a scheme $Z$ one has
\[
    f^! ∘ \dualize_{\stack X} \cong \dualize_{Z} ∘ f^![-2d].
\]
The Verdier duality functor then allows us to define the \emph{non-standard functors} $f_!$ and $f^*$ for any schematic morphism $f\colon \stack X → \stack Y$ by
\begin{align*}
    f^* & = \dualize_{\stack X} ∘ f^! ∘ \dualize_{\stack Y} \colon \catDModHol{\stack Y} → \catDModHol{\stack X} \\
    \intertext{and}
    f_! & = \dualize_{\stack Y} ∘ f_* ∘ \dualize_{\stack X} \colon \catDModHol{\stack X} → \catDModHol{\stack Y}.
\end{align*}
We obtain adjoint pairs $(f_!,\, f^!)$ and $(f^*,\, f_*)$.
In some situations we can identify the non-standard functors with their standard counterparts.
If $f$ is smooth of relative dimension $d$ then $f^* = f^![-2d]$.
If $f$ is proper then $f_! = f_*$ and in particular $f_*$ is left adjoint to $f^!$.
The objects $ω_{\stack X}$ and $k_{\stack X}$ are always holonomic and
\[
    \dualize_{\stack X} ω_{\stack X} = k_{\stack X}.
\]
We have $k_{\stack X} = f^* k_{\stack Y}$ and if $\stack X$ is smooth, then $k_{\stack X} = ω_{\stack X}[-2\dim \stack X]$.

We will make use of the following lemma which follows from \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions}.

\begin{Lem}
    For a smooth and schematic morphism $f$ the functor $f^!$ is conservative.
\end{Lem}

\begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
    \label{prop:d-mod:pre:base-change}%
    Consider a Cartesian square
    \[
        \begin{tikzcd}
            \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
            \stack X₂ \arrow[r, "g"] & \stack Y
        \end{tikzcd}
    \]
    with schematic morphism $f$ (and hence $p$).
    Then there is a base change isomorphism
    \[
        p_* q^! \isoto g^! f_*
    \]
    of functors from $\catDMod{\stack{X₁}}$ to $\catDMod{\stack{X₂}}$.
    If furthermore $f$ (and hence $p$) is proper, then this isomorphism coincides with the natural transformation
    \[
        p_* q^! →
        p_* q^! f^! f_* =
        p_* p^! g^! f_* →
        g^! f_*
    \]
    induced by $(f_*,\,f^!)$ and $(p_*,\, p^!)$ adjunctions.
\end{Prop}

\begin{Prop}
    \label{prop:d-mod:pre:projection-formula}%
    If $f\colon \stack X → \stack Y$ is a schematic morphism then the projection formula holds, i.e.~there is a functorial isomorphism
    \[
        \sheaf F \otimes f_*(\sheaf G) \cong f_*\bigl( f^! \sheaf F \otimes \sheaf G)
    \]
    for $\sheaf F ∈ \catDMod{\stack Y}$ and $\sheaf G ∈ \catDMod{\stack X}$.
\end{Prop}

\begin{Rem}
    Propositions \ref{prop:d-mod:pre:base-change} and \ref{prop:d-mod:pre:projection-formula} hold more generally when $f$ is merely a \enquote{safe} morphism.
    Alternatively they hold in full generality after replacing $f_*$ by the \enquote{renormalized de Rham pushforward}.
    We fill not use either notion in this thesis and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
\end{Rem}

For D-modules on stacks we have the usual recollement package.
Let $i\colon \stack Z \hookrightarrow \stack X$ be a closed embedding and $j\colon \stack U \hookrightarrow \stack X$ the complementary open.
We have adjoint pairs $(i_*,\, i^!)$ and $(j^!,\, j_*)$.

\begin{Prop}[{\cite[Section~2.5]{GaitsgoryRozenblyum:2014:CrystalsAndDModules}}]
    \label{prop:d-mod:recollement-std}%
    There is an exact triangle of functors
    \[
        i_*i^! → \id → j_*j^!
    \]
    on $\catDMod{\stack X}$, the adjunction morphisms
    \[
        \id → i^!i_*
        \quad\text{and}\quad
        j^!j_* → \id
    \]
    are isomorphisms, the functors $j^!i_*$ and $i^!j_*$ vanish and $i_*$ and $j_*$ are full embeddings.
\end{Prop}

On holonomic D-modules we have the additional adjoint pairs $(i^*,\, i_*)$ and $(j_!,\, j^*)$.
By applying duality to Proposition~\ref{prop:d-mod:recollement-std} we obtain the distinguished triangle
\[
    j_! j^* → \id → i_*i^*
\]
and the identity $i^*j_! = 0$ on holonomic D-modules.
Further, the functor $j_!$ is a full embedding $\catDModHol{\stack U} \hookrightarrow \catDModHol{\stack X}$.

It is often useful to consider the pullback of a D-module on $\stack X$ to a smooth cover.

\begin{Def}
    \label{def:d-mod:pre:monodromic}%
    Let $X$ be a scheme with an action of an algebraic group $G$ and let $p\colon X → X/G$ be the quotient map.
    The \emph{monodromic} subcategory $\catDModMon{X}{G} ⊆ \catDMod{X}$ is the full subcategory generated by the essential image of $p^!\colon \catDMod{X/G} → \catDMod{X}$ (or equivalently by the essential image of $p^*$).
\end{Def}

\begin{Thm}[Contraction principle~{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
    \label{thm:d-mod:pre:contraction_principle}%
    Let $X$ be a scheme with an action by $\Gm$ that extends to an action of the monoid $\as 1$.
    Let $i\colon X^0 \hookrightarrow X$ be the closed subscheme of $\Gm$-fixed points and let $π\colon X → X^0$ be the contraction morphism induced by the $\Gm$-equivariant morphism $\as 1 → \{0\}$.
    Then there is an isomorphism of functors
    \[
        i^* \cong π_* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}.
    \]
\end{Thm}

\subsection{Monads}
\label{sec:d-mod:pre:monads}

We will deduce Theorem~\ref{thm:d-mod:main} from a isomorphism of monads on $\catDMod{\stack X}$.
In this section we give a short introduction to the theory of monads and the specific constructions that we will use.
However, in the interest of readability we will mainly do so informally, skipping over the intricacies of $∞$-categories.
The interested reader can find the correct $∞$-categorical formulations in the given references.

Thus we think of a \emph{monad} on a category $\cat C$ as consisting of a triple $(T, η, μ)$, where $T\colon \cat C → \cat C$ is an endofunctor of $\cat C$, and $η\colon \id_{\cat C} → T$ and $μ\colon T∘T → T$ are natural transformations such that the diagrams
\begin{equation}
    \label{eq:d-mod:pre:monad-identities}
    \begin{tikzcd}
        T³ \arrow[r, "Tμ"] \arrow[d, "μT"'] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
    \quad\text{and}\quad
    \begin{tikzcd}
        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
        T² \arrow[r, "μ"'] & T
    \end{tikzcd}
\end{equation}
commute.
Alternatively, we can think of $T$ being a monoid in the category of endofunctors of $\cat C$ with the monoidal structure given by composition of endofunctors.
This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2014-draft:HigherAlgebra}.

Let $X$ be an object of the category $\cat C$.
Then $T$ gives the vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
\[
    (f,g) \mapsto μ_X ∘ Tf ∘ g,
\]
\[
    \begin{tikzcd}
        X \arrow[r, "g"] & TX \arrow[r, "Tf"] & T²X \arrow[r, "μ_X"] & TX.
    \end{tikzcd}
\]
The identities~\ref{eq:d-mod:pre:monad-identities} ensure that the algebra is associative and unital.

The most common source of monads is from a pair of adjoint functors $F\colon \cat C \rightleftarrows \cat D \cocolon G$.
One simply sets $T = G ∘ F$ and $η$ and $μ$ are given by the adjunction morphisms
\[
    \id[\cat C] → G ∘ F = T
    \qquad\text{and}\qquad
    T² = G ∘ (F ∘ G) ∘ F → G ∘ F = T.
\]
We note that the correct construction in more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2014-draft:HigherAlgebra}.
For any $X ∈ \cat C$ the algebra construction above gives an isomorphism of algebras
\[
    \Hom_{\cat C}(X, (GF)(X)) \cong
    \Hom_{\cat D}(FX, FX).
\]

Another common way to obtain monads in geometry is via a groupoid.
Recall that a groupoid $G_{\cx}$ in stacks consists of a stack $\stack G₀$ of \enquote{objects} and a stack $\stack G₁$ of \enquote{morphisms} together with
\begin{itemize}
    \item \emph{source} and \emph{target} maps $s,t\colon \stack G₁ \rightrightarrows \stack G₀$,
    \item a \emph{unit} $e\colon G₀ → G₁$,
    \item a \emph{multiplication} (or \emph{composition}) map $m\colon \stack G₁ ×\limits_{s,\stack G₀,t} \stack G₁ → \stack G₁$,
    \item an \emph{inverse} map $ι\colon \stack G₁ → \stack G₁$,
\end{itemize}
such that
\begin{itemize}
    \item $s ∘ e = t ∘ e = \id_{\stack G₀}$,
    \item $s ∘ m = s ∘ p₂$ and $t ∘ m = t ∘ p₁$ (where $p_i\colon \stack G₁ ×_{s,\stack G₀,t} \stack G₁$ are the projection maps).
    \item $m$ is associative,
    \item $ι$ interchanges $s$ and $t$ and is an inverse for $m$,
\end{itemize}
where all identities have to be understood in the correct $∞$-categorical way \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory}.

\begin{Ex}
    For our purpose the most important example is the following:
    Let $f\colon \stack X → \stack S$ be a morphism of stacks.
    We set $\stack G_0 = \stack X$ and $\stack G₁ = \stack X ×_\stack S \stack X$.
    The source and target maps are given by $p₁$ and $p₂$, the unit by the diagonal $Δ\colon \stack X → \stack X×_\stack S\stack X$, the inverse by interchanging the factors and multiplication is $p₁₃\colon \stack X ×_\stack S \stack X ×_\stack S \stack X → \stack X×_\stack S\stack X$.
\end{Ex}

Let us for the moment assume that $s$ (and hence $t$) is proper and schematic.
In this case the maps $e$ and $m$ are also proper, since $s ∘ e = \id_{\stack G₀}$ and $s ∘ m = s ∘ p₂$ are proper.
In particular the functors $e^!\colon \catDMod{\stack G₁} → \catDMod{\stack G₀}$ and $m^!\colon \catDMod{\stack G₁} → \catDMod{\stack G₁ ×_{\stack G₀} \stack G₁}$ have left adjoints given by $e_*$ and $m_*$ respectively.
This allows us to give the endofunctor $T = s_*t^!$ of $\catDMod{\stack G₀}$ the structure of a monad in the following way:

\begin{itemize}
    \item By $(e_*,e^!)$-adjunction we have a transformation
        \[
            \id = (s∘e)_*(t∘e)^! = s_*e_*e^!t^! → s_*t^! = T.
        \]
    \item Consider the following commutative diagram
        \[
            \begin{tikzcd}[column sep=small]
                {} & & \stack G₁ \arrow[dddll, bend right, "s"] \arrow[dddrr, bend left, "t"] & & \\
                & & \stack G₁ ×_{\stack G₀} \stack G₁ \arrow[u, "m"] \arrow[dl, "p₂"] \arrow[dr, "p₁"] & & \\
                & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & \\
                \stack G₀ & & \stack G₀ & & \stack G₀
            \end{tikzcd}
        \]
        with Cartesian middle square.
        Proper base change and $(m_*,m^!)$-adjunction gives a transformation
        \[
            T² =
            s_*t^!s_*t^! =
            (s∘p₂)_*(t∘p₁)^! =
            (s∘m)_*(t∘m)^! =
            s_*m_*m^!t^! →
            s_*t^! =
            T.
        \]
\end{itemize}

In the non-$∞$-categorical setting one could easily check by hand that this is indeed a monad.
To obtain the corresponding derived statement one applies an argument similar to \cite[Section~\RomanNum{II}.1.7.2]{GaitsgoryRozenblyum:prelim:StudyInDAG}.
We will discuss a version of this below.

Let now $f\colon \stack X → \stack Y$ be schematic and proper.
The Cartesian diagram
\[
    \begin{tikzcd}
        \stack X ×_{\stack Y} \stack X \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack X \arrow[d, "f"] \\
        \stack X \arrow[r, "f"] & \stack Y
    \end{tikzcd}
\]
induces a groupoid with $\stack{G}₀ = \stack X$ and $\stack{G}₁ = \stack X ×_{\stack Y} \stack X$.
The above constructions now give two monads on $\catDMod{\stack{X}}$: one by $(f_*,f^!)$ adjunction and one from the groupoid structure.
The base change isomorphism
\[
    p_{t,*} p_s^! → f^! f_*
\]
gives an identification of these monads and hence of the algebras that they induce, i.e.~for any $\sheaf F ∈ \catDMod{\stack X}$ we have
\[
    \Hom(\sheaf F,\, p_{t,*} p_s^!\sheaf F) \cong
    \Hom(\sheaf F,\, f^! f_* \sheaf F) \cong
    \Hom(f_*\sheaf F,\, f_* \sheaf F).
\]

We will need to apply this construction for non-proper $f$.
Unfortunately, in this case none of the adjunctions used to define the monads are available.
We rectify this by restricting to the full subcategory of of holonomic D-modules and using the $!$-pushforward functors instead of the $*$-pushforward ones.
Of course, by doing so we do not automatically have base change isomorphisms available anymore.
Thus we have to explicitly require that all necessary base changes hold (this is usually called the Beck-Chevalley condition).

In order to formulate the condition, we need the concept of the \emph{nerve} of a groupoid.
This is the simplicial stack, also denoted $\stack{G}_\cx$, with
\[
    \stack G_i = \underbrace{\stack G₁ ×_{\stack G₀} \dotsb ×_{\stack G₀} \stack G₁}_{\text{$i$ factors}}.
\]
We refer to \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory} for the correct $∞$-categorical setup.
The following lemma is now an immediate corollary of \cite[Lemma~\RomanNum{II}.1.7.1.4]{GaitsgoryRozenblyum:prelim:StudyInDAG} or \cite[Theorem~4.7.6.2]{Lurie:2014-draft:HigherAlgebra}.

\begin{Lem}
    \label{lem:d-mod:pre:groupoid_monad_hol}%
    Let $f\colon \stack X → \stack Y$ be a schematic morphism of stacks and let $\stack G_\cx$ be the corresponding groupoid.
    For each map $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ consider the corresponding square
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[r, "p_s"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
        \end{tikzcd}
    \]
    where the vertical arrows are induced by $F$.
    Assume that for each such square the base change composition
    \[
        p_{F+1,!} p_s^! →
        p_{F+1,!} p_s^! p_F^! p_{F,!} =
        p_{F+1,!} p_{F+1}^! p_s^!  p_{F,!} →
        p_s^! p_{F,!}
    \]
    given by the adjunction morphisms is an isomorphism of functors from the category $\catDModHol{\stack G_n}$ to $\catDModHol{\stack G_{m+1}}$.
    Then the endofunctor $p_{t,!} p_s^!$ of $\catDModHol{\stack X}$ has a canonical structure of a monad and as such is isomorphic to the adjunction monad $f^!f_!$.
\end{Lem}

\subsection{Hochschild cohomology}

We recall that the Hochschild cohomology of a dg category $\cat C$ is the algebra of derived endomorphisms of the identity functor,
\[
    \HCoh(\cat C) = \mathbb{R}\mathrm{Hom}(\id[\cat C],\, \id[\cat C]).
\]
For the exact definition of the category $\mathbb{R}\mathrm{Hom} = \cat{Funct}(\cat C, \cat C)$ we refer to \cite{Keller:2006:OnDGCategories}.
Instead we will give a more concrete construction via kernels which can be applied to $\catDMod{\stack X}$.
For this let us restrict to the case of co-complete dg categories and let $\cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)$ be the full subcategory of $\cat{Funct}(\cat C, \cat C)$ spanned by the continuous functors.
Then, since $\id[\cat C]$ is evidently continuous, we have
\[
    \HCoh(\cat C) =
    \Hom_{\cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
\]
Let us further assume that $\cat C$ is dualizable with dual $\cat C^\dual$.
Thus there is a unit map
\[
    η\colon \catVect → \cat C^\dual \otimes \cat C
\]
and a counit map
\[
    ε\colon \cat C^\dual \otimes \cat C → \catVect
\]
fulfilling the usual compatibilities (cf.~\cite[Section~2]{BenZviNadler:arXiv:NonlinearTraces}).
Let $u = η(k)$.
Then to each continuous endofunctor $F$ of $\cat C$ we can associate its kernel $\id[\cat C^\dual] \otimes F(u) ∈ \cat C^\dual \otimes \cat C$ and conversely to each kernel $Q ∈ \cat C^\dual \otimes \cat C$ we can associate the endofunctor
\[
    \cat C
    \xrightarrow{\id[\cat C] \otimes Q}
    \cat C \otimes \cat C^\dual \otimes \cat C
    \xrightarrow{ε \otimes \id[\cat C]}
    \cat C.
\]
These assignments are mutually inverse and give an equivalence of dg categories
\[
    \cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)
    \cong
    \cat C^\dual \otimes \cat C.
\]
In particular, the kernel for the identity is $u$ and hence we have
\[
    \HCoh(\cat C) =
    \Hom_{\cat C^\dual \otimes \cat C}(u, u).
\]
Let us now consider the case of $\cat C = \catDMod{\stack X}$ for a stack $X$.
Let $p\colon \stack X → \pt$ be the structure morphism and $Δ\colon \stack X → \stack X × \stack X$ the diagonal.
By \cite[Section~8.4]{DrinfeldGaitsgory:2013:FinitenessQuestions} the category $\catDMod{\stack X}$ is dualizable and there is a canonical indentification
\[
    \catDMod{\stack X}^\dual \otimes \catDMod{\stack X} \cong \catDMod{\stack X × \stack X}
\]
such that the unit map is given by $Δ_*p^!$ and thus we have
\[
    u = Δ_*ω_{\stack X}.
\]
We summarize the above discussion in the following lemma.

\begin{Lem}\label{lem:d-mod:pre:hcoh}
    Let $\stack X$ be a stack.
    Then the Hochschild cohomology of $\catDMod{\stack X}$ is given by the dg algebra
    \[
        \HCoh(\catDMod{\stack X}) =
        \Hom_{\catDMod{\stack X × \stack X}}(Δ_*ω_{\stack X},\, Δ_*ω_{\stack X}).
    \]
\end{Lem}

\section{Base change for non-proper maps}
\label{ch:d-mod:strategy}

Let $\stack X$ be any stack, where we recall that all stacks are assumed to be QCA.
We are interested in computing the Hochschild cohomology
\[
    \HCoh\bigl(\catDMod{\stack X}\bigr).
\]
Let $Δ\colon \stack X → \stack X × \stack X$ is the diagonal map, which by assumption is schematic.
The dualizing module $ω_{\stack X}$ is always holonomic.
Thus we have $\dualize Δ_* ω_{\stack X} = Δ_! k_{\stack X}$.
With this we observe that
\begin{align*}
    \HCoh\bigl(\catDMod{\stack X}\bigr)
    & = \Hom_{\catDMod{\stack X × \stack X}}(Δ_* ω_{\stack X},\, Δ_* ω_{\stack X}) & &\text{(Lemma~\ref{lem:d-mod:pre:hcoh})} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(Δ_! k_{\stack X},\, Δ_! k_{\stack X})} & & \text{(duality)} \\
    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})} & & \text{(adjunction)} \\
    & = \opalg{\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr)},
\end{align*}
where the algebra structure on $\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr) = \Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})$ is the one induced by the $(Δ_!,Δ^!)$-adjunction monad.
Consider the Cartesian square
\[
    \begin{tikzcd}
        \ls{\stack X} \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
        \stack X \arrow[r, "Δ"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us assume for the moment that $Δ$ (and hence $p_i$) was proper.
Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:d-mod:pre:monads} we have an isomorphism of monads
\begin{equation}
    \label{eq:d-mod:central_iso}
    p_{2,!} p₁^! → Δ^!Δ_!,
\end{equation}
which induces an isomorphism of algebras
\[
    \ΓdR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)
    →
    \ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr).
\]
Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
Thus in general \eqref{eq:d-mod:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{2,!} p₁^!$.
We would like to apply Lemma~\ref{lem:d-mod:pre:groupoid_monad_hol} to construct a monad in special cases.
Thus the goal of this chapter is to give a criterion for the assumptions of Lemma~\ref{lem:d-mod:pre:groupoid_monad_hol}, i.e.~for base change to hold.

\begin{Ex}
    The base change morphism \eqref{eq:d-mod:central_iso} is also an isomorphism if $Δ$ is smooth.
    In particular this implies that the \enquote{naive expectation} holds for $\stack X = \B G$ for any algebraic group $G$, i.e.~we have
    \[
        \HCoh(\catDMod{\B G}) = \opalg{\ΓdR\bigl(\B G,\, p_{2,!} p₁^! k_{\B G}\bigr)}.
    \]
    An argument similar to \cite{BenZvi:mathoverflow:CohomologyOfGmodG} shows that there is a further isomorphism
    \[
        \ΓdR\bigl(\B G,\, p_{2,!} p₁^! k_{\stack X}\bigr) \cong
        \ΓdR(G, k_G)^\dual \otimes \ΓdR(\B G, k_{\B G}).
    \]
    Alternatively, we can use the identification
    \[
        \catDMod{\B G} \cong \catModules{\ΓdR(G, k_{G})^\dual},
    \]
    where the algebra structure on $\ΓdR(G, k_G)^\dual$ is induced by the group multiplication \cite[Section~7.2]{DrinfeldGaitsgory:2013:FinitenessQuestions}.
    If $G$ is reductive, then $\ΓdR(G, k_G)^\dual$ is an exterior algebra and thus its Hochschild cohomology can be computed directly.
\end{Ex}

\subsection{A lemma on base change}\label{sec:d-mod:strategy:base-change}

Consider a Cartesian diagram of stacks
\[
    \begin{tikzcd}
        \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
        \stack X₂ \arrow[r, "g"] & \stack Y
    \end{tikzcd}
\]
with $f$ and $g$ schematic.
We have a morphism of functors $\catDModHol{\stack X₁} → \catDModHol{\stack X₂}$,
\begin{equation}
    \label{eq:d-mod:base-change-morphism}
     p_! q^! → g^! f_!
\end{equation}
induced by adjunctions
\begin{equation}
    \label{eq:d-mod:base-change-adjunctions}
    p_! q^! →
    p_! q^! f^! f_! =
    p_! p^! g^! f_! →
    g^! f_!.
\end{equation}
If $f$ is proper, then \eqref{eq:d-mod:base-change-morphism} is an isomorphism by Proposition~\ref{prop:d-mod:pre:base-change}.
To understand the behavior for non-proper $f$, we will approximate it by a proper morphism.

\begin{Def}
    A \emph{relative compactification} of a morphism $f\colon \stack X → \stack Y$ is a commutative diagram
    \[
        \begin{tikzcd}
            \stack X \arrow[r, hook, "j"] \arrow[dr, "f"'] & \bar{\stack X} \arrow[d, "\bar f"] \\
            & \stack Y
        \end{tikzcd}
    \]
    where $j$ is an open embedding and $\bar f$ is proper.
\end{Def}

\begin{Ex}
    A famous example of such a relative compactification is Drinfeld's compactification of the morphism $\Bun_B → \Bun_G$, where $\Bun_G$ is the stack of $G$-bundles on a curve $C$ with $G$ reductive and $B$ is a Borel subgroup of $G$ \cite{BravermanGaitsgory:2002:GeometricEisensteinSeries}.
\end{Ex}

Let us assume that in the above situation there exists a relative compactification of $f\colon \stack X₁ → \stack Y$.
Let $\stack X₁^c$ be the closed complement of the open inclusion $j\colon \stack X₁ \hookrightarrow \bar{\stack X}₁$.
Similarly, we let $\bar{\stack Z} = \stack X₂ ×_{\stack Y} \bar{\stack X}₁$ and $\stack Z^c = \stack X₂ ×_{\stack Y} \stack X₁^c$.
The notation for the corresponding inclusion and projection maps is summarized in the following Cartesian diagrams.
\[
    \begin{tikzcd}
        \bar{\stack Z} \arrow[d, "\bar p"] \arrow[r, "\bar q"] & \bar{\stack X}₁ \arrow[d, "\bar f"] \\
        \stack X₂ \arrow[r, "g"] & \stack Y
    \end{tikzcd}
    \qquad\qquad
    \begin{tikzcd}
        \stack Z^c \arrow[r, hook, "i"] \arrow[d] & \bar{\stack Z} \arrow[d, "\bar q"] \\
        \stack X₁^c \arrow[r, hook] & \bar{\stack X}₁
    \end{tikzcd}
\]
We note that $\bar{\stack Z}$ is the disjoint union of the closed substack $\stack Z^c$ and the open substack $\stack Z$.

\begin{Lem}
    \label{lem:d-mod:base-change-criterion}%
    The cone of the morphism~\eqref{eq:d-mod:base-change-morphism} is
    \[
        \bar p_! i_*i^* \bar{q}^! j_!.
    \]
    In particular, if $i^* \bar{q}^! j_! = 0$, then~\eqref{eq:d-mod:base-change-morphism} is an isomorphism of functors.
\end{Lem}

\begin{proof}
    Let $\tilde\jmath\colon \stack Z \hookrightarrow \bar{\stack Z}$ be the open inclusion complement to $i$.
    We split the adjunction in \eqref{eq:d-mod:base-change-adjunctions} in two by using the compositions
    \[
        f = \bar f ∘ j
        ,\
        p = \bar p ∘ \tilde\jmath
        \text{ and }
        q = \bar q ∘ \tilde\jmath.
    \]
    Thus the adjunction $p_!q^!→ p_!q^!f^!f_!$ becomes the sequence
    \[
        p_!q^! →
        p_!q^! j^! j_! →
        p_!q^! j^! \bar f^! \bar f_! j_!.
    \]
    The equality $p_! q^! f^! f_! = p_! p^! g^! f_!$ then becomes
    \[
        p_! q^! j^! \bar f^! \bar f_! j_! =
        p_! \tilde\jmath^! \bar q^! \bar f^! \bar f_! j_! =
        p_! \tilde\jmath^! \bar p^! g^! \bar f_! j_!.
    \]
    Finally the adjunction $p_! p^! g^! f_! → g^! f_!$ becomes
    \[
        p_! \tilde\jmath^! \bar p^! g^! \bar f_! j_! =
        \bar p_! \tilde\jmath_! \tilde\jmath^! \bar p^! g^! \bar f_! j_! →
        \bar p_! \bar p^! g^! \bar f_! j_! →
        g^! \bar f_! j_! =
        g^! f_!.
    \]
    Let us apply the same adjunction morphisms in a different order.
    First the inclusions
    \[
        p_!q^!
        \xrightarrow{α}
        p_!q^! j^! j_!
        =
        \bar p_! \tilde\jmath_! \tilde\jmath^! \bar q^! j_!
        \xrightarrow{β}
        \bar p_! \bar q^! j_!,
    \]
    and then the actual base change
    \begin{equation}
        \label{eq:lem:d-mod:base-change-criterion:pf:split_morphism_base_change}
        \bar p_! \bar q^! j_!
        →
        \bar p_! \bar q^! \bar f^! \bar f_! j_!
        =
        \bar p_! \bar p^! g^! \bar f_! j_!
        →
        g^! \bar f_! j_!
        =
        g^! f_!.
    \end{equation}
    We note that the adjunction $α\colon \id → j^!j_!$ is an isomorphism and the composition of the maps in \eqref{eq:lem:d-mod:base-change-criterion:pf:split_morphism_base_change} is exactly the isomorphism of proper base change (cf.~Proposition~\ref{prop:d-mod:pre:base-change}).
    Thus the cone of the whole composition is the same as the cone of the morphism $β$, which is given by the recollement triangle
    \[
        \bar p_! \tilde\jmath_! \tilde\jmath^! \bar q^! j_!
        \xrightarrow{β}
        \bar p_! \bar q^! j_!
        \xrightarrow{\phantom{β}}
        \bar p_! i_* i^* \bar q^! j_!
        \xrightarrow{+1}.
        \qedhere
    \]
\end{proof}

\subsection{Relative compactification for quotient stacks}
\label{sec:d-mod:strategy:compactification}%

In the preceding section we simply assumed that a relative compactification of the diagonal exists.
We will now construct such a compactification for quotient stacks.
Thus let $X$ be a scheme of finite type over $k$ and let $G$ be an affine algebraic group over $k$ acting on $X$.
Let $\stack X = X/G$ be the corresponding quotient stack.

Constructing a relative compactification of $Δ\colon \stack X → \stack X × \stack X$ is the same as first constructing a $G × G$-equivariant relative compactification of $(\proj2, a)\colon G × X → X × X$ (where $a\colon G × X → X$ is the action map) and then taking the quotient by the $G × G$ action\footnote{%
    Here $G × G$ acts on $G × X$ by $(s₁,s₂) \cdot (g,x) = (s₂gs₁^{-1},\, s₁x)$.
}.
We let
\[
    Γ = \bigl\{(g, x, x, gx) ∈ G × X × X × X\bigr\}
\]
be the graph of $(\proj2, a)$.

We pick a $G×G$-equivariant compactification $\bar G$ of $G$ and let $\bar Γ$ be the closure of $Γ$ in $\bar G × X × X × X$.
We have an open embedding $j$ of $G × X \cong Γ$ into $\bar Γ$ and proper map $f\colon \bar Γ → X × X$ given by projection on the last two factors.
The composition $f ∘ j$ is equal to $(\proj2, a)$.

Instead of viewing $Γ$ as the graph of $(\proj2, a)$ we can drop the third factor and regard $Γ$ as the graph of the action map, i.e.
\[
    \Γsub{a} = \bigl\{(g, x, gx) ∈ G × X × X\bigr\}.
\]
The closure $\bar{ \Γsub{a}}$ of $\Γsub a$ in $\bar G × X × X$ identifies with $\bar Γ$.
Thus for ease of notation we will from now on always set $Γ = \Γsub a$ and $\bar Γ = \bar{\Γsub a}$.

\begin{Def}
    Let $\stack X = X/G$.
    With the above construction we set
    \[
        \bar{\stack X} = \rquot{\bar Γ}{G×G}.
    \]
    We have an open embedding $j\colon X \hookrightarrow \bar{\stack X}$ and a proper morphism $\bar Δ\colon \bar{\stack X} → \stack X × \stack X$ induced by the map $f$ above, such that $Δ = \bar Δ ∘ j$.
\end{Def}

\begin{Rem}
    In the case of $G = \Gm$ the compactification $\bar Γ$ is explicitly described in \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
    In particular, if $X$ is smooth it is shown there that $\bar Γ$ is smooth over $\bar G = \ps1$.
    It is possible to extend the methods of \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden} to quotients by higher dimensional tori.
    The resulting constructions are highly useful for doing explicit computations.
\end{Rem}

It is useful to consider only partial compactifications.
For this let $V$ be a $G$-stable subvariety of $\bar G$ and let $\bar{\Γsub V}$ be the closure of $Γ$ in $G × V$.
We set
\[
    \bar{\stack X}_V = \rquot{\bar{\Γsub V}}{G×G}.
\]
Clearly, if $\left\{V_i\right\}$ is an open cover of $\bar G$ by $G$-stable subvarieties, then $\left\{\bar{\stack X}_{V_i}\right\}$ is an open cover of $\bar{\stack X}$.

\subsection{\Goodstack\ stacks}

Let $\stack X = X/G$ be a quotient stack as before.
For any morphism of stacks $h\colon \stack Y → \stack X$ we set $\lsY{\stack X} = \stack X ×_{\stack X × \stack X} \stack Y$.
Thus we have the Cartesian diagram
\[
    \begin{tikzcd}
        \lsY \stack X \arrow[r, "q_{\stack Y}"] \arrow[d] & \stack X \arrow[d, "Δ"] \\
        \stack Y \arrow[r, "Δ∘h"] & \stack X × \stack X
    \end{tikzcd}
\]
Let us fix a relative compactification $\bar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:d-mod:strategy:compactification}.
Using the notation of Section~\ref{sec:d-mod:strategy:base-change} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
We let $\bar q_{\stack Y}\colon \clsY\stack X → \bar{\stack X}$ be the projection morphism and $i_{\stack Y}\colon \lscY\stack X \hookrightarrow \clsY\stack X$ the inclusion.
Thus we have the following central diagram
\[
    \begin{tikzcd}
        \lsY\stack X \arrow[r, hook] \arrow[d, "q_{\stack Y}"] & \clsY\stack X \arrow[d, "\bar q_{\stack Y}"] & \lscY\stack X \arrow[l, hook', "i_{\stack Y}"'] \arrow[d] \\
        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
    \end{tikzcd}
\]

\begin{Def}
    A quotient stack $\stack X = X/G$ is called \emph{\goodstack} if for every quotient stack $\stack Y = Y/G$ and schematic morphism $\stack Y → \stack X$ the functor $i_{\stack Y}^* \bar q_{\stack Y}^! j_!$ vanishes on $\catDModHol{\stack X}$.
\end{Def}

We will show in Chapter~\ref{ch:d-mod:torus} that any stack of the form $\rquot{X}{\Gm^n}$ is \goodstack.
The reason for this definition is the following theorem which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodstack\ quotient stacks.

\begin{Thm}\label{thm:d-mod:good-is-good}
    If $\stack X = X/G$ is \goodstack, then there exists a canonical structure of monad on $p_{2,!}p₁^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
    In particular there is an isomorphism of algebras
    \[
        \HCoh\bigl(\catDMod{\stack X}\bigr)
        \cong
        \opalg{\ΓdR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)}.
    \]
\end{Thm}

In other words, Theorem~\ref{thm:d-mod:main} holds for \goodstack\ stacks.

\begin{proof}
    We apply Lemma~\ref{lem:d-mod:pre:groupoid_monad_hol} to the groupoid $\ls\stack X \rightrightarrows \stack X$.
    Thus we let $\stack G_\cx$ be the simplicial stack with
    \[
        \stack G_i = \underbrace{\ls\stack X ×_{\stack X} \dotsb ×_{\stack X} \ls\stack X}_{\text{$i$ factors}}.
    \]
    Any morphism $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ induces a diagram
    \[
        \begin{tikzcd}
            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
        \end{tikzcd}
    \]
    We have to show that base change holds along the left-hand square.
    But by the assumption and Lemma~\ref{lem:d-mod:base-change-criterion}, base change holds along the outer rectangle and the left-hand square.
    Thus it also holds along the left-hand square.
\end{proof}

\begin{Rem}
    We expect that most quotient stacks are not \goodstack.
    For example, a direct computation shows that Theorem~\ref{thm:d-mod:main} does not hold for the stack $\ps1/\as1$, and hence it is not \goodstack.
    For non-\goodstack\ stacks, Lemma~\ref{lem:d-mod:base-change-criterion} instead gives a description of how much the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$ fails.
\end{Rem}

We finish this section with some useful observations for proving that a stack is \goodstack.

\begin{Lem}
    If $\stack X₁ = X₁/G₁$ and $\stack X₂ = X₂/G₂$ are \goodstack, then $\stack X₁ × \stack X₂$ is \goodstack.
\end{Lem}

\begin{proof}
    Follows from compatibility of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_!$ with $\boxtimes$ and coproducts.
    (Note that $\lscY{(\stack X₁ × \stack X₂)} = \lscY \stack{X₁} × \clsY \stack{X₂} ∪ \clsY{\stack X₁} × \lscY{\stack X₂}$.)
\end{proof}

\begin{Lem}
    Let $U$ be a $G$-equivariant open subset of $X$.
    If $X/G$ is \goodstack\ then $U/G$ is \goodstack.
\end{Lem}

\begin{proof}
    Let $\stack U = U/G$ and let $\stack Y$ be a quotient stack mapping into $\stack U$ (and hence also into $\stack X$).
    Consider the diagram
    \begin{equation}
        \label{eq:lem:d-mod:cover:diagram}
        \begin{tikzcd}
            \lscY \stack U \arrow[r, hook, "i_{\stack U, \stack Y}"] \arrow[d, hook, "α"] & \clsY{\stack U} \arrow[r, "\bar q_{\stack U,\stack Y}"] \arrow[d, hook, "β"] & \bar{\stack U} \arrow[d, hook, "γ"] & \stack U \arrow[l, hook', "j_{\stack U}"'] \arrow[d, hook, "δ"] \\
            \lscY \stack X \arrow[r, hook, "i_{\stack X, \stack Y}"]                      & \clsY{\stack X} \arrow[r, "\bar q_{\stack X,\stack Y}"]                      & \bar{\stack X}                      & \stack X \arrow[l, hook', "j_{\stack X}"']
        \end{tikzcd}
    \end{equation}
    The vertical arrows are open embeddings and all squares are Cartesian (where we use the same compactification of $G$ for $\bar{\stack X}$ and $\bar{\stack U}$).
    Thus
    \begin{equation*}
        i_{\stack U, \stack Y}^* \bar q_{\stack U,\stack Y}^! j_{\stack U,!} =
        i_{\stack U, \stack Y}^* \bar q_{\stack U,\stack Y}^! j_{\stack U,!} δ^* δ_*=
        α^* i_{\stack X, \stack Y}^* \bar q_{\stack X, \stack Y}^! j_{\stack X,!} δ_* =
        0.
        \qedhere
    \end{equation*}
\end{proof}

The same argument can be used to reduce the computation to a smooth cover.
We will now introduce notation for the special case of the cover $\bar Γ → \bar{\stack X}$.
The corresponding covers of the other relevant stacks are introduced in the following diagram with Cartesian squares.
\begin{equation}
    \label{eq:d-mod:strategy:scheme-cover}
    \begin{tikzcd}
        \schemelscY \stack X \arrow[r, hook, "\schemei_{\stack Y}"] \arrow[d] & \schemeclsY \stack X \arrow[r, "\bar\schemeq_{\stack Y}"] \arrow[d] & \bar Γ \arrow[d] & Γ \arrow[l, hook', "\schemej"'] \arrow[d] \\
        \lscY \stack X \arrow[r, hook, "i_{\stack Y}"]                        & \clsY \stack X \arrow[r, "\bar q_{\stack Y}"]                       & \bar{\stack X}   & \stack X \arrow[l, hook', "j"']
    \end{tikzcd}
\end{equation}
We note that all vertical morphisms are smooth and the spaces in the top row are schemes.
Let $\schemeh\colon X → Y$ be the $G$-equivariant morphism of schemes inducing $h$ on quotient stacks.
Then the scheme $\schemeclsY \stack X$ is given by
\[
    \schemeclsY \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ
    \biggr\}.
\]

\begin{Lem}\label{lem:d-mod:strategy:scheme-cover}
    A stack $X/G$ is \goodstack\ if and only if for each morphism $Y/G → X/G$ the composition $\schemei_{\stack Y}^* \bar\schemeq_{\stack Y}^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
\end{Lem}

\begin{proof}
    Follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:d-mod:strategy:scheme-cover} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and permutes with the other morphisms up to a shift.
\end{proof}

\begin{Lem}
    \label{lem:d-mod:strategy:cover}%
    If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ are \goodstack, then $X/G$ is \goodstack.
\end{Lem}

\begin{proof}
    Let $\stack U_i = U_i/G$ be the corresponding quotient stacks.
    We first show that the stacks $\lscY{\stack U_i}$ form an open cover of $\lscY{\stack X}$\footnote{
        This is not completely obvious, since the $\bar{\stack U}_i$ do not necessarily form a cover of $\bar{\stack X}$.
        For example, consider $\ps1$ with the usual linear $\Gm$-action and the usual affine cover.
    }.
    For this it suffices to show that the open subschemes $\schemeclsY \stack U_i$ cover $\schemeclsY \stack X$.
    Let $(g₁, y, g₂)$ be a point of $\schemeclsY \stack X$.
    Then there exists some $U_i$ with $h'(y) ∈ U_i$.
    But then $g₁h'(y)$ is also in $U_i$ and hence $(h'(y), g₂, g₁h'(y)) ∈ \bar{\stack U}_i$.
    Thus $(g₁, y, g₂)$ is in $\schemeclsY \stack U_i$.

    It now suffices to show that the restrictions of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_! \sheaf F$ to $\lscY{\stack U_i}$ vanish for every $\sheaf F ∈ \catDMod{\stack X}$.
    But this follows from the diagram~\eqref{eq:lem:d-mod:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the \goodness\ of $\stack U_i$.
\end{proof}

Let $\left\{V_i\right\}$ be a $G$-stable open cover of $\bar G$ and consider the corresponding open cover $\left\{\bar{\stack X}_{V_i}\right\}$ of $\stack X$.
We obtain open covers $\left\{\cls_{V_i,\stack Y} \stack X\right\}$ and $\left\{\lsc_{V_i,\stack Y} \stack X\right\}$ of $\clsY{\stack X}$ and $\lscY{\stack X}$ respectively.
We let $i_{V_i,\stack X}$, $\bar q_{V_i,\stack X}$ and $j_{V_i}$ be the corresponding maps, i.e.
\[
    \begin{tikzcd}
        \cls_{V_i,\stack Y} \stack X \arrow[r, hook, "i_{V_i,\stack X}"] &
        \lsc_{V_i,\stack Y} \stack X \arrow[r, "\bar q_{V_i,\stack X}"] &
        \bar{\stack X}_{V_i} &
        \stack X \arrow[l, hook', "j_{V_i}"'].
    \end{tikzcd}
\]

\begin{Lem}\label{lem:d-mod:strategy:cover-by-relative-compactifications}
    With the above notation, the $\stack X$ is \goodstack\ if and only $i_{V_i,\stack Y}^* \bar q_{V_i,\stack Y}^! j_{V_i,!}$ vanishes on $\catDModHol{\stack X}$ for all $V_i$ and all $\stack Y → \stack X$.
\end{Lem}

\begin{proof}
    Similar to the proof of Lemma~\ref{lem:d-mod:strategy:cover}.
\end{proof}

\section{Torus quotients}
\label{ch:d-mod:torus}

In this chapter we will apply the tools from the previous chapter to torus quotient stacks.
Specifically, we will prove the following theorem.

\begin{Thm}
    \label{thm:d-mod:torus:is-good}%
    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
    Then the stack $\stack X = X/G$ is good.
\end{Thm}

Together with Theorem~\ref{thm:d-mod:good-is-good} this implies our main result, Theorem~\ref{thm:d-mod:main}.

\begin{Rem}
    We only use the assumption that the action is locally linear to prove Lemma~\ref{lem:d-mod:finitely_many_stabilizers}, i.e.~that $\Stab\stack X$ is locally finite.
    Thus it would suffice to assume that $X$ can be covered by open subschemes for which Lemma~\ref{lem:d-mod:finitely_many_stabilizers} holds.
\end{Rem}

\begin{Rem}
    Theorem~\ref{thm:d-mod:torus:is-good} actually holds for $G$ the product of a torus and a finite Abelian group.
    The argument is exactly the same.
\end{Rem}

By Lemma~\ref{lem:d-mod:strategy:cover}, it suffices to prove Theorem~\ref{thm:d-mod:torus:is-good} for stacks $X/G$ with $X$ affine.
We fix an isomorphism $G \cong \Gm^n$ and compactify $G$ to $\bigl(\ps1\bigr)^n$.
The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
Thus by Lemma~\ref{lem:d-mod:strategy:cover-by-relative-compactifications}, it suffices to check \goodness\ for the relative compactification $\Gm^n \subseteq \as n$.
To simplify notation, we drop the subscript $\as n$ from the notation and set $\bar{\stack X} = \bar{\stack X}_{\as n}$ and similarly for the various maps.

We fix a quotient stack $\stack Y = Y/G$ and a morphism $h\colon \stack Y → \stack X$, induced by a $G$-equivariant morphism $\schemeh\colon Y → X$.
According to Lemma~\ref{lem:d-mod:strategy:scheme-cover}, rather than working with stack directly, we can base change to schemes.
We will use the notation of Lemma~\ref{lem:d-mod:strategy:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ from the maps.
Thus we are concerned with the diagram
\[
    \begin{tikzcd}
        \schemelscY \stack X \arrow[r, hook, "\schemei"] &
        \schemeclsY \stack X \arrow[r, "\bar\schemeq"] &
        \bar Γ &
        Γ \arrow[l, hook', "\schemej"'],
    \end{tikzcd}
\]
where we have to show that $\schemei^* \bar\schemeq^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.

The general idea is to introduce a $\Gm$-action that contracts $\schemelscY \stack X$ onto $\schemeclsY \stack X$.
In order to do so, we will cut the scheme
\[
    \schemeclsY \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ
    \biggr\}
\]
into pieces according to the subgroups of $G$ that stabilize $\schemeh(y)$.
For this let $\Stab\stack X$ be the set of all closed subgroups of $G$ that are stabilizers of points of $X$, i.e.
\[
    \Stab\stack X = \{ G_x : x ∈ X \}.
\]

\begin{Lem}
    \label{lem:d-mod:finitely_many_stabilizers}%
    The set $\Stab\stack X$ is finite.
\end{Lem}

\begin{proof}
    Since $X$ is affine, it can be embedded $G$-equivariantly into some $\as m$ with a linear $T$-action.
    For $\as m/T$ the statement is easy to see.
\end{proof}

Let $S$ be closed subgroup of $G$ and let $X^S$ be the $S$-fixed points of $X$.
Since $G$ is Abelian (and hence $S$ a normal subgroup), $X^S$ is a $G$-stable closed subscheme of $X$.
Hence $X^S/G$ is a closed substack of $\stack X$.
Let $\bar S$ be the closure of $S$ in $\bar G = \as n$ and consider the space
\[
    \schemecls[S]_{\stack Y} \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^S,\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S
    \biggr\}
    ⊆ 
    \schemecls_{\stack Y} \stack X.
\]

\begin{Lem}
    \label{lem:d-mod:stabilizers_cover}%
    The subspaces $\schemecls[S]_{\stack Y} \stack X$ for $S ∈ \Stab\stack X$ cover $\schemecls_{\stack Y}\stack X$.
\end{Lem}

\begin{proof}
    Let $\schemelsY \stack X$ be the smooth cover of $\ls_{\stack Y}\stack X$.
    Consider the spaces
    \[
        \schemelsY[S] \stack X = 
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × G : \schemeh(y) ∈ X^S,\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ Γ \text{ and } g₂ ∈ g₁S
        \biggr\}
        \subseteq \schemelsY \stack X.
    \]
    The closure of $\schemelsY[S] \stack X$ in $\schemeclsY \stack X$ is exactly $\schemeclsY[S] \stack X$.
    It is easy to see that the subspaces $\schemelsY[S] \stack X$ for $S ∈ \Stab \stack X$ cover $\schemelsY[S] \stack X$.
    Now the statement follows from the fact that the closure of a finite union is the union of the individual closures.
\end{proof}

It will be useful to have a slight generalization of the schemes $\schemeclsY[S] \stack X$.
Let $S₁ \subseteq S₂$ be two subgroups of $G$ contained in $\Stab\stack X$.
We set
\[
    \schemeclsY[S₁,S₂] \stack X =
    \biggl\{
        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
    \biggr\}.
\]
Clearly we have $\schemeclsY[S₁,S₂]{\stack X} \subseteq \schemecls[S₁]{\stack X}$ and $\schemeclsY[S] \stack X = \schemeclsY[S,S] \stack X$.

Consider the Cartesian square of closed embeddings
\[
    \begin{tikzcd}
        \schemelscY[S₁,S₂] \stack X \arrow[r, hook, "i_{S₁,S₂}^c"] \arrow[d, hook, "\schemei^{S₁,S₂}"] & \schemelscY\stack X \arrow[d, hook, "\schemei"] 
        \\
        \schemeclsY[S₁,S₂] \stack X \arrow[r, hook, "i_{S₁,S₂}"]   & \schemeclsY\stack X 
    \end{tikzcd}
\]

\begin{Lem}\label{lem:d-mod:key_for_stablizier}%
    For any $S₁ ⊆ S₂$ in $\Stab\stack X$ and any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ we have
    \[
        \schemei^{S₁,S₂,*} i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F = 0.
    \]
\end{Lem}

\begin{proof}
    The scheme $\schemelsc[S₁,S₂] \stack X$ is given by
    \[
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁(\bar S₁ \setminus S₁)
        \biggr\}.
    \]
    If $S₁ = \bar S₁$ the statement is trivially true.
    Otherwise the scheme $\bar S₁ \setminus S₁$ is the union of hyperplanes $H_i$ of $\bar S₁$.
    It suffices to prove the statement when further restricting to 
    \[
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H_i
        \biggr\}.
    \]
    for all $i$. 
    Let $H$ be one such hyperplane.
    We will assume that $H$ is contained in the closure of the connected component of $1 ∈ S₁$. 
    The proof for $H$ in a different component is the same, up to a shift by an element of $G$.
    Let $\schemei_H$ be the inclusion of
    \[
        Z = 
        \biggl\{
            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H
        \biggr\}
    \]
    into $\schemeclsY[S₁,S₂] \stack X$.
    We want to compute
    \[
        \schemei_H^{*} i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F.
    \]
    We will do so be introducing a contractive $\Gm$-action on $\bar Γ$ and $\schemelsY[S₁,S₂]\stack X$ such that the morphism
    \[
        κ ∘ i_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ
    \]
    is $\Gm$-equivariant.

    We write $G \cong G₁ × S₁$ for some subgroup $G₁$ of $G$.
    This given a corresponding decomposition of the monad $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
    Let $H' = \bar G₁ H$.
    We note that $G ∩ H' = \emptyset$.

    We chose an action $μ$ of $\Gm$ on $\bar S₁$ that contracts $\bar S₁$ onto $H$.
    This induces an action of $\Gm$ on $\bar G = \bar G₁ \bar S₁$ by $u \cdot ts = tμ(u,s)$, contracting $\bar G$ onto $H'$.
    Further we obtain an action of $\Gm$ on $\bar Γ$ that keeps the first $X$ coordinate fixed.
    By construction this action contracts $\bar Γ$ onto a closed subvariety of $\bar Γ \setminus Γ$.
    We will denote this subvariety by $Z₁$ and the contraction morphism $π₁\colon \bar Γ → Z₁$ by $π₁$.

    We can also lift the action to $\schemeclsY[S₁,S₂]\stack X$ where it contracts onto $Z$.
    We will denote the corresponding contraction morphism by $π\colon \schemeclsY[S₁,S₂]\stack X → Z$.
    The morphism $κ ∘ i_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ$ is equivariant with respect to these $\Gm$-actions and on its image the action keeps the second $X$-coordinate fixed.

    We note that the D-modules $\schemej_!\sheaf F$ and $i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F$ are monodromic with respect to these $\Gm$-actions.
    Thus the contraction principle Theorem~\ref{thm:d-mod:pre:contraction_principle} implies that
    \[
        \schemei_H^* i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F = π_* i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F.
    \]
    By construction, the square
    \[
        \begin{tikzcd}
            \schemecls[S₁,S₂] \stack X \arrow[r, "π"] \arrow[d, "\schemeq ∘ i_{S₁,S₂}"] & Z \arrow[d] \\
            \bar Γ \arrow[r, "π₁"] & Z₁
        \end{tikzcd}
    \]
    is Cartesian. 
    Let us call the right vertical map $f$.
    Base change yields
    \[
        π_* i_{S₁,S₂}^!\bar\schemeq^!\schemej_! \sheaf F = 
        f^!π_{1,*} \schemej_! \sheaf F.
    \]
    Finally, let $i_{Z₁}\colon Z₁ \hookrightarrow \bar Γ$ be the inclusion.
    Applying the contraction principle again we obtain
    \[
        f^!π_{1,*} \schemej_! \sheaf F =
        f^!i_{Z₁}^* \schemej_! \sheaf F =
        0.
        \qedhere
    \]
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm:d-mod:torus:is-good}]
    By Lemma~\ref{lem:d-mod:stabilizers_cover} the closed subschemes $\schemeclsY[S]\stack X$ for $S ∈ \Stab \stack X$ cover $\schemeclsY\stack X$.
    If $S₁,\, S₂ ∈ \Stab\stack X$, then
    \[
        \schemeclsY[S₁]\stack X ∩ \schemeclsY[S₂]\stack X = 
        \schemeclsY[S₁∩S₂,\, S₁S₂].
    \]
    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemmas~\ref{lem:d-mod:key_for_stablizier}.
\end{proof}

\printbibliography

\end{document}

### 2015-05-20 paper.tex
Use the new article class.
Add abstract from thesis.

@@
-\documentclass[english]{short-notes}
+\documentclass[english]{ck-article}
 
@@
 \maketitle
+
+\begin{abstract}
+    This article is dedicated to understanding the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of equivariant D-modules.
+    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
+    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
+\end{abstract}
 

### 2015-06-23 paper.tex
some small changes

--- 2015-05-20 paper.tex
@@
 \maketitle
+
+\begin{abstract}
+    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
+    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
+    This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of equivariant D-modules.
+\end{abstract}
 
@@
 
-\subsection{Hochschild cohomology}
+\section{Hochschild cohomology}
 
@@
 \]
-such that the unit map is given by $Δ_*p^!$ and thus we have
+such that the unit map is given by $Δ_*p^!$, i.e.~we have
 \[
@@
 \end{Lem}
-
-\section{Base change for non-proper maps}
-\label{ch:d-mod:strategy}
 
@@
 
+\section{Base change}
 \subsection{A lemma on base change}\label{sec:d-mod:strategy:base-change}

### 2015-06-23 paper.tex
Adapt labeling.

@@
 A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
-We will review the general setup and basic properties of D-modules on (QCA) stacks in Chapter~\ref{ch:d-mod:pre}.
+We will review the general setup and basic properties of D-modules on (QCA) stacks in Section~\ref{sec:pre}.
 The upshot is that we have an isomorphism of dg algebras
 \begin{equation}
-    \label{eq:intro:d-mod:d-mod-hcoh}
+    \label{eq:intro:d-mod-hcoh}
     \HCoh(\catDMod{\stack X}) \cong \Hom_{\catDMod{X×X}}(Δ_*ω_{\stack X}, Δ_*ω_{\stack X}),
@@
 
-By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod:d-mod-hcoh} as
+By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod-hcoh} as
 \[
@@
 \begin{equation}
-    \label{eq:intro:d-mod:naive}
+    \label{eq:intro:naive}
     \ΓdR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
@@
 
-In Chapter~\ref{ch:d-mod:strategy} we will investigate how to quantify the cone of the morphism
+In Section~\ref{sec:base-change} we will investigate how to quantify the cone of the morphism
 \[
@@
 \]
-and thus the failure of the naive isomorphism \eqref{eq:intro:d-mod:naive} to hold.
-As an application, we will prove the following theorem, giving a class of stacks where \eqref{eq:intro:d-mod:naive} is indeed an isomorphism.
-
-\begin{Thm}\label{thm:d-mod:main}
+and thus the failure of the naive isomorphism \eqref{eq:intro:naive} to hold.
+As an application, we will prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.
+
+\begin{Thm}\label{thm:main}
     Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
@@
 \section{Prerequisites}%
-\label{ch:d-mod:pre}
+\label{sec:pre}
 
@@
 All stacks in this thesis are assumed to be algebraic QCA stacks over $k$.
-As we will summarize in Section~\ref{sec:d-mod:pre:d-mods}, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
+As we will summarize in Section~\ref{sec:pre:d-mods}, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
 In particular for any stack $\stack X$ we have:
@@
 \subsection{D-modules on stacks}
-\label{sec:d-mod:pre:d-mods}
+\label{sec:pre:d-mods}
 
@@
 \begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
-    \label{prop:d-mod:pre:base-change}%
+    \label{prop:pre:base-change}%
     Consider a Cartesian square
@@
 \begin{Prop}
-    \label{prop:d-mod:pre:projection-formula}%
+    \label{prop:pre:projection-formula}%
     If $f\colon \stack X → \stack Y$ is a schematic morphism then the projection formula holds, i.e.~there is a functorial isomorphism
@@
 \begin{Rem}
-    Propositions \ref{prop:d-mod:pre:base-change} and \ref{prop:d-mod:pre:projection-formula} hold more generally when $f$ is merely a \enquote{safe} morphism.
+    Propositions \ref{prop:pre:base-change} and \ref{prop:pre:projection-formula} hold more generally when $f$ is merely a \enquote{safe} morphism.
     Alternatively they hold in full generality after replacing $f_*$ by the \enquote{renormalized de Rham pushforward}.
@@
 \begin{Prop}[{\cite[Section~2.5]{GaitsgoryRozenblyum:2014:CrystalsAndDModules}}]
-    \label{prop:d-mod:recollement-std}%
+    \label{prop:recollement-std}%
     There is an exact triangle of functors
@@
 On holonomic D-modules we have the additional adjoint pairs $(i^*,\, i_*)$ and $(j_!,\, j^*)$.
-By applying duality to Proposition~\ref{prop:d-mod:recollement-std} we obtain the distinguished triangle
+By applying duality to Proposition~\ref{prop:recollement-std} we obtain the distinguished triangle
 \[
@@
 \begin{Def}
-    \label{def:d-mod:pre:monodromic}%
+    \label{def:pre:monodromic}%
     Let $X$ be a scheme with an action of an algebraic group $G$ and let $p\colon X → X/G$ be the quotient map.
@@
 \begin{Thm}[Contraction principle~{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
-    \label{thm:d-mod:pre:contraction_principle}%
+    \label{thm:pre:contraction_principle}%
     Let $X$ be a scheme with an action by $\Gm$ that extends to an action of the monoid $\as 1$.
@@
 \subsection{Monads}
-\label{sec:d-mod:pre:monads}
-
-We will deduce Theorem~\ref{thm:d-mod:main} from a isomorphism of monads on $\catDMod{\stack X}$.
+\label{sec:pre:monads}
+
+We will deduce Theorem~\ref{thm:main} from a isomorphism of monads on $\catDMod{\stack X}$.
 In this section we give a short introduction to the theory of monads and the specific constructions that we will use.
@@
 \begin{equation}
-    \label{eq:d-mod:pre:monad-identities}
+    \label{eq:pre:monad-identities}
     \begin{tikzcd}
@@
 \]
-The identities~\ref{eq:d-mod:pre:monad-identities} ensure that the algebra is associative and unital.
+The identities~\ref{eq:pre:monad-identities} ensure that the algebra is associative and unital.
 
@@
 \begin{Lem}
-    \label{lem:d-mod:pre:groupoid_monad_hol}%
+    \label{lem:pre:groupoid_monad_hol}%
     Let $f\colon \stack X → \stack Y$ be a schematic morphism of stacks and let $\stack G_\cx$ be the corresponding groupoid.
@@
 
-\begin{Lem}\label{lem:d-mod:pre:hcoh}
+\begin{Lem}\label{lem:pre:hcoh}
     Let $\stack X$ be a stack.
@@
     \HCoh\bigl(\catDMod{\stack X}\bigr)
-    & = \Hom_{\catDMod{\stack X × \stack X}}(Δ_* ω_{\stack X},\, Δ_* ω_{\stack X}) & &\text{(Lemma~\ref{lem:d-mod:pre:hcoh})} \\
+    & = \Hom_{\catDMod{\stack X × \stack X}}(Δ_* ω_{\stack X},\, Δ_* ω_{\stack X}) & &\text{(Lemma~\ref{lem:pre:hcoh})} \\
     & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(Δ_! k_{\stack X},\, Δ_! k_{\stack X})} & & \text{(duality)} \\
@@
 Let us assume for the moment that $Δ$ (and hence $p_i$) was proper.
-Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:d-mod:pre:monads} we have an isomorphism of monads
+Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:pre:monads} we have an isomorphism of monads
 \begin{equation}
-    \label{eq:d-mod:central_iso}
+    \label{eq:central_iso}
     p_{2,!} p₁^! → Δ^!Δ_!,
@@
 Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
-Thus in general \eqref{eq:d-mod:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{2,!} p₁^!$.
-We would like to apply Lemma~\ref{lem:d-mod:pre:groupoid_monad_hol} to construct a monad in special cases.
-Thus the goal of this chapter is to give a criterion for the assumptions of Lemma~\ref{lem:d-mod:pre:groupoid_monad_hol}, i.e.~for base change to hold.
+Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{2,!} p₁^!$.
+We would like to apply Lemma~\ref{lem:pre:groupoid_monad_hol} to construct a monad in special cases.
+Thus the goal of this chapter is to give a criterion for the assumptions of Lemma~\ref{lem:pre:groupoid_monad_hol}, i.e.~for base change to hold.
 
 \begin{Ex}
-    The base change morphism \eqref{eq:d-mod:central_iso} is also an isomorphism if $Δ$ is smooth.
+    The base change morphism \eqref{eq:central_iso} is also an isomorphism if $Δ$ is smooth.
     In particular this implies that the \enquote{naive expectation} holds for $\stack X = \B G$ for any algebraic group $G$, i.e.~we have
@@
 \section{Base change}
-\subsection{A lemma on base change}\label{sec:d-mod:strategy:base-change}
+\label{sec:base-change}
+\subsection{A lemma on base change}\label{sec:base-change:base-change}
 
@@
 \begin{equation}
-    \label{eq:d-mod:base-change-morphism}
+    \label{eq:base-change-morphism}
      p_! q^! → g^! f_!
@@
 \begin{equation}
-    \label{eq:d-mod:base-change-adjunctions}
+    \label{eq:base-change-adjunctions}
     p_! q^! →
@@
 \end{equation}
-If $f$ is proper, then \eqref{eq:d-mod:base-change-morphism} is an isomorphism by Proposition~\ref{prop:d-mod:pre:base-change}.
+If $f$ is proper, then \eqref{eq:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
 To understand the behavior for non-proper $f$, we will approximate it by a proper morphism.
@@
 \begin{Lem}
-    \label{lem:d-mod:base-change-criterion}%
-    The cone of the morphism~\eqref{eq:d-mod:base-change-morphism} is
+    \label{lem:base-change-criterion}%
+    The cone of the morphism~\eqref{eq:base-change-morphism} is
     \[
@@
     \]
-    In particular, if $i^* \bar{q}^! j_! = 0$, then~\eqref{eq:d-mod:base-change-morphism} is an isomorphism of functors.
+    In particular, if $i^* \bar{q}^! j_! = 0$, then~\eqref{eq:base-change-morphism} is an isomorphism of functors.
 \end{Lem}
@@
     Let $\tilde\jmath\colon \stack Z \hookrightarrow \bar{\stack Z}$ be the open inclusion complement to $i$.
-    We split the adjunction in \eqref{eq:d-mod:base-change-adjunctions} in two by using the compositions
+    We split the adjunction in \eqref{eq:base-change-adjunctions} in two by using the compositions
     \[
@@
     \begin{equation}
-        \label{eq:lem:d-mod:base-change-criterion:pf:split_morphism_base_change}
+        \label{eq:lem:base-change-criterion:pf:split_morphism_base_change}
         \bar p_! \bar q^! j_!
@@
     \end{equation}
-    We note that the adjunction $α\colon \id → j^!j_!$ is an isomorphism and the composition of the maps in \eqref{eq:lem:d-mod:base-change-criterion:pf:split_morphism_base_change} is exactly the isomorphism of proper base change (cf.~Proposition~\ref{prop:d-mod:pre:base-change}).
+    We note that the adjunction $α\colon \id → j^!j_!$ is an isomorphism and the composition of the maps in \eqref{eq:lem:base-change-criterion:pf:split_morphism_base_change} is exactly the isomorphism of proper base change (cf.~Proposition~\ref{prop:pre:base-change}).
     Thus the cone of the whole composition is the same as the cone of the morphism $β$, which is given by the recollement triangle
@@
 \subsection{Relative compactification for quotient stacks}
-\label{sec:d-mod:strategy:compactification}%
+\label{sec:base-change:compactification}%
 
@@
 \]
-Let us fix a relative compactification $\bar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:d-mod:strategy:compactification}.
-Using the notation of Section~\ref{sec:d-mod:strategy:base-change} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
+Let us fix a relative compactification $\bar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
+Using the notation of Section~\ref{sec:base-change:base-change} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
 We let $\bar q_{\stack Y}\colon \clsY\stack X → \bar{\stack X}$ be the projection morphism and $i_{\stack Y}\colon \lscY\stack X \hookrightarrow \clsY\stack X$ the inclusion.
@@
 
-We will show in Chapter~\ref{ch:d-mod:torus} that any stack of the form $\rquot{X}{\Gm^n}$ is \goodstack.
+We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ is \goodstack.
 The reason for this definition is the following theorem which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodstack\ quotient stacks.
 
-\begin{Thm}\label{thm:d-mod:good-is-good}
+\begin{Thm}\label{thm:good-is-good}
     If $\stack X = X/G$ is \goodstack, then there exists a canonical structure of monad on $p_{2,!}p₁^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
@@
 
-In other words, Theorem~\ref{thm:d-mod:main} holds for \goodstack\ stacks.
+In other words, Theorem~\ref{thm:main} holds for \goodstack\ stacks.
 
 \begin{proof}
-    We apply Lemma~\ref{lem:d-mod:pre:groupoid_monad_hol} to the groupoid $\ls\stack X \rightrightarrows \stack X$.
+    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid $\ls\stack X \rightrightarrows \stack X$.
     Thus we let $\stack G_\cx$ be the simplicial stack with
@@
     We have to show that base change holds along the left-hand square.
-    But by the assumption and Lemma~\ref{lem:d-mod:base-change-criterion}, base change holds along the outer rectangle and the left-hand square.
+    But by the assumption and Lemma~\ref{lem:base-change-criterion}, base change holds along the outer rectangle and the left-hand square.
     Thus it also holds along the left-hand square.
@@
     We expect that most quotient stacks are not \goodstack.
-    For example, a direct computation shows that Theorem~\ref{thm:d-mod:main} does not hold for the stack $\ps1/\as1$, and hence it is not \goodstack.
-    For non-\goodstack\ stacks, Lemma~\ref{lem:d-mod:base-change-criterion} instead gives a description of how much the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$ fails.
+    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\as1$, and hence it is not \goodstack.
+    For non-\goodstack\ stacks, Lemma~\ref{lem:base-change-criterion} instead gives a description of how much the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$ fails.
 \end{Rem}
@@
     \begin{equation}
-        \label{eq:lem:d-mod:cover:diagram}
+        \label{eq:lem:cover:diagram}
         \begin{tikzcd}
@@
 \begin{equation}
-    \label{eq:d-mod:strategy:scheme-cover}
+    \label{eq:base-change:scheme-cover}
     \begin{tikzcd}
@@
 
-\begin{Lem}\label{lem:d-mod:strategy:scheme-cover}
+\begin{Lem}\label{lem:base-change:scheme-cover}
     A stack $X/G$ is \goodstack\ if and only if for each morphism $Y/G → X/G$ the composition $\schemei_{\stack Y}^* \bar\schemeq_{\stack Y}^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
@@
 \begin{proof}
-    Follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:d-mod:strategy:scheme-cover} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and permutes with the other morphisms up to a shift.
+    Follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:base-change:scheme-cover} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and permutes with the other morphisms up to a shift.
 \end{proof}
@@
 \begin{Lem}
-    \label{lem:d-mod:strategy:cover}%
+    \label{lem:base-change:cover}%
     If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ are \goodstack, then $X/G$ is \goodstack.
@@
     It now suffices to show that the restrictions of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_! \sheaf F$ to $\lscY{\stack U_i}$ vanish for every $\sheaf F ∈ \catDMod{\stack X}$.
-    But this follows from the diagram~\eqref{eq:lem:d-mod:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the \goodness\ of $\stack U_i$.
+    But this follows from the diagram~\eqref{eq:lem:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the \goodness\ of $\stack U_i$.
 \end{proof}
@@
 
-\begin{Lem}\label{lem:d-mod:strategy:cover-by-relative-compactifications}
+\begin{Lem}\label{lem:base-change:cover-by-relative-compactifications}
     With the above notation, the $\stack X$ is \goodstack\ if and only $i_{V_i,\stack Y}^* \bar q_{V_i,\stack Y}^!
@@
 \begin{proof}
-    Similar to the proof of Lemma~\ref{lem:d-mod:strategy:cover}.
+    Similar to the proof of Lemma~\ref{lem:base-change:cover}.
 \end{proof}
@@
 \section{Torus quotients}
-\label{ch:d-mod:torus}
+\label{sec:torus}
 
@@
 \begin{Thm}
-    \label{thm:d-mod:torus:is-good}%
+    \label{thm:torus:is-good}%
     Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
@@
 
-Together with Theorem~\ref{thm:d-mod:good-is-good} this implies our main result, Theorem~\ref{thm:d-mod:main}.
+Together with Theorem~\ref{thm:good-is-good} this implies our main result, Theorem~\ref{thm:main}.
 
 \begin{Rem}
-    We only use the assumption that the action is locally linear to prove Lemma~\ref{lem:d-mod:finitely_many_stabilizers}, i.e.~that $\Stab\stack X$ is locally finite.
-    Thus it would suffice to assume that $X$ can be covered by open subschemes for which Lemma~\ref{lem:d-mod:finitely_many_stabilizers} holds.
+    We only use the assumption that the action is locally linear to prove Lemma~\ref{lem:finitely_many_stabilizers}, i.e.~that $\Stab\stack X$ is locally finite.
+    Thus it would suffice to assume that $X$ can be covered by open subschemes for which Lemma~\ref{lem:finitely_many_stabilizers} holds.
 \end{Rem}
@@
 \begin{Rem}
-    Theorem~\ref{thm:d-mod:torus:is-good} actually holds for $G$ the product of a torus and a finite Abelian group.
+    Theorem~\ref{thm:torus:is-good} actually holds for $G$ the product of a torus and a finite Abelian group.
     The argument is exactly the same.
@@
 
-By Lemma~\ref{lem:d-mod:strategy:cover}, it suffices to prove Theorem~\ref{thm:d-mod:torus:is-good} for stacks $X/G$ with $X$ affine.
+By Lemma~\ref{lem:base-change:cover}, it suffices to prove Theorem~\ref{thm:torus:is-good} for stacks $X/G$ with $X$ affine.
 We fix an isomorphism $G \cong \Gm^n$ and compactify $G$ to $\bigl(\ps1\bigr)^n$.
 The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
-Thus by Lemma~\ref{lem:d-mod:strategy:cover-by-relative-compactifications}, it suffices to check \goodness\ for the relative compactification $\Gm^n \subseteq \as n$.
+Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodness\ for the relative compactification $\Gm^n \subseteq \as n$.
 To simplify notation, we drop the subscript $\as n$ from the notation and set $\bar{\stack X} = \bar{\stack X}_{\as n}$ and similarly for the various maps.
@@
 We fix a quotient stack $\stack Y = Y/G$ and a morphism $h\colon \stack Y → \stack X$, induced by a $G$-equivariant morphism $\schemeh\colon Y → X$.
-According to Lemma~\ref{lem:d-mod:strategy:scheme-cover}, rather than working with stack directly, we can base change to schemes.
-We will use the notation of Lemma~\ref{lem:d-mod:strategy:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ from the maps.
+According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working with stack directly, we can base change to schemes.
+We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ from the maps.
 Thus we are concerned with the diagram
@@
 \begin{Lem}
-    \label{lem:d-mod:finitely_many_stabilizers}%
+    \label{lem:finitely_many_stabilizers}%
     The set $\Stab\stack X$ is finite.
@@
 \begin{Lem}
-    \label{lem:d-mod:stabilizers_cover}%
+    \label{lem:stabilizers_cover}%
     The subspaces $\schemecls[S]_{\stack Y} \stack X$ for $S ∈ \Stab\stack X$ cover $\schemecls_{\stack Y}\stack X$.
@@
 
-\begin{Lem}\label{lem:d-mod:key_for_stablizier}%
+\begin{Lem}\label{lem:key_for_stablizier}%
     For any $S₁ ⊆ S₂$ in $\Stab\stack X$ and any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ we have
@@
     We note that the D-modules $\schemej_!\sheaf F$ and $i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F$ are monodromic with respect to these $\Gm$-actions.
-    Thus the contraction principle Theorem~\ref{thm:d-mod:pre:contraction_principle} implies that
+    Thus the contraction principle Theorem~\ref{thm:pre:contraction_principle} implies that
     \[
@@
 
-\begin{proof}[Proof of Theorem~\ref{thm:d-mod:torus:is-good}]
-    By Lemma~\ref{lem:d-mod:stabilizers_cover} the closed subschemes $\schemeclsY[S]\stack X$ for $S ∈ \Stab \stack X$ cover $\schemeclsY\stack X$.
+\begin{proof}[Proof of Theorem~\ref{thm:torus:is-good}]
+    By Lemma~\ref{lem:stabilizers_cover} the closed subschemes $\schemeclsY[S]\stack X$ for $S ∈ \Stab \stack X$ cover $\schemeclsY\stack X$.
     If $S₁,\, S₂ ∈ \Stab\stack X$, then
@@
     \]
-    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemmas~\ref{lem:d-mod:key_for_stablizier}.
+    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemmas~\ref{lem:key_for_stablizier}.
 \end{proof}

### 2015-06-23 paper.tex
A better subsection name (and G_a)

@@
 \end{equation}
-Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\as1$ is an easy counter-example).
+Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\Ga$ is an easy counter-example).
 
@@
 \label{sec:base-change}
-\subsection{A lemma on base change}\label{sec:base-change:base-change}
+\subsection{The cone of the base-change map}\label{sec:base-change:cone}
 
@@
 Let us fix a relative compactification $\bar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
-Using the notation of Section~\ref{sec:base-change:base-change} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
+Using the notation of Section~\ref{sec:base-change:cone} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
 We let $\bar q_{\stack Y}\colon \clsY\stack X → \bar{\stack X}$ be the projection morphism and $i_{\stack Y}\colon \lscY\stack X \hookrightarrow \clsY\stack X$ the inclusion.
@@
     We expect that most quotient stacks are not \goodstack.
-    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\as1$, and hence it is not \goodstack.
+    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it is not \goodstack.
     For non-\goodstack\ stacks, Lemma~\ref{lem:base-change-criterion} instead gives a description of how much the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$ fails.

### 2015-06-23 paper.tex
/bar -> /overline
Remove the word "thesis" and fix the flow between sections.

@@
 \let\stack\mathbf
+\let\bar\overline
 
@@
 
-This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme yields the singular support of coherent sheaves which already served as the motivation for the first part of this thesis.
-More concretely, Arinkin and Gaitsgory used singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture \cite{ArinkinGaitsgory:2015:SingularSupport}.
+This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
+More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
 By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.
@@
 We fix an algebraically closed base field $k$ of characteristic $0$.
-All stacks in this thesis are assumed to be algebraic QCA stacks over $k$.
-As we will summarize in Section~\ref{sec:pre:d-mods}, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
+All stacks will be assumed to be algebraic QCA stacks over $k$.
+As we will summarize below, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
 In particular for any stack $\stack X$ we have:
@@
 We will switch between those two languages without explicitly mentioning the intervening constructions and apply results from \cite{Lurie:2014-draft:HigherAlgebra} to dg categories.
-Fortunately, a superficial knowledge of dg/$∞$-categories should be sufficient for reading this thesis.
+Fortunately, a superficial knowledge of dg/$∞$-categories should be sufficient for reading this article.
 
@@
     Alternatively they hold in full generality after replacing $f_*$ by the \enquote{renormalized de Rham pushforward}.
-    We fill not use either notion in this thesis and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
+    We fill not use either notion here and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
 \end{Rem}
@@
 Let $p\colon \stack X → \pt$ be the structure morphism and $Δ\colon \stack X → \stack X × \stack X$ the diagonal.
-By \cite[Section~8.4]{DrinfeldGaitsgory:2013:FinitenessQuestions} the category $\catDMod{\stack X}$ is dualizable and there is a canonical indentification
+By \cite[Section~8.4]{DrinfeldGaitsgory:2013:FinitenessQuestions} the category $\catDMod{\stack X}$ is dualizable and there is a canonical identification
 \[
@@
 
-Let $\stack X$ be any stack, where we recall that all stacks are assumed to be QCA.
-We are interested in computing the Hochschild cohomology
-\[
-    \HCoh\bigl(\catDMod{\stack X}\bigr).
-\]
-Let $Δ\colon \stack X → \stack X × \stack X$ is the diagonal map, which by assumption is schematic.
-The dualizing module $ω_{\stack X}$ is always holonomic.
+Recall now that we assume $Δ$ to be schematic schematic and that the dualizing module $ω_{\stack X}$ is always holonomic.
 Thus we have $\dualize Δ_* ω_{\stack X} = Δ_! k_{\stack X}$.
@@
 We would like to apply Lemma~\ref{lem:pre:groupoid_monad_hol} to construct a monad in special cases.
-Thus the goal of this chapter is to give a criterion for the assumptions of Lemma~\ref{lem:pre:groupoid_monad_hol}, i.e.~for base change to hold.
+Thus the goal of the next section is to give a criterion for the assumptions of Lemma~\ref{lem:pre:groupoid_monad_hol}, i.e.~for base change to hold.
 
@@
 
-In this chapter we will apply the tools from the previous chapter to torus quotient stacks.
+In this section we will apply the tools from the previous section to torus quotient stacks.
 Specifically, we will prove the following theorem.

### 2015-06-23 paper.tex
Remove cyrillic letters.

@@
 
-%\newcommand\schemels[1]{\mathcal{L}\mkern2.5mu #1}
-%\newcommand\schemecls[1]{\overline{\mathcal{L}}\mkern2.5mu #1}
-%\newcommand\schemelsc[1]{\mathcal{L}\mkern2.5mu^c #1}
-\newcommand\schemels[2][]{\cyrmath{Л}\mkern1.5mu^{#1}#2}
+\newcommand\schemels[2][]{L^{#1}#2}
 \newcommand\schemelsY[2][]{\schemels[#1]{_{\stack Y}#2}}
-\newcommand\schemecls[2][]{\overline{\cyrmath{Л}}\mkern1.5mu^{#1}#2}
+\newcommand\schemecls[2][]{\overline{L}^{#1}#2}
 \newcommand\schemeclsY[2][]{\schemecls[#1]{_{\stack Y}#2}}
-\newcommand\schemelsc[2][]{\cyrmath{Л}\mkern1.5mu^{\if\relax\detokenize{#1}\relax\else#1,\fi c} #2}
+\newcommand\schemelsc[2][]{L^{\if\relax\detokenize{#1}\relax\else#1,\fi c} #2}
 \newcommand\schemelscY[2][]{\schemelsc[#1]{_{\stack Y}#2}}
 
-\newcommand\schemei{\cyrmath{и}}
-\newcommand\schemej{\cyrmath{й}}
-\newcommand\schemeq{\cyrmath{к}}
+\newcommand\schemei{i'}
+\newcommand\schemej{j'}
+\newcommand\schemeq{q'}
+\newcommand\schemebarq{\bar{q}'}
+\newcommand\dropprimes{%
+    \renewcommand\schemei{i}%
+    \renewcommand\schemej{j}%
+    \renewcommand\schemeq{q}%
+    \renewcommand\schemebarq{\bar{q}}%
+}
 \newcommand\schemeh{h'}
-%\newcommand\schemep{\cyrmath{п}}
-%\newcommand\schemei{\tilde{\imath}}
-%\newcommand\schemej{\tilde{\jmath}}
-%\newcommand\schemeq{\tilde{q}}
-%\newcommand\schemeh{\tilde{h}}
 
@@
     \begin{tikzcd}
-        \schemelscY \stack X \arrow[r, hook, "\schemei_{\stack Y}"] \arrow[d] & \schemeclsY \stack X \arrow[r, "\bar\schemeq_{\stack Y}"] \arrow[d] & \bar Γ \arrow[d] & Γ \arrow[l, hook', "\schemej"'] \arrow[d] \\
+        \schemelscY \stack X \arrow[r, hook, "\schemei_{\stack Y}"] \arrow[d] & \schemeclsY \stack X \arrow[r, "\schemebarq_{\stack Y}"] \arrow[d] & \bar Γ \arrow[d] & Γ \arrow[l, hook', "\schemej"'] \arrow[d] \\
         \lscY \stack X \arrow[r, hook, "i_{\stack Y}"]                        & \clsY \stack X \arrow[r, "\bar q_{\stack Y}"]                       & \bar{\stack X}   & \stack X \arrow[l, hook', "j"']
@@
 \begin{Lem}\label{lem:base-change:scheme-cover}
-    A stack $X/G$ is \goodstack\ if and only if for each morphism $Y/G → X/G$ the composition $\schemei_{\stack Y}^* \bar\schemeq_{\stack Y}^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
+    A stack $X/G$ is \goodstack\ if and only if for each morphism $Y/G → X/G$ the composition $(\schemei_{\stack Y})^* (\schemebarq_{\stack Y})^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
 \end{Lem}
@@
 According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working with stack directly, we can base change to schemes.
-We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ from the maps.
+We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ and the primes from the maps.
+\dropprimes%
 Thus we are concerned with the diagram
@@
         \schemelscY \stack X \arrow[r, hook, "\schemei"] &
-        \schemeclsY \stack X \arrow[r, "\bar\schemeq"] &
+        \schemeclsY \stack X \arrow[r, "\schemebarq"] &
         \bar Γ &
@@
 \]
-where we have to show that $\schemei^* \bar\schemeq^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
+where we have to show that $\schemei^* \schemebarq^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
 
@@
     \begin{tikzcd}
-        \schemelscY[S₁,S₂] \stack X \arrow[r, hook, "i_{S₁,S₂}^c"] \arrow[d, hook, "\schemei^{S₁,S₂}"] & \schemelscY\stack X \arrow[d, hook, "\schemei"] 
+        \schemelscY[S₁,S₂] \stack X \arrow[r, hook, "α_{S₁,S₂}^c"] \arrow[d, hook, "\schemei^{S₁,S₂}"] & \schemelscY\stack X \arrow[d, hook, "\schemei"] 
         \\
-        \schemeclsY[S₁,S₂] \stack X \arrow[r, hook, "i_{S₁,S₂}"]   & \schemeclsY\stack X 
+        \schemeclsY[S₁,S₂] \stack X \arrow[r, hook, "α_{S₁,S₂}"]   & \schemeclsY\stack X 
     \end{tikzcd}
@@
     \[
-        \schemei^{S₁,S₂,*} i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F = 0.
+        \schemei^{S₁,S₂,*} α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F = 0.
     \]
@@
     \[
-        \schemei_H^{*} i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F.
+        (\schemei_H)^{*} α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F.
     \]
@@
     \[
-        κ ∘ i_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ
+        \schemebarq ∘ α_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ
     \]
@@
     We will denote the corresponding contraction morphism by $π\colon \schemeclsY[S₁,S₂]\stack X → Z$.
-    The morphism $κ ∘ i_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ$ is equivariant with respect to these $\Gm$-actions and on its image the action keeps the second $X$-coordinate fixed.
-
-    We note that the D-modules $\schemej_!\sheaf F$ and $i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F$ are monodromic with respect to these $\Gm$-actions.
+    The morphism $\schemebarq ∘ α_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ$ is equivariant with respect to these $\Gm$-actions and on its image the action keeps the second $X$-coordinate fixed.
+
+    We note that the D-modules $\schemej_!\sheaf F$ and $α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F$ are monodromic with respect to these $\Gm$-actions.
     Thus the contraction principle Theorem~\ref{thm:pre:contraction_principle} implies that
     \[
-        \schemei_H^* i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F = π_* i_{S₁,S₂}^! \bar\schemeq^! \schemej_! \sheaf F.
+        (\schemei_H)^* α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F = π_* α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F.
     \]
@@
         \begin{tikzcd}
-            \schemecls[S₁,S₂] \stack X \arrow[r, "π"] \arrow[d, "\schemeq ∘ i_{S₁,S₂}"] & Z \arrow[d] \\
+            \schemecls[S₁,S₂] \stack X \arrow[r, "π"] \arrow[d, "\schemebarq ∘ α_{S₁,S₂}"] & Z \arrow[d] \\
             \bar Γ \arrow[r, "π₁"] & Z₁
@@
     \[
-        π_* i_{S₁,S₂}^!\bar\schemeq^!\schemej_! \sheaf F = 
+        π_* α_{S₁,S₂}^!\schemebarq^!\schemej_! \sheaf F = 
         f^!π_{1,*} \schemej_! \sheaf F.

### 2015-06-24 paper.tex
Remove space at end of line.
Improvements.

@@
 \let\stack\mathbf
+\let\shortbar\bar
 \let\bar\overline
@@
 \newcommand\Γsub[1]{\Gamma_{\mkern-3mu#1}}
+\newcommand\barΓsub[1]{\bar{\Gamma}_{\mkern-3mu#1}}
 
@@
 
-Given a manifold $X$ and a category of sheaves on $X$, microlocal geometry asks whether these sheaves can be localized not just on $X$ but also with respect to codirections, i.e.~on the cotangent space $T^*X$.
+Given a manifold $X$ and a category of sheaves on $X$, microlocal geometry asks whether the sheaves can be localized not just on $X$ but also with respect to codirections, i.e.~on the cotangent space $T^*X$.
 For example, for constructible sheaves this leads to the notion of microsupport discussed in detail in \cite{KashiwaraSchapira:1994:SheavesOnManifolds}.
@@
 
-We are led to consider the universal algebra acting on the category with this construction, i.e.~the \emph{Hochschild cohomology} of $\cat C$.
+We are led to consider the universal algebra acting on $\cat C$ by this construction, i.e.~the \emph{Hochschild cohomology} of $\cat C$.
 For a complete (pre-triangulated) dg category $\cat C$ the Hochschild cohomology is the dg algebra of derived endomorphisms of the identity functor of $\cat C$:
@@
 \]
-The ring $R = \bigoplus \operatorname{HH}^{2n}(\HCoh(\cat C)$ is commutative and hence one can define for each $A ∈ \cat C$ the support $\supp_R A$ as a subset of $\Spec R$.
+The ring $R = \bigoplus \operatorname{HH}^{2n}(\cat C)$ is commutative and hence one can define for each $A ∈ \cat C$ the support $\supp_R A$ as a subset of $\Spec R$.
 Thus understanding the Hochschild cohomology of a dg category can be an important step to understanding the category itself.
 
-This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
+This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
 More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
@@
 is the (derived) loop space of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
-Naively we could expect the existence of an isomorphism
+We could expect the existence of an isomorphism
 \begin{equation}
@@
 \end{equation}
+We refer to this as the \enquote{naive expectation}.
 Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\Ga$ is an easy counter-example).
@@
 As we will summarize below, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
-In particular for any stack $\stack X$ we have:
+Thus by definition for any stack $\stack X$ we have:
 \begin{itemize}
@@
 It is often useful to consider the pullback of a D-module on $\stack X$ to a smooth cover.
+For quotient stacks we give the resulting subcategory a special name.
 
@@
 \end{Def}
+
+For reference, we state the following theorem which will be a crucial ingredient in the proof of Theorem~\ref{thm:main}.
 
@@
 
-Recall now that we assume $Δ$ to be schematic schematic and that the dualizing module $ω_{\stack X}$ is always holonomic.
+Recall now that we assume $Δ$ to be schematic and that the dualizing module $ω_{\stack X}$ is always holonomic.
 Thus we have $\dualize Δ_* ω_{\stack X} = Δ_! k_{\stack X}$.
@@
 
-In the preceding section we simply assumed that a relative compactification of the diagonal exists.
-We will now construct such a compactification for quotient stacks.
+In the preceding section we simply assumed that a relative compactification of the given map exists.
+We will now construct such a compactification for the diagonal map of a quotient stack.
 Thus let $X$ be a scheme of finite type over $k$ and let $G$ be an affine algebraic group over $k$ acting on $X$.
@@
 \]
-The closure $\bar{ \Γsub{a}}$ of $\Γsub a$ in $\bar G × X × X$ identifies with $\bar Γ$.
-Thus for ease of notation we will from now on always set $Γ = \Γsub a$ and $\bar Γ = \bar{\Γsub a}$.
+The closure $\barΓsub{a}$ of $\Γsub a$ in $\bar G × X × X$ identifies with $\bar Γ$.
+Thus for ease of notation we will from now on always set $Γ = \Γsub a$ and $\bar Γ = \barΓsub{a}$.
 
@@
     \]
-    We have an open embedding $j\colon X \hookrightarrow \bar{\stack X}$ and a proper morphism $\bar Δ\colon \bar{\stack X} → \stack X × \stack X$ induced by the map $f$ above, such that $Δ = \bar Δ ∘ j$.
+    We have an open embedding $j\colon X \hookrightarrow \bar{\stack X}$ and a proper morphism $\shortbar Δ\colon \bar{\stack X} → \stack X × \stack X$ induced by the map $f$ above, such that $Δ = \shortbar Δ ∘ j$.
 \end{Def}
@@
     It is possible to extend the methods of \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden} to quotients by higher dimensional tori.
-    The resulting constructions are highly useful for doing explicit computations.
+    The resulting constructions are useful for doing explicit computations.
 \end{Rem}
@@
 It is useful to consider only partial compactifications.
-For this let $V$ be a $G$-stable subvariety of $\bar G$ and let $\bar{\Γsub V}$ be the closure of $Γ$ in $G × V$.
+For this let $V$ be a $G$-stable subvariety of $\bar G$ and let $\barΓsub{V}$ be the closure of $Γ$ in $G × V$.
 We set
 \[
-    \bar{\stack X}_V = \rquot{\bar{\Γsub V}}{G×G}.
+    \bar{\stack X}_V = \rquot{\barΓsub{V}}{G×G}.
 \]
@@
 \]
-Let us fix a relative compactification $\bar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
+Let us fix a relative compactification $\shortbar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
 Using the notation of Section~\ref{sec:base-change:cone} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
@@
     We have to show that base change holds along the left-hand square.
-    But by the assumption and Lemma~\ref{lem:base-change-criterion}, base change holds along the outer rectangle and the left-hand square.
+    But by the assumption and Lemma~\ref{lem:base-change-criterion}, base change holds along the outer rectangle and the right-hand square.
     Thus it also holds along the left-hand square.
@@
     For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it is not \goodstack.
-    For non-\goodstack\ stacks, Lemma~\ref{lem:base-change-criterion} instead gives a description of how much the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$ fails.
+    For non-\goodstack\ stacks, the sheaf $i_{\stack X}^* \bar q_{\stack X}^!
+j_!
+k_{\stack X}$ instead gives a measurement for the failure of the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$.
 \end{Rem}
@@
 The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
-Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodness\ for the relative compactification $\Gm^n \subseteq \as n$.
+Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodness\ for the partial compactification $\Gm^n \subseteq \as n$.
 To simplify notation, we drop the subscript $\as n$ from the notation and set $\bar{\stack X} = \bar{\stack X}_{\as n}$ and similarly for the various maps.
@@
 We fix a quotient stack $\stack Y = Y/G$ and a morphism $h\colon \stack Y → \stack X$, induced by a $G$-equivariant morphism $\schemeh\colon Y → X$.
-According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working with stack directly, we can base change to schemes.
+According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working directly with the stacks, we can base change to schemes.
 We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ and the primes from the maps.
@@
 Hence $X^S/G$ is a closed substack of $\stack X$.
-Let $\bar S$ be the closure of $S$ in $\bar G = \as n$ and consider the space
+Let $\bar S$ be the closure of $S$ in $\bar G = \as n$ and consider the closed subspace
 \[
@@
     We write $G \cong G₁ × S₁$ for some subgroup $G₁$ of $G$.
-    This given a corresponding decomposition of the monad $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
+    This gives a corresponding decomposition of the monoid $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
     Let $H' = \bar G₁ H$.
@@
     \]
-    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemmas~\ref{lem:key_for_stablizier}.
+    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemma~\ref{lem:key_for_stablizier}.
 \end{proof}

### 2015-06-24 paper.tex
Acknowledgment and improved abstract.

@@
     We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
-    This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of equivariant D-modules.
+    This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of D-modules on stacks.
 \end{abstract}
@@
 \end{Thm}
+
+\subsection*{Acknowledgments}
+I would like to thank my advisor, David Nadler, for the original motivation for this project and many discussions concerning it.
 

### 2015-06-24 paper.tex
Remove cyrillic font setup.
A version that compiles with pdflatex.
Make tex repo self-sufficient.
TeX Live 2011 on arXiv!!???

@@
 \author{Clemens Koppensteiner}
-
-\usepackage{math-gl}
+\date{June~24, 2015}
 
@@
 
+\usepackage{xparse}
+
+% categories
+\newcommand\cat{\mathbf}
+\newcommand\catIndCoh[2][]{\cat{IndCoh}_{#1}(#2)}
+\newcommand\catVect[1][]{\cat{Vect}_{#1}}
+\NewDocumentCommand \catModules {O{} O{} m} {       % modules
+    \cat{Mod}^{#1}_{#2}(#3)
+}
+\newcommand\catDMod[2][]{\cat{DMod}_{#1}(#2)}
+\newcommand\catDModHol[1]{\catDMod[\mathrm{hol}]{#1}}
+\newcommand\catDModMon[2]{\catDMod{#1}^{#2-\mathrm{mon}}}
+\newcommand\catDModHolMon[2]{\catDModHol{#1}^{#2-\mathrm{mon}}}
+
+\DeclareMathOperator\Hom{Hom}
+\newcommand\id[1][]{{\mathrm{Id}_{#1}}}
+\newcommand\isoto\similarrightarrow
+\newcommand\cocolon{%                   % colon on the right side (i.e. for an adjunction)
+    \nobreak \mskip 6muplus1mu \mathpunct {}\nonscript \mkern -\thinmuskip{:}\mskip 2mu\relax%
+}
+
+% spaces
 \let\stack\mathbf
+\DeclareMathOperator\Spec{Spec}
+\newcommand\LocSys{\operatorname{LocSys}}
+\newcommand\Bun{\operatorname{Bun}}
+\newcommand\ps[2][]{\mathbb P^{#2}_{#1}}
+\newcommand\as[2][]{\mathbb A^{#2}_{#1}}
+\newcommand\Ga{\mathbb{G}_{\mathrm{a}}}
+\newcommand\Gm{\mathbb{G}_{\mathrm{m}}}
+\newcommand\pt{\mathrm{pt}}
+\newcommand\B{\stack{B}}
+
+% misc
+\let\sheaf\mathcal
 \let\shortbar\bar
 \let\bar\overline
-
-\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}
-\newcommand\catDModMon[2]{\catDMod{#1}^{#2-\mathup{mon}}}
-\newcommand\catDModHolMon[2]{\catDModHol{#1}^{#2-\mathup{mon}}}
+\newcommand\dual{\vee}
+\DeclareMathOperator\supp{supp}
+\newcommand\cx\bullet
+\newcommand\proj[1]{\operatorname{pr}_{#1}}
+\newcommand\rquot[2]{%
+    \mathchoice%
+        {\left.#1\kern-0.2ex\middle/\kern-0.3ex\lower0.7ex\hbox{$\displaystyle #2$}\right.}%
+        {\left.#1\middle/#2\right.}%
+        {\left.#1\middle/#2\right.}%
+        {\left.#1\middle/#2\right.}%
+}
+\newcommand\opalg[1]{#1^{\mathrm{op}}}
+
+% specific
 
 \newcommand\dR{\mathrm{dR}}
-\newcommand{\renstar}{\blacktriangle}
+\newcommand\ΓdR{Γ_{\mkern-4mu\dR}}
 
 \newcommand{\HCoh}{\operatorname{HH}^\cx}
-\newcommand\ΓdR{Γ_{\mkern-4mu\dR}}
-
-\newcommand\opalg[1]{#1^{\mathrm{op}}}
-
-\renewcommand\B{\stack{B}}
-\newcommand\mappingstack{\mathbfup{Maps}}
-\newcommand\X{\mathbb{X}}
 
@@
 
-\newcommand\ls[1]{\mathbfcal{L} #1}
-\newcommand\lsY[1]{\mathbfcal{L}_{\stack Y} #1}
-\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
-\newcommand\clsY[1]{\overline{\mathbfcal{L}}_{\stack Y} #1}
-\newcommand\lsc[1]{\mathbfcal{L}^c #1}
-\newcommand\lscY[1]{\mathbfcal{L}_{\stack Y}^c #1}
-
-\newfontfamily\cyrillicfont[Script=Cyrillic]{XITS}
-\newcommand\cyrmath[1]{\textit{\cyrillicfont #1}}
+\newcommand\ls[1]{\mathcal{L} #1}
+\newcommand\lsY[1]{\mathcal{L}_{\stack Y} #1}
+\newcommand\cls[1]{\overline{\mathcal{L}} #1}
+\newcommand\clsY[1]{\overline{\mathcal{L}}_{\stack Y} #1}
+\newcommand\lsc[1]{\mathcal{L}^c #1}
+\newcommand\lscY[1]{\mathcal{L}_{\stack Y}^c #1}
 
@@
 % Formatting of upper case roman numerals (in references).
-\newcommand{\RomanNum}[1]{\textsc{\MakeLowercase{#1}}}
+\newcommand{\RomanNum}[1]{#1}
 
@@
     \begin{tikzcd}
-        \ls \stack X \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
-        \stack X \arrow[r, "Δ"] & \stack X × \stack X
+        \ls \stack X \arrow{r}{p₁} \arrow{d}{p₂} & \stack X \arrow{d}{Δ} \\
+        \stack X \arrow{r}{Δ} & \stack X × \stack X
     \end{tikzcd}
@@
 \[
-    \ls \stack X = \stack X ×\limits_{\stack X × \stack X} \stack X
+    \ls \stack X = \stack X ×_{\stack X × \stack X} \stack X
 \]
@@
 
-\begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
+\begin{Prop}[{\cite[Paragraph~\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
     \label{prop:pre:base-change}%
@@
         \begin{tikzcd}
-            \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
-            \stack X₂ \arrow[r, "g"] & \stack Y
+            \stack Z \arrow{d}{p} \arrow{r}{q} & \stack X₁ \arrow{d}{f} \\
+            \stack X₂ \arrow{r}{g} & \stack Y
         \end{tikzcd}
@@
     \begin{tikzcd}
-        T³ \arrow[r, "Tμ"] \arrow[d, "μT"'] & T² \arrow[d, "μ"] \\
-        T² \arrow[r, "μ"'] & T
+        T³ \arrow{r}{Tμ} \arrow{d}[swap]{μT} & T² \arrow{d}{μ} \\
+        T² \arrow{r}[swap]{μ} & T
     \end{tikzcd}
@@
     \begin{tikzcd}
-        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
-        T² \arrow[r, "μ"'] & T
+        T \arrow{r}{Tη} \arrow{d}[swap]{ηT} \arrow{dr}[description]{\id} & T² \arrow{d}{μ} \\
+        T² \arrow{r}[swap]{μ} & T
     \end{tikzcd}
@@
     \begin{tikzcd}
-        X \arrow[r, "g"] & TX \arrow[r, "Tf"] & T²X \arrow[r, "μ_X"] & TX.
+        X \arrow{r}{g} & TX \arrow{r}{Tf} & T²X \arrow{r}{μ_X} & TX.
     \end{tikzcd}
@@
     \item a \emph{unit} $e\colon G₀ → G₁$,
-    \item a \emph{multiplication} (or \emph{composition}) map $m\colon \stack G₁ ×\limits_{s,\stack G₀,t} \stack G₁ → \stack G₁$,
+    \item a \emph{multiplication} (or \emph{composition}) map $m\colon \stack G₁ ×_{s,\stack G₀,t} \stack G₁ → \stack G₁$,
     \item an \emph{inverse} map $ι\colon \stack G₁ → \stack G₁$,
@@
             \begin{tikzcd}[column sep=small]
-                {} & & \stack G₁ \arrow[dddll, bend right, "s"] \arrow[dddrr, bend left, "t"] & & \\
-                & & \stack G₁ ×_{\stack G₀} \stack G₁ \arrow[u, "m"] \arrow[dl, "p₂"] \arrow[dr, "p₁"] & & \\
-                & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & \\
+                {} & & \stack G₁ \arrow[bend right]{dddll}[swap]{s} \arrow[bend left]{dddrr}{t} & & \\
+                & & \stack G₁ ×_{\stack G₀} \stack G₁ \arrow{u}{m} \arrow{dl}{p₂} \arrow{dr}{p₁} & & \\
+                & \stack G₁ \arrow{dl}{s} \arrow{dr}{t} & & \stack G₁ \arrow{dl}{s} \arrow{dr}{t} & \\
                 \stack G₀ & & \stack G₀ & & \stack G₀
@@
     \begin{tikzcd}
-        \stack X ×_{\stack Y} \stack X \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack X \arrow[d, "f"] \\
-        \stack X \arrow[r, "f"] & \stack Y
+        \stack X ×_{\stack Y} \stack X \arrow{r}{p_s} \arrow{d}{p_t} & \stack X \arrow{d}{f} \\
+        \stack X \arrow{r}{f} & \stack Y
     \end{tikzcd}
@@
         \begin{tikzcd}
-            \stack G_{n+1} \arrow[r, "p_s"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
-            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
+            \stack G_{n+1} \arrow{r}{p_s} \arrow{d}{p_{F+1}} & \stack G_n \arrow{d}{p_F} \\
+            \stack G_{m+1} \arrow{r}{p_s} & \stack G_m
         \end{tikzcd}
@@
     \begin{tikzcd}
-        \ls{\stack X} \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
-        \stack X \arrow[r, "Δ"] & \stack X × \stack X
+        \ls{\stack X} \arrow{r}{p₁} \arrow{d}{p₂} & \stack X \arrow{d}{Δ} \\
+        \stack X \arrow{r}{Δ} & \stack X × \stack X
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
-        \stack X₂ \arrow[r, "g"] & \stack Y
+        \stack Z \arrow{d}{p} \arrow{r}{q} & \stack X₁ \arrow{d}{f} \\
+        \stack X₂ \arrow{r}{g} & \stack Y
     \end{tikzcd}
@@
         \begin{tikzcd}
-            \stack X \arrow[r, hook, "j"] \arrow[dr, "f"'] & \bar{\stack X} \arrow[d, "\bar f"] \\
+            \stack X \arrow[hook]{r}{j} \arrow{dr}[swap]{f} & \bar{\stack X} \arrow{d}{\bar f} \\
             & \stack Y
@@
     \begin{tikzcd}
-        \bar{\stack Z} \arrow[d, "\bar p"] \arrow[r, "\bar q"] & \bar{\stack X}₁ \arrow[d, "\bar f"] \\
-        \stack X₂ \arrow[r, "g"] & \stack Y
+        \bar{\stack Z} \arrow{d}{\bar p} \arrow{r}{\bar q} & \bar{\stack X}₁ \arrow{d}{\bar f} \\
+        \stack X₂ \arrow{r}{g} & \stack Y
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \stack Z^c \arrow[r, hook, "i"] \arrow[d] & \bar{\stack Z} \arrow[d, "\bar q"] \\
-        \stack X₁^c \arrow[r, hook] & \bar{\stack X}₁
+        \stack Z^c \arrow[hook]{r}{i} \arrow{d} & \bar{\stack Z} \arrow{d}{\bar q} \\
+        \stack X₁^c \arrow[hook]{r} & \bar{\stack X}₁
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \lsY \stack X \arrow[r, "q_{\stack Y}"] \arrow[d] & \stack X \arrow[d, "Δ"] \\
-        \stack Y \arrow[r, "Δ∘h"] & \stack X × \stack X
+        \lsY \stack X \arrow{r}{q_{\stack Y}} \arrow{d} & \stack X \arrow{d}{Δ} \\
+        \stack Y \arrow{r}{Δ∘h} & \stack X × \stack X
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \lsY\stack X \arrow[r, hook] \arrow[d, "q_{\stack Y}"] & \clsY\stack X \arrow[d, "\bar q_{\stack Y}"] & \lscY\stack X \arrow[l, hook', "i_{\stack Y}"'] \arrow[d] \\
-        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
+        \lsY\stack X \arrow[hook]{r} \arrow{d}{q_{\stack Y}} & \clsY\stack X \arrow{d}{\bar q_{\stack Y}} \arrow[hookleftarrow]{r}{i_{\stack Y}} & \lscY\stack X \arrow{d} \\
+        \stack X \arrow[hook]{r}{j} & \bar{\stack X} \arrow[hookleftarrow]{r} & \stack X^c
     \end{tikzcd}
@@
         \begin{tikzcd}
-            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
-            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
+            \stack G_{n+1} \arrow{d} \arrow{r} & \stack G_{m+1} \arrow{d} \arrow{r} & \stack X \arrow{d}{Δ} \\
+            \stack G_{n} \arrow{r} & \stack G_m \arrow{r} & \stack X × \stack X
         \end{tikzcd}
@@
         \begin{tikzcd}
-            \lscY \stack U \arrow[r, hook, "i_{\stack U, \stack Y}"] \arrow[d, hook, "α"] & \clsY{\stack U} \arrow[r, "\bar q_{\stack U,\stack Y}"] \arrow[d, hook, "β"] & \bar{\stack U} \arrow[d, hook, "γ"] & \stack U \arrow[l, hook', "j_{\stack U}"'] \arrow[d, hook, "δ"] \\
-            \lscY \stack X \arrow[r, hook, "i_{\stack X, \stack Y}"]                      & \clsY{\stack X} \arrow[r, "\bar q_{\stack X,\stack Y}"]                      & \bar{\stack X}                      & \stack X \arrow[l, hook', "j_{\stack X}"']
+            \lscY \stack U \arrow[hook]{r}{i_{\stack U, \stack Y}} \arrow[hook]{d}{α} & \clsY{\stack U} \arrow{r}{\bar q_{\stack U,\stack Y}} \arrow[hook]{d}{β} & \bar{\stack U} \arrow[hook]{d}{γ} \arrow[hookleftarrow]{r}{j_{\stack U}} & \stack U  \arrow[hook]{d}{δ} \\
+            \lscY \stack X \arrow[hook]{r}{i_{\stack X, \stack Y}}                    & \clsY{\stack X} \arrow{r}{\bar q_{\stack X,\stack Y}}                    & \bar{\stack X}                    \arrow[hookleftarrow]{r}{j_{\stack X}} & \stack X
         \end{tikzcd}
@@
     \begin{tikzcd}
-        \schemelscY \stack X \arrow[r, hook, "\schemei_{\stack Y}"] \arrow[d] & \schemeclsY \stack X \arrow[r, "\schemebarq_{\stack Y}"] \arrow[d] & \bar Γ \arrow[d] & Γ \arrow[l, hook', "\schemej"'] \arrow[d] \\
-        \lscY \stack X \arrow[r, hook, "i_{\stack Y}"]                        & \clsY \stack X \arrow[r, "\bar q_{\stack Y}"]                       & \bar{\stack X}   & \stack X \arrow[l, hook', "j"']
+        \schemelscY \stack X \arrow[hook]{r}{\schemei_{\stack Y}} \arrow{d} & \schemeclsY \stack X \arrow{r}{\schemebarq_{\stack Y}} \arrow{d} & \bar Γ \arrow{d} \arrow[hookleftarrow]{r}{\schemej} & Γ \arrow{d} \\
+        \lscY \stack X \arrow[hook]{r}{i_{\stack Y}}                        & \clsY \stack X \arrow{r}{\bar q_{\stack Y}}                      & \bar{\stack X}   \arrow[hookleftarrow]{r}{j} & \stack X
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \cls_{V_i,\stack Y} \stack X \arrow[r, hook, "i_{V_i,\stack X}"] &
-        \lsc_{V_i,\stack Y} \stack X \arrow[r, "\bar q_{V_i,\stack X}"] &
-        \bar{\stack X}_{V_i} &
-        \stack X \arrow[l, hook', "j_{V_i}"'].
+        \cls_{V_i,\stack Y} \stack X \arrow[hook]{r}{i_{V_i,\stack X}} &
+        \lsc_{V_i,\stack Y} \stack X \arrow{r}{\bar q_{V_i,\stack X}} &
+        \bar{\stack X}_{V_i} \arrow[hookleftarrow]{r}{j_{V_i}} &
+        \stack X.
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \schemelscY \stack X \arrow[r, hook, "\schemei"] &
-        \schemeclsY \stack X \arrow[r, "\schemebarq"] &
-        \bar Γ &
-        Γ \arrow[l, hook', "\schemej"'],
+        \schemelscY \stack X \arrow[hook]{r}{\schemei} &
+        \schemeclsY \stack X \arrow{r}{\schemebarq} &
+        \bar Γ \arrow[hookleftarrow]{r}{\schemej} &
+        Γ,
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \schemelscY[S₁,S₂] \stack X \arrow[r, hook, "α_{S₁,S₂}^c"] \arrow[d, hook, "\schemei^{S₁,S₂}"] & \schemelscY\stack X \arrow[d, hook, "\schemei"]
+        \schemelscY[S₁,S₂] \stack X \arrow[hook]{r}{α_{S₁,S₂}^c} \arrow[hook]{d}{\schemei^{S₁,S₂}} & \schemelscY\stack X \arrow[hook]{d}{\schemei}
         \\
-        \schemeclsY[S₁,S₂] \stack X \arrow[r, hook, "α_{S₁,S₂}"]   & \schemeclsY\stack X
+        \schemeclsY[S₁,S₂] \stack X \arrow[hook]{r}{α_{S₁,S₂}}   & \schemeclsY\stack X
     \end{tikzcd}
@@
         \begin{tikzcd}
-            \schemecls[S₁,S₂] \stack X \arrow[r, "π"] \arrow[d, "\schemebarq ∘ α_{S₁,S₂}"] & Z \arrow[d] \\
-            \bar Γ \arrow[r, "π₁"] & Z₁
+            \schemecls[S₁,S₂] \stack X \arrow{r}{π} \arrow{d}{\schemebarq ∘ α_{S₁,S₂}} & Z \arrow{d} \\
+            \bar Γ \arrow{r}{π₁} & Z₁
         \end{tikzcd}

### 2017-05-08 paper.tex
Force pdflatex.
No colors.
Numeric references and bw mode for submission.
Make things compile again.

--- 2015-06-24 paper.tex
@@
 
-\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}
+%\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}
 \newcommand\catDModMon[2]{\catDMod{#1}^{#2-\mathup{mon}}}
@@
 \newcommand{\HCoh}{\operatorname{HH}^\cx}
-\newcommand\ΓdR{Γ_{\mkern-4mu\dR}}
+\newcommand\GammadR{Γ_{\mkern-4mu\dR}}
 
@@
 
-\newcommand\Γsub[1]{\Gamma_{\mkern-3mu#1}}
-\newcommand\barΓsub[1]{\bar{\Gamma}_{\mkern-3mu#1}}
-
-\newcommand\ls[1]{\mathbfcal{L} #1}
+\newcommand\Gammasub[1]{\Gamma_{\mkern-3mu#1}}
+\newcommand\barGammasub[1]{\bar{\Gamma}_{\mkern-3mu#1}}
+
+\renewcommand\ls[1]{\mathbfcal{L} #1}
 \newcommand\lsY[1]{\mathbfcal{L}_{\stack Y} #1}
@@
 \newcommand\lscY[1]{\mathbfcal{L}_{\stack Y}^c #1}
-
-\newfontfamily\cyrillicfont[Script=Cyrillic]{XITS}
-\newcommand\cyrmath[1]{\textit{\cyrillicfont #1}}
 
@@
     \opalg{\Hom_{\catDMod{X}}(k_{\stack X}, Δ^!Δ_!k_{\stack X})} =
-    \opalg{\ΓdR(\stack X, Δ^!Δ_!k_{\stack X})}.
+    \opalg{\GammadR(\stack X, Δ^!Δ_!k_{\stack X})}.
 \]
@@
 \[
-    \ls \stack X = \stack X ×\limits_{\stack X × \stack X} \stack X
+    \ls \stack X = \stack X \mathop{×}\limits_{\stack X × \stack X} \stack X
 \]
@@
     \label{eq:intro:naive}
-    \ΓdR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
-    \ΓdR(\stack X, p_{2,!}p₁^! k_{\stack X}).
+    \GammadR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
+    \GammadR(\stack X, p_{2,!}p₁^! k_{\stack X}).
 \end{equation}
@@
         \cong
-        \opalg{\ΓdR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)},
-    \]
-    where the algebra structure on $\ΓdR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
+        \opalg{\GammadR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)},
+    \]
+    where the algebra structure on $\GammadR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
 \end{Thm}
@@
 \[
-    \ΓdR(\stack X,\, {-}) = p_*({-}) \colon \catDMod{\stack X} → \catVect.
-\]
-The functor $\ΓdR$ is representable by a D-module $k_{\stack X}$, i.e.
-\[
-    \ΓdR(\stack X,\, {-}) = \Hom_{\catDMod{\stack X}}(k_{\stack X},\, {-}).
-\]
-Again we note that $\ΓdR(\stack X,\, {-})$ is usually not continuous and hence the object $k_{\stack X}$ not compact.
+    \GammadR(\stack X,\, {-}) = p_*({-}) \colon \catDMod{\stack X} → \catVect.
+\]
+The functor $\GammadR$ is representable by a D-module $k_{\stack X}$, i.e.
+\[
+    \GammadR(\stack X,\, {-}) = \Hom_{\catDMod{\stack X}}(k_{\stack X},\, {-}).
+\]
+Again we note that $\GammadR(\stack X,\, {-})$ is usually not continuous and hence the object $k_{\stack X}$ not compact.
 
@@
     \item a \emph{unit} $e\colon G₀ → G₁$,
-    \item a \emph{multiplication} (or \emph{composition}) map $m\colon \stack G₁ ×\limits_{s,\stack G₀,t} \stack G₁ → \stack G₁$,
+    \item a \emph{multiplication} (or \emph{composition}) map $m\colon \stack G₁ \mathop{×}\limits_{s,\stack G₀,t} \stack G₁ → \stack G₁$,
     \item an \emph{inverse} map $ι\colon \stack G₁ → \stack G₁$,
@@
     & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})} & & \text{(adjunction)} \\
-    & = \opalg{\ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr)},
+    & = \opalg{\GammadR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr)},
 \end{align*}
-where the algebra structure on $\ΓdR\bigl(\stack X,\, Δ^!
+where the algebra structure on $\GammadR\bigl(\stack X,\, Δ^!
 Δ_!
@@
 \[
-    \ΓdR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)
+    \GammadR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)
     →
-    \ΓdR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr).
+    \GammadR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr).
 \]
@@
     \[
-        \HCoh(\catDMod{\B G}) = \opalg{\ΓdR\bigl(\B G,\, p_{2,!} p₁^! k_{\B G}\bigr)}.
+        \HCoh(\catDMod{\B G}) = \opalg{\GammadR\bigl(\B G,\, p_{2,!} p₁^! k_{\B G}\bigr)}.
     \]
@@
     \[
-        \ΓdR\bigl(\B G,\, p_{2,!} p₁^! k_{\stack X}\bigr) \cong
-        \ΓdR(G, k_G)^\dual \otimes \ΓdR(\B G, k_{\B G}).
+        \GammadR\bigl(\B G,\, p_{2,!} p₁^! k_{\stack X}\bigr) \cong
+        \GammadR(G, k_G)^\dual \otimes \GammadR(\B G, k_{\B G}).
     \]
@@
     \[
-        \catDMod{\B G} \cong \catModules{\ΓdR(G, k_{G})^\dual},
-    \]
-    where the algebra structure on $\ΓdR(G, k_G)^\dual$ is induced by the group multiplication \cite[Section~7.2]{DrinfeldGaitsgory:2013:FinitenessQuestions}.
-    If $G$ is reductive, then $\ΓdR(G, k_G)^\dual$ is an exterior algebra and thus its Hochschild cohomology can be computed directly.
+        \catDMod{\B G} \cong \catModules{\GammadR(G, k_{G})^\dual},
+    \]
+    where the algebra structure on $\GammadR(G, k_G)^\dual$ is induced by the group multiplication \cite[Section~7.2]{DrinfeldGaitsgory:2013:FinitenessQuestions}.
+    If $G$ is reductive, then $\GammadR(G, k_G)^\dual$ is an exterior algebra and thus its Hochschild cohomology can be computed directly.
 \end{Ex}
@@
 \[
-    \Γsub{a} = \bigl\{(g, x, gx) ∈ G × X × X\bigr\}.
-\]
-The closure $\barΓsub{a}$ of $\Γsub a$ in $\bar G × X × X$ identifies with $\bar Γ$.
-Thus for ease of notation we will from now on always set $Γ = \Γsub a$ and $\bar Γ = \barΓsub{a}$.
+    \Gammasub{a} = \bigl\{(g, x, gx) ∈ G × X × X\bigr\}.
+\]
+The closure $\barGammasub{a}$ of $\Gammasub a$ in $\bar G × X × X$ identifies with $\bar Γ$.
+Thus for ease of notation we will from now on always set $Γ = \Gammasub a$ and $\bar Γ = \barGammasub{a}$.
 
@@
 It is useful to consider only partial compactifications.
-For this let $V$ be a $G$-stable subvariety of $\bar G$ and let $\barΓsub{V}$ be the closure of $Γ$ in $G × V$.
+For this let $V$ be a $G$-stable subvariety of $\bar G$ and let $\barGammasub{V}$ be the closure of $Γ$ in $G × V$.
 We set
 \[
-    \bar{\stack X}_V = \rquot{\barΓsub{V}}{G×G}.
+    \bar{\stack X}_V = \rquot{\barGammasub{V}}{G×G}.
 \]
@@
         \cong
-        \opalg{\ΓdR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)}.
+        \opalg{\GammadR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)}.
     \]

### 2017-05-09 paper.tex
Improving the intro and some other stuff.

@@
 
+\setcounter{tocdepth}{1}
+\tableofcontents
+
 \section{Introduction}
@@
 A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
-We will review the general setup and basic properties of D-modules on (QCA) stacks in Section~\ref{sec:pre}.
-The upshot is that we have an isomorphism of dg algebras
+Representing the identity functor by its kernel, we obtain an isomorphism of dg algebras
 \begin{equation}
@@
 where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
-In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Lemma show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
-However, if $\stack X$ is not an algebraic space (and hence $Δ$ is not proper) then the situation becomes more complicated.
+In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
+However, if $\stack X$ is a general stack, then $Δ$ is not proper and the situation becomes more complicated.
 
@@
 \]
-is the (derived) loop space of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
+is the derived loop space (or inertia stack) of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
 We could expect the existence of an isomorphism
@@
 
-In Section~\ref{sec:base-change} we will investigate how to quantify the cone of the morphism
-\[
+In this paper we investigate how to quantify the cone of the morphism
+\begin{equation}\label{eq:intro:central_cone}
     p_{2,!}p₁^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
-\]
+\end{equation}
 and thus the failure of the naive isomorphism \eqref{eq:intro:naive} to hold.
-As an application, we will prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.
+As an application, we prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.
 
@@
 
+Since, to the author's knowledge, there is currently no comprehensive account of the theory of D-modules on stacks available in the literature, we review the basic formalism in Section~\ref{sec:d-mods}.
+In essence, most of the familiar six functor formalism of holonomic D-modules works in a general context.
+It is convenient to rephrase Theorem~\ref{thm:main} as an equivalence of monads.
+Thus in Section~\ref{sec:monads} we review some constructions of monads in our setting.
+In Section~\ref{sec:HH} we explain how morphism~\eqref{eq:intro:central_cone} arises as a morphism of monads and make precise its relationship with Hochschild cohomology of $\catDMod{\stack X}$.
+
+In Section~\ref{sec:base-change} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.
+Finally, in Section~\ref{sec:torus} we deduce Theorem~\ref{thm:main} from this description, using geometric considerations and the contraction principle of Drinfeld--Gaitsgory \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
+
+The present paper represents only the first step in the study of Hochschild cohomology and associated support theories for D-modules.
+In future work we intend to expand upon the foundations laid out in this paper.
+Of particular interest are quotients stacks $X/G$ with $G$ an affine algebraic group and the stack $\Bun_G(C)$ of $G$-bundles on a curve $C$.
+Following the constructions laid out in Section~\ref{sec:base-change:compactification}, for the former we need a good $G×G$-equivariant compactification of $G$.
+Thus groups with a wonderful compactification are of particular interest for study with our methods.
+For the latter, relative compactifications of the diagonal of $\Bun_G(C)$ have been proposed by Lafforgue and Drinfeld.
+These spaces are under active study and we expect that any computations of Hochschild cohomology to have deep connections with the \enquote{pseudo-identity} that is needed in the formulation of the geometric (categorical) Langlands conjecture.
+[reference?]
+
 \subsection*{Acknowledgments}
@@
 
-\section{Prerequisites}%
-\label{sec:pre}
+\section{D-modules on stacks}
+\label{sec:d-mods}
 
 We fix an algebraically closed base field $k$ of characteristic $0$.
-All stacks will be assumed to be algebraic QCA stacks over $k$.
-As we will summarize below, the QCA condition ensures that the category of D-modules on stacks is well-behaved.
+All stacks will be assumed to be algebraic over $k$ and quasi-compact with affine automorphism group (QCA).
 Thus by definition for any stack $\stack X$ we have:
@@
 \end{itemize}
-The first two conditions ensure that the stack is algebraic, the other three that it is quasi-compact with affine automorphism group (QCA).
+The QCA condition guarantees a reasonable theory of D-modules on $\stack X$.
 For details on QCA stacks we refer to~\cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
@@
 We refer to \cite{Keller:2006:OnDGCategories} for an introduction to dg categories.
-It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2014-draft:HigherAlgebra}, which can be done via the nerve construction \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}.
+It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2014-draft:HigherAlgebra}, which can be done via the nerve construction.% \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}.
 %\cite[Section~1.3.1]{Lurie:2014-draft:HigherAlgebra}
@@
 
-\subsection{D-modules on stacks}
-\label{sec:pre:d-mods}
-
-We will be primarily concerned with D-modules on (quotient) stacks.
-Unfortunately there is currently no comprehensive text available that covers all the basic constructions and properties of D-modules on stacks (or even the \emph{dg category} of D-modules on schemes).
-Thus we collect all the relevant properties (without proof) in this section.
-The upshot is that the familiar \enquote{six functors formalism} essentially works for holonomic D-modules and schematic morphisms of stacks.
-
 The category of D-modules on a stack $\stack X$ can be either constructed via descent \cite{BeilinsonDrifeld:unpublished:Hitchin,DrinfeldGaitsgory:2013:FinitenessQuestions} or equivalently as ind-coherent sheaves on the de Rham space of $\stack X$ \cite{GaitsgoryRozenblyum:2014:CrystalsAndDModules}.
@@
 It is explained in detail in the upcoming book \cite{GaitsgoryRozenblyum:prelim:StudyInDAG} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
-Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and most of the following assertions are taken from there.
-
-For any morphism $f\colon \stack X → \stack Y$ the constructions yield a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and (after some work) a not necessarily continuous functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
-If $p\colon \stack X → \pt$ is the structure map then we set
+Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and unless stated otherwise proofs for the assertions in this section can be found there.
+
+For any morphism $f\colon \stack X → \stack Y$ we obtain a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
+If $p\colon \stack X → \pt$ is the structure map, we set
 \[
@@
 \]
-Again we note that $\GammadR(\stack X,\, {-})$ is usually not continuous and hence the object $k_{\stack X}$ not compact.
+As $\GammadR(\stack X,\, {-})$ is usually not continuous and the object $k_{\stack X}$ is usually not a compact object of $\catDMod{\stack X}$.
 
 Let $Δ\colon \stack X → \stack X × \stack X$ be the diagonal.
-The category $\catDMod{\stack X}$ has a monoidal structure given by the tensor product
-\[
-    \sheaf F \otimes \sheaf G = Δ^!\bigl( \sheaf F \boxtimes \sheaf G \bigr).
-\]
-The unit for this monoidal structure is $ω_{\stack X} = p^! k$.
+The category $\catDMod{\stack X}$ has a monoidal structure given by the tensor product $\sheaf F \otimes \sheaf G \coloneq Δ^!\bigl( \sheaf F \boxtimes \sheaf G \bigr)$ with unit $ω_{\stack X} = p^!
+k$.
 
@@
 
-The Verdier duality functor on schemes induces an involutive anti auto-equivalence
+The Verdier duality functor on schemes induces an involutive anti-auto-equivalence
 \[
@@
 
-\subsection{Monads}
-\label{sec:pre:monads}
+\section{Monads}
+\label{sec:monads}
 
@@
 \section{Hochschild cohomology}
+\label{sec:HH}
 
@@
 Let us assume for the moment that $Δ$ (and hence $p_i$) was proper.
-Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:pre:monads} we have an isomorphism of monads
+Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:monads} we have an isomorphism of monads
 \begin{equation}

### 2017-05-11 paper.tex
Various improvements.

@@
     \HCoh(\cat C)
-    = \operatorname{\mathbf{R}Hom}(\id[\cat C], \id[\cat C])
+    = \mathbb{R}\mathrm{Hom}(\id[\cat C], \id[\cat C])
     = \Hom_{\cat{Funct}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
@@
 For the latter, relative compactifications of the diagonal of $\Bun_G(C)$ have been proposed by Lafforgue and Drinfeld.
-These spaces are under active study and we expect that any computations of Hochschild cohomology to have deep connections with the \enquote{pseudo-identity} that is needed in the formulation of the geometric (categorical) Langlands conjecture.
-[reference?]
+These spaces are under active study and we expect that any computations of Hochschild cohomology to have deep connections with the \enquote{pseudo-identity} that is needed in the formulation of the geometric (categorical) Langlands conjecture.% \cite{Gaitsgory:preprint:StrangeFunctionalEquationForEisensteinSeries}
 
@@
 
-For reference, we state the following theorem which will be a crucial ingredient in the proof of Theorem~\ref{thm:main}.
-
-\begin{Thm}[Contraction principle~{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
+In Section~\ref{sec:torus} we will be concerned with $\Gm^n$-monodromic D-modules.
+For the case of $n = 1$ one has the following powerful theorem, known as the \emph{contraction principle}.
+It will be a crucial ingredient for our proof of Theorem~\ref{thm:main}.
+
+\begin{Thm}[{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
     \label{thm:pre:contraction_principle}%
@@
 Let $X$ be an object of the category $\cat C$.
-Then $T$ gives the vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
+Then $T$ gives the dg vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
 \[
@@
     \item $s ∘ e = t ∘ e = \id_{\stack G₀}$,
-    \item $s ∘ m = s ∘ p₂$ and $t ∘ m = t ∘ p₁$ (where $p_i\colon \stack G₁ ×_{s,\stack G₀,t} \stack G₁$ are the projection maps).
+    \item $s ∘ m = s ∘ p₂$ and $t ∘ m = t ∘ p₁$ (where $p_i\colon \stack G₁ ×_{s,\stack G₀,t} \stack G₁ → \stack G₁$ are the projection maps).
     \item $m$ is associative,
@@
 To obtain the corresponding derived statement one applies an argument similar to \cite[Section~\RomanNum{II}.1.7.2]{GaitsgoryRozenblyum:prelim:StudyInDAG}.
-We will discuss a version of this below.
 
@@
 Of course, by doing so we do not automatically have base change isomorphisms available anymore.
-Thus we have to explicitly require that all necessary base changes hold (this is usually called the Beck-Chevalley condition).
-
-In order to formulate the condition, we need the concept of the \emph{nerve} of a groupoid.
-This is the simplicial stack, also denoted $\stack{G}_\cx$, with
+Thus we have to explicitly require the \emph{Beck--Chevalley condition}, saying that all necessary base changes hold.
+
+The Beck--Chevalley condition us formulated using the \emph{nerve} of the groupoid $\stack G_\cx$.
+Intuitively, this is the simplicial stack, usually also denoted $\stack{G}_\cx$, with
 \[
@@
     \]
-    given by the adjunction morphisms is an isomorphism of functors from the category $\catDModHol{\stack G_n}$ to $\catDModHol{\stack G_{m+1}}$.
+    given by the adjunction morphisms is an isomorphism of functors from $\catDModHol{\stack G_n}$ to $\catDModHol{\stack G_{m+1}}$.
     Then the endofunctor $p_{t,!} p_s^!$ of $\catDModHol{\stack X}$ has a canonical structure of a monad and as such is isomorphic to the adjunction monad $f^!f_!$.
@@
 \]
-fulfilling the usual compatibilities (cf.~\cite[Section~2]{BenZviNadler:arXiv:NonlinearTraces}).
+satisfying the usual compatibilities (cf.~\cite[Section~2]{BenZviNadler:arXiv:NonlinearTraces}).
 Let $u = η(k)$.
-Then to each continuous endofunctor $F$ of $\cat C$ we can associate its kernel $\id[\cat C^\dual] \otimes F(u) ∈ \cat C^\dual \otimes \cat C$ and conversely to each kernel $Q ∈ \cat C^\dual \otimes \cat C$ we can associate the endofunctor
+To each continuous endofunctor $F$ of $\cat C$ we can associate its kernel $\id[\cat C^\dual] \otimes F(u) ∈ \cat C^\dual \otimes \cat C$ and conversely to each kernel $Q ∈ \cat C^\dual \otimes \cat C$ we can associate the endofunctor
 \[
@@
 \]
-Let us now consider the case of $\cat C = \catDMod{\stack X}$ for a stack $X$.
+Let us now consider the case of $\cat C = \catDMod{\stack X}$ for a stack $\stack X$.
 Let $p\colon \stack X → \pt$ be the structure morphism and $Δ\colon \stack X → \stack X × \stack X$ the diagonal.
@@
 \]
-Let us assume for the moment that $Δ$ (and hence $p_i$) was proper.
+Let us assume for the moment that $Δ$ (and hence $p_i$) is proper.
 Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:monads} we have an isomorphism of monads
@@
 
-\section{Base change}
+\section{Base change along the diagonal}
 \label{sec:base-change}
+
 \subsection{The cone of the base-change map}\label{sec:base-change:cone}
@@
 Consider a Cartesian diagram of stacks
-\[
+\begin{equation}
+    \label{eq:base-change:square}
     \begin{tikzcd}
@@
     \end{tikzcd}
-\]
+\end{equation}
 with $f$ and $g$ schematic.
@@
 
-\begin{Ex}
 A famous example of such a relative compactification is Drinfeld's compactification of the morphism $\Bun_B → \Bun_G$, where $\Bun_G$ is the stack of $G$-bundles on a curve $C$ with $G$ reductive and $B$ is a Borel subgroup of $G$ \cite{BravermanGaitsgory:2002:GeometricEisensteinSeries}.
-\end{Ex}
-
-Let us assume that in the above situation there exists a relative compactification of $f\colon \stack X₁ → \stack Y$.
+
+Let us now assume that in the situation of diagram \eqref{eq:base-change:square} there exists a relative compactification of $f\colon \stack X₁ → \stack Y$.
 Let $\stack X₁^c$ be the closed complement of the open inclusion $j\colon \stack X₁ \hookrightarrow \bar{\stack X}₁$.
-Similarly, we let $\bar{\stack Z} = \stack X₂ ×_{\stack Y} \bar{\stack X}₁$ and $\stack Z^c = \stack X₂ ×_{\stack Y} \stack X₁^c$.
-The notation for the corresponding inclusion and projection maps is summarized in the following Cartesian diagrams.
+Similarly, we denote by $\bar{\stack Z} = \stack X₂ ×_{\stack Y} \bar{\stack X}₁$ and $\stack Z^c = \stack X₂ ×_{\stack Y} \stack X₁^c$ the corresponding fiber products.
+The corresponding inclusion and projection maps are denoted as is indicated in the following Cartesian diagrams.
 \[
@@
 We note that $\bar{\stack Z}$ is the disjoint union of the closed substack $\stack Z^c$ and the open substack $\stack Z$.
+We can now quantify the failure of the base change morphism to be an isomorphism.
 
@@
     \label{lem:base-change-criterion}%
-    The cone of the morphism~\eqref{eq:base-change-morphism} is
+    In the situation of the Cartesian square \eqref{eq:base-change:square}, the cone of the base change morphism $p_! q^! → g^! f_!$ is given by
     \[
@@
     \]
-    In particular, if $i^* \bar{q}^! j_! = 0$, then~\eqref{eq:base-change-morphism} is an isomorphism of functors.
+    In particular, if $i^* \bar{q}^! j_! = 0$, then $p_! q^! \cong g^! f_!$ is an isomorphism of functors.
 \end{Lem}
@@
     Let $\tilde\jmath\colon \stack Z \hookrightarrow \bar{\stack Z}$ be the open inclusion complement to $i$.
-    We split the adjunction in \eqref{eq:base-change-adjunctions} in two by using the compositions
+    We split the adjunctions in \eqref{eq:base-change-adjunctions} in two by using the compositions
     \[
         f = \bar f ∘ j
-        ,\
+        ,\quad
         p = \bar p ∘ \tilde\jmath
-        \text{ and }
+        \quad\text{and}\quad
         q = \bar q ∘ \tilde\jmath.
@@
     \]
-    The equality $p_! q^! f^! f_! = p_! p^! g^! f_!$ then becomes
+    The equality $p_! q^! f^! f_! = p_! p^! g^! f_!$ becomes
     \[
@@
     Let us apply the same adjunction morphisms in a different order.
-    First the inclusions
+    First the recollement adjunctions
     \[
@@
     \end{equation}
-    We note that the adjunction $α\colon \id → j^!j_!$ is an isomorphism and the composition of the maps in \eqref{eq:lem:base-change-criterion:pf:split_morphism_base_change} is exactly the isomorphism of proper base change (cf.~Proposition~\ref{prop:pre:base-change}).
+    We note that the adjunction $α\colon \id → j^!j_!$ is an isomorphism and the maps in \eqref{eq:lem:base-change-criterion:pf:split_morphism_base_change} compose exactly to the isomorphism of proper base change (cf.~Proposition~\ref{prop:pre:base-change}).
     Thus the cone of the whole composition is the same as the cone of the morphism $β$, which is given by the recollement triangle
@@
 
-\subsection{Relative compactification for quotient stacks}
+\subsection{Relative compactifications for quotient stacks}
 \label{sec:base-change:compactification}%
@@
 It is useful to consider only partial compactifications.
-For this let $V$ be a $G$-stable subvariety of $\bar G$ and let $\barGammasub{V}$ be the closure of $Γ$ in $G × V$.
+For this let $V$ be a $G$-stable subvariety of $\bar G$ containing $G$, and let $\barGammasub{V}$ be the closure of $Γ$ in $V × X × X$.
 We set
@@
 We let $\bar q_{\stack Y}\colon \clsY\stack X → \bar{\stack X}$ be the projection morphism and $i_{\stack Y}\colon \lscY\stack X \hookrightarrow \clsY\stack X$ the inclusion.
-Thus we have the following central diagram
+Thus we have the following diagram which is central to remainder of this paper.
 \[
@@
 \]
+Motivated by Lemma~\ref{lem:base-change-criterion} we make the following definition.
 
@@
 We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ is \goodstack.
-The reason for this definition is the following theorem which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodstack\ quotient stacks.
+Theorem~\ref{thm:main} then immediately follows from the following theorem which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodstack\ quotient stacks.
 
@@
 \end{Thm}
-
-In other words, Theorem~\ref{thm:main} holds for \goodstack\ stacks.
 
@@
 \begin{proof}
-    Follows from compatibility of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_!$ with $\boxtimes$ and coproducts.
+    This follows from compatibility of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_!$ with $\boxtimes$ and coproducts.
     (Note that $\lscY{(\stack X₁ × \stack X₂)} = \lscY \stack{X₁} × \clsY \stack{X₂} ∪ \clsY{\stack X₁} × \lscY{\stack X₂}$.)
@@
 \begin{proof}
-    Follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:base-change:scheme-cover} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and permutes with the other morphisms up to a shift.
+    This follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:base-change:scheme-cover} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and commutes with the other morphisms up to a shift.
 \end{proof}

### 2017-05-12 paper.tex
start

@@
     given by the adjunction morphisms is an isomorphism of functors from $\catDModHol{\stack G_n}$ to $\catDModHol{\stack G_{m+1}}$.
+    Further assume that the same is true along 
+    \[
+        \begin{tikzcd}
+            \stack G₁ \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack G₀ \arrow[d, "f"] \\
+            \stack G₀ \arrow[r, "f"] & \stack Y
+        \end{tikzcd}
+    \]
     Then the endofunctor $p_{t,!} p_s^!$ of $\catDModHol{\stack X}$ has a canonical structure of a monad and as such is isomorphic to the adjunction monad $f^!f_!$.
@@
 
-\begin{Def}
+\begin{Def}\label{def:good}
     A quotient stack $\stack X = X/G$ is called \emph{\goodstack} if for every quotient stack $\stack Y = Y/G$ and schematic morphism $\stack Y → \stack X$ the functor $i_{\stack Y}^* \bar q_{\stack Y}^!
@@
 \begin{proof}
-    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid $\ls\stack X \rightrightarrows \stack X$.
+    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid induced by $Δ\colon \stack X → \stack X × \stack X$.
     Thus we let $\stack G_\cx$ be the simplicial stack with
     \[
-        \stack G_i = \underbrace{\ls\stack X ×_{\stack X} \dotsb ×_{\stack X} \ls\stack X}_{\text{$i$ factors}}.
-    \]
-    Any morphism $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ induces a diagram
+        \stack G_i = \underbrace{\stack X \mathop{×}\limits_{\stack X × \stack X} \dotsb \mathop{×}\limits_{\stack X × \stack X} \stack X}_{\text{$i+1$ factors}}.
+    \]
+    Setting $\stack Y = \stack X$ in Definition~\ref{def:good} it follows from Lemma~\ref{lem:base-change-criterion} that base change holds along the square
+    \[
+        \begin{tikzcd}
+            \stack G₁ \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack G₀ \arrow[d, "f"] \\
+            \stack G₀ \arrow[r, "f"] & \stack X × \stack X
+        \end{tikzcd}
+    \]
+    Let $F\colon [n] → [m]$ be a morphism in $\cat{Δ}^{\mathrm{op}}$ and consider the induced diagram
     \[
@@
     \]
+    We note that $\stack G_{m+1} = \stack G_m ×_{\stack X × \stack X} \stack X$ and similarly for $\stack G_n$.
+    Thus a relative compactification of $\stack G_{m+1} → \stack G_m$ is given by $\stack G_m ×_{\stack X × \stack X} \bar{\stack X} → \stack G_m$.
+    The map $j$ then identifies as the inclusion of $\stack G_m ×_{\stack X × \stack X} \stack X$.
     We have to show that base change holds along the left-hand square.

### 2017-05-24 paper.tex
Stronger condition on good stacks.

@@
 
+\newcommand\XXtimes{%
+    \mathchoice%
+        {\mathop{×}\limits_{\stack X × \stack X}}
+        {×_{\stack X × \stack X}}
+        {×_{\stack X × \stack X}}
+        {×_{\stack X × \stack X}}
+    }
 \renewcommand\ls[1]{\mathbfcal{L} #1}
-\newcommand\lsY[1]{\mathbfcal{L}_{\stack Y} #1}
+\newcommand\lsY[2][\stack Y]{\mathbfcal{L}_{#1} #2}
 \newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
-\newcommand\clsY[1]{\overline{\mathbfcal{L}}_{\stack Y} #1}
+\newcommand\clsY[2][\stack Y]{\overline{\mathbfcal{L}}_{#1} #2}
 \newcommand\lsc[1]{\mathbfcal{L}^c #1}
-\newcommand\lscY[1]{\mathbfcal{L}_{\stack Y}^c #1}
+\newcommand\lscY[2][\stack Y]{\mathbfcal{L}_{#1}^c #2}
+
+\newcommand\sls[1]{L#1}
+\newcommand\slsY[2][\stack Y]{L_{#1}#2}
+\newcommand\scls[1]{\overline{L}#1}
+\newcommand\sclsY[2][\stack Y]{\overline{L}_{#1}#2}
+\newcommand\slsc[1]{L^c #1}
+\newcommand\slscY[2][\stack Y]{L^c_{#1}#2}
 
@@
 
-\newcommand\goodstack{good}
-\newcommand\Goodstack{Good}
-\newcommand\goodness{goodness}
+\newcommand\goodstack{XXXgoodXXX}
+\newcommand\Goodstack{XXXGoodXXX}
+\newcommand\goodness{property \textbf{(!)}}
+\newcommand\goodnessshort{\textbf{(!)}}
+\newcommand\isgood{has property \textbf{(!)}}
+\newcommand\aregood{have property \textbf{(!)}}
+\newcommand\isnotgood{does not have property \textbf{(!)}}
+\newcommand\arenotgood{do not have property \textbf{(!)}}
+\newcommand\goodX[1]{#1 with property \textbf{(!)}}
+\newcommand\goodnessb{property \textbf{(!')}}
+\newcommand\goodnessbshort{\textbf{(!')}}
+\newcommand\isgoodb{has property \textbf{(!')}}
+\newcommand\aregoodb{have property \textbf{(!')}}
+\newcommand\goodbX[1]{#1 with property \textbf{(!')}}
 
@@
 
-Let $\stack X = X/G$ be a quotient stack as before.
-For any morphism of stacks $h\colon \stack Y → \stack X$ we set $\lsY{\stack X} = \stack X ×_{\stack X × \stack X} \stack Y$.
-Thus we have the Cartesian diagram
-\[
-    \begin{tikzcd}
-        \lsY \stack X \arrow[r, "q_{\stack Y}"] \arrow[d] & \stack X \arrow[d, "Δ"] \\
-        \stack Y \arrow[r, "Δ∘h"] & \stack X × \stack X
-    \end{tikzcd}
-\]
-Let us fix a relative compactification $\shortbar Δ \colon \bar{\stack X} → \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
-Using the notation of Section~\ref{sec:base-change:cone} we set $\clsY{\stack X} = \bar{\stack X} ×_{\stack X × \stack X} \stack Y$ and $\lscY{\stack X} = {\stack X}^c ×_{\stack X × \stack X} \stack Y$.
-We let $\bar q_{\stack Y}\colon \clsY\stack X → \bar{\stack X}$ be the projection morphism and $i_{\stack Y}\colon \lscY\stack X \hookrightarrow \clsY\stack X$ the inclusion.
-Thus we have the following diagram which is central to remainder of this paper.
-\[
-    \begin{tikzcd}
-        \lsY\stack X \arrow[r, hook] \arrow[d, "q_{\stack Y}"] & \clsY\stack X \arrow[d, "\bar q_{\stack Y}"] & \lscY\stack X \arrow[l, hook', "i_{\stack Y}"'] \arrow[d] \\
-        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
-    \end{tikzcd}
-\]
-Motivated by Lemma~\ref{lem:base-change-criterion} we make the following definition.
+Let $\stack Y$ be a stack over $\stack X$.
+To simplify notation, we set
+\[
+    \lsY = \stack Y \XXtimes \stack X,
+\]
+where the fiber product is taken over the maps $\stack Y → \stack X \xrightarrow{Δ} \stack X × \stack X$ and $Δ$.
+Further if $f\colon \stack Y₁ → \stack Y₂$ is a morphism of stacks over $\stack X$ we write $\ls f$ for the induced morphism $\lsY[\stack Y₁]{\stack X} → \lsY[\stack Y₂]{\stack X}$.
 
 \begin{Def}\label{def:good}
-    A quotient stack $\stack X = X/G$ is called \emph{\goodstack} if for every quotient stack $\stack Y = Y/G$ and schematic morphism $\stack Y → \stack X$ the functor $i_{\stack Y}^* \bar q_{\stack Y}^!
-j_!$ vanishes on $\catDModHol{\stack X}$.
+    We say that a quotient stack $\stack X = X/G$ \emph{\isgood} if the following two conditions hold.
+    \begin{enumerate}
+        \item $!$-base-change holds along the Cartesian square
+            \[
+                \begin{tikzcd}
+                    \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
+                    \stack X \arrow[r, "Δ"] & \stack X × \stack X
+                \end{tikzcd}
+            \]
+            i.e.~the canonical morphism $p_{1,!}p₂^! → Δ^!Δ_!$ is an isomorphism on holonomic D-modules.
+        \item For any schematic morphism $f\colon \stack Y₁ = Y₁/G → \stack Y₂ = Y₂/G$ of $G$-quotient stacks over $\stack X$, $!$-base-change holds along the Cartesian diagram
+            \[
+                \begin{tikzcd}
+                    \lsY[\stack Y₂]{\stack X} \arrow[r, "\ls f"] \arrow[d, "π₂"] & \lsY[\stack Y₁]{\stack X} \arrow[d, "π₁"]\\
+                    \stack Y₂ \arrow[r, "f"] & \stack Y₁
+                \end{tikzcd}
+            \]
+            i.e.~the canonical morphism $π_{2,!}(\ls f)^! → f^! π_{1,!}$ is an isomorphism on holonomic D-modules.
+    \end{enumerate}
 \end{Def}
 
-We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ is \goodstack.
-Theorem~\ref{thm:main} then immediately follows from the following theorem which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodstack\ quotient stacks.
-
-\begin{Thm}\label{thm:good-is-good}
-    If $\stack X = X/G$ is \goodstack, then there exists a canonical structure of monad on $p_{2,!}p₁^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
+We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ \isgood.
+Theorem~\ref{thm:main} then immediately follows from the following observation which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodX{quotient stacks}.
+
+\begin{Prop}\label{prop:good-is-good}
+    If $\stack X = X/G$ \isgood, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
     In particular there is an isomorphism of algebras
@@
         \cong
-        \opalg{\GammadR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)}.
-    \]
-\end{Thm}
+        \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
+    \]
+\end{Prop}
 
@@
     \]
-    Setting $\stack Y = \stack X$ in Definition~\ref{def:good} it follows from Lemma~\ref{lem:base-change-criterion} that base change holds along the square
-    \[
-        \begin{tikzcd}
-            \stack G₁ \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack G₀ \arrow[d, "f"] \\
-            \stack G₀ \arrow[r, "f"] & \stack X × \stack X
-        \end{tikzcd}
-    \]
+    The second base change condition of Lemma~\ref{lem:pre:groupoid_monad_hol} holds by definition.
     Let $F\colon [n] → [m]$ be a morphism in $\cat{Δ}^{\mathrm{op}}$ and consider the induced diagram
@@
     We note that $\stack G_{m+1} = \stack G_m ×_{\stack X × \stack X} \stack X$ and similarly for $\stack G_n$.
-    Thus a relative compactification of $\stack G_{m+1} → \stack G_m$ is given by $\stack G_m ×_{\stack X × \stack X} \bar{\stack X} → \stack G_m$.
-    The map $j$ then identifies as the inclusion of $\stack G_m ×_{\stack X × \stack X} \stack X$.
-    We have to show that base change holds along the left-hand square.
-    But by the assumption and Lemma~\ref{lem:base-change-criterion}, base change holds along the outer rectangle and the right-hand square.
-    Thus it also holds along the left-hand square.
+    Thus setting $\stack Y₁ = \stack G_n$ and $\stack Y₂ = \stack G_m$ in the definition of \goodness, we see that all the required base changes holds.
 \end{proof}
@@
 \begin{Rem}
-    We expect that most quotient stacks are not \goodstack.
-    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it is not \goodstack.
-    For non-\goodstack\ stacks, the sheaf $i_{\stack X}^* \bar q_{\stack X}^!
-j_!
-k_{\stack X}$ instead gives a measurement for the failure of the naive expectation for $\HCoh\bigl(\catDMod{\stack X}\bigr)$.
+    We expect that most quotient stacks \arenotgood.
+    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it \isnotgood.
 \end{Rem}
 
-We finish this section with some useful observations for proving that a stack is \goodstack.
-
-\begin{Lem}
-    If $\stack X₁ = X₁/G₁$ and $\stack X₂ = X₂/G₂$ are \goodstack, then $\stack X₁ × \stack X₂$ is \goodstack.
-\end{Lem}
-
-\begin{proof}
-    This follows from compatibility of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_!$ with $\boxtimes$ and coproducts.
-    (Note that $\lscY{(\stack X₁ × \stack X₂)} = \lscY \stack{X₁} × \clsY \stack{X₂} ∪ \clsY{\stack X₁} × \lscY{\stack X₂}$.)
-\end{proof}
+We will use Lemma~\ref{lem:base-change-criterion} in order to check the base change criteria in Definition~\ref{def:good}.
+In order to do so we unfortunately have to introduce some additional notation.
+Let us fix a compactification $\bar G$ of $G$ and a relative compactification $\stack X \xrightarrow{j} \bar{\stack X} \xrightarrow{\bar Δ} \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
+For any $\stack Y → \stack X$ this induces a relative compactification $\clsY{\stack X} = \stack Y \XXtimes \bar{\stack X}$.
+Let us write $j_{\stack Y}\colon \lsY{\stack X} \hookrightarrow \clsY{\stack X}$ for the open inclusion and $i_{\stack Y}\colon \lscY{\stack X} = \stack Y \XXtimes \stack X^c → \clsY{\stack X}$ for the complement.
+Thus we have the following two diagrams with Cartesian squares which are central to the remainder of this paper.
+The first describes the situation for a loop stack:
+\begin{equation}\label{eq:diag:central1}
+    \begin{tikzcd}
+        \ls\stack X \arrow[r, "j_{\stack X}", hook] \arrow[d, "p₂"] & \cls\stack X \arrow[d, "\bar p₂"] & \lsc\stack X \arrow[l, hook', "i_{\stack X}"']  \arrow[d] \\
+        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
+    \end{tikzcd}
+\end{equation}
+For the second let $\stack Y₁ → \stack Y₂$ be a morphism of stacks over $\stack X$:
+\begin{equation}\label{eq:diag:central2}
+    \begin{tikzcd}
+        \lsY[\stack Y₁]{\stack X} \arrow[r, "j_{\stack Y₁}", hook] \arrow[d, "\ls f"] & \clsY[\stack Y₁]{\stack X} \arrow[d, "{\cls f}"] & \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']  \arrow[d] \\
+        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] & \clsY[\stack Y₂]{\stack X} & \lscY[\stack Y₂]{\stack X} \arrow[l, hook']
+    \end{tikzcd}
+\end{equation}
+With this setup we make the following definition.
+\begin{Def}\label{def:good'}
+    We say that a quotient stack $\stack X = X/G$ \emph{\isgoodb} if the following two conditions hold.
+    \begin{enumerate}
+        \item $i_{\stack X}^* \bar p₂^! j_!$ vanishes on $\catDModHol{\stack X}$.
+        \item For any schematic morphism $f\colon \stack Y₁ → \stack Y₂$ of $G$-quotient stacks over $\stack X$ the composition $i_{\stack Y₁}^* (\bar{\ls f})^!
+j_{\stack Y₂,!}$ vanishes on $\catDModHol{\lsY[\stack Y₂]{\stack X}}$.
+    \end{enumerate}
+\end{Def}
+
+Lemma~\ref{lem:base-change-criterion} says that $\goodnessbshort$\ implies $\goodnessshort$.
+In the remainder of this section we will discuss several reduction steps for showing that a given stack \isgoodb.
+
+%\begin{Lem}
+%    If $\stack X₁ = X₁/G₁$ and $\stack X₂ = X₂/G₂$ are \goodstack, then $\stack X₁ × \stack X₂$ is \goodstack.
+%\end{Lem}
+%
+%\begin{proof}
+%    This follows from compatibility of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_!$ with $\boxtimes$ and coproducts.
+%    (Note that $\lscY{(\stack X₁ × \stack X₂)} = \lscY \stack{X₁} × \clsY \stack{X₂} ∪ \clsY{\stack X₁} × \lscY{\stack X₂}$.)
+%\end{proof}
 
@@
     Let $U$ be a $G$-equivariant open subset of $X$.
-    If $X/G$ is \goodstack\ then $U/G$ is \goodstack.
+    If $X/G$ \isgoodb\ then $U/G$ \isgoodb.
 \end{Lem}
@@
 \begin{proof}
-    Let $\stack U = U/G$ and let $\stack Y$ be a quotient stack mapping into $\stack U$ (and hence also into $\stack X$).
+    Set $\stack U = U/G$.
+    We will only show the second condition of Definition~\ref{def:good'}, the first one is similar.
+    Thus let $f\colon \stack Y₁ → \stack Y₂$ be a map of quotient stacks over $\stack U$ (and hence also over $U$).
+    We note that since $\stack U$ is an open subset we have isomorphisms $\lsY[\stack Y_i]{\stack U} \cong \stack Y_i \XXtimes \stack U$.
     Consider the diagram
@@
         \begin{tikzcd}
-            \lscY \stack U \arrow[r, hook, "i_{\stack U, \stack Y}"] \arrow[d, hook, "α"] & \clsY{\stack U} \arrow[r, "\bar q_{\stack U,\stack Y}"] \arrow[d, hook, "β"] & \bar{\stack U} \arrow[d, hook, "γ"] & \stack U \arrow[l, hook', "j_{\stack U}"'] \arrow[d, hook, "δ"] \\
-            \lscY \stack X \arrow[r, hook, "i_{\stack X, \stack Y}"]                      & \clsY{\stack X} \arrow[r, "\bar q_{\stack X,\stack Y}"]                      & \bar{\stack X}                      & \stack X \arrow[l, hook', "j_{\stack X}"']
+            \lsY[\stack Y₂]{\stack U} \arrow[r, hook, "j_{\stack Y₂}^{\stack U}"] \arrow[d, hook, "α"] &
+            \clsY[\stack Y₂]{\stack U} \arrow[d, hook, "β"] &
+            \clsY[\stack Y₁]{\stack U} \arrow[l, "{\cls f}^{\stack U}"'] \arrow[d, hook, "γ"] &
+            \lscY[\stack Y₁]{\stack U} \arrow[l, hook', "i^{\stack U}_{\stack Y₁}"'] \arrow[d, hook, "δ"] \\
+            %
+            \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}^{\stack X}"] &
+            \clsY[\stack Y₂]{\stack X} &
+            \clsY[\stack Y₁]{\stack X} \arrow[l, "{\cls f}^{\stack X}"'] &
+            \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i^{\stack X}_{\stack Y₁}"']
         \end{tikzcd}
@@
     \begin{equation*}
-        i_{\stack U, \stack Y}^* \bar q_{\stack U,\stack Y}^! j_{\stack U,!} =
-        i_{\stack U, \stack Y}^* \bar q_{\stack U,\stack Y}^! j_{\stack U,!} δ^* δ_*=
-        α^* i_{\stack X, \stack Y}^* \bar q_{\stack X, \stack Y}^! j_{\stack X,!} δ_* =
+        i^{\stack U,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack U} =
+        i^{\stack U,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack U} α^* α_*=
+        δ^* i^{\stack X,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack X} α_*=
         0.
@@
 
-The same argument can be used to reduce the computation to a smooth cover.
-We will now introduce notation for the special case of the cover $\bar Γ → \bar{\stack X}$.
-The corresponding covers of the other relevant stacks are introduced in the following diagram with Cartesian squares.
+A similar can be used to reduce the computation to a smooth cover.
+In particular we will want to reduce to computations on a schematic cover.
+On such a cover we will use primes to indicate maps on schemes and will use $\schemels{}$ instead of $\ls{}$ for the covers of the loop spaces.
+If we start with the cover $\bar Γ → \bar{\stack X}$, the pullbacks to the part of diagram \eqref{eq:diag:central1} of interest are
 \begin{equation}
-    \label{eq:base-change:scheme-cover}
-    \begin{tikzcd}
-        \schemelscY \stack X \arrow[r, hook, "\schemei_{\stack Y}"] \arrow[d] & \schemeclsY \stack X \arrow[r, "\schemebarq_{\stack Y}"] \arrow[d] & \bar Γ \arrow[d] & Γ \arrow[l, hook', "\schemej"'] \arrow[d] \\
-        \lscY \stack X \arrow[r, hook, "i_{\stack Y}"]                        & \clsY \stack X \arrow[r, "\bar q_{\stack Y}"]                       & \bar{\stack X}   & \stack X \arrow[l, hook', "j"']
+    \label{eq:diag:scheme-cover1}
+    \begin{tikzcd}
+        Γ \arrow[r, hook, "j'"] \arrow[d] &
+        \bar Γ \arrow[d] &
+        \scls \stack X \arrow[l, "\bar p₂'"'] \arrow[d] &
+        \slsc \stack X \arrow[l, hook', "i_{\stack X}'"'] \arrow[d]\\
+        %
+        \stack X \arrow[r, hook, "j"] &
+        \bar{\stack X} &
+        \cls \stack X \arrow[l, "\bar p₂"'] &
+        \lsc \stack X \arrow[l, hook', "i_{\stack X}"']
     \end{tikzcd}
 \end{equation}
-We note that all vertical morphisms are smooth and the spaces in the top row are schemes.
-Let $\schemeh\colon X → Y$ be the $G$-equivariant morphism of schemes inducing $h$ on quotient stacks.
-Then the scheme $\schemeclsY \stack X$ is given by
-\[
-    \schemeclsY \stack X =
+Similarly, the interesting parts of diagram \eqref{eq:diag:central2} become
+\begin{equation}
+    \label{eq:diag:scheme-cover2}
+    \begin{tikzcd}
+        \slsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}'"] \arrow[d] &
+        \sclsY[\stack Y₂]{\stack X} \arrow[d] &
+        \sclsY[\stack Y₁]{\stack X} \arrow[l, "\schemecls f"'] \arrow[d] &
+        \slscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}'"'] \arrow[d]\\
+        %
+        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] &
+        \clsY[\stack Y₂]{\stack X} &
+        \clsY[\stack Y₁]{\stack X} \arrow[l, "\cls f"'] &
+        \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']
+    \end{tikzcd}
+\end{equation}
+In both diagrams all vertical morphisms are smooth and the spaces in the top row are schemes.
+Explicitly, if $h'\colon Y → X$ is a $G$-equivariant morphism of schemes inducing the structure map $\stack Y → \stack X$, then
+\[
+    \sclsY \stack X =
     \biggl\{
@@
 \begin{Lem}\label{lem:base-change:scheme-cover}
-    A stack $X/G$ is \goodstack\ if and only if for each morphism $Y/G → X/G$ the composition $(\schemei_{\stack Y})^* (\schemebarq_{\stack Y})^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
+    A stack $X/G$ \isgoodb\ if and only if the following two conditions hold:
+    \begin{enumerate}
+        \item The composition $(i_{\stack X}')^*(\bar p₂')^! j'_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
+        \item For each equivariant morphism $f'\colon Y₁ → Y₂$ of $G$-schemes the composition $(i_{\stack Y₁}')^*(\scls f)^!
+j'_{\stack Y₂,!}$ vanishes on $\catDModHolMon{\slsY[\stack Y₂]{\stack X}}{G×G}$.
+    \end{enumerate}
 \end{Lem}
@@
 \begin{proof}
-    This follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:base-change:scheme-cover} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and commutes with the other morphisms up to a shift.
+    This follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:diag:scheme-cover1} and \eqref{eq:diag:scheme-cover2} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and commutes with the other morphisms up to a shift.
 \end{proof}
@@
     \label{lem:base-change:cover}%
-    If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ are \goodstack, then $X/G$ is \goodstack.
+    If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ \aregoodb, then $X/G$ \isgoodb.
 \end{Lem}
@@
     Let $\stack U_i = U_i/G$ be the corresponding quotient stacks.
-    We first show that the stacks $\lscY{\stack U_i}$ form an open cover of $\lscY{\stack X}$\footnote{
+    We will again only show the second condition, the first being simpler.
+
+    Let us first show that for any $\stack Y → \stack X$ the stacks $\lscY{\stack U_i}$ form an open cover of $\lscY{\stack X}$\footnote{
         This is not completely obvious, since the $\bar{\stack U}_i$ do not necessarily form a cover of $\bar{\stack X}$.
@@
     }.
-    For this it suffices to show that the open subschemes $\schemeclsY \stack U_i$ cover $\schemeclsY \stack X$.
-    Let $(g₁, y, g₂)$ be a point of $\schemeclsY \stack X$.
+    For this it suffices to show that the open subschemes $\sclsY \stack U_i$ cover $\sclsY \stack X$.
+    Let $(g₁, y, g₂)$ be a point of $\sclsY \stack X$.
     Then there exists some $U_i$ with $h'(y) ∈ U_i$.
     But then $g₁h'(y)$ is also in $U_i$ and hence $(h'(y), g₂, g₁h'(y)) ∈ \bar{\stack U}_i$.
-    Thus $(g₁, y, g₂)$ is in $\schemeclsY \stack U_i$.
-
-    It now suffices to show that the restrictions of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_! \sheaf F$ to $\lscY{\stack U_i}$ vanish for every $\sheaf F ∈ \catDMod{\stack X}$.
-    But this follows from the diagram~\eqref{eq:lem:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the \goodness\ of $\stack U_i$.
+    Thus $(g₁, y, g₂)$ is in $\sclsY \stack U_i$.
+
+    It now suffices to show that the restrictions of $i_{\stack Y₁}^*\cls{f}^!j_{\stack Y₂,!} \sheaf F$ to $\lscY[\stack Y₁]{\stack U_i}$ vanish for every $\sheaf F ∈ \catDModHol{\lsY[\stack Y₂]{\stack X}}$.
+    But this follows from the diagram~\eqref{eq:lem:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the assumption on $\stack U_i$.
 \end{proof}
+
+-------------
 

### 2017-05-25 paper.tex
Finish the stuff about good stacks.

@@
 
-It is useful to consider only partial compactifications.
-For this let $V$ be a $G$-stable subvariety of $\bar G$ containing $G$, and let $\barGammasub{V}$ be the closure of $Γ$ in $V × X × X$.
-We set
-\[
-    \bar{\stack X}_V = \rquot{\barGammasub{V}}{G×G}.
-\]
-Clearly, if $\left\{V_i\right\}$ is an open cover of $\bar G$ by $G$-stable subvarieties, then $\left\{\bar{\stack X}_{V_i}\right\}$ is an open cover of $\bar{\stack X}$.
-
 \subsection{\Goodstack\ stacks}
@@
 
--------------
-
-Let $\left\{V_i\right\}$ be a $G$-stable open cover of $\bar G$ and consider the corresponding open cover $\left\{\bar{\stack X}_{V_i}\right\}$ of $\stack X$.
-We obtain open covers $\left\{\cls_{V_i,\stack Y} \stack X\right\}$ and $\left\{\lsc_{V_i,\stack Y} \stack X\right\}$ of $\clsY{\stack X}$ and $\lscY{\stack X}$ respectively.
-We let $i_{V_i,\stack X}$, $\bar q_{V_i,\stack X}$ and $j_{V_i}$ be the corresponding maps, i.e.
-\[
-    \begin{tikzcd}
-        \cls_{V_i,\stack Y} \stack X \arrow[r, hook, "i_{V_i,\stack X}"] &
-        \lsc_{V_i,\stack Y} \stack X \arrow[r, "\bar q_{V_i,\stack X}"] &
-        \bar{\stack X}_{V_i} &
-        \stack X \arrow[l, hook', "j_{V_i}"'].
-    \end{tikzcd}
+Finally, it will be useful to consider only partial compactifications.
+That is, in the constructions of Section~\ref{sec:base-change:compactification}, instead of going all the way to $\bar G$ we only some subvariety of it.
+Thus let $H$ be a $G×G$-stable subvariety of $\bar G$ containing $G$, and let $^H\bar{Γ}$ be the closure of $Γ$ in $H × X × X$.
+We set
+\[
+    ^H\bar{\stack X} = \rquot{^H\bar{Γ}}{G×G}.
+\]
+Clearly, if $\left\{H_i\right\}$ is an open cover of $\bar G$ by $G×G$-stable subvarieties (each containing $G$), then $\left\{{}^{H_i}\bar{\stack X}\right\}$ is an open cover of $\bar{\stack X}$.
+
+Let us fix such an open cover.
+For any $\stack Y$ over $\stack X$ we obtain corresponding open covers $\left\{ {}^{H_i}\cls_{\stack Y} \stack X\right\}$ and $\left\{{}^{H_i}\lsc_{\stack Y} \stack X\right\}$ of $\clsY{\stack X}$ and $\lscY{\stack X}$ respectively.
+We get our usual diagrams for these partial compactifications:
+\[
+    \begin{tikzcd}
+        \stack X \arrow[r, hook, "{}^{H_i}j"] &
+        {}^{H_i}\bar{\stack X} &
+        {}^{H_i}\clsY[\stack X]{\stack X} \arrow[l, "{}^{H_i}p_{2}"'] &
+        {}^{H_i}\lscY[\stack X]{\stack X} \arrow[l, hook', "{}^{H_i}i_{\stack X}"']
+    \end{tikzcd}
+\]
+and
+\[
+    \begin{tikzcd}
+        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "{}^{H_i}j_{\stack Y₂}"] &
+        {}^{H_i}\clsY[\stack Y₂]{\stack X} &
+        {}^{H_i}\clsY[\stack Y₁]{\stack X} \arrow[l, "{}^{H_i}\cls f"'] &
+        {}^{H_i}\lscY[\stack Y₁]{\stack X}. \arrow[l, hook', "{}^{H_i}i_{\stack Y₁}"']
+    \end{tikzcd}.
 \]
@@
 \begin{Lem}\label{lem:base-change:cover-by-relative-compactifications}
-    With the above notation, the $\stack X$ is \goodstack\ if and only $i_{V_i,\stack Y}^* \bar q_{V_i,\stack Y}^!
-j_{V_i,!}$ vanishes on $\catDModHol{\stack X}$ for all $V_i$ and all $\stack Y → \stack X$.
+    Let $H_i$ be an open cover of $\bar G$ by $G×G$-stable subvarieties, each containing $G$.
+    Then $\stack X = X/G$ \isgoodb\ if and only if the following two conditions hold for each $i$:
+    \begin{enumerate}
+        \item The composition $({}^{H_i}i_{\stack X})^*({}^{H_i}\bar p₂)^! ({}^{H_i}j)_!$ vanishes on $\catDModHol{\stack X}$.
+        \item For each schematic morphism of $G$-quotient stacks $f\colon \stack Y₁ → \stack Y₂$ the composition $({}^{H_i}i_{\stack Y₁})^*({}^{H_i}\cls f)^!
+({}^{H_i}j_{\stack Y₂})_!$ vanishes on $\catDModHol{\lsY[\stack Y₂]{\stack X}}$.
+    \end{enumerate}
 \end{Lem}

### 2017-05-30 paper.tex
Fixed proof of the main theorem.

@@
 \newcommand\slscY[2][\stack Y]{L^c_{#1}#2}
+
+\newcommand\stabls[2]{L^{#1}#2}
+\newcommand\stabcls[2]{\overline{L}^{#1}#2}
+\newcommand\stablsc[2]{L^{#1,c}#2}
+\newcommand\stablsY[3][\stack Y]{L_{#1}^{#2}#3}
+\newcommand\stabclsY[3][\stack Y]{\overline{L}_{#1}^{#2}#3}
+\newcommand\stablscY[3][\stack Y]{L_{#1}^{#2,c}#3}
 
@@
 \maketitle
+
+[$p₂$ <-> $p₁$]
+[subvariety <-> subscheme]
+[$Y₁$ <-> $Y₂$]
+\dropprimes%
+[macros]
+[-advisor]
+[map in contraction principle]
 
@@
     Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
-    Then the stack $\stack X = X/G$ is good.
+    Then the stack $\stack X = X/G$ \isgoodb.
 \end{Thm}
 
-Together with Theorem~\ref{thm:good-is-good} this implies our main result, Theorem~\ref{thm:main}.
-
-\begin{Rem}
-    We only use the assumption that the action is locally linear to prove Lemma~\ref{lem:finitely_many_stabilizers}, i.e.~that $\Stab\stack X$ is locally finite.
-    Thus it would suffice to assume that $X$ can be covered by open subschemes for which Lemma~\ref{lem:finitely_many_stabilizers} holds.
-\end{Rem}
+Together with Lemma~\ref{lem:base-change-criterion} and Proposition~\ref{prop:good-is-good} this implies our main result, Theorem~\ref{thm:main}.
+Here by a \enquote{locally linear action} we mean that it is possible to cover $X$ by open $G$-stable subschemes $U_i$ such that each $U_i$ is $G$-equivariantly isomorphic to an open subscheme of some affine space $\as m$ with linear $G$-action.
+This assumption is actually stricter than needed, see Remark~\ref{rem:why_locally_linear} below.
 
@@
     Theorem~\ref{thm:torus:is-good} actually holds for $G$ the product of a torus and a finite Abelian group.
-    The argument is exactly the same.
+    The argument is exactly the same as in our case, but for the sake of keeping notational complexity down we will not present it here.
 \end{Rem}
@@
 The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
-Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodness\ for the partial compactification $\Gm^n \subseteq \as n$.
-To simplify notation, we drop the subscript $\as n$ from the notation and set $\bar{\stack X} = \bar{\stack X}_{\as n}$ and similarly for the various maps.
-
-We fix a quotient stack $\stack Y = Y/G$ and a morphism $h\colon \stack Y → \stack X$, induced by a $G$-equivariant morphism $\schemeh\colon Y → X$.
+Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodnessb\ for the partial compactification $\Gm^n \subseteq \as n$.
+To simplify notation, we drop the superscript $\as n$ from the notation and set $\bar{\stack X} = {}^{\as n}\bar{\stack X}$ and similarly for all other spaces and the various maps.
+In other words, from now on all compactifications will implicitly be only with respect to $G \subseteq \as n$ (rather than $G \subseteq (\ps 1)^n$).
+
+We fix a morphisms of $G$-quotient stacks $f\colon \stack Y₂ → \stack Y₁$ over $\stack X$, induced by a $G$-equivariant morphism of schemes $f'\colon Y₂ → Y₁$.
+Further let $h_i'\colon Y_i → X$ be the structure maps.
 According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working directly with the stacks, we can base change to schemes.
-We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the subscript $\stack Y$ and the primes from the maps.
-\dropprimes%
-Thus we are concerned with the diagram
-\[
-    \begin{tikzcd}
-        \schemelscY \stack X \arrow[r, hook, "\schemei"] &
-        \schemeclsY \stack X \arrow[r, "\schemebarq"] &
-        \bar Γ &
-        Γ \arrow[l, hook', "\schemej"'],
-    \end{tikzcd}
-\]
-where we have to show that $\schemei^* \schemebarq^! \schemej_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
-
-The general idea is to introduce a $\Gm$-action that contracts $\schemelscY \stack X$ onto $\schemeclsY \stack X$.
-In order to do so, we will cut the scheme
-\[
-    \schemeclsY \stack X =
+We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the primes and the \enquote{$\stack Y$} from the maps.
+The following diagram summarizes all the spaces and maps that we need to consider.
+\[
+    \begin{tikzcd}
+        Γ \arrow[d, hook, "j"] & & \slsY[\stack Y₁]{\stack X} \arrow[d, hook, "j₁"] & \\
+        \bar Γ & \scls{\stack X} \arrow[l, "\bar p₂"'] & \sclsY[\stack Y₁]{\stack X} \arrow[l, gray, "\scls{h₁}"'] & \sclsY[\stack Y₂]{\stack X} \arrow[l, "\scls{f}"'] \\
+        & \slsc{\stack X} \arrow[u, hook, "i"] &  & \slscY[\stack Y₂]{\stack X} \arrow[u, hook, "i₂"]
+    \end{tikzcd}
+\]
+We want to show that our usual push-pull operations vanish along the two zig-zags (for $G×G$-mododromic holonomic D-modules).
+To unify notation, let us set $Y₀ = X$ and $h_0 = \id[X]$
+
+The general idea is now to introduce $\Gm$-actions that contracts $\sclsY[\stack Y_i] \stack X$ onto $\slscY[\stack Y_i] \stack X$.
+In order to do so, we will cut the schemes
+\[
+    \sclsY[\stack Y_i] \stack X =
     \biggl\{
-        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ
+        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ
     \biggr\}
 \]
-into pieces according to the subgroups of $G$ that stabilize $\schemeh(y)$.
+into pieces according to the subgroups of $G$ that stabilize $h_i(y)$.
 For this let $\Stab\stack X$ be the set of all closed subgroups of $G$ that are stabilizers of points of $X$, i.e.
 \[
-    \Stab\stack X = \{ G_x : x ∈ X \}.
+    \Stab\stack X = \bigl\{ G_x : x ∈ X \bigr\}.
 \]
@@
 \begin{proof}
-    Since $X$ is affine, it can be embedded $G$-equivariantly into some $\as m$ with a linear $T$-action.
-    For $\as m/T$ the statement is easy to see.
+    Since $X$ is affine, it can be embedded $G$-equivariantly into some $\as m$ with a linear $G$-action.
+    For $\as m/G$ the statement is easy to see.
 \end{proof}
+
+\begin{Rem}\label{rem:why_locally_linear}
+    We only use the assumption that the action is locally linear to prove Lemma~\ref{lem:finitely_many_stabilizers}, i.e.~that $\Stab\stack X$ is locally finite.
+    Thus it would suffice to assume in Theorem~\ref{thm:torus:is-good} that $X$ can be covered by open subschemes for which Lemma~\ref{lem:finitely_many_stabilizers} holds.
+\end{Rem}
 
@@
 \[
-    \schemecls[S]_{\stack Y} \stack X =
+    \stabclsY[\stack Y_i]{S}{\stack X} =
     \biggl\{
-        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^S,\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S
+        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^S,\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S
     \biggr\}
     ⊆
-    \schemecls_{\stack Y} \stack X.
+    \sclsY[\stack Y_i] \stack X.
 \]
@@
     \label{lem:stabilizers_cover}%
-    The subspaces $\schemecls[S]_{\stack Y} \stack X$ for $S ∈ \Stab\stack X$ cover $\schemecls_{\stack Y}\stack X$.
+    For $i \in \{0,1,2\}$, the subspaces $\stabclsY[\stack Y_i]{S}{\stack X}$ for $S ∈ \Stab\stack X$ cover $\sclsY[\stack Y_i]{\stack X}$.
 \end{Lem}
@@
 \begin{proof}
-    Let $\schemelsY \stack X$ be the smooth cover of $\ls_{\stack Y}\stack X$.
     Consider the spaces
     \[
-        \schemelsY[S] \stack X =
+        \stablsY[\stack Y_i]{S}{\stack X} =
         \biggl\{
-            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × G : \schemeh(y) ∈ X^S,\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ Γ \text{ and } g₂ ∈ g₁S
+            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × G : h_i(y) ∈ X^S,\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ Γ \text{ and } g₂ ∈ g₁S
         \biggr\}
-        \subseteq \schemelsY \stack X.
-    \]
-    The closure of $\schemelsY[S] \stack X$ in $\schemeclsY \stack X$ is exactly $\schemeclsY[S] \stack X$.
-    It is easy to see that the subspaces $\schemelsY[S] \stack X$ for $S ∈ \Stab \stack X$ cover $\schemelsY[S] \stack X$.
+        \subseteq \slsY[\stack Y_i] \stack X.
+    \]
+    The closure of $\stablsY[\stack Y_i]{S}{\stack X}$ in $\sclsY[\stack Y_i] \stack X$ is exactly $\stabclsY[\stack Y_i]{S}{\stack X}$.
+    It is easy to see that the subspaces $\stablsY[\stack Y_i]{S}{\stack X}$ for $S ∈ \Stab \stack X$ cover $\slsY[\stack Y_i] \stack X$.
     Now the statement follows from the fact that the closure of a finite union is the union of the individual closures.
@@
 
-It will be useful to have a slight generalization of the schemes $\schemeclsY[S] \stack X$.
-Let $S₁ \subseteq S₂$ be two subgroups of $G$ contained in $\Stab\stack X$.
-We set
-\[
-    \schemeclsY[S₁,S₂] \stack X =
+The upshot of this is that we can check vanishing by restricting to all $\stabclsY[\stack Y_i]{S}{\stack X}$.
+However, since these spaces are closed we will need to make use of a Mayer--Vietoris argument.
+Thus we need to also consider intersections of these schemes.
+For this let $S₁ \subseteq S₂$ be two subgroups of $G$ contained in $\Stab\stack X$ and set
+\[
+    \stabclsY[\stack Y_i]{S₁,S₂} \stack X =
     \biggl\{
-        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
+        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
     \biggr\}.
 \]
-Clearly we have $\schemeclsY[S₁,S₂]{\stack X} \subseteq \schemecls[S₁]{\stack X}$ and $\schemeclsY[S] \stack X = \schemeclsY[S,S] \stack X$.
-
-Consider the Cartesian square of closed embeddings
-\[
-    \begin{tikzcd}
-        \schemelscY[S₁,S₂] \stack X \arrow[r, hook, "α_{S₁,S₂}^c"] \arrow[d, hook, "\schemei^{S₁,S₂}"] & \schemelscY\stack X \arrow[d, hook, "\schemei"]
-        \\
-        \schemeclsY[S₁,S₂] \stack X \arrow[r, hook, "α_{S₁,S₂}"]   & \schemeclsY\stack X
-    \end{tikzcd}
-\]
-
-\begin{Lem}\label{lem:key_for_stablizier}%
-    For any $S₁ ⊆ S₂$ in $\Stab\stack X$ and any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ we have
-    \[
-        \schemei^{S₁,S₂,*} α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F = 0.
-    \]
+Clearly we have $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \subseteq \stabclsY[\stack Y_i]{S₁}{\stack X}$ and $\stabclsY[\stack Y_i]{S}{\stack X} = \stabclsY[\stack Y_i]{S,S}{\stack X}$.
+Similarly, we set
+\[
+    \bar Γ^{S₁,S₂} = \bigl\{ (g,x,y) ∈ \bar Γ : x ∈ X^{S₂} \text{ and there exists $g' ∈ G$ such that $g ∈ g'S₁$}  \bigr\}.
+\]
+As in Lemma~\ref{lem:stabilizers_cover} one sees that the closed subschemes $\bar Γ^{S,S}$ cover $\bar Γ$.
+Denote the inclusions by
+\[
+    α_i^{S₁,S₂}\colon \stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \hookrightarrow \sclsY[\stack Y_i]{\stack X}
+    \qquad\text{and}\qquad
+    α_{-1}^{S₁,S₂}\colon \bar Γ^{S₁,S₂} \hookrightarrow \bar Γ.
+\]
+We are now ready to formulate the main technical lemma of this section.
+It will allow us to cut up our spaces into pieces on which we have control over the sheaves of interest.
+
+\begin{Lem}\label{lem:torus:key}
+    Fix any $S₁ ⊆ S₂$ in $\Stab\stack X$ and a component $H$ of $\bar G \setminus G$ (hence $H$ is a hyperplane of $\as n$).
+    Write $Z_i$ for the closed subschemes of $\slscY[\stack Y_i]\stack X$ with $g₂ ∈ H$, and similarly $Z_{-1} = \bar Γ ∩ H × X × X$.
+    Consider the Cartesian diagrams
+    \begin{equation}\label{eq:lem:torus:key:cartesian}
+        \begin{tikzcd}
+            Z₂ \arrow[r, hook, "i₂^H"] \arrow[d, "\scls f^H"] & \sclsY[\stack Y₂]{\stack X} \arrow[d, "\scls f"] \\
+            Z₁ \arrow[r, hook, "i₂^H"] & \sclsY[\stack Y₁]{\stack X}
+        \end{tikzcd}
+        \qquad\text{and}\qquad
+        \begin{tikzcd}
+            Z₀ \arrow[r, hook, "i₀^H"] \arrow[d, "\bar p₂^H"] & \scls{\stack X} \arrow[d, "\bar p₂"] \\
+            Z_{-1} \arrow[r, hook, "i_{-1}^H"] & \bar Γ
+        \end{tikzcd}. 
+    \end{equation}
+    Then the canonical morphisms [Write up the morphisms?]
+    \[
+        i^{H,*}_0 α_{0,*}^{S₁,S₂}α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F
+        →
+        \bar p₂^{H,!} i^{H,*}_{-1} α_{-1,*}^{S₁,S₂}α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
+    \]
+    and
+    \[
+        i^{H,*}_2 α_{2,*}^{S₁,S₂}α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G
+        →
+        {\scls f}^{H,!} i^{H,*}_1 α_{1,*}^{S₁,S₂}α₁^{S₁,S₂,!} j_{1,!} \sheaf G.
+    \]
+    are isomorphisms for any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ and $\sheaf G ∈ \catDModHolMon{\slsY[\stack Y₁]{\stack X}}{G×G}$.
 \end{Lem}
 
-\begin{proof}
-    The scheme $\schemelsc[S₁,S₂] \stack X$ is given by
+Before proving the lemma, let us first finish the proof of Theorem~\ref{thm:torus:is-good}, assuming the Lemma.
+
+\begin{proof}[Proof of Theorem~\ref{thm:torus:is-good}]
+    We have to prove that 
+    \[
+        i₀^* \bar p₂^! j_{!} \sheaf F = 0
+        \qquad\text{and}\qquad
+        i₂^{*} {\scls f}^! j_{1,!} \sheaf G = 0
+    \]
+    for any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ and $\sheaf G ∈ \catDModHolMon{\slsY[\stack Y₁]{\stack X}}{G×G}$.
+    Let $H$ be a component of $\bar G \setminus G$, i.e.~one of the coordinate hyperplanes of $\as n$.
+    It suffices to prove that 
+    \[
+        i₀^{H,*} \bar p₂^! j_{!} \sheaf F = 0
+        \qquad\text{and}\qquad
+        i₂^{H,*} {\scls f}^! j_{1,!} \sheaf G = 0
+    \]
+    for any such $H$.
+    We will prove the second of these statements.
+    The first follows in exactly the same way, using $\bar Γ$ and $\scls\stack X$ instead of $\sclsY[\stack Y₁]{\stack X}$ and $\sclsY[\stack Y₂]{\stack X}$.
+    The idea is to compare the above sheaves each with a sheaf that is evidently zero by cutting the space into pieces and using Mayer--Vietoris triangles.
+
+    By Lemma~\ref{lem:stabilizers_cover} the closed subschemes $\stabclsY[\stack Y_i]{S}\stack X$ for $S ∈ \Stab \stack X$ cover $\sclsY[\stack Y_i]{\stack X}$.
+    If $S₁,\, S₂ ∈ \Stab\stack X$, then
+    \[
+        \stabclsY[\stack Y_i]{S₁}{\stack X} ∩ \stabclsY[\stack Y_i]{S₂}{\stack X} =
+        \stabclsY[\stack Y_i]{S₁∩S₂,\, S₁S₂}\stack X.
+    \]
+    Thus, using the notation of diagram~\eqref{eq:lem:torus:key:cartesian}, we can use Mayer--Vietoris triangles to write $i₂^{H,*} {\scls f}^!
+j_{1,!} \sheaf G$ as an iterated extension of (direct sums of) sheaves of the form
+    \[
+        i^{H,*}_2 α_{2,*}^{S₁,S₂}α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G, \qquad S₁ ⊆ S₂ ∈ \Stab \stack X.
+    \]
+    Similarly we can write ${\scls f}^{H,!} i^{H,*}_1 j_{1,!}$ as an iterated extension of
+    \[
+        {\scls f}^{H,!} i^{H,*}_1 α_{1,*}^{S₁,S₂}α₁^{S₁,S₂,!} j_{1,!} \sheaf G, \qquad S₁ ⊆ S₂ ∈ \Stab \stack X.
+    \]
+    We have canonical maps between each of the sheaves in these triangles.
+    By Lemma~\ref{lem:torus:key} each of them, except possibly between the original sheaves, are isomorphisms.
+    But then also the canonical map
+    \[
+        i₂^{H,*} {\scls f}^! j_{1,!} \sheaf G → {\scls f}^{H,!} i^{H,*}_1 j_{1,!} \sheaf G
+    \]
+    is an isomorphism.
+    Finally, ${\scls f}^{H,!} i^{H,*}_1 j_{1,!} \sheaf G$ mush vanish, as $i^{H,*}$ can be factored through the $*$-restriction to $\slscY[\stack Y₁]{\stack X}$.
+\end{proof}
+
+\begin{proof}[Proof of Lemma~\ref{lem:torus:key}]
+    The schemes $\stablscY[\stack Y_i]{S₁,S₂}{\stack X} = \slscY[\stack Y_i]{\stack X} ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ are given by
     \[
         \biggl\{
-            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁(\bar S₁ \setminus S₁)
+            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁(\bar S₁ \setminus S₁)
         \biggr\}.
     \]
-    If $S₁ = \bar S₁$ the statement is trivially true.
-    Otherwise the scheme $\bar S₁ \setminus S₁$ is the union of hyperplanes $H_i$ of $\bar S₁$.
-    It suffices to prove the statement when further restricting to
-    \[
+    Set $H' = H ∩ \bar S₁$ and $Z_i' = Z_i ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$Z_{-1}' = Z_{-1} ∩ \bar Γ^{S₁,S₂}$).
+    These schemes can be described as
+    \[
+        Z_i'
         \biggl\{
-            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H_i
+            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H'
         \biggr\}.
     \]
-    for all $i$.
-    Let $H$ be one such hyperplane.
-    We will assume that $H$ is contained in the closure of the connected component of $1 ∈ S₁$.
-    The proof for $H$ in a different component is the same, up to a shift by an element of $G$.
-    Let $\schemei_H$ be the inclusion of
-    \[
-        Z =
-        \biggl\{
-            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \schemeh(y) ∈ X^{S₂},\, \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H
-        \biggr\}
-    \]
-    into $\schemeclsY[S₁,S₂] \stack X$.
-    We want to compute
-    \[
-        (\schemei_H)^{*} α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F.
-    \]
-    We will do so be introducing a contractive $\Gm$-action on $\bar Γ$ and $\schemelsY[S₁,S₂]\stack X$ such that the morphism
-    \[
-        \schemebarq ∘ α_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ
-    \]
-    is $\Gm$-equivariant.
+    and similarly for $Z_{-1}'$.
+    If $H' = \emptyset$ then the $Z_i'$ are empty and the statements of the lemma are trivially true.
+    Thus assume that $H'$ is not empty.
+    Let $i_i^{H'}$ be the inclusion of $Z_i'$ into $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$\bar Γ^{S₁,S₂}$).
+    We have to show that the canonical maps
+    \[
+        i^{H',*}_0 α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F
+        →
+        \bar p₂^{H',!} i^{H',*}_{-1} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
+    \]
+    and
+    \[
+        i^{H',*}_2 α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G
+        →
+        {\scls f}^{H',!} i^{H',*}_1 α₁^{S₁,S₂,!} j_{1,!} \sheaf G.
+    \]
+    are isomorphisms.
+
+    We will do so by using the Contraction Principle of Theorem~\ref{thm:pre:contraction_principle}.
+    For this we will introducing a contractive $\Gm$-action on $\bar Γ$ and all $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ such that the morphisms
+    \begin{equation}
+        \label{eq:torus:middle_row}
+        \begin{tikzcd}
+            \bar Γ^{S₁,S₂} &
+            \stabcls{S₁,S₂}{\stack X} \arrow[l, "\bar p₂"'] &
+            \stabclsY[\stack Y₁]{S₁,S₂}{\stack X} \arrow[l, "\scls{h₁}"'] &
+            \stabclsY[\stack Y₂]{S₁,S₂}{\stack X} \arrow[l, "\scls{f}"']
+        \end{tikzcd}
+    \end{equation}
+    are $\Gm$-equivariant (where we abuse notation to denote the restrictions of the morphisms with the same name).
 
@@
     This gives a corresponding decomposition of the monoid $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
-    Let $H' = \bar G₁ H$.
-    We note that $G ∩ H' = \emptyset$.
-
-    We chose an action $μ$ of $\Gm$ on $\bar S₁$ that contracts $\bar S₁$ onto $H$.
-    This induces an action of $\Gm$ on $\bar G = \bar G₁ \bar S₁$ by $u \cdot ts = tμ(u,s)$, contracting $\bar G$ onto $H'$.
-    Further we obtain an action of $\Gm$ on $\bar Γ$ that keeps the first $X$ coordinate fixed.
-    By construction this action contracts $\bar Γ$ onto a closed subvariety of $\bar Γ \setminus Γ$.
-    We will denote this subvariety by $Z₁$ and the contraction morphism $π₁\colon \bar Γ → Z₁$ by $π₁$.
-
-    We can also lift the action to $\schemeclsY[S₁,S₂]\stack X$ where it contracts onto $Z$.
-    We will denote the corresponding contraction morphism by $π\colon \schemeclsY[S₁,S₂]\stack X → Z$.
-    The morphism $\schemebarq ∘ α_{S₁,S₂}\colon \schemeclsY[S₁,S₂]\stack X → \bar Γ$ is equivariant with respect to these $\Gm$-actions and on its image the action keeps the second $X$-coordinate fixed.
-
-    We note that the D-modules $\schemej_!\sheaf F$ and $α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F$ are monodromic with respect to these $\Gm$-actions.
-    Thus the contraction principle Theorem~\ref{thm:pre:contraction_principle} implies that
-    \[
-        (\schemei_H)^* α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F = π_* α_{S₁,S₂}^! \schemebarq^! \schemej_! \sheaf F.
-    \]
-    By construction, the square
-    \[
-        \begin{tikzcd}
-            \schemecls[S₁,S₂] \stack X \arrow[r, "π"] \arrow[d, "\schemebarq ∘ α_{S₁,S₂}"] & Z \arrow[d] \\
-            \bar Γ \arrow[r, "π₁"] & Z₁
-        \end{tikzcd}
-    \]
-    is Cartesian.
-    Let us call the right vertical map $f$.
-    Base change yields
-    \[
-        π_* α_{S₁,S₂}^!\schemebarq^!\schemej_! \sheaf F =
-        f^!π_{1,*} \schemej_! \sheaf F.
-    \]
-    Finally, let $i_{Z₁}\colon Z₁ \hookrightarrow \bar Γ$ be the inclusion.
-    Applying the contraction principle again we obtain
-    \[
-        f^!π_{1,*} \schemej_! \sheaf F =
-        f^!i_{Z₁}^* \schemej_! \sheaf F =
-        0.
-        \qedhere
-    \]
+    Chose an action $μ$ of $\Gm$ on the identity component of $\bar S₁$ that contracts $\bar S₁$ onto $H'$ .
+    This induces an action of $\Gm$ on $\bar G = \bar G₁ \bar S₁$ by $u \cdot ts = tμ(u,s)$, contracting $\bar G$ to (a closed subset of) $H$.
+
+    In turn this action induces contractive actions on $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ and $\bar Γ^{S₁,S₂}$.
+    We write 
+    \[
+        π_i\colon \stabclsY[\stack Y_i]{S₁,S₂}{\stack X} → Z_i'
+        \qquad\text{and}\qquad
+        π_{-1}\colon \bar Γ^{S₁,S₂} → Z_{-1}'
+    \]
+    for the corresponding contraction morphisms.
+
+    We note that all D-modules are monodromic with respect to these $\Gm$-actions.
+    Thus we can apply the contraction principle and base change to obtain the canonical isomorphisms
+    \[
+        i^{H',*}_0 α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F =
+        π_{0,*} \bar p₂^! α_{-1}^{S₁,S₂,!} j_{!} \sheaf F =
+        \bar p₂^{H',!} π_{-1,*} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F =
+        \bar p₂^{H',!} i^{H',*}_{-1} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
+    \]
+    and
+    \[
+        i^{H',*}_2 α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G = 
+        π_{2,*} {\scls f}^! α₁^{S₁,S₂,!} j_{1,!} \sheaf G = 
+        {\scls f}^{H',!} π_{1,*} α₁^{S₁,S₂,!} j_{1,!} \sheaf G = 
+        {\scls f}^{H',!} i^{H',*}_1 α₁^{S₁,S₂,!} j_{1,!} \sheaf G
+    \]
+    as required.
 \end{proof}
 
-\begin{proof}[Proof of Theorem~\ref{thm:torus:is-good}]
-    By Lemma~\ref{lem:stabilizers_cover} the closed subschemes $\schemeclsY[S]\stack X$ for $S ∈ \Stab \stack X$ cover $\schemeclsY\stack X$.
-    If $S₁,\, S₂ ∈ \Stab\stack X$, then
-    \[
-        \schemeclsY[S₁]\stack X ∩ \schemeclsY[S₂]\stack X =
-        \schemeclsY[S₁∩S₂,\, S₁S₂].
-    \]
-    Thus the theorem follows from an iterated Mayer-Vietoris argument using Lemma~\ref{lem:key_for_stablizier}.
-\end{proof}
-
 \printbibliography

### 2017-05-30 paper.tex
Fixes

@@
 
-\newcommand\schemels[2][]{L^{#1}#2}
-\newcommand\schemelsY[2][]{\schemels[#1]{_{\stack Y}#2}}
-\newcommand\schemecls[2][]{\overline{L}^{#1}#2}
-\newcommand\schemeclsY[2][]{\schemecls[#1]{_{\stack Y}#2}}
-\newcommand\schemelsc[2][]{L^{\if\relax\detokenize{#1}\relax\else#1,\fi c} #2}
-\newcommand\schemelscY[2][]{\schemelsc[#1]{_{\stack Y}#2}}
-
-\newcommand\schemei{i'}
-\newcommand\schemej{j'}
-\newcommand\schemeq{q'}
-\newcommand\schemebarq{\bar{q}'}
-\newcommand\dropprimes{%
-    \renewcommand\schemei{i}%
-    \renewcommand\schemej{j}%
-    \renewcommand\schemeq{q}%
-    \renewcommand\schemebarq{\bar{q}}%
-}
-\newcommand\schemeh{h'}
-
 \newcommand\Stab{\operatorname{Stab}}
 
-\newcommand\goodstack{XXXgoodXXX}
-\newcommand\Goodstack{XXXGoodXXX}
 \newcommand\goodness{property \textbf{(!)}}
@@
 [$Y₁$ <-> $Y₂$]
-\dropprimes%
 [macros]
@@
 
-\subsection{\Goodstack\ stacks}
+\subsection{The !-base-change property}
 
@@
 In particular we will want to reduce to computations on a schematic cover.
-On such a cover we will use primes to indicate maps on schemes and will use $\schemels{}$ instead of $\ls{}$ for the covers of the loop spaces.
+On such a cover we will use primes to indicate maps on schemes and will use $\sls{}$ instead of $\ls{}$ for the covers of the loop spaces.
 If we start with the cover $\bar Γ → \bar{\stack X}$, the pullbacks to the part of diagram \eqref{eq:diag:central1} of interest are
@@
         \sclsY[\stack Y₂]{\stack X} \arrow[d] &
-        \sclsY[\stack Y₁]{\stack X} \arrow[l, "\schemecls f"'] \arrow[d] &
+        \sclsY[\stack Y₁]{\stack X} \arrow[l, "\scls f"'] \arrow[d] &
         \slscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}'"'] \arrow[d]\\
@@
     \biggl\{
-        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, \schemeh(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ
+        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, h'(y),\, g₁h'(y)\bigr) ∈ \bar Γ
     \biggr\}.
@@
     \biggl\{
-        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁\schemeh(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
+        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
     \biggr\}.
@@
     \[
-        Z_i'
+        Z_i' =
         \biggl\{

### 2017-05-30 paper.tex
Order of Y_i.

@@
 [subvariety <-> subscheme]
-[$Y₁$ <-> $Y₂$]
 [macros]
@@
 where the fiber product is taken over the maps $\stack Y → \stack X \xrightarrow{Δ} \stack X × \stack X$ and $Δ$.
-Further if $f\colon \stack Y₁ → \stack Y₂$ is a morphism of stacks over $\stack X$ we write $\ls f$ for the induced morphism $\lsY[\stack Y₁]{\stack X} → \lsY[\stack Y₂]{\stack X}$.
+Further if $f\colon \stack Y₂ → \stack Y₁$ is a morphism of stacks over $\stack X$ we write $\ls f$ for the induced morphism $\lsY[\stack Y₂]{\stack X} → \lsY[\stack Y₁]{\stack X}$.
 
@@
             i.e.~the canonical morphism $p_{1,!}p₂^! → Δ^!Δ_!$ is an isomorphism on holonomic D-modules.
-        \item For any schematic morphism $f\colon \stack Y₁ = Y₁/G → \stack Y₂ = Y₂/G$ of $G$-quotient stacks over $\stack X$, $!$-base-change holds along the Cartesian diagram
+        \item For any schematic morphism $f\colon \stack Y₂ = Y₂/G → \stack Y₁ = Y₁/G$ of $G$-quotient stacks over $\stack X$, $!$-base-change holds along the Cartesian diagram
             \[
@@
     We note that $\stack G_{m+1} = \stack G_m ×_{\stack X × \stack X} \stack X$ and similarly for $\stack G_n$.
-    Thus setting $\stack Y₁ = \stack G_n$ and $\stack Y₂ = \stack G_m$ in the definition of \goodness, we see that all the required base changes holds.
+    Thus setting $\stack Y₂ = \stack G_n$ and $\stack Y₁ = \stack G_m$ in the definition of \goodness, we see that all the required base changes holds.
 \end{proof}
@@
 \end{equation}
-For the second let $\stack Y₁ → \stack Y₂$ be a morphism of stacks over $\stack X$:
+For the second let $\stack Y₂ → \stack Y₁$ be a morphism of stacks over $\stack X$:
 \begin{equation}\label{eq:diag:central2}
     \begin{tikzcd}
-        \lsY[\stack Y₁]{\stack X} \arrow[r, "j_{\stack Y₁}", hook] \arrow[d, "\ls f"] & \clsY[\stack Y₁]{\stack X} \arrow[d, "{\cls f}"] & \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']  \arrow[d] \\
-        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] & \clsY[\stack Y₂]{\stack X} & \lscY[\stack Y₂]{\stack X} \arrow[l, hook']
+        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] \arrow[d, "\ls f"] & \clsY[\stack Y₂]{\stack X} \arrow[d, "{\cls f}"] & \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']  \arrow[d] \\
+        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}"] & \clsY[\stack Y₁]{\stack X} & \lscY[\stack Y₁]{\stack X} \arrow[l, hook']
     \end{tikzcd}
@@
         \item $i_{\stack X}^* \bar p₂^! j_!$ vanishes on $\catDModHol{\stack X}$.
-        \item For any schematic morphism $f\colon \stack Y₁ → \stack Y₂$ of $G$-quotient stacks over $\stack X$ the composition $i_{\stack Y₁}^* (\bar{\ls f})^!
-j_{\stack Y₂,!}$ vanishes on $\catDModHol{\lsY[\stack Y₂]{\stack X}}$.
+        \item For any schematic morphism $f\colon \stack Y₂ → \stack Y₁$ of $G$-quotient stacks over $\stack X$ the composition $i_{\stack Y₂}^* (\bar{\ls f})^!
+j_{\stack Y₁,!}$ vanishes on $\catDModHol{\lsY[\stack Y₁]{\stack X}}$.
     \end{enumerate}
@@
     We will only show the second condition of Definition~\ref{def:good'}, the first one is similar.
-    Thus let $f\colon \stack Y₁ → \stack Y₂$ be a map of quotient stacks over $\stack U$ (and hence also over $U$).
+    Thus let $f\colon \stack Y₂ → \stack Y₁$ be a map of quotient stacks over $\stack U$ (and hence also over $U$).
     We note that since $\stack U$ is an open subset we have isomorphisms $\lsY[\stack Y_i]{\stack U} \cong \stack Y_i \XXtimes \stack U$.
@@
         \begin{tikzcd}
-            \lsY[\stack Y₂]{\stack U} \arrow[r, hook, "j_{\stack Y₂}^{\stack U}"] \arrow[d, hook, "α"] &
-            \clsY[\stack Y₂]{\stack U} \arrow[d, hook, "β"] &
-            \clsY[\stack Y₁]{\stack U} \arrow[l, "{\cls f}^{\stack U}"'] \arrow[d, hook, "γ"] &
-            \lscY[\stack Y₁]{\stack U} \arrow[l, hook', "i^{\stack U}_{\stack Y₁}"'] \arrow[d, hook, "δ"] \\
+            \lsY[\stack Y₁]{\stack U} \arrow[r, hook, "j_{\stack Y₁}^{\stack U}"] \arrow[d, hook, "α"] &
+            \clsY[\stack Y₁]{\stack U} \arrow[d, hook, "β"] &
+            \clsY[\stack Y₂]{\stack U} \arrow[l, "{\cls f}^{\stack U}"'] \arrow[d, hook, "γ"] &
+            \lscY[\stack Y₂]{\stack U} \arrow[l, hook', "i^{\stack U}_{\stack Y₂}"'] \arrow[d, hook, "δ"] \\
             %
-            \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}^{\stack X}"] &
-            \clsY[\stack Y₂]{\stack X} &
-            \clsY[\stack Y₁]{\stack X} \arrow[l, "{\cls f}^{\stack X}"'] &
-            \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i^{\stack X}_{\stack Y₁}"']
+            \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}^{\stack X}"] &
+            \clsY[\stack Y₁]{\stack X} &
+            \clsY[\stack Y₂]{\stack X} \arrow[l, "{\cls f}^{\stack X}"'] &
+            \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i^{\stack X}_{\stack Y₂}"']
         \end{tikzcd}
@@
     \begin{equation*}
-        i^{\stack U,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack U} =
-        i^{\stack U,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack U} α^* α_*=
-        δ^* i^{\stack X,*}_{\stack Y₁} {\cls f}^{\stack U,!} j_{\stack Y₂,!}^{\stack X} α_*=
+        i^{\stack U,*}_{\stack Y₂} {\cls f}^{\stack U,!} j_{\stack Y₁,!}^{\stack U} =
+        i^{\stack U,*}_{\stack Y₂} {\cls f}^{\stack U,!} j_{\stack Y₁,!}^{\stack U} α^* α_*=
+        δ^* i^{\stack X,*}_{\stack Y₂} {\cls f}^{\stack U,!} j_{\stack Y₁,!}^{\stack X} α_*=
         0.
@@
     \begin{tikzcd}
-        \slsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}'"] \arrow[d] &
-        \sclsY[\stack Y₂]{\stack X} \arrow[d] &
-        \sclsY[\stack Y₁]{\stack X} \arrow[l, "\scls f"'] \arrow[d] &
-        \slscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}'"'] \arrow[d]\\
+        \slsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}'"] \arrow[d] &
+        \sclsY[\stack Y₁]{\stack X} \arrow[d] &
+        \sclsY[\stack Y₂]{\stack X} \arrow[l, "\scls f"'] \arrow[d] &
+        \slscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₂}'"'] \arrow[d]\\
         %
-        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] &
-        \clsY[\stack Y₂]{\stack X} &
-        \clsY[\stack Y₁]{\stack X} \arrow[l, "\cls f"'] &
-        \lscY[\stack Y₁]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']
+        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}"] &
+        \clsY[\stack Y₁]{\stack X} &
+        \clsY[\stack Y₂]{\stack X} \arrow[l, "\cls f"'] &
+        \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₂}"']
     \end{tikzcd}
@@
         \item The composition $(i_{\stack X}')^*(\bar p₂')^! j'_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
-        \item For each equivariant morphism $f'\colon Y₁ → Y₂$ of $G$-schemes the composition $(i_{\stack Y₁}')^*(\scls f)^!
-j'_{\stack Y₂,!}$ vanishes on $\catDModHolMon{\slsY[\stack Y₂]{\stack X}}{G×G}$.
+        \item For each equivariant morphism $f'\colon Y₂ → Y₁$ of $G$-schemes the composition $(i_{\stack Y₂}')^*(\scls f)^!
+j'_{\stack Y₁,!}$ vanishes on $\catDModHolMon{\slsY[\stack Y₁]{\stack X}}{G×G}$.
     \end{enumerate}
@@
 
-    It now suffices to show that the restrictions of $i_{\stack Y₁}^*\cls{f}^!j_{\stack Y₂,!} \sheaf F$ to $\lscY[\stack Y₁]{\stack U_i}$ vanish for every $\sheaf F ∈ \catDModHol{\lsY[\stack Y₂]{\stack X}}$.
+    It now suffices to show that the restrictions of $i_{\stack Y₂}^*\cls{f}^!j_{\stack Y₁,!} \sheaf F$ to $\lscY[\stack Y₂]{\stack U_i}$ vanish for every $\sheaf F ∈ \catDModHol{\lsY[\stack Y₁]{\stack X}}$.
     But this follows from the diagram~\eqref{eq:lem:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the assumption on $\stack U_i$.
@@
     \begin{tikzcd}
-        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "{}^{H_i}j_{\stack Y₂}"] &
-        {}^{H_i}\clsY[\stack Y₂]{\stack X} &
-        {}^{H_i}\clsY[\stack Y₁]{\stack X} \arrow[l, "{}^{H_i}\cls f"'] &
-        {}^{H_i}\lscY[\stack Y₁]{\stack X}. \arrow[l, hook', "{}^{H_i}i_{\stack Y₁}"']
+        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "{}^{H_i}j_{\stack Y₁}"] &
+        {}^{H_i}\clsY[\stack Y₁]{\stack X} &
+        {}^{H_i}\clsY[\stack Y₂]{\stack X} \arrow[l, "{}^{H_i}\cls f"'] &
+        {}^{H_i}\lscY[\stack Y₂]{\stack X}. \arrow[l, hook', "{}^{H_i}i_{\stack Y₂}"']
     \end{tikzcd}.
@@
         \item The composition $({}^{H_i}i_{\stack X})^*({}^{H_i}\bar p₂)^! ({}^{H_i}j)_!$ vanishes on $\catDModHol{\stack X}$.
-        \item For each schematic morphism of $G$-quotient stacks $f\colon \stack Y₁ → \stack Y₂$ the composition $({}^{H_i}i_{\stack Y₁})^*({}^{H_i}\cls f)^!
-({}^{H_i}j_{\stack Y₂})_!$ vanishes on $\catDModHol{\lsY[\stack Y₂]{\stack X}}$.
+        \item For each schematic morphism of $G$-quotient stacks $f\colon \stack Y₂ → \stack Y₁$ the composition $({}^{H_i}i_{\stack Y₂})^*({}^{H_i}\cls f)^!
+({}^{H_i}j_{\stack Y₁})_!$ vanishes on $\catDModHol{\lsY[\stack Y₁]{\stack X}}$.
     \end{enumerate}

### 2017-05-30 paper.tex
p₁ <-> p₂

@@
 
-[$p₂$ <-> $p₁$]
 [subvariety <-> subscheme]
@@
     \begin{tikzcd}
-        \ls \stack X \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
+        \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
         \stack X \arrow[r, "Δ"] & \stack X × \stack X
@@
     \GammadR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
-    \GammadR(\stack X, p_{2,!}p₁^! k_{\stack X}).
+    \GammadR(\stack X, p_{1,!}p₂^! k_{\stack X}).
 \end{equation}
@@
 \begin{equation}\label{eq:intro:central_cone}
-    p_{2,!}p₁^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
+    p_{1,!}p₂^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
 \end{equation}
@@
         \cong
-        \opalg{\GammadR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)},
-    \]
-    where the algebra structure on $\GammadR\bigl(X/G,\,p_{2,!} p₁^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
+        \opalg{\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)},
+    \]
+    where the algebra structure on $\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
 \end{Thm}
@@
     \begin{tikzcd}
-        \ls{\stack X} \arrow[r, "p₁"] \arrow[d, "p₂"] & \stack X \arrow[d, "Δ"] \\
+        \ls{\stack X} \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
         \stack X \arrow[r, "Δ"] & \stack X × \stack X
@@
 Let us assume for the moment that $Δ$ (and hence $p_i$) is proper.
-Then $Δ_* = Δ_!$ and $p_{2,*} = p_{2,!}$ and by Section~\ref{sec:monads} we have an isomorphism of monads
+Then $Δ_* = Δ_!$ and $p_{1,*} = p_{1,!}$ and by Section~\ref{sec:monads} we have an isomorphism of monads
 \begin{equation}
     \label{eq:central_iso}
-    p_{2,!} p₁^! → Δ^!Δ_!,
+    p_{1,!} p₂^! → Δ^!Δ_!,
 \end{equation}
@@
 \[
-    \GammadR\bigl(\stack X,\, p_{2,!} p₁^! k_{\stack X}\bigr)
+    \GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)
     →
@@
 Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
-Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{2,!} p₁^!$.
+Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{1,!} p₂^!$.
 We would like to apply Lemma~\ref{lem:pre:groupoid_monad_hol} to construct a monad in special cases.
@@
     \[
-        \HCoh(\catDMod{\B G}) = \opalg{\GammadR\bigl(\B G,\, p_{2,!} p₁^! k_{\B G}\bigr)}.
+        \HCoh(\catDMod{\B G}) = \opalg{\GammadR\bigl(\B G,\, p_{1,!} p₂^! k_{\B G}\bigr)}.
     \]
@@
     \[
-        \GammadR\bigl(\B G,\, p_{2,!} p₁^! k_{\stack X}\bigr) \cong
+        \GammadR\bigl(\B G,\, p_{1,!} p₂^! k_{\stack X}\bigr) \cong
         \GammadR(G, k_G)^\dual \otimes \GammadR(\B G, k_{\B G}).

### 2017-05-30 paper.tex
More small changes.

@@
 
-[subvariety <-> subscheme]
 [macros]
-[-advisor]
-[map in contraction principle]
 
@@
 \subsection*{Acknowledgments}
-I would like to thank my advisor, David Nadler, for the original motivation for this project and many discussions concerning it.
+I would like to thank David Nadler for the original motivation for this project and many discussions concerning it.
 
@@
     Let $i\colon X^0 \hookrightarrow X$ be the closed subscheme of $\Gm$-fixed points and let $π\colon X → X^0$ be the contraction morphism induced by the $\Gm$-equivariant morphism $\as 1 → \{0\}$.
-    Then there is an isomorphism of functors
-    \[
-        i^* \cong π_* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}.
+    Then there is a canonical isomorphism of functors
+    \[
+        π_* \cong i^* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}
+    \]
+    given by adjunction
+    \[
+        π_* → π_* i_* i^* = (π ∘ i)_* i^* = i^*.
     \]
@@
 Finally, it will be useful to consider only partial compactifications.
-That is, in the constructions of Section~\ref{sec:base-change:compactification}, instead of going all the way to $\bar G$ we only some subvariety of it.
+That is, in the constructions of Section~\ref{sec:base-change:compactification}, instead of going all the way to $\bar G$ we only use some subvariety of it.
 Thus let $H$ be a $G×G$-stable subvariety of $\bar G$ containing $G$, and let $^H\bar{Γ}$ be the closure of $Γ$ in $H × X × X$.
@@
 
-    We will do so by using the Contraction Principle of Theorem~\ref{thm:pre:contraction_principle}.
+    We will do so by using the contraction principle of Theorem~\ref{thm:pre:contraction_principle}.
     For this we will introducing a contractive $\Gm$-action on $\bar Γ$ and all $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ such that the morphisms

### 2017-10-03 rewrite.tex
Start a completely new approach.

\documentclass{ck-article}

\title{Hochschild cohomology of torus equivariant D-modules: New approach}
\author{Clemens Koppensteiner}

\usepackage{math-ag}
\addbibresource{math.bib}

\newcommand\bc{\textbf{($\mathbf{*}$)}}

\newcommand\cs{\stack{B}}

\begin{document}
\maketitle

\section{Base change along the diagonal}

\begin{Def}
    Let $\stack X$ be any QCA stack.
    Consider the Cartesian diagram
    \[
        \begin{tikzcd}
            \ls \stack X \arrow[d, "p_1"] \arrow[r, "p_2"] & \stack X \arrow[d, "\Delta"] \\
            \stack X \arrow[r, "\Delta"] & \stack X \times \stack X
        \end{tikzcd}
    \]
    We say that $\stack X$ has property \bc\ if the canonical morphism
    \[
        p_{1,!}p_2^! \to \Delta^!\Delta_!
    \]
    of endofunctors of $\catDModHol{\stack X}$ is an equivalence.
\end{Def}

\begin{Lem}
    Property \bc\ holds whenever the diagonal $\Delta\colon \stack X \to \stack X \times \stack X$ is either proper or smooth.
    In particular it holds for schemes and classifying stacks $\cs{G}$.
\end{Lem}

\subsection{Some reduction steps}

\begin{Lem}\label{lem:bc_lc_immersion}
    If $i\colon\stack Y \hookrightarrow \stack X$ is a locally closed immersion and $\stack X$ has property \bc, then $\stack Y$ has property \bc.
\end{Lem}

[Fix the following proof notationally.]

\begin{proof}
    Let us first assume that $i$ is open.
    It suffices to show that $p_{\stack Y,1,!}p_{\stack Y,2}^!i^! \to \Delta_{\stack Y}^!\Delta_{\stack Y,!}i^!$ is an equivalence.
    Now, using the assumption on $\stack X$ and the fact that $i^! = i^*$ we get
    \[
        p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
        p_{\stack Y,1,!} i^! p_{\stack X,2}^! \cong
        i^! p_{\stack X,1,!} p_{\stack X,2}^! \isoto
        i^! \Delta_{\stack X}^! \Delta_{\stack X,!} =
        \Delta_{\stack Y}^! (i\times i)^! \Delta_{\stack X,!} \cong
        \Delta_{\stack Y}^! \Delta_{\stack X,!} i^!.
    \]
    Now let $i$ be a closed immersion.
    As above, it suffices to show that $i_!p_{\stack Y,1,!}p_{\stack Y,2}^!i^! \to i_!\Delta_{\stack Y}^!\Delta_{\stack Y,!}i^!$ is an equivalence.
    Now, using the assumption on $\stack X$ and the fact that $i_! = i_*$ we get
    \[
        i_! p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
        p_{\stack X,1,!} i_! p_{\stack Y,2}^!i^! \cong
        p_{\stack X,1,!} p_{\stack X,2}^! i_!i^! \isoto
        \Delta_{\stack X}^! \Delta_{\stack X,!} i_!i^! \cong
        \Delta_{\stack Y}^! (i\times i)_! \Delta_{\stack X,!}i^! =
        i_! \Delta_{\stack Y}^! \Delta_{\stack X,!} i^!.
        \qedhere
    \]

\end{proof}

\begin{Lem}\label{lem:bc_open_cover}
    If $\stack X$ has an open cover by substacks $\stack U_i$ with property $\bc$, then $\stack X$ has property $\bc$.
\end{Lem}

\begin{Lem}\label{lem:bc_product}
    If $\stack{X_1}$ and $\stack{X_2}$ both have property \bc, then so does $\stack{X_1} \times \stack{X_2}$.
\end{Lem}

\begin{proof}
    The category $\catDMod{\stack X_1 \times \stack X_2}$ is generated by elements of the form $\sheaf F_1 \boxtimes \sheaf F_2$ with $\sheaf F_i \in \catDModHol{\stack X_i}$.
    For any schematic morphism $f\colon \stack Y \to \stack Z$ of QCA stacks the functor $f^!$ is continuous on $\catDMod{\stack Z}$ and $f_!$ is preservers colimits in $\catDModHol{\stack Y}$, since it has a right adjoint.
    Thus it is sufficient to check that property \bc\ holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catDModHol{\stack X_1 \times \stack X_2}$.
    This is now clear because all functors respect $\boxtimes$.
\end{proof}

% Is there a strengthening to fiber products?

\subsection{Contractible stacks}

\begin{Lem}
    Assume that $\stack X$ is contractible and both $\stack X_0$ and $\stack X\setminus \stack X_0$ have property \bc.
    Then so does $\stack X$.
\end{Lem}

\section{Torus quotients}

\begin{Thm}
    Let $X$ be a normal variety with an action of a torus $T$.
    Then $\stack X = X/T$ has property \bc.
\end{Thm}

\begin{proof}[Proof idea]
    By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions} and Lemma~\ref{lem:bc_open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
    By Lemma~\ref{lem:bc_lc_immersion} it further suffices to consider the case that $\stack X = \as{m}/T$ for some $n$.
    By Lemma~\ref{lem:bc_product}, we can further decompose $\as{m}$ into $T$-eigenspaces.
    Each of those splits into copies of $\as{1}/T \cong \as{1}/\Gm \times BT'$.
    This can now be done by a direct calculation using the contraction principle.
\end{proof}

\printbibliography

\end{document}

### 2017-10-05 rewrite.tex
Notation for loop stacks of subspaces.
Things start to come together.

@@
 \newcommand\bc{\textbf{($\mathbf{*}$)}}
+\newcommand\hbc{\textbf{($\mathbf{**}$)}}
 
@@
 
-\begin{Lem}
-    Property \bc\ holds whenever the diagonal $\Delta\colon \stack X \to \stack X \times \stack X$ is either proper or smooth.
-    In particular it holds for schemes and classifying stacks $\cs{G}$.
+\begin{Lem}\label{lem:bc_smooth_or_proper}
+    Property \bc\ holds for $\stack X$ whenever the diagonal $\Delta\colon \stack X \to \stack X \times \stack X$ is either proper or smooth.
+    In particular it holds for (separated) schemes and classifying stacks $\cs{G}$.
 \end{Lem}
@@
 
+Let $i\colon\stack Y \to \stack X$ be an open (or closed) immersion.
+We have $\ls Y \cong \stack Y \times_{\stack X \times \stack X} \stack Y$ and it follows that there is a canonical open (resp.~closed) immersion of loop stacks $\ls i\colon \ls \stack Y \to \ls \stack X$.
+
 \begin{Lem}\label{lem:bc_lc_immersion}
@@
 \end{Lem}
-
-[Fix the following proof notationally.]
 
@@
         p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
-        p_{\stack Y,1,!} i^! p_{\stack X,2}^! \cong
+        p_{\stack Y,1,!} (\ls i)^! p_{\stack X,2}^! \cong
         i^! p_{\stack X,1,!} p_{\stack X,2}^! \isoto
@@
         i_! p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
-        p_{\stack X,1,!} i_! p_{\stack Y,2}^!i^! \cong
+        p_{\stack X,1,!} (\ls i)_! p_{\stack Y,2}^!i^! \cong
         p_{\stack X,1,!} p_{\stack X,2}^! i_!i^! \isoto
@@
     \]
-
 \end{proof}
@@
 \begin{Lem}\label{lem:bc_open_cover}
-    If $\stack X$ has an open cover by substacks $\stack U_i$ with property $\bc$, then $\stack X$ has property $\bc$.
+    If $\stack X$ has an open cover by substacks $\stack U_i$ with property \bc, then $\stack X$ has property \bc.
 \end{Lem}
@@
 
-\begin{Lem}
-    Assume that $\stack X$ is contractible and both $\stack X_0$ and $\stack X\setminus \stack X_0$ have property \bc.
+\begin{Lem}\label{lem:bc_contractive}
+    Assume that $\stack X$ has a trivial contractive $\Gm$-action and that both $\stack X_0$ and $\stack X\setminus \stack X_0$ have property \bc.
     Then so does $\stack X$.
 \end{Lem}
+
+\begin{proof}
+    Let $i\colon \stack X_0 \hookrightarrow \stack X$ and let $j\colon \stack U =\stack X\setminus \stack X_0 \hookrightarrow \stack X$ be its complement.
+    Consider the distinguished triangle
+    \[
+        i_!i^! \Delta^!\Delta_! \to \Delta^!\Delta_! \to j_*j^*\Delta^!\Delta_!
+    \]
+    on $\catDModHol{\stack X}$.
+    It suffices to show that the canonical maps on the outside terms to $i_!i^! p_{1,!}p_2^!$ and $j_*j^* p_{1,!}p_2^!$ are isomorphisms.
+
+    Using the fact that $j^* = j^!$, base change and the assumption we see that
+    \[
+        j_*j^*\Delta^!\Delta_! \cong
+        j_*\Delta^!\Delta_!j^* \isoto
+        j_*p_{\stack U,1,!}p_{\stack U,2}^! j^* \cong
+        j_*j^* p_{1,!}p_2^!
+    \]
+    is an equivalence.
+
+    Write $\pi\colon \stack X \to \stack X_0$ for the contraction map opposite to $i$.
+    Then by the contraction principle,
+    \begin{equation}\label{eq:lem:bc_contractive}
+        i_!i^! \Delta^!\Delta_! =
+        i_!\Delta_{\stack X_0}^!(i\times i)^! \Delta_! \cong
+        i_!\Delta_{\stack X_0}^!(\pi\times \pi)_! \Delta_! =
+        i_!\Delta_{\stack X_0}^!\Delta_{\stack X_0,!} \pi_! \cong
+        i_!\Delta_{\stack X_0}^!\Delta_{\stack X_0,!} i^!.
+    \end{equation}
+    Write $\ls i \colon \ls\stack X_0 \hookrightarrow \ls\stack X$ for the corresponfing closed inclusion of loop stacks.
+    We note that $\ls\stack X$ inherits a contractive $\Gm$ action form $\stack X$.
+    Let $\ls \pi\colon \ls\stack X \to \ls\stack X_0$ be the corresponding contraction map.
+    Then by assumption and the contraction principle, \eqref{eq:lem:bc_contractive} is equivalent to
+    \[
+        i_!p_{\stack X_0,1,!}p_{\stack X_0,2}^! i^! =
+        i_!p_{\stack X_0,1,!} (\ls i)^! p_{2}^! \cong
+        i_!p_{\stack X_0,1,!} (\ls \pi)_! p_{2}^! =
+        i_! \pi_! p_{1,!} p_{2}^! =
+        i_! i^! p_{1,!} p_{2}^!. \qedhere
+    \]
+\end{proof}
+
+\section{Compatibility base changes}
+
+Let us write $\stack G_\bullet = \stack G_\bullet(\stack X)$ for the nerve of the groupoid associated to $\ls\stack X \rightrightarrows \stack X$.
+Thus
+\[
+    \stack G_m(\stack X) = \underbrace{\stack X \times_{\stack X \times \stack X} \dotsb \times_{\stack X \times \stack X} \stack X}_{m+1\text{ times}}.
+\]
+If $i\colon \stack Y \hookrightarrow \stack X$ is a closed (or open) substack, then $\stack G_m(\stack Y)$ is a closed (resp.~open) substack of $\stack G_m(\stack X)$.
+Sbsuing notation, we will continue to denote this inclusion by $i$.
+
+\begin{Def}
+    Consider the cartesian square
+    \[
+        \begin{tikzcd}
+            \stack G_{n+1} \arrow[r] \arrow[d] & \stack G_n \arrow[d] \\
+            \stack G_{m+1} \arrow[r] & \stack G_m
+        \end{tikzcd}
+    \]
+    [describe maps].
+    We say that $\stack X$ has property \hbc\ if the canonical morphism
+    \[
+        ...
+    \]
+    of functors $\catDModHol{\stack G_n} \to \catDModHol{\stack G_m+1}$ is an equivalence.
+\end{Def}
+
+\begin{Lem}
+    If the diagonal  morphism $\Delta\colon \stack X \to \stack X \times \stack X$ is proper, then property \hbc\ holds for $\stack X$.
+    In particular it holds for (separated) schemes.
+\end{Lem}
+
+\begin{proof}
+    It suffices to show the base change for face and degeneracy maps, where the vertical arrows turn out to be proper.
+    [Fill in the details.]
+\end{proof}
+
+\begin{Lem}
+    Let $G$ be an affine algebraic group. 
+    Then property \hbc\ holds  for the classifying stack $\cs{G}$
+\end{Lem}
+
+\begin{Lem}\label{lem:hbc_lc_immersion}
+    If $i\colon\stack Y \hookrightarrow \stack X$ is a locally closed immersion and $\stack X$ has property \bc, then $\stack Y$ has property \bc.
+\end{Lem}
+
+\begin{proof}
+    As for Lemma~\ref{lem:bc_lc_immersion}.
+\end{proof}
+
+\begin{Lem}\label{lem:hbc_open_cover}
+    If $\stack X$ has an open cover by substacks $\stack U_i$ with property \hbc, then $\stack X$ has property \hbc.
+\end{Lem}
+
+\begin{Lem}\label{lem:hbc_product}
+    If $\stack{X_1}$ and $\stack{X_2}$ both have property \hbc, then so does $\stack{X_1} \times \stack{X_2}$.
+\end{Lem}
+
+\begin{proof}
+    Denote by $\stack G_\bullet(\stack X_i)$ the groupoid associated to $\stack X_i \to \stack X_i \times \stack X_i$.
+    Then we have a natural decomposition $\stack G_m(\stack X_1 \times \stack X_2) \cong \stack G_m(\stack X_1) \times \stack G_m(\stack X_2)$.
+    Thus the method of the proof of Lemma~\ref{lem:bc_product} can also be applied to show the corresponding statement for property \hbc.
+\end{proof}
 
@@
     Each of those splits into copies of $\as{1}/T \cong \as{1}/\Gm \times BT'$.
-    This can now be done by a direct calculation using the contraction principle.
+
+    By Lemma~\ref{lem:bc_smooth_or_proper} it remains to consider the stack $\as{1}/\Gm$, where $\Gm$ acts nontrivially.
+    If the $\Gm$ action is contractive this case follows immediatley from Lemma~\ref{lem:bc_contractive} and Lemma~\ref{lem:bc_smooth_or_proper}.
+    [Say something about the anti-contractive case.]
 \end{proof}
+
+For property \hbc\ one can do a similar reduction to a computation for $\as{1}/\Gm$.
+For the special case the contraction principle is again a useful tool.
 

### 2017-10-05 rewrite.tex
Writeup of the main argument.

--- 2017-10-03 rewrite.tex
@@
 \newcommand\bc{\textbf{($\mathbf{*}$)}}
+\newcommand\hbc{\textbf{($\mathbf{**}$)}}
 
 \newcommand\cs{\stack{B}}
+\newcommand\catCoSimplicial{\cat{\Delta}^{\mathrm{op}}}
 
@@
 
-\begin{Lem}
-    Property \bc\ holds whenever the diagonal $\Delta\colon \stack X \to \stack X \times \stack X$ is either proper or smooth.
-    In particular it holds for schemes and classifying stacks $\cs{G}$.
+Let us write $\stack G_\bullet = \stack G_\bullet(\stack X)$ for the nerve of the groupoid associated to $\ls\stack X \rightrightarrows \stack X$.
+Thus
+\[
+    \stack G_m(\stack X) = \underbrace{\stack X \times_{\stack X \times \stack X} \dotsb \times_{\stack X \times \stack X} \stack X}_{m+1\text{ times}}.
+\]
+
+\begin{Def}
+    Let $\stack X$ be a QCA stack and consider the cartesian square
+    \[
+        \begin{tikzcd}
+            \stack G_{n+1} \arrow[r, "p_{s}"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
+            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
+        \end{tikzcd}
+    \]
+    where the horizontal maps are induced by a map $F\colon [n] \to [m]$ in $\catCoSimplicial$.
+    We say that $\stack X$ has property \hbc\ if for each such $F$ the canonical morphism
+    \[
+        p_{F+1,!}p_s^! \to p_s^!p_{F,!}
+    \]
+    of functors $\catDModHol{\stack G_n} \to \catDModHol{\stack G_{m+1}}$ is an equivalence.
+\end{Def}
+
+\begin{Lem}\label{lem:smooth_or_proper}
+    Let $\stack X$ be a QCA stack with diagonal moprhism $\Delta\colon \stack X \to \stack X \times \stack X$. Then,
+    \begin{enumerate}
+        \item\label{lem:smooth_or_proper:bc} If $\Delta$ is either proper of smooth, then $\stack X$ has property \bc.
+        \item\label{lem:smooth_or_proper:hbc} If $\Delta$ is proper, then $\stack X$ has property \hbc.
+        \item\label{lem:smooth_or_proper:scheme} If $\stack X$ is a (separated) scheme, then $\stack X$ has both properties \bc\ and \hbc.
+        \item\label{lem:smooth_or_proper:bg} Let $G$ be an affine algebraic group. Then the classifying stack $\cs{G}$ has both properties \bc\ and \hbc.
+    \end{enumerate}
 \end{Lem}
+
+\begin{proof}
+    Statement \ref{lem:smooth_or_proper:bc} is a direct consquence of the base change theorem [reference].
+
+    We only need to show \ref{lem:smooth_or_proper:hbc} under the additional assumption that $F$ is a face or degeneracy map.
+    In either case it follows immediately that $p_{F}$ is proper and we can again apply base change.
+
+    Statement \ref{lem:smooth_or_proper:scheme} is just a special case of \ref{lem:smooth_or_proper:bc} and \ref{lem:smooth_or_proper:hbc}.
+
+    The diagonal morphism of $\cs{G}$ is smooth, so that property \hbc\ follows from \ref{lem:smooth_or_proper:bc}.
+    Note that $\stack G_m(\cs{G}) \cong G^m \times \cs{G}$.
+    Thus one sees that the maps $\stack G_m(\cs{G}) \to \stack G_{m-1}(\cs{G})$ are smooth, while the maps $\stack G_m(\cs{G}) \to \stack G_{m+1}(\cs{G})$ are closed immersions (and hence proper).
+    Thus property \hbc\ follows from smooth and proper base change.
+\end{proof}
 
@@
 
-\begin{Lem}\label{lem:bc_lc_immersion}
-    If $i\colon\stack Y \hookrightarrow \stack X$ is a locally closed immersion and $\stack X$ has property \bc, then $\stack Y$ has property \bc.
+Let $i\colon\stack Y \to \stack X$ be an open (or closed) immersion.
+We have $\ls Y \cong \stack Y \times_{\stack X \times \stack X} \stack Y$ and it follows that there is a canonical open (resp.~closed) immersion of loop stacks $\ls i\colon \ls \stack Y \to \ls \stack X$.
+
+More generally, $\stack G_m(\stack Y)$ is an open (resp.~closed) substack of $\stack G_m(\stack X)$.
+Absuing notation, we will sometimes continue to denote this inclusion by $i$.
+%In the special case $m=1$, we will also write $\ls i\colon \ls \stack Y \to \ls \stack X$.
+
+\begin{Lem}\label{lem:lc_immersion}
+    Let $i\colon\stack Y \hookrightarrow \stack X$ is a locally closed immersion of QCA stacks.
+    If $\stack X$ has property \bc\ (resp.~property \hbc), then so does $\stack Y$.
 \end{Lem}
 
-[Fix the following proof notationally.]
-
 \begin{proof}
+    We will show the statement for property \bc.
+    The proof for \hbc\ is essentally the same.
     Let us first assume that $i$ is open.
@@
     \]
-
 \end{proof}
 
-\begin{Lem}\label{lem:bc_open_cover}
-    If $\stack X$ has an open cover by substacks $\stack U_i$ with property $\bc$, then $\stack X$ has property $\bc$.
+Since all operations are local we can check the properties on open covers.
+
+\begin{Lem}\label{lem:open_cover}
+    If $\stack X$ has an open cover by substacks $\stack U_i$ with property \bc\ (resp.~with property \hbc), then $\stack X$ has property \bc\ (resp.~property \hbc).
 \end{Lem}
 
-\begin{Lem}\label{lem:bc_product}
-    If $\stack{X_1}$ and $\stack{X_2}$ both have property \bc, then so does $\stack{X_1} \times \stack{X_2}$.
+\begin{Lem}\label{lem:product}
+    If $\stack{X_1}$ and $\stack{X_2}$ both have property \bc\ (resp.~property \hbc), then so does $\stack{X_1} \times \stack{X_2}$.
 \end{Lem}
@@
     Thus it is sufficient to check that property \bc\ holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catDModHol{\stack X_1 \times \stack X_2}$.
-    This is now clear because all functors respect $\boxtimes$.
+
+    Note that $\ls(\stack X_1 \times \stack X_2) \cong \ls \stack X_1 \times \ls \stack X_2$ and more generally $\stack G_m(\stack X_1 \times \stack X_2) \cong \stack G_m(\stack X_1) \times \stack G_m(\stack X_2)$.
+    The statement now follows because all functors respect $\boxtimes$.
 \end{proof}
@@
 
-\begin{Lem}
-    Assume that $\stack X$ is contractible and both $\stack X_0$ and $\stack X\setminus \stack X_0$ have property \bc.
+\begin{Lem}\label{lem:contractive}
+    Assume that $\stack X$ has a trivial contractive $\Gm$-action and that both $\stack X_0$ and $\stack U = \stack X\setminus \stack X_0$ have property \bc (respectively poperty \hbc).
     Then so does $\stack X$.
 \end{Lem}
+
+\begin{proof}
+    Let us first prove the statement for property \bc.
+    Let $i\colon \stack X_0 \hookrightarrow \stack X$ and let $j\colon \stack U \hookrightarrow \stack X$ be its complement.
+    Consider the distinguished triangle
+    \[
+        i_!i^! \Delta^!\Delta_! \to \Delta^!\Delta_! \to j_*j^*\Delta^!\Delta_!
+    \]
+    on $\catDModHol{\stack X}$.
+    It suffices to show that the canonical maps on the outside terms to $i_!i^! p_{1,!}p_2^!$ and $j_*j^* p_{1,!}p_2^!$ are isomorphisms.
+
+    Using the fact that $j^* = j^!$, base change and the assumption we see that
+    \[
+        j_*j^*\Delta^!\Delta_! \cong
+        j_*\Delta^!\Delta_!j^* \isoto
+        j_*p_{\stack U,1,!}p_{\stack U,2}^! j^* \cong
+        j_*j^* p_{1,!}p_2^!
+    \]
+    is an equivalence.
+
+    Write $\pi\colon \stack X \to \stack X_0$ for the contraction map opposite to $i$.
+    Then by the contraction principle,
+    \begin{equation}\label{eq:lem:bc_contractive}
+        i_!i^! \Delta^!\Delta_! =
+        i_!\Delta_{\stack X_0}^!(i\times i)^! \Delta_! \cong
+        i_!\Delta_{\stack X_0}^!(\pi\times \pi)_! \Delta_! =
+        i_!\Delta_{\stack X_0}^!\Delta_{\stack X_0,!} \pi_! \cong
+        i_!\Delta_{\stack X_0}^!\Delta_{\stack X_0,!} i^!.
+    \end{equation}
+    Write $\ls i \colon \ls\stack X_0 \hookrightarrow \ls\stack X$ for the corresponfing closed inclusion of loop stacks.
+    We note that $\ls\stack X$ inherits a contractive $\Gm$ action form $\stack X$.
+    Let $\ls \pi\colon \ls\stack X \to \ls\stack X_0$ be the corresponding contraction map.
+    Then by assumption and the contraction principle, \eqref{eq:lem:bc_contractive} is equivalent to
+    \[
+        i_!p_{\stack X_0,1,!}p_{\stack X_0,2}^! i^! =
+        i_!p_{\stack X_0,1,!} (\ls i)^! p_{2}^! \cong
+        i_!p_{\stack X_0,1,!} (\ls \pi)_! p_{2}^! =
+        i_! \pi_! p_{1,!} p_{2}^! =
+        i_! i^! p_{1,!} p_{2}^!.
+    \]
+    Finally, we note that the $\Gm$-action on $\stack X$ induces contractive $\Gm$-actions on each $\stack G_m(\stack X)$ with $(\stack G_m(\stack X))_0 = \stack G_m(\stack X_0)$.
+    Thus the statement for property \hbc\ follows in the same way as above.
+\end{proof}
 
@@
     Let $X$ be a normal variety with an action of a torus $T$.
-    Then $\stack X = X/T$ has property \bc.
+    Then $\stack X = X/T$ has properties \bc\ and \hbc.
 \end{Thm}
 
-\begin{proof}[Proof idea]
-    By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions} and Lemma~\ref{lem:bc_open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
-    By Lemma~\ref{lem:bc_lc_immersion} it further suffices to consider the case that $\stack X = \as{m}/T$ for some $n$.
-    By Lemma~\ref{lem:bc_product}, we can further decompose $\as{m}$ into $T$-eigenspaces.
+\begin{proof}
+    By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions} and Lemma~\ref{lem:open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
+    By Lemma~\ref{lem:lc_immersion} it further suffices to consider the case that $\stack X = \as{m}/T$ for some $n$.
+    By Lemma~\ref{lem:product}, we can further decompose $\as{m}$ into $T$-eigenspaces.
     Each of those splits into copies of $\as{1}/T \cong \as{1}/\Gm \times BT'$.
-    This can now be done by a direct calculation using the contraction principle.
+
+    By Lemma~\ref{lem:smooth_or_proper} it remains to consider the stack $\as{1}/\Gm$, where $\Gm$ acts nontrivially.
+    If the $\Gm$ action is contractive this case follows immediatley from Lemma~\ref{lem:contractive} and Lemma~\ref{lem:smooth_or_proper}.
+    Otherwise the inverse of the $\Gm$-action on $\as1$ is contractive and we can use the contraction principle (and hence Lemma~\ref{lem:contractive}) with the monoid $\as1 = \Gm \cup \{\infty\}$ instead of $\Gm \cup \{0\}$.
 \end{proof}

### 2017-10-05 rewrite.tex
Continuing on...

@@
 \newcommand\catCoSimplicial{\cat{\Delta}^{\mathrm{op}}}
+\newcommand\dR{\mathrm{dR}}
+\newcommand\GammadR{Γ_{\mkern-4mu\dR}}
+\newcommand{\HCoh}{\operatorname{HH}^\cx}   % Hochschild cohomology
+\newcommand\opalg[1]{#1^{\mathrm{op}}}
 
@@
 
+\begin{Cor}\label{cor:properties_imply_monads}
+    If $\stack X$ has properties \bc\ and \hbc, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
+    In particular there is an isomorphism of algebras
+    \[
+        \HCoh\bigl(\catDMod{\stack X}\bigr)
+        \cong
+        \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
+    \]
+\end{Cor}
+
+\begin{proof}
+    This is just a restatement of Lemma~\ref{lem:pre:groupoid_monad_hol} together with ?.
+\end{proof}
+
+\begin{Rem}
+    We expect that most quotient stacks do not have property \bc.
+    For example, a direct computation shows that the transformation of property \bc\ is not an isomorphism for the D-module $k$ on the stack $\ps1/\Ga$.
+\end{Rem}
+
 \begin{Lem}\label{lem:smooth_or_proper}
-    Let $\stack X$ be a QCA stack with diagonal moprhism $\Delta\colon \stack X \to \stack X \times \stack X$. Then,
+    Let $\stack X$ be a QCA stack with diagonal morphism $\Delta\colon \stack X \to \stack X \times \stack X$. Then,
     \begin{enumerate}
@@
     For any schematic morphism $f\colon \stack Y \to \stack Z$ of QCA stacks the functor $f^!$ is continuous on $\catDMod{\stack Z}$ and $f_!$ is preservers colimits in $\catDModHol{\stack Y}$, since it has a right adjoint.
-    Thus it is sufficient to check that property \bc\ holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catDModHol{\stack X_1 \times \stack X_2}$.
+    Since the inclusion of a full subcategory reflects all colimits it is thus sufficient to check that the properties holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catDModHol{\stack X_1 \times \stack X_2}$.
 
@@
 
-% Is there a strengthening to fiber products?
-
 \subsection{Contractible stacks}
@@
 \begin{Lem}\label{lem:contractive}
-    Assume that $\stack X$ has a trivial contractive $\Gm$-action and that both $\stack X_0$ and $\stack U = \stack X\setminus \stack X_0$ have property \bc (respectively poperty \hbc).
+    Assume that $\stack X$ has a trivial contractive $\Gm$-action and that both $\stack X_0$ and $\stack U = \stack X\setminus \stack X_0$ have property \bc\ (respectively property \hbc).
     Then so does $\stack X$.

### 2017-10-05 rewrite.tex
Contraction principle.

@@
 
-\subsection{Contractible stacks}
+\subsection{Contractive \texorpdfstring{$\Gm$}{Gm}-actions}
 
-\begin{Lem}\label{lem:contractive}
-    Assume that $\stack X$ has a trivial contractive $\Gm$-action and that both $\stack X_0$ and $\stack U = \stack X\setminus \stack X_0$ have property \bc\ (respectively property \hbc).
+Let $\stack X$ be a QCA stack with an action of $\Gm$.
+We call the action \emph{contractive} if it can be extended to an action of the monoid $\as 1$.
+Following the convention of \cite[Appendix~C]{DrinfeldGaitsgory:arXiv:CompactGenerationOfDModOnBunG} we denote by $\stack X^0$ the stack of $\{0,1\}$-equivariant maps $\{0\} \to \stack X$.
+The map $\{0\} \to \{0,1\}$ induces a \emph{contraction morphism} $\pi\colon \stack X \to \stack X^0$.
+
+We then have the following \emph{contraction principle} (cf.~also \cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}).
+
+\begin{Thm}[{\cite[Corollary~C.5.4]{DrinfeldGaitsgory:arXiv:CompactGenerationOfDModOnBunG}}]
+    \label{thm:contraction_principle}%
+    Let $X$ be a scheme with a trivial contractive $\Gm$-action.
+    Then there is a canonical isomorphism of functors
+    \[
+        π_! \cong i^! \colon \catDModHol{\stack X} → \catDModHol{\stack X^0}
+    \]
+    given by adjunction
+    \[
+        π_! → i^! i_! π_!  = i^! (π ∘ i)_! = i^!.
+    \]
+\end{Thm}
+
+\begin{Prop}\label{prop:contractive}
+    Assume that $\stack X$ has a trivial contractive $\Gm$-action such that $i\colon \stack X^0 \to \stack X$ is a closed immersion and both $\stack X^0$ and $\stack U = \stack X\setminus \stack X^0$ have property \bc\ (respectively property \hbc).
     Then so does $\stack X$.
-\end{Lem}
+\end{Prop}
 
@@
     Let us first prove the statement for property \bc.
-    Let $i\colon \stack X_0 \hookrightarrow \stack X$ and let $j\colon \stack U \hookrightarrow \stack X$ be its complement.
+    Let $j\colon \stack U \hookrightarrow \stack X$ be the (open) complement of $i$.
     Consider the distinguished triangle
@@
 
-    Write $\pi\colon \stack X \to \stack X_0$ for the contraction map opposite to $i$.
+    Write $\pi\colon \stack X \to \stack X^0$ for the contraction map opposite to $i$.
     Then by the contraction principle,
@@
     \end{equation}
-    Write $\ls i \colon \ls\stack X_0 \hookrightarrow \ls\stack X$ for the corresponfing closed inclusion of loop stacks.
+    Write $\ls i \colon \ls\stack X^0 \hookrightarrow \ls\stack X$ for the corresponding closed inclusion of loop stacks.
     We note that $\ls\stack X$ inherits a contractive $\Gm$ action form $\stack X$.
-    Let $\ls \pi\colon \ls\stack X \to \ls\stack X_0$ be the corresponding contraction map.
-    Then by assumption and the contraction principle, \eqref{eq:lem:bc_contractive} is equivalent to
+    Let $\ls \pi\colon \ls\stack X \to \ls\stack X^0$ be the corresponding contraction map.
+    Then by assumption and the contraction principle (Theorem~\ref{thm:contraction_principle}), \eqref{eq:lem:bc_contractive} is equivalent to
     \[
@@
     \]
-    Finally, we note that the $\Gm$-action on $\stack X$ induces contractive $\Gm$-actions on each $\stack G_m(\stack X)$ with $(\stack G_m(\stack X))_0 = \stack G_m(\stack X_0)$.
+    Finally, we note that the $\Gm$-action on $\stack X$ induces contractive $\Gm$-actions on each $\stack G_m(\stack X)$ with $(\stack G_m(\stack X))^0 = \stack G_m(\stack X^0)$.
     Thus the statement for property \hbc\ follows in the same way as above.
@@
     By Lemma~\ref{lem:smooth_or_proper} it remains to consider the stack $\as{1}/\Gm$, where $\Gm$ acts nontrivially.
-    If the $\Gm$ action is contractive this case follows immediatley from Lemma~\ref{lem:contractive} and Lemma~\ref{lem:smooth_or_proper}.
-    Otherwise the inverse of the $\Gm$-action on $\as1$ is contractive and we can use the contraction principle (and hence Lemma~\ref{lem:contractive}) with the monoid $\as1 = \Gm \cup \{\infty\}$ instead of $\Gm \cup \{0\}$.
+    If the $\Gm$ action is contractive this case follows immediately from Proposition~\ref{prop:contractive} and Lemma~\ref{lem:smooth_or_proper}.
+    Otherwise the inverse of the $\Gm$-action on $\as1$ is contractive and we can use the contraction principle (and hence Proposition~\ref{prop:contractive}) with the monoid $\as1 = \Gm \cup \{\infty\}$ instead of $\Gm \cup \{0\}$.
 \end{proof}

### 2017-10-06 rewrite.tex
Add stuff form old version and some new things.

@@
 \newcommand\opalg[1]{#1^{\mathrm{op}}}
+\newcommand\LocSys{\operatorname{LocSys}}   % local systems
+\newcommand\Bun{\operatorname{Bun}}         % bundles
+\newcommand\dualize{\mathbb D}
+\newcommand\Gammasub[1]{\Gamma_{\mkern-3mu#1}}
+\newcommand\barGammasub[1]{\bar{\Gamma}_{\mkern-3mu#1}}
+
+\renewcommand\ls[1]{\mathbfcal{L} #1}
+\newcommand\lsY[2][\stack Y]{\mathbfcal{L}_{#1} #2}
+\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
+\newcommand\clsY[2][\stack Y]{\overline{\mathbfcal{L}}_{#1} #2}
+\newcommand\lsc[1]{\mathbfcal{L}^c #1}
+\newcommand\lscY[2][\stack Y]{\mathbfcal{L}_{#1}^c #2}
+
+\newcommand\goodness{property \textbf{(!)}}
+\newcommand\goodnessshort{\textbf{(!)}}
+\newcommand\isgood{has property \textbf{(!)}}
+\newcommand\aregood{have property \textbf{(!)}}
+\newcommand\isnotgood{does not have property \textbf{(!)}}
+\newcommand\arenotgood{do not have property \textbf{(!)}}
+\newcommand\goodX[1]{#1 with property \textbf{(!)}}
+\newcommand\goodnessb{property \textbf{(!')}}
+\newcommand\goodnessbshort{\textbf{(!')}}
+\newcommand\isgoodb{has property \textbf{(!')}}
+\newcommand\aregoodb{have property \textbf{(!')}}
+\newcommand\goodbX[1]{#1 with property \textbf{(!')}}
+
+\newcommand\XXtimes{%
+    \mathchoice%
+        {\mathop{×}\limits_{\stack X × \stack X}}
+        {×_{\stack X × \stack X}}
+        {×_{\stack X × \stack X}}
+        {×_{\stack X × \stack X}}
+    }
+
+% overrides
+\let\shortbar\bar
+\let\bar\overline
+
+% Formatting of upper case roman numerals (in references).
+\newcommand{\RomanNum}[1]{\textsc{\MakeLowercase{#1}}}
 
@@
 
+\begin{abstract}
+    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
+    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
+    This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of D-modules on stacks.
+\end{abstract}
+
+\setcounter{tocdepth}{1}
+\tableofcontents
+
+\section{Introduction}
+
+Given a manifold $X$ and a category of sheaves on $X$, microlocal geometry asks whether the sheaves can be localized not just on $X$ but also with respect to codirections, i.e.~on the cotangent space $T^*X$.
+For example, for constructible sheaves this leads to the notion of microsupport discussed in detail in \cite{KashiwaraSchapira:1994:SheavesOnManifolds}.
+More generally, given a category of sheaves on a space $X$, we can ask whether it is possible to localize them on some space that is strictly larger than $X$ itself.
+
+Even more generally one can ask the following question: Given a $k$-linear category $\cat C$, can one find a space over which $\cat C$ localizes?
+For co-complete compactly generated triangulated categories one answer is provided by \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
+To each map from a graded-commutative ring $R$ to the center of $\cat C$ the authors associate the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
+This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves).
+
+We are led to consider the universal algebra acting on $\cat C$ by this construction, i.e.~the \emph{Hochschild cohomology} of $\cat C$.
+For a complete (pre-triangulated) dg category $\cat C$ the Hochschild cohomology is the dg algebra of derived endomorphisms of the identity functor of $\cat C$:
+\[
+    \HCoh(\cat C)
+    = \mathbb{R}\mathrm{Hom}(\id[\cat C], \id[\cat C])
+    = \Hom_{\cat{Funct}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
+\]
+The ring $R = \bigoplus \operatorname{HH}^{2n}(\cat C)$ is commutative and hence one can define for each $A ∈ \cat C$ the support $\supp_R A$ as a subset of $\Spec R$.
+Thus understanding the Hochschild cohomology of a dg category can be an important step to understanding the category itself.
+
+This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
+More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
+By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.
+
+A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
+Representing the identity functor by its kernel, we obtain an isomorphism of dg algebras
+\begin{equation}
+    \label{eq:intro:d-mod-hcoh}
+    \HCoh(\catDMod{\stack X}) \cong \Hom_{\catDMod{X×X}}(Δ_*ω_{\stack X}, Δ_*ω_{\stack X}),
+\end{equation}
+where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
+In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
+However, if $\stack X$ is a general stack, then $Δ$ is not proper and the situation becomes more complicated.
+
+By Verdier duality and adjunction we can always rewrite \eqref{eq:intro:d-mod-hcoh} as
+\[
+    \HCoh(\catDMod{\stack X}) \cong
+    \opalg{\Hom_{\catDMod{X}}(k_{\stack X}, Δ^!Δ_!k_{\stack X})} =
+    \opalg{\GammadR(\stack X, Δ^!Δ_!k_{\stack X})}.
+\]
+It is now tempting to look at the Cartesian square
+\[
+    \begin{tikzcd}
+        \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
+        \stack X \arrow[r, "Δ"] & \stack X × \stack X
+    \end{tikzcd}
+\]
+where
+\[
+    \ls \stack X = \stack X \mathop{×}\limits_{\stack X × \stack X} \stack X
+\]
+is the derived loop space (or inertia stack) of $\stack X$ and try to express the Hochschild cohomology as the cohomology of some sheaf on $\ls \stack X$.
+We could expect the existence of an isomorphism
+\begin{equation}
+    \label{eq:intro:naive}
+    \GammadR(\stack X, Δ^!Δ_!k_{\stack X}) \cong
+    \GammadR(\stack X, p_{1,!}p₂^! k_{\stack X}).
+\end{equation}
+We refer to this as the \enquote{naive expectation}.
+Unfortunately, the two sides are in general not isomorphic (the stack $\stack X = \ps1/\Ga$ is an easy counter-example).
+
+In this paper we investigate how to quantify the cone of the morphism
+\begin{equation}\label{eq:intro:central_cone}
+    p_{1,!}p₂^! k_{\stack X} → Δ^!Δ_! k_{\stack X}
+\end{equation}
+and thus the failure of the naive isomorphism \eqref{eq:intro:naive} to hold.
+As an application, we prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.
+
+\begin{Thm}\label{thm:main}
+    Let $G \cong \Gm^n$ be a torus acting on a normal scheme $X$ of finite type over $k$.
+    Then there is a canonical isomorphism of algebras
+    \[
+        \HCoh\bigl(\catDMod{X/G}\bigr)
+        \cong
+        \opalg{\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)},
+    \]
+    where the algebra structure on $\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
+\end{Thm}
+
+Since, to the author's knowledge, there is currently no comprehensive account of the theory of D-modules on stacks available in the literature, we review the basic formalism in Section~\ref{sec:d-mods}.
+In essence, most of the familiar six functor formalism of holonomic D-modules works in a general context.
+It is convenient to rephrase Theorem~\ref{thm:main} as an equivalence of monads.
+Thus in Section~\ref{sec:monads} we review some constructions of monads in our setting.
+In Section~\ref{sec:HH} we explain how morphism~\eqref{eq:intro:central_cone} arises as a morphism of monads and make precise its relationship with Hochschild cohomology of $\catDMod{\stack X}$.
+
+In Section~\ref{sec:base-change} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.
+Finally, in Section~\ref{sec:torus} we deduce Theorem~\ref{thm:main} from this description, using geometric considerations and the contraction principle of Drinfeld--Gaitsgory \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
+
+The present paper represents only the first step in the study of Hochschild cohomology and associated support theories for D-modules.
+In future work we intend to expand upon the foundations laid out in this paper.
+Of particular interest are quotients stacks $X/G$ with $G$ an affine algebraic group and the stack $\Bun_G(C)$ of $G$-bundles on a curve $C$.
+Following the constructions laid out in Section~\ref{sec:base-change:compactification}, for the former we need a good $G×G$-equivariant compactification of $G$.
+Thus groups with a wonderful compactification are of particular interest for study with our methods.
+For the latter, relative compactifications of the diagonal of $\Bun_G(C)$ have been proposed by Lafforgue and Drinfeld.
+These spaces are under active study and we expect that any computations of Hochschild cohomology to have deep connections with the \enquote{pseudo-identity} that is needed in the formulation of the geometric (categorical) Langlands conjecture.% \cite{Gaitsgory:preprint:StrangeFunctionalEquationForEisensteinSeries}
+
+\subsection*{Acknowledgments}
+I would like to thank David Nadler for the original motivation for this project and many discussions concerning it.
+
+\section{D-modules on stacks}
+\label{sec:d-mods}
+
+We fix an algebraically closed base field $k$ of characteristic $0$.
+All stacks will be assumed to be algebraic over $k$ and quasi-compact with affine automorphism group (QCA).
+Thus by definition for any stack $\stack X$ we have:
+\begin{itemize}
+    \item The diagonal morphism $Δ\colon \stack X → \stack X × \stack X$ is schematic.
+    \item There exists a scheme $Z$ with a smooth and surjective map $Z → \stack X$.
+    \item $\stack X$ is quasi-compact.
+    \item The automorphism groups of the geometric points of $\stack X$ are affine.
+    \item The loop space (or inertia stack) $\ls \stack X = \stack X ×_{\stack X × \stack X} \stack X$ is of finite presentation over $\stack X$.
+\end{itemize}
+The QCA condition guarantees a reasonable theory of D-modules on $\stack X$.
+For details on QCA stacks we refer to~\cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
+Every quotient of a scheme of finite type over $k$ by an affine algebraic group is a QCA stack, and we will be mainly interested in these.
+
+In order to correctly define categories of D-modules on stacks it is necessary to work with dg-categories.
+We refer to \cite{Keller:2006:OnDGCategories} for an introduction to dg categories.
+It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2014-draft:HigherAlgebra}, which can be done via the nerve construction.% \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}.
+%\cite[Section~1.3.1]{Lurie:2014-draft:HigherAlgebra}
+We will switch between those two languages without explicitly mentioning the intervening constructions and apply results from \cite{Lurie:2014-draft:HigherAlgebra} to dg categories.
+Fortunately, a superficial knowledge of dg/$∞$-categories should be sufficient for reading this article.
+
+The category of D-modules on a stack $\stack X$ can be either constructed via descent \cite{BeilinsonDrifeld:unpublished:Hitchin,DrinfeldGaitsgory:2013:FinitenessQuestions} or equivalently as ind-coherent sheaves on the de Rham space of $\stack X$ \cite{GaitsgoryRozenblyum:2014:CrystalsAndDModules}.
+While the first construction is more \enquote{hands on}, the second construction is often more useful from a theoretical point of view.
+It is explained in detail in the upcoming book \cite{GaitsgoryRozenblyum:prelim:StudyInDAG} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
+Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and unless stated otherwise proofs for the assertions in this section can be found there.
+
+For any morphism $f\colon \stack X → \stack Y$ we obtain a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
+If $p\colon \stack X → \pt$ is the structure map, we set
+\[
+    \GammadR(\stack X,\, {-}) = p_*({-}) \colon \catDMod{\stack X} → \catVect.
+\]
+The functor $\GammadR$ is representable by a D-module $k_{\stack X}$, i.e.
+\[
+    \GammadR(\stack X,\, {-}) = \Hom_{\catDMod{\stack X}}(k_{\stack X},\, {-}).
+\]
+As $\GammadR(\stack X,\, {-})$ is usually not continuous and the object $k_{\stack X}$ is usually not a compact object of $\catDMod{\stack X}$.
+
+Let $Δ\colon \stack X → \stack X × \stack X$ be the diagonal.
+The category $\catDMod{\stack X}$ has a monoidal structure given by the tensor product $\sheaf F \otimes \sheaf G \coloneq Δ^!\bigl( \sheaf F \boxtimes \sheaf G \bigr)$ with unit $ω_{\stack X} = p^!
+k$.
+
+We will be mainly concerned with the subcategory of holonomic D-modules since they enjoy extended functoriality.
+\begin{Def}
+    A $D$-module $\sheaf F ∈ \catDMod{\stack X}$ is called \emph{holonomic} if $f^!\sheaf F$ is holonomic for any smooth morphism $f\colon Z → \stack X$ from a scheme $Z$.
+    The full subcategory of holonomic D-modules will be denoted $\catDModHol{\stack X}$.
+\end{Def}
+
+The following assertions mostly follow from their corresponding counterparts for schemes.
+We refer to \cite{Braverman:LecturesOnAlgebraicDmodules} for proofs in the case of non-smooth schemes.
+
+\begin{Prop}
+    Let $f\colon \stack X → \stack Y$ be a schematic morphism.
+    Then $f^!$ and $f_*$ restrict to functors
+    \[
+        f^!\colon \catDModHol{\stack Y} → \catDModHol{\stack X}
+        \quad\text{and}\quad
+        f_*\colon \catDModHol{\stack X} → \catDModHol{\stack Y}.
+    \]
+\end{Prop}
+
+The Verdier duality functor on schemes induces an involutive anti-auto-equivalence
+\[
+    \dualize_{\stack X}\colon \catDModHol{\stack X}^\mathrm{op} → \catDModHol{\stack X}
+\]
+such that for each smooth morphism $Z → \stack X$ of relative dimension $d$ from a scheme $Z$ one has
+\[
+    f^! ∘ \dualize_{\stack X} \cong \dualize_{Z} ∘ f^![-2d].
+\]
+The Verdier duality functor then allows us to define the \emph{non-standard functors} $f_!$ and $f^*$ for any schematic morphism $f\colon \stack X → \stack Y$ by
+\begin{align*}
+    f^* & = \dualize_{\stack X} ∘ f^! ∘ \dualize_{\stack Y} \colon \catDModHol{\stack Y} → \catDModHol{\stack X} \\
+    \intertext{and}
+    f_! & = \dualize_{\stack Y} ∘ f_* ∘ \dualize_{\stack X} \colon \catDModHol{\stack X} → \catDModHol{\stack Y}.
+\end{align*}
+We obtain adjoint pairs $(f_!,\, f^!)$ and $(f^*,\, f_*)$.
+In some situations we can identify the non-standard functors with their standard counterparts.
+If $f$ is smooth of relative dimension $d$ then $f^* = f^![-2d]$.
+If $f$ is proper then $f_! = f_*$ and in particular $f_*$ is left adjoint to $f^!$.
+The objects $ω_{\stack X}$ and $k_{\stack X}$ are always holonomic and
+\[
+    \dualize_{\stack X} ω_{\stack X} = k_{\stack X}.
+\]
+We have $k_{\stack X} = f^* k_{\stack Y}$ and if $\stack X$ is smooth, then $k_{\stack X} = ω_{\stack X}[-2\dim \stack X]$.
+
+We will make use of the following lemma which follows from \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions}.
+
+\begin{Lem}
+    For a smooth and schematic morphism $f$ the functor $f^!$ is conservative.
+\end{Lem}
+
+\begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
+    \label{prop:pre:base-change}%
+    Consider a Cartesian square
+    \[
+        \begin{tikzcd}
+            \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
+            \stack X₂ \arrow[r, "g"] & \stack Y
+        \end{tikzcd}
+    \]
+    with schematic morphism $f$ (and hence $p$).
+    Then there is a base change isomorphism
+    \[
+        p_* q^! \isoto g^! f_*
+    \]
+    of functors from $\catDMod{\stack{X₁}}$ to $\catDMod{\stack{X₂}}$.
+    If furthermore $f$ (and hence $p$) is proper, then this isomorphism coincides with the natural transformation
+    \[
+        p_* q^! →
+        p_* q^! f^! f_* =
+        p_* p^! g^! f_* →
+        g^! f_*
+    \]
+    induced by $(f_*,\,f^!)$ and $(p_*,\, p^!)$ adjunctions.
+    Similarly, if $f$ is an open immersion, then the base change isomorphism coincides with the natural transformation resulting from the adjunctions $(f^!,f_*)$ and $(p^!, p_*)$.
+\end{Prop}
+
+\begin{Prop}
+    \label{prop:pre:projection-formula}%
+    If $f\colon \stack X → \stack Y$ is a schematic morphism then the projection formula holds, i.e.~there is a functorial isomorphism
+    \[
+        \sheaf F \otimes f_*(\sheaf G) \cong f_*\bigl( f^! \sheaf F \otimes \sheaf G)
+    \]
+    for $\sheaf F ∈ \catDMod{\stack Y}$ and $\sheaf G ∈ \catDMod{\stack X}$.
+\end{Prop}
+
+\begin{Rem}
+    Propositions \ref{prop:pre:base-change} and \ref{prop:pre:projection-formula} hold more generally when $f$ is merely a \enquote{safe} morphism.
+    Alternatively they hold in full generality after replacing $f_*$ by the \enquote{renormalized de Rham pushforward}.
+    We fill not use either notion here and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
+\end{Rem}
+
+For D-modules on stacks we have the usual recollement package.
+Let $i\colon \stack Z \hookrightarrow \stack X$ be a closed embedding and $j\colon \stack U \hookrightarrow \stack X$ the complementary open.
+We have adjoint pairs $(i_*,\, i^!)$ and $(j^!,\, j_*)$.
+
+\begin{Prop}[{\cite[Section~2.5]{GaitsgoryRozenblyum:2014:CrystalsAndDModules}}]
+    \label{prop:recollement-std}%
+    There is an exact triangle of functors
+    \[
+        i_*i^! → \id → j_*j^!
+    \]
+    on $\catDMod{\stack X}$, the adjunction morphisms
+    \[
+        \id → i^!i_*
+        \quad\text{and}\quad
+        j^!j_* → \id
+    \]
+    are isomorphisms, the functors $j^!i_*$ and $i^!j_*$ vanish and $i_*$ and $j_*$ are full embeddings.
+\end{Prop}
+
+On holonomic D-modules we have the additional adjoint pairs $(i^*,\, i_*)$ and $(j_!,\, j^*)$.
+By applying duality to Proposition~\ref{prop:recollement-std} we obtain the distinguished triangle
+\[
+    j_! j^* → \id → i_*i^*
+\]
+and the identity $i^*j_! = 0$ on holonomic D-modules.
+Further, the functor $j_!$ is a full embedding $\catDModHol{\stack U} \hookrightarrow \catDModHol{\stack X}$.
+
+\section{Monads}
+\label{sec:monads}
+
+We will deduce Theorem~\ref{thm:main} from a isomorphism of monads on $\catDMod{\stack X}$.
+In this section we give a short introduction to the theory of monads and the specific constructions that we will use.
+However, in the interest of readability we will mainly do so informally, skipping over the intricacies of $∞$-categories.
+The interested reader can find the correct $∞$-categorical formulations in the given references.
+
+Thus we think of a \emph{monad} on a category $\cat C$ as consisting of a triple $(T, η, μ)$, where $T\colon \cat C → \cat C$ is an endofunctor of $\cat C$, and $η\colon \id_{\cat C} → T$ and $μ\colon T∘T → T$ are natural transformations such that the diagrams
+\begin{equation}
+    \label{eq:pre:monad-identities}
+    \begin{tikzcd}
+        T³ \arrow[r, "Tμ"] \arrow[d, "μT"'] & T² \arrow[d, "μ"] \\
+        T² \arrow[r, "μ"'] & T
+    \end{tikzcd}
+    \quad\text{and}\quad
+    \begin{tikzcd}
+        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
+        T² \arrow[r, "μ"'] & T
+    \end{tikzcd}
+\end{equation}
+commute.
+Alternatively, we can think of $T$ being a monoid in the category of endofunctors of $\cat C$ with the monoidal structure given by composition of endofunctors.
+This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2014-draft:HigherAlgebra}.
+
+Let $X$ be an object of the category $\cat C$.
+Then $T$ gives the dg vector space $\Hom_{\cat C}(X, TX)$ the structure of a dg algebra with multiplication map
+\[
+    (f,g) \mapsto μ_X ∘ Tf ∘ g,
+\]
+\[
+    \begin{tikzcd}
+        X \arrow[r, "g"] & TX \arrow[r, "Tf"] & T²X \arrow[r, "μ_X"] & TX.
+    \end{tikzcd}
+\]
+The identities~\ref{eq:pre:monad-identities} ensure that the algebra is associative and unital.
+
+The most common source of monads is from a pair of adjoint functors $F\colon \cat C \rightleftarrows \cat D \cocolon G$.
+One simply sets $T = G ∘ F$ and $η$ and $μ$ are given by the adjunction morphisms
+\[
+    \id[\cat C] → G ∘ F = T
+    \qquad\text{and}\qquad
+    T² = G ∘ (F ∘ G) ∘ F → G ∘ F = T.
+\]
+We note that the correct construction in more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2014-draft:HigherAlgebra}.
+For any $X ∈ \cat C$ the algebra construction above gives an isomorphism of algebras
+\[
+    \Hom_{\cat C}(X, (GF)(X)) \cong
+    \Hom_{\cat D}(FX, FX).
+\]
+
+Another common way to obtain monads in geometry is via a groupoid.
+Recall that a groupoid $G_{\cx}$ in stacks consists of a stack $\stack G₀$ of \enquote{objects} and a stack $\stack G₁$ of \enquote{morphisms} together with
+\begin{itemize}
+    \item \emph{source} and \emph{target} maps $s,t\colon \stack G₁ \rightrightarrows \stack G₀$,
+    \item a \emph{unit} $e\colon G₀ → G₁$,
+    \item a \emph{multiplication} (or \emph{composition}) map $m\colon \stack G₁ \mathop{×}\limits_{s,\stack G₀,t} \stack G₁ → \stack G₁$,
+    \item an \emph{inverse} map $ι\colon \stack G₁ → \stack G₁$,
+\end{itemize}
+such that
+\begin{itemize}
+    \item $s ∘ e = t ∘ e = \id_{\stack G₀}$,
+    \item $s ∘ m = s ∘ p₂$ and $t ∘ m = t ∘ p₁$ (where $p_i\colon \stack G₁ ×_{s,\stack G₀,t} \stack G₁ → \stack G₁$ are the projection maps).
+    \item $m$ is associative,
+    \item $ι$ interchanges $s$ and $t$ and is an inverse for $m$,
+\end{itemize}
+where all identities have to be understood in the correct $∞$-categorical way \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory}.
+
+\begin{Ex}
+    For our purpose the most important example is the following:
+    Let $f\colon \stack X → \stack S$ be a morphism of stacks.
+    We set $\stack G_0 = \stack X$ and $\stack G₁ = \stack X ×_\stack S \stack X$.
+    The source and target maps are given by $p₁$ and $p₂$, the unit by the diagonal $Δ\colon \stack X → \stack X×_\stack S\stack X$, the inverse by interchanging the factors and multiplication is $p₁₃\colon \stack X ×_\stack S \stack X ×_\stack S \stack X → \stack X×_\stack S\stack X$.
+\end{Ex}
+
+Let us for the moment assume that $s$ (and hence $t$) is proper and schematic.
+In this case the maps $e$ and $m$ are also proper, since $s ∘ e = \id_{\stack G₀}$ and $s ∘ m = s ∘ p₂$ are proper.
+In particular the functors $e^!\colon \catDMod{\stack G₁} → \catDMod{\stack G₀}$ and $m^!\colon \catDMod{\stack G₁} → \catDMod{\stack G₁ ×_{\stack G₀} \stack G₁}$ have left adjoints given by $e_*$ and $m_*$ respectively.
+This allows us to give the endofunctor $T = s_*t^!$ of $\catDMod{\stack G₀}$ the structure of a monad in the following way:
+
+\begin{itemize}
+    \item By $(e_*,e^!)$-adjunction we have a transformation
+        \[
+            \id = (s∘e)_*(t∘e)^! = s_*e_*e^!t^! → s_*t^! = T.
+        \]
+    \item Consider the following commutative diagram
+        \[
+            \begin{tikzcd}[column sep=small]
+                {} & & \stack G₁ \arrow[dddll, bend right, "s"] \arrow[dddrr, bend left, "t"] & & \\
+                & & \stack G₁ ×_{\stack G₀} \stack G₁ \arrow[u, "m"] \arrow[dl, "p₂"] \arrow[dr, "p₁"] & & \\
+                & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & \\
+                \stack G₀ & & \stack G₀ & & \stack G₀
+            \end{tikzcd}
+        \]
+        with Cartesian middle square.
+        Proper base change and $(m_*,m^!)$-adjunction gives a transformation
+        \[
+            T² =
+            s_*t^!s_*t^! =
+            (s∘p₂)_*(t∘p₁)^! =
+            (s∘m)_*(t∘m)^! =
+            s_*m_*m^!t^! →
+            s_*t^! =
+            T.
+        \]
+\end{itemize}
+
+In the non-$∞$-categorical setting one could easily check by hand that this is indeed a monad.
+To obtain the corresponding derived statement one applies an argument similar to \cite[Section~\RomanNum{II}.1.7.2]{GaitsgoryRozenblyum:prelim:StudyInDAG}.
+
+Let now $f\colon \stack X → \stack Y$ be schematic and proper.
+The Cartesian diagram
+\[
+    \begin{tikzcd}
+        \stack X ×_{\stack Y} \stack X \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack X \arrow[d, "f"] \\
+        \stack X \arrow[r, "f"] & \stack Y
+    \end{tikzcd}
+\]
+induces a groupoid with $\stack{G}₀ = \stack X$ and $\stack{G}₁ = \stack X ×_{\stack Y} \stack X$.
+The above constructions now give two monads on $\catDMod{\stack{X}}$: one by $(f_*,f^!)$ adjunction and one from the groupoid structure.
+The base change isomorphism
+\[
+    p_{t,*} p_s^! → f^! f_*
+\]
+gives an identification of these monads and hence of the algebras that they induce, i.e.~for any $\sheaf F ∈ \catDMod{\stack X}$ we have
+\[
+    \Hom(\sheaf F,\, p_{t,*} p_s^!\sheaf F) \cong
+    \Hom(\sheaf F,\, f^! f_* \sheaf F) \cong
+    \Hom(f_*\sheaf F,\, f_* \sheaf F).
+\]
+
+We will need to apply this construction for non-proper $f$.
+Unfortunately, in this case none of the adjunctions used to define the monads are available.
+We rectify this by restricting to the full subcategory of of holonomic D-modules and using the $!$-pushforward functors instead of the $*$-pushforward ones.
+Of course, by doing so we do not automatically have base change isomorphisms available anymore.
+Thus we have to explicitly require the \emph{Beck--Chevalley condition}, saying that all necessary base changes hold.
+
+The Beck--Chevalley condition us formulated using the \emph{nerve} of the groupoid $\stack G_\cx$.
+Intuitively, this is the simplicial stack, usually also denoted $\stack{G}_\cx$, with
+\[
+    \stack G_i = \underbrace{\stack G₁ ×_{\stack G₀} \dotsb ×_{\stack G₀} \stack G₁}_{\text{$i$ factors}}.
+\]
+We refer to \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory} for the correct $∞$-categorical setup.
+The following lemma is now an immediate corollary of \cite[Lemma~\RomanNum{II}.1.7.1.4]{GaitsgoryRozenblyum:prelim:StudyInDAG} or \cite[Theorem~4.7.6.2]{Lurie:2014-draft:HigherAlgebra}.
+
+\begin{Lem}
+    \label{lem:pre:groupoid_monad_hol}%
+    Let $f\colon \stack X → \stack Y$ be a schematic morphism of stacks and let $\stack G_\cx$ be the corresponding groupoid.
+    For each map $F\colon [n] → [m]$ in $\cat{Δ}^{\mathrm{op}}$ consider the corresponding square
+    \[
+        \begin{tikzcd}
+            \stack G_{n+1} \arrow[r, "p_s"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
+            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
+        \end{tikzcd}
+    \]
+    where the vertical arrows are induced by $F$.
+    Assume that for each such square the base change composition
+    \[
+        p_{F+1,!} p_s^! →
+        p_{F+1,!} p_s^! p_F^! p_{F,!} =
+        p_{F+1,!} p_{F+1}^! p_s^!  p_{F,!} →
+        p_s^! p_{F,!}
+    \]
+    given by the adjunction morphisms is an isomorphism of functors from $\catDModHol{\stack G_n}$ to $\catDModHol{\stack G_{m+1}}$.
+    Further assume that the same is true along 
+    \[
+        \begin{tikzcd}
+            \stack G₁ \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack G₀ \arrow[d, "f"] \\
+            \stack G₀ \arrow[r, "f"] & \stack Y
+        \end{tikzcd}
+    \]
+    Then the endofunctor $p_{t,!} p_s^!$ of $\catDModHol{\stack X}$ has a canonical structure of a monad and as such is isomorphic to the adjunction monad $f^!f_!$.
+\end{Lem}
+
+\section{Hochschild cohomology}
+\label{sec:HH}
+
+We recall that the Hochschild cohomology of a dg category $\cat C$ is the algebra of derived endomorphisms of the identity functor,
+\[
+    \HCoh(\cat C) = \mathbb{R}\mathrm{Hom}(\id[\cat C],\, \id[\cat C]).
+\]
+For the exact definition of the category $\mathbb{R}\mathrm{Hom} = \cat{Funct}(\cat C, \cat C)$ we refer to \cite{Keller:2006:OnDGCategories}.
+Instead we will give a more concrete construction via kernels which can be applied to $\catDMod{\stack X}$.
+For this let us restrict to the case of co-complete dg categories and let $\cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)$ be the full subcategory of $\cat{Funct}(\cat C, \cat C)$ spanned by the continuous functors.
+Then, since $\id[\cat C]$ is evidently continuous, we have
+\[
+    \HCoh(\cat C) =
+    \Hom_{\cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)}(\id[\cat C], \id[\cat C]).
+\]
+Let us further assume that $\cat C$ is dualizable with dual $\cat C^\dual$.
+Thus there is a unit map
+\[
+    η\colon \catVect → \cat C^\dual \otimes \cat C
+\]
+and a counit map
+\[
+    ε\colon \cat C^\dual \otimes \cat C → \catVect
+\]
+satisfying the usual compatibilities (cf.~\cite[Section~2]{BenZviNadler:arXiv:NonlinearTraces}).
+Let $u = η(k)$.
+To each continuous endofunctor $F$ of $\cat C$ we can associate its kernel $\id[\cat C^\dual] \otimes F(u) ∈ \cat C^\dual \otimes \cat C$ and conversely to each kernel $Q ∈ \cat C^\dual \otimes \cat C$ we can associate the endofunctor
+\[
+    \cat C
+    \xrightarrow{\id[\cat C] \otimes Q}
+    \cat C \otimes \cat C^\dual \otimes \cat C
+    \xrightarrow{ε \otimes \id[\cat C]}
+    \cat C.
+\]
+These assignments are mutually inverse and give an equivalence of dg categories
+\[
+    \cat{Funct}_{\mathrm{cont}}(\cat C, \cat C)
+    \cong
+    \cat C^\dual \otimes \cat C.
+\]
+In particular, the kernel for the identity is $u$ and hence we have
+\[
+    \HCoh(\cat C) =
+    \Hom_{\cat C^\dual \otimes \cat C}(u, u).
+\]
+Let us now consider the case of $\cat C = \catDMod{\stack X}$ for a stack $\stack X$.
+Let $p\colon \stack X → \pt$ be the structure morphism and $Δ\colon \stack X → \stack X × \stack X$ the diagonal.
+By \cite[Section~8.4]{DrinfeldGaitsgory:2013:FinitenessQuestions} the category $\catDMod{\stack X}$ is dualizable and there is a canonical identification
+\[
+    \catDMod{\stack X}^\dual \otimes \catDMod{\stack X} \cong \catDMod{\stack X × \stack X}
+\]
+such that the unit map is given by $Δ_*p^!$, i.e.~we have
+\[
+    u = Δ_*ω_{\stack X}.
+\]
+We summarize the above discussion in the following lemma.
+
+\begin{Lem}\label{lem:pre:hcoh}
+    Let $\stack X$ be a stack.
+    Then the Hochschild cohomology of $\catDMod{\stack X}$ is given by the dg algebra
+    \[
+        \HCoh(\catDMod{\stack X}) =
+        \Hom_{\catDMod{\stack X × \stack X}}(Δ_*ω_{\stack X},\, Δ_*ω_{\stack X}).
+    \]
+\end{Lem}
+
+Recall now that we assume $Δ$ to be schematic and that the dualizing module $ω_{\stack X}$ is always holonomic.
+Thus we have $\dualize Δ_* ω_{\stack X} = Δ_! k_{\stack X}$.
+With this we observe that
+\begin{align*}
+    \HCoh\bigl(\catDMod{\stack X}\bigr)
+    & = \Hom_{\catDMod{\stack X × \stack X}}(Δ_* ω_{\stack X},\, Δ_* ω_{\stack X}) & &\text{(Lemma~\ref{lem:pre:hcoh})} \\
+    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(Δ_! k_{\stack X},\, Δ_! k_{\stack X})} & & \text{(duality)} \\
+    & = \opalg{\Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^! Δ_! k_{\stack X})} & & \text{(adjunction)} \\
+    & = \opalg{\GammadR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr)},
+\end{align*}
+where the algebra structure on $\GammadR\bigl(\stack X,\, Δ^!
+Δ_!
+k_{\stack X}\bigr) = \Hom_{\catDMod{\stack X × \stack X}}(k_{\stack X},\, Δ^!
+Δ_!
+k_{\stack X})$ is the one induced by the $(Δ_!,Δ^!)$-adjunction monad.
+Consider the Cartesian square
+\[
+    \begin{tikzcd}
+        \ls{\stack X} \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
+        \stack X \arrow[r, "Δ"] & \stack X × \stack X
+    \end{tikzcd}
+\]
+Let us assume for the moment that $Δ$ (and hence $p_i$) is proper.
+Then $Δ_* = Δ_!$ and $p_{1,*} = p_{1,!}$ and by Section~\ref{sec:monads} we have an isomorphism of monads on $\catDModHol{\stack X}$
+\begin{equation}
+    \label{eq:central_iso}
+    p_{1,!} p₂^! → Δ^!Δ_!,
+\end{equation}
+which induces an isomorphism of algebras
+\[
+    \GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)
+    →
+    \GammadR\bigl(\stack X,\, Δ^! Δ_! k_{\stack X}\bigr).
+\]
+Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
+Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{1,!} p₂^!$.
+We would like to apply Lemma~\ref{lem:pre:groupoid_monad_hol} to construct a monad in special cases.
+Thus the goal of the next section is to give a criterion for the assumptions of Lemma~\ref{lem:pre:groupoid_monad_hol}, i.e.~for base change to hold.
+
+\begin{Ex}
+    The base change morphism \eqref{eq:central_iso} is also an isomorphism if $Δ$ is smooth.
+    In particular this implies that the \enquote{naive expectation} holds for $\stack X = \cs{G}$ for any algebraic group $G$, i.e.~we have
+    \[
+        \HCoh(\catDMod{\cs G}) = \opalg{\GammadR\bigl(\cs G,\, p_{1,!} p₂^! k_{\cs G}\bigr)}.
+    \]
+    An argument similar to \cite{BenZvi:mathoverflow:CohomologyOfGmodG} shows that there is a further isomorphism
+    \begin{equation}\label{eq:HH_BG_decomp}
+        \GammadR\bigl(\cs G,\, p_{1,!} p₂^! k_{\stack X}\bigr) \cong
+        \GammadR(G, k_G)^\dual \otimes \GammadR(\cs G, k_{\cs G}).
+    \end{equation}
+    Alternatively, we can use the identification
+    \[
+        \catDMod{\cs G} \cong \catModules{\GammadR(G, k_{G})^\dual},
+    \]
+    where the algebra structure on $\GammadR(G, k_G)^\dual$ is induced by the group multiplication \cite[Section~7.2]{DrinfeldGaitsgory:2013:FinitenessQuestions}.
+    If $G$ is reductive, then $\GammadR(G, k_G)^\dual$ is an exterior algebra and thus its Hochschild cohomology can be computed directly.
+\end{Ex}
+
+From \eqref{eq:HH_BG_decomp} we see that $\HCoh(\catDMod{\cs G})$ contains a copy of $\opalg{\GammadR(\cs G, k_{\cs G})}$.
+Indeed this is a general phenomenon.
+
+\begin{Prop}
+    \label{prop:mono-from-cohomology}%
+    There is a canonical monomorphism 
+    \[
+      \opalg{\GammadR\bigl(\stack X,\, k_{\stack X}\bigr)}
+        \hookrightarrow
+        \HCoh\bigl(\catDMod{\stack X}\bigr).
+    \]
+\end{Prop}
+
+\begin{proof}
+    Consider the sequence of maps
+    \[
+        \stack X \xrightarrow{Δ} \stack X × \stack X \xrightarrow{\proj{1}} \stack X.
+    \]
+    Since the composition is the identity, the functor $(\proj{1})_! ∘ Δ_!$ is faithful.
+    Hence $Δ_!$ is faithful too.
+    Thus the adjunction map
+    \[
+        \eta\colon \id[\catDModHol{\stack X}] → Δ^!Δ_!
+    \]
+    is a monomorphism.
+    Completing to a distinguished triangle
+    \[
+        k_{\stack X} \xrightarrow{\eta} Δ^!Δ_! k_{\stack X} → \sheaf F \xrightarrow{δ}
+    \]
+    for some $\sheaf F \in \catDModHol{\stack X}$, we see that the connection morphism $δ$ is the zero morphism (indeed $\eta \circ \delta[1] = 0$ and $\eta$ is mono).
+    This in turn implies that the induced map
+    \[
+        \GammadR\bigl(\stack X,\, k_{\stack X}\bigr)
+        →
+        \GammadR\bigl(\stack X,\, Δ^!Δ_! k_{\stack X}\bigr)
+        \cong
+        \opalg{\HCoh\bigl(\catDMod{\stack X}\bigr)}
+    \]
+    on cohomology is a monomorphism as well.
+\end{proof}
+
 \section{Base change along the diagonal}
+
+Consider a Cartesian diagram of stacks
+\begin{equation}
+    \label{eq:base-change:square}
+    \begin{tikzcd}
+        \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
+        \stack X₂ \arrow[r, "g"] & \stack Y
+    \end{tikzcd}
+\end{equation}
+with $f$ and $g$ schematic.
+We have a morphism of functors $\catDModHol{\stack X₁} → \catDModHol{\stack X₂}$,
+\begin{equation}
+    \label{eq:base-change-morphism}
+     p_! q^! → g^! f_!
+\end{equation}
+induced by adjunctions
+\begin{equation}
+    \label{eq:base-change-adjunctions}
+    p_! q^! →
+    p_! q^! f^! f_! =
+    p_! p^! g^! f_! →
+    g^! f_!.
+\end{equation}
+If $f$ is proper, then \eqref{eq:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
+
+\subsection{The required base changes}
 
@@
 \begin{proof}
-    Statement \ref{lem:smooth_or_proper:bc} is a direct consquence of the base change theorem [reference].
+    Statement \ref{lem:smooth_or_proper:bc} is a direct consequence of the base change theorem, Proposition~\ref{prop:pre:base-change}.
+    To be more explicit, the smooth version follows from Proposition~\ref{prop:pre:base-change} by duality and the fact that $f^!$ agrees with $f^*$ up to shift.
 
@@
 
+Theorem~\ref{thm:main} is now an immediate consequence of Theorem~\ref{thm:torus_quotient} and Corollary~\ref{cor:properties_imply_monads}
+
+[Put an example here.]
+
+\appendix
+
+\section{Base change and compactification}
+
+Consider a Cartesian diagram of stacks
+\begin{equation}
+    \label{eq:base-change:square}
+    \begin{tikzcd}
+        \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
+        \stack X₂ \arrow[r, "g"] & \stack Y
+    \end{tikzcd}
+\end{equation}
+with $f$ and $g$ schematic.
+We have a morphism of functors $\catDModHol{\stack X₁} → \catDModHol{\stack X₂}$,
+\begin{equation}
+    \label{eq:base-change-morphism}
+     p_! q^! → g^! f_!
+\end{equation}
+induced by adjunctions
+\begin{equation}
+    \label{eq:base-change-adjunctions}
+    p_! q^! →
+    p_! q^! f^! f_! =
+    p_! p^! g^! f_! →
+    g^! f_!.
+\end{equation}
+If $f$ is proper, then \eqref{eq:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
+To understand the behavior for non-proper $f$, we will approximate it by a proper morphism.
+
+\begin{Def}
+    A \emph{relative compactification} of a morphism $f\colon \stack X → \stack Y$ is a commutative diagram
+    \[
+        \begin{tikzcd}
+            \stack X \arrow[r, hook, "j"] \arrow[dr, "f"'] & \bar{\stack X} \arrow[d, "\bar f"] \\
+            & \stack Y
+        \end{tikzcd}
+    \]
+    where $j$ is an open embedding and $\bar f$ is proper.
+\end{Def}
+
+A famous example of such a relative compactification is Drinfeld's compactification of the morphism $\Bun_B → \Bun_G$, where $\Bun_G$ is the stack of $G$-bundles on a curve $C$ with $G$ reductive and $B$ is a Borel subgroup of $G$ \cite{BravermanGaitsgory:2002:GeometricEisensteinSeries}.
+
+Let us now assume that in the situation of diagram \eqref{eq:base-change:square} there exists a relative compactification of $f\colon \stack X₁ → \stack Y$.
+Let $\stack X₁^c$ be the closed complement of the open inclusion $j\colon \stack X₁ \hookrightarrow \bar{\stack X}₁$.
+Similarly, we denote by $\bar{\stack Z} = \stack X₂ ×_{\stack Y} \bar{\stack X}₁$ and $\stack Z^c = \stack X₂ ×_{\stack Y} \stack X₁^c$ the corresponding fiber products.
+The corresponding inclusion and projection maps are denoted as is indicated in the following Cartesian diagrams.
+\[
+    \begin{tikzcd}
+        \bar{\stack Z} \arrow[d, "\bar p"] \arrow[r, "\bar q"] & \bar{\stack X}₁ \arrow[d, "\bar f"] \\
+        \stack X₂ \arrow[r, "g"] & \stack Y
+    \end{tikzcd}
+    \qquad\qquad
+    \begin{tikzcd}
+        \stack Z^c \arrow[r, hook, "i"] \arrow[d] & \bar{\stack Z} \arrow[d, "\bar q"] \\
+        \stack X₁^c \arrow[r, hook] & \bar{\stack X}₁
+    \end{tikzcd}
+\]
+We note that $\bar{\stack Z}$ is the disjoint union of the closed substack $\stack Z^c$ and the open substack $\stack Z$.
+We can now quantify the failure of the base change morphism to be an isomorphism.
+
+\begin{Lem}
+    \label{lem:base-change-criterion}%
+    In the situation of the Cartesian square \eqref{eq:base-change:square}, the cone of the base change morphism $p_! q^! → g^! f_!$ is given by
+    \[
+        \bar p_! i_*i^* \bar{q}^! j_!.
+    \]
+    In particular, if $i^* \bar{q}^! j_! = 0$, then $p_! q^! \cong g^! f_!$ is an isomorphism of functors.
+\end{Lem}
+
+\begin{proof}
+    Let $\tilde\jmath\colon \stack Z \hookrightarrow \bar{\stack Z}$ be the open inclusion complement to $i$.
+    We split the adjunctions in \eqref{eq:base-change-adjunctions} in two by using the compositions
+    \[
+        f = \bar f ∘ j
+        ,\quad
+        p = \bar p ∘ \tilde\jmath
+        \quad\text{and}\quad
+        q = \bar q ∘ \tilde\jmath.
+    \]
+    Thus the adjunction $p_!q^!→ p_!q^!f^!f_!$ becomes the sequence
+    \[
+        p_!q^! →
+        p_!q^! j^! j_! →
+        p_!q^! j^! \bar f^! \bar f_! j_!.
+    \]
+    The equality $p_! q^! f^! f_! = p_! p^! g^! f_!$ becomes
+    \[
+        p_! q^! j^! \bar f^! \bar f_! j_! =
+        p_! \tilde\jmath^! \bar q^! \bar f^! \bar f_! j_! =
+        p_! \tilde\jmath^! \bar p^! g^! \bar f_! j_!.
+    \]
+    Finally the adjunction $p_! p^! g^! f_! → g^! f_!$ becomes
+    \[
+        p_! \tilde\jmath^! \bar p^! g^! \bar f_! j_! =
+        \bar p_! \tilde\jmath_! \tilde\jmath^! \bar p^! g^! \bar f_! j_! →
+        \bar p_! \bar p^! g^! \bar f_! j_! →
+        g^! \bar f_! j_! =
+        g^! f_!.
+    \]
+    Let us apply the same adjunction morphisms in a different order.
+    First the recollement adjunctions
+    \[
+        p_!q^!
+        \xrightarrow{α}
+        p_!q^! j^! j_!
+        =
+        \bar p_! \tilde\jmath_! \tilde\jmath^! \bar q^! j_!
+        \xrightarrow{β}
+        \bar p_! \bar q^! j_!,
+    \]
+    and then the actual base change
+    \begin{equation}
+        \label{eq:lem:base-change-criterion:pf:split_morphism_base_change}
+        \bar p_! \bar q^! j_!
+        →
+        \bar p_! \bar q^! \bar f^! \bar f_! j_!
+        =
+        \bar p_! \bar p^! g^! \bar f_! j_!
+        →
+        g^! \bar f_! j_!
+        =
+        g^! f_!.
+    \end{equation}
+    We note that the adjunction $α\colon \id → j^!j_!$ is an isomorphism and the maps in \eqref{eq:lem:base-change-criterion:pf:split_morphism_base_change} compose exactly to the isomorphism of proper base change (cf.~Proposition~\ref{prop:pre:base-change}).
+    Thus the cone of the whole composition is the same as the cone of the morphism $β$, which is given by the recollement triangle
+    \[
+        \bar p_! \tilde\jmath_! \tilde\jmath^! \bar q^! j_!
+        \xrightarrow{β}
+        \bar p_! \bar q^! j_!
+        \xrightarrow{\phantom{β}}
+        \bar p_! i_* i^* \bar q^! j_!
+        \xrightarrow{+1}.
+        \qedhere
+    \]
+\end{proof}
+
+\subsection{Relative compactifications for quotient stacks}
+\label{sec:base-change:compactification}%
+
+In the preceding section we simply assumed that a relative compactification of the given map exists.
+We will now construct such a compactification for the diagonal map of a quotient stack.
+Thus let $X$ be a scheme of finite type over $k$ and let $G$ be an affine algebraic group over $k$ acting on $X$.
+Let $\stack X = X/G$ be the corresponding quotient stack.
+
+Constructing a relative compactification of $Δ\colon \stack X → \stack X × \stack X$ is the same as first constructing a $G × G$-equivariant relative compactification of $(\proj2, a)\colon G × X → X × X$ (where $a\colon G × X → X$ is the action map) and then taking the quotient by the $G × G$ action\footnote{%
+    Here $G × G$ acts on $G × X$ by $(s₁,s₂) \cdot (g,x) = (s₂gs₁^{-1},\, s₁x)$.
+}.
+We let
+\[
+    Γ = \bigl\{(g, x, x, gx) ∈ G × X × X × X\bigr\}
+\]
+be the graph of $(\proj2, a)$.
+
+We pick a $G×G$-equivariant compactification $\bar G$ of $G$ and let $\bar Γ$ be the closure of $Γ$ in $\bar G × X × X × X$.
+We have an open embedding $j$ of $G × X \cong Γ$ into $\bar Γ$ and proper map $f\colon \bar Γ → X × X$ given by projection on the last two factors.
+The composition $f ∘ j$ is equal to $(\proj2, a)$.
+
+Instead of viewing $Γ$ as the graph of $(\proj2, a)$ we can drop the third factor and regard $Γ$ as the graph of the action map, i.e.
+\[
+    \Gammasub{a} = \bigl\{(g, x, gx) ∈ G × X × X\bigr\}.
+\]
+The closure $\barGammasub{a}$ of $\Gammasub a$ in $\bar G × X × X$ identifies with $\bar Γ$.
+Thus for ease of notation we will from now on always set $Γ = \Gammasub a$ and $\bar Γ = \barGammasub{a}$.
+
+\begin{Def}
+    Let $\stack X = X/G$.
+    With the above construction we set
+    \[
+        \bar{\stack X} = \rquot{\bar Γ}{G×G}.
+    \]
+    We have an open embedding $j\colon X \hookrightarrow \bar{\stack X}$ and a proper morphism $\shortbar Δ\colon \bar{\stack X} → \stack X × \stack X$ induced by the map $f$ above, such that $Δ = \shortbar Δ ∘ j$.
+\end{Def}
+
+\begin{Rem}
+    In the case of $G = \Gm$ the compactification $\bar Γ$ is explicitly described in \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
+    In particular, if $X$ is smooth it is shown there that $\bar Γ$ is smooth over $\bar G = \ps1$.
+    It is possible to extend the methods of \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden} to quotients by higher dimensional tori.
+    The resulting constructions are useful for doing explicit computations.
+\end{Rem}
+
+\subsection{The !-base-change property}
+
+Let $\stack Y$ be a stack over $\stack X$.
+To simplify notation, we set
+\[
+    \lsY = \stack Y \XXtimes \stack X,
+\]
+where the fiber product is taken over the maps $\stack Y → \stack X \xrightarrow{Δ} \stack X × \stack X$ and $Δ$.
+Further if $f\colon \stack Y₂ → \stack Y₁$ is a morphism of stacks over $\stack X$ we write $\ls f$ for the induced morphism $\lsY[\stack Y₂]{\stack X} → \lsY[\stack Y₁]{\stack X}$.
+
+\begin{Def}\label{def:good}
+    We say that a quotient stack $\stack X = X/G$ \emph{\isgood} if the following two conditions hold.
+    \begin{enumerate}
+        \item $!$-base-change holds along the Cartesian square
+            \[
+                \begin{tikzcd}
+                    \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
+                    \stack X \arrow[r, "Δ"] & \stack X × \stack X
+                \end{tikzcd}
+            \]
+            i.e.~the canonical morphism $p_{1,!}p₂^! → Δ^!Δ_!$ is an isomorphism on holonomic D-modules.
+        \item For any schematic morphism $f\colon \stack Y₂ = Y₂/G → \stack Y₁ = Y₁/G$ of $G$-quotient stacks over $\stack X$, $!$-base-change holds along the Cartesian diagram
+            \[
+                \begin{tikzcd}
+                    \lsY[\stack Y₂]{\stack X} \arrow[r, "\ls f"] \arrow[d, "π₂"] & \lsY[\stack Y₁]{\stack X} \arrow[d, "π₁"]\\
+                    \stack Y₂ \arrow[r, "f"] & \stack Y₁
+                \end{tikzcd}
+            \]
+            i.e.~the canonical morphism $π_{2,!}(\ls f)^! → f^! π_{1,!}$ is an isomorphism on holonomic D-modules.
+    \end{enumerate}
+\end{Def}
+
+We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ \isgood.
+Theorem~\ref{thm:main} then immediately follows from the following observation which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodX{quotient stacks}.
+
+\begin{Prop}\label{prop:good-is-good}
+    If $\stack X = X/G$ \isgood, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
+    In particular there is an isomorphism of algebras
+    \[
+        \HCoh\bigl(\catDMod{\stack X}\bigr)
+        \cong
+        \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
+    \]
+\end{Prop}
+
+\begin{proof}
+    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid induced by $Δ\colon \stack X → \stack X × \stack X$.
+    Thus we let $\stack G_\cx$ be the simplicial stack with
+    \[
+        \stack G_i = \underbrace{\stack X \mathop{×}\limits_{\stack X × \stack X} \dotsb \mathop{×}\limits_{\stack X × \stack X} \stack X}_{\text{$i+1$ factors}}.
+    \]
+    The second base change condition of Lemma~\ref{lem:pre:groupoid_monad_hol} holds by definition.
+    Let $F\colon [n] → [m]$ be a morphism in $\cat{Δ}^{\mathrm{op}}$ and consider the induced diagram
+    \[
+        \begin{tikzcd}
+            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
+            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
+        \end{tikzcd}
+    \]
+    We note that $\stack G_{m+1} = \stack G_m ×_{\stack X × \stack X} \stack X$ and similarly for $\stack G_n$.
+    Thus setting $\stack Y₂ = \stack G_n$ and $\stack Y₁ = \stack G_m$ in the definition of \goodness, we see that all the required base changes holds.
+\end{proof}
+
+\begin{Rem}
+    We expect that most quotient stacks \arenotgood.
+    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it \isnotgood.
+\end{Rem}
+
+We will use Lemma~\ref{lem:base-change-criterion} in order to check the base change criteria in Definition~\ref{def:good}.
+In order to do so we unfortunately have to introduce some additional notation.
+Let us fix a compactification $\bar G$ of $G$ and a relative compactification $\stack X \xrightarrow{j} \bar{\stack X} \xrightarrow{\bar Δ} \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
+For any $\stack Y → \stack X$ this induces a relative compactification $\clsY{\stack X} = \stack Y \XXtimes \bar{\stack X}$.
+Let us write $j_{\stack Y}\colon \lsY{\stack X} \hookrightarrow \clsY{\stack X}$ for the open inclusion and $i_{\stack Y}\colon \lscY{\stack X} = \stack Y \XXtimes \stack X^c → \clsY{\stack X}$ for the complement.
+Thus we have the following two diagrams with Cartesian squares which are central to the remainder of this paper.
+The first describes the situation for a loop stack:
+\begin{equation}\label{eq:diag:central1}
+    \begin{tikzcd}
+        \ls\stack X \arrow[r, "j_{\stack X}", hook] \arrow[d, "p₂"] & \cls\stack X \arrow[d, "\bar p₂"] & \lsc\stack X \arrow[l, hook', "i_{\stack X}"']  \arrow[d] \\
+        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
+    \end{tikzcd}
+\end{equation}
+
 \printbibliography

### 2017-10-06 rewrite.tex
Update some references.

@@
 
-\begin{Prop}[{\cite[\RomanNum{III}.4.2.1.3]{GaitsgoryRozenblyum:prelim:StudyInDAG}}]
+\begin{Prop}[{\cite[Section~4.2.1.3]{GaitsgoryRozenblyum:2017:StudyInDAG:2}}]
     \label{prop:pre:base-change}%
@@
 In the non-$∞$-categorical setting one could easily check by hand that this is indeed a monad.
-To obtain the corresponding derived statement one applies an argument similar to \cite[Section~\RomanNum{II}.1.7.2]{GaitsgoryRozenblyum:prelim:StudyInDAG}.
+To obtain the corresponding derived statement one applies an argument similar to \cite[Section~4.7.2]{GaitsgoryRozenblyum:2017:StudyInDAG:1}.
 
@@
 We refer to \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory} for the correct $∞$-categorical setup.
-The following lemma is now an immediate corollary of \cite[Lemma~\RomanNum{II}.1.7.1.4]{GaitsgoryRozenblyum:prelim:StudyInDAG} or \cite[Theorem~4.7.6.2]{Lurie:2014-draft:HigherAlgebra}.
+The following lemma is now an immediate corollary of \cite[Lemma~4.7.1.4]{GaitsgoryRozenblyum:2017:StudyInDAG:2} or \cite[Theorem~4.7.6.2]{Lurie:2014-draft:HigherAlgebra}.
 
@@
 
-\begin{Thm}
+\begin{Thm}\label{thm:torus_quotient}
     Let $X$ be a normal variety with an action of a torus $T$.

### 2017-10-10 rewrite.tex
Cleaning up the first half.

@@
 \begin{abstract}
-    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
-    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
+  We discuss the Hochschild cohomology of the category of D-modules associated to an algebraic.
+  In particular we describe the Hochschild cohomology of the category of torus-equivariant D-modules as the cohomology of a D-module on the loop space of the quotient stack.
+  Finally, we give an approach for understanding the Hochschild cohomology of D-modules on general stacks via a relative compactification of the diagonal.
   This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of D-modules on stacks.
@@
 Even more generally one can ask the following question: Given a $k$-linear category $\cat C$, can one find a space over which $\cat C$ localizes?
-For co-complete compactly generated triangulated categories one answer is provided by \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
+For co-complete compactly generated triangulated categories one answer is provided by Benson, Iyengar and Krause \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
 To each map from a graded-commutative ring $R$ to the center of $\cat C$ the authors associate the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
-This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves).
+This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves mentioned above).
 
@@
 
-This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
+This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced by Arinkin and Gaitsgory \cite{ArinkinGaitsgory:2015:SingularSupport}.
 More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
@@
 where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
-In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de Rham cohomology of $\stack X$.
+In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de~Rham cohomology of $\stack X$.
 However, if $\stack X$ is a general stack, then $Δ$ is not proper and the situation becomes more complicated.
@@
 
-In this paper we investigate how to quantify the cone of the morphism
+In this paper we investigate how the morphism
 \begin{equation}\label{eq:intro:central_cone}
@@
 \end{equation}
-and thus the failure of the naive isomorphism \eqref{eq:intro:naive} to hold.
+and thus when the naive isomorphism \eqref{eq:intro:naive} holds.
 As an application, we prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.
@@
 \end{Thm}
+
+\subsection*{Contents}
 
@@
 In Section~\ref{sec:HH} we explain how morphism~\eqref{eq:intro:central_cone} arises as a morphism of monads and make precise its relationship with Hochschild cohomology of $\catDMod{\stack X}$.
-
-In Section~\ref{sec:base-change} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.
-Finally, in Section~\ref{sec:torus} we deduce Theorem~\ref{thm:main} from this description, using geometric considerations and the contraction principle of Drinfeld--Gaitsgory \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
+As a simple application of this formalism, we also show that $\HCoh{\catDMod{\stack X}}$ always has a subalgebra isomorphic to $\opalg{\GammadR(\stack X,\ k_{\stack X})}$.
+
+In Section~\ref{sec:base-change} we give criteria for morphism~\eqref{eq:intro:central_cone} to be an isomorphism.
+In particular, we will use the contraction principle of Drinfeld--Gaitsgory \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}\remark{Better reference?}\ to understand the case of so-called contractive stacks.
+Using the theory developed in Section~\ref{sec:base-change}, the proof of Theorem~\ref{thm:main} is given in Section~\ref{sec:torus}.
+
+Finally, in Section~\ref{sec:compactification} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.
+
+\subsection*{Future directions}
 
@@
 Of particular interest are quotients stacks $X/G$ with $G$ an affine algebraic group and the stack $\Bun_G(C)$ of $G$-bundles on a curve $C$.
-Following the constructions laid out in Section~\ref{sec:base-change:compactification}, for the former we need a good $G×G$-equivariant compactification of $G$.
+Following the constructions laid out in Section~\ref{sec:compactification:quotient}, for the former we need a good $G×G$-equivariant compactification of $G$.
 Thus groups with a wonderful compactification are of particular interest for study with our methods.
@@
 
-\section{D-modules on stacks}
-\label{sec:d-mods}
+\section{D-modules on stacks}\label{sec:d-mods}
 
@@
 We refer to \cite{Keller:2006:OnDGCategories} for an introduction to dg categories.
-It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2014-draft:HigherAlgebra}, which can be done via the nerve construction.% \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}.
+It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2017-draft:HigherAlgebra}, which can be done via the nerve construction.
+% \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}.
 %\cite[Section~1.3.1]{Lurie:2014-draft:HigherAlgebra}
-We will switch between those two languages without explicitly mentioning the intervening constructions and apply results from \cite{Lurie:2014-draft:HigherAlgebra} to dg categories.
+We will switch between those two languages without explicitly mentioning the intervening constructions and apply results from \cite{Lurie:2017-draft:HigherAlgebra} to dg categories.
 Fortunately, a superficial knowledge of dg/$∞$-categories should be sufficient for reading this article.
@@
 While the first construction is more \enquote{hands on}, the second construction is often more useful from a theoretical point of view.
-It is explained in detail in the upcoming book \cite{GaitsgoryRozenblyum:prelim:StudyInDAG} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
+It is explained in detail in the book \cite{GaitsgoryRozenblyum:2017:StudyInDAG:2} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
 Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and unless stated otherwise proofs for the assertions in this section can be found there.
@@
     \]
-    with schematic morphism $f$ (and hence $p$).
+    with schematic morphism $f$ (and hence also schematic $p$).
     Then there is a base change isomorphism
@@
 
-\section{Monads}
-\label{sec:monads}
+\section{Monads}\label{sec:monads}
 
@@
 Alternatively, we can think of $T$ being a monoid in the category of endofunctors of $\cat C$ with the monoidal structure given by composition of endofunctors.
-This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2014-draft:HigherAlgebra}.
+This definition also gives the correct generalization to $∞$-categories \cite[Definition~4.7.0.1]{Lurie:2017-draft:HigherAlgebra}.
 
@@
 \]
-We note that the correct construction in more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2014-draft:HigherAlgebra}.
+We note that the correct construction in more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2017-draft:HigherAlgebra}.
 For any $X ∈ \cat C$ the algebra construction above gives an isomorphism of algebras
@@
 We refer to \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory} for the correct $∞$-categorical setup.
-The following lemma is now an immediate corollary of \cite[Lemma~4.7.1.4]{GaitsgoryRozenblyum:2017:StudyInDAG:2} or \cite[Theorem~4.7.6.2]{Lurie:2014-draft:HigherAlgebra}.
+The following lemma is now an immediate corollary of \cite[Lemma~4.7.1.4]{GaitsgoryRozenblyum:2017:StudyInDAG:2} or \cite[Theorem~4.7.5.2]{Lurie:2017-draft:HigherAlgebra}.
 
@@
 
-\section{Hochschild cohomology}
-\label{sec:HH}
+\section{Hochschild cohomology and kernels}\label{sec:HH}
 
@@
 
-\section{Base change along the diagonal}
+\section{Base change along the diagonal}\label{sec:base-change}
 
@@
 \begin{proof}
-    This is just a restatement of Lemma~\ref{lem:pre:groupoid_monad_hol} together with ?.
+  This is just a restatement of Lemma~\ref{lem:pre:groupoid_monad_hol} applied to the construction in Section~\ref{sec:HH}.
 \end{proof}
@@
 Let $i\colon\stack Y \to \stack X$ be an open (or closed) immersion.
-We have $\ls Y \cong \stack Y \times_{\stack X \times \stack X} \stack Y$ and it follows that there is a canonical open (resp.~closed) immersion of loop stacks $\ls i\colon \ls \stack Y \to \ls \stack X$.
-
-More generally, $\stack G_m(\stack Y)$ is an open (resp.~closed) substack of $\stack G_m(\stack X)$.
-Absuing notation, we will sometimes continue to denote this inclusion by $i$.
+We have $\ls \stack Y \cong \stack Y \times_{\stack X \times \stack X} \stack Y$ and it follows that there is a canonical open (resp.~closed) immersion of loop stacks $\ls i\colon \ls \stack Y \to \ls \stack X$.
+
+More generally, each $\stack G_m(\stack Y)$ is an open (resp.~closed) substack of $\stack G_m(\stack X)$.
+Abusing notation, we will sometimes continue to denote this inclusion by $i$.
 %In the special case $m=1$, we will also write $\ls i\colon \ls \stack Y \to \ls \stack X$.
@@
     Let $i\colon\stack Y \hookrightarrow \stack X$ is a locally closed immersion of QCA stacks.
-    If $\stack X$ has property \bc\ (resp.~property \hbc), then so does $\stack Y$.
+    If $\stack X$ has property \bc\ or property \hbc, then so does $\stack Y$.
 \end{Lem}
@@
     Now, using the assumption on $\stack X$ and the fact that $i^! = i^*$ we get
-    \[
+    \begin{multline*}
         p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
         p_{\stack Y,1,!} (\ls i)^! p_{\stack X,2}^! \cong
-        i^! p_{\stack X,1,!} p_{\stack X,2}^! \isoto
+        i^! p_{\stack X,1,!} p_{\stack X,2}^! \isoto \\
         i^! \Delta_{\stack X}^! \Delta_{\stack X,!} =
@@
         \Delta_{\stack Y}^! \Delta_{\stack X,!} i^!.
-    \]
+    \end{multline*}
     Now let $i$ be a closed immersion.
@@
     Now, using the assumption on $\stack X$ and the fact that $i_! = i_*$ we get
-    \[
+    \begin{multline*}
         i_! p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
         p_{\stack X,1,!} (\ls i)_! p_{\stack Y,2}^!i^! \cong
-        p_{\stack X,1,!} p_{\stack X,2}^! i_!i^! \isoto
+        p_{\stack X,1,!} p_{\stack X,2}^! i_!i^! \isoto \\
         \Delta_{\stack X}^! \Delta_{\stack X,!} i_!i^! \cong
@@
         \qedhere
-    \]
+    \end{multline*}
 \end{proof}
@@
 \begin{Lem}\label{lem:open_cover}
-    If $\stack X$ has an open cover by substacks $\stack U_i$ with property \bc\ (resp.~with property \hbc), then $\stack X$ has property \bc\ (resp.~property \hbc).
+    If $\stack X$ has an cover by open substacks $\stack U_i$ with property \bc\ (resp.~with property \hbc), then $\stack X$ has property \bc\ (resp.~property \hbc).
 \end{Lem}
@@
 Let $\stack X$ be a QCA stack with an action of $\Gm$.
-We call the action \emph{contractive} if it can be extended to an action of the monoid $\as 1$.
-Following the convention of \cite[Appendix~C]{DrinfeldGaitsgory:arXiv:CompactGenerationOfDModOnBunG} we denote by $\stack X^0$ the stack of $\{0,1\}$-equivariant maps $\{0\} \to \stack X$.
+We call the action \emph{(globally) contractive} if it can be extended to an action of the monoid $\as 1$.
+Following the convention of \cite[Appendix~C]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} we denote by $\stack X^0$ the stack of $\{0,1\}$-equivariant maps $\{0\} \to \stack X$.
 The map $\{0\} \to \{0,1\}$ induces a \emph{contraction morphism} $\pi\colon \stack X \to \stack X^0$.
@@
 
-\begin{Thm}[{\cite[Corollary~C.5.4]{DrinfeldGaitsgory:arXiv:CompactGenerationOfDModOnBunG}}]
+\begin{Thm}[{\cite[Corollary~C.5.4]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}}]
     \label{thm:contraction_principle}%
-    Let $X$ be a scheme with a trivial contractive $\Gm$-action.
+    Let $\stack X$ be a contractive stack with a trivial $\Gm$-action.
     Then there is a canonical isomorphism of functors
@@
 \end{Thm}
+
+\begin{Rem}
+  For our intended application in the proof of Theorem~\ref{thm:torus_quotient}, the special case of this statement for $\Gm$-quotient stacks is sufficient.
+  In this case the statement can be proved directly without having to show the full \enquote{stacky} version, cf.~\cite[Proposition~5.3.2]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}.
+\end{Rem}
 
@@
 
-\section{Torus quotients}
+\section{Torus quotients}\label{sec:torus}
 
@@
 
-\appendix
-
-\section{Base change and compactification}
+\section{Base change and compactification}\label{sec:compactification}
 
@@
 
-\subsection{Relative compactifications for quotient stacks}
-\label{sec:base-change:compactification}%
+\subsection{Relative compactifications for quotient stacks}\label{sec:compactification:quotient}%
 

### 2017-10-10 rewrite.tex
Fiber products, part 1

@@
 \newcommand\hbc{\textbf{($\mathbf{**}$)}}
+
+\newcommand\catK[2][]{\cat{K}_{#1}(#2)}
+\newcommand\catKHol[1]{\catK[\mathrm{hol}]{#1}}
 
@@
 
+In order for the isomorphism \eqref{eq:intro:naive} to hold, we only need know that the base change morphism is an isomorphism on $k_{\stack X}$.
+However, it is often useful to pass to substacks, so that we need to prove the isomorphism of a slightly larger class of D-modules.
+Thus we introduce the following subcategories.
+
+\begin{Def}
+  Let $\catK{\stack X}$ be the full subcategory of $\catDMod{\stack X}$ generated by $k_{\stack X}$ and let $\catKHol{\stack X}$ be its full subcategory consisting of holonomic objects.
+\end{Def}
+
+With this we can write down the two properties that we need to check in order to get a good
+
 \begin{Def}
@@
     \]
-    of endofunctors of $\catDModHol{\stack X}$ is an equivalence.
+    of functors $\catKHol{\stack X} \to \catDModHol{\stack X}$ is an equivalence.
 \end{Def}
@@
     \]
-    of functors $\catDModHol{\stack G_n} \to \catDModHol{\stack G_{m+1}}$ is an equivalence.
+    of functors $\catKHol{\stack G_n} \to \catDModHol{\stack G_{m+1}}$ is an equivalence.
 \end{Def}
@@
 \begin{Cor}\label{cor:properties_imply_monads}
+  \remark{This needs to be fixed as we don't have endofunctors anymore.}
     If $\stack X$ has properties \bc\ and \hbc, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
@@
     We will show the statement for property \bc.
-    The proof for \hbc\ is essentally the same.
+    The proof for \hbc\ is essentially the same.
+    First we note that if $\sheaf F \in \catKHol{\stack Y}$, then $i_*\sheaf F \in \catKHol{\stack X}$ since
+    \[
+      \Hom_{\catDMod{\stack X}}(k_{\stack X}, i_*\sheaf F) \cong
+      \Hom_{\catDMod{\stack Y}}(i^*k_{\stack X}, \sheaf F) \cong
+      \Hom_{\catDMod{\stack Y}}(k_{\stack Y}, \sheaf F) \ncong 0.
+    \]
+    Thus it suffices to show that $p_{\stack Y,1,!}p_{\stack Y,2}^!i^! \to \Delta_{\stack Y}^!\Delta_{\stack Y,!}i^!$ is an isomorphism of $\catKHol{\stack X}$.
+    We split $i$ into a closed immersion followed by an open one and prove the two cases separately.
+
     Let us first assume that $i$ is open.
-    It suffices to show that $p_{\stack Y,1,!}p_{\stack Y,2}^!i^! \to \Delta_{\stack Y}^!\Delta_{\stack Y,!}i^!$ is an equivalence.
     Now, using the assumption on $\stack X$ and the fact that $i^! = i^*$ we get
@@
     If $\stack X$ has an cover by open substacks $\stack U_i$ with property \bc\ (resp.~with property \hbc), then $\stack X$ has property \bc\ (resp.~property \hbc).
+    \qed
 \end{Lem}
@@
     For any schematic morphism $f\colon \stack Y \to \stack Z$ of QCA stacks the functor $f^!$ is continuous on $\catDMod{\stack Z}$ and $f_!$ is preservers colimits in $\catDModHol{\stack Y}$, since it has a right adjoint.
-    Since the inclusion of a full subcategory reflects all colimits it is thus sufficient to check that the properties holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catDModHol{\stack X_1 \times \stack X_2}$.
+    Since the inclusion of a full subcategory reflects all colimits it is thus sufficient to check that the properties holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catKHol{\stack X_1 \times \stack X_2}$.
 
@@
     The statement now follows because all functors respect $\boxtimes$.
+\end{proof}
+
+We would like to have an extension of Lemma~\ref{lem:product} to fiber products.
+Unfortunately, as the discussion on \cite[Section~1.2]{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup} shows, the category of D-modules on a fiber product $\stack X_1 \times_{\stack Y} \stack X_2$ is rather badly behaved unless $\stack Y$ is a scheme.
+Thus we have to restrict ourselves to the following partial result which is sufficient for our applications.
+
+\begin{Lem}\label{lem:product_quotient}
+  Let $G$ be an affine algebraic group acting on schemes $X_1$ and $X_2$.
+  Suppose the quotient stacks $\stack X_1 = X_1/G$ and $\stack X_2 = X_2/G$ both have property \bc\ (resp.~property \hbc).
+  Then so does $(X_1 \times X_2)/G$.
+\end{Lem}
+
+\begin{proof}
+  The stack $(X_1 \times X_2)/G$ can be rewritten as $\stack X_1 \times_{\cs{G}} \stack X_2$.
+  Thus the results of \cite[Section~5.2]{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup} show that $!$-pullback exhibits the category $\catDMod{\stack X_1} \otimes_{\catDMod{\cs{G}}} \catDMod{\stack X_2}$ as a full subcategory of $\catDMod{\stack X_1 \times_{\cs{G}} \stack X_2}$ containing $\catK{\stack X_1 \times_{\cs{G}} \stack X_2}$.
+  This category can be described as the limit of the cosimplicial category with cosimplices
+  \[
+    \catDMod{\stack X_1 \times \cs{G} \times \dotsb \times \cs{G} \times \stack X_2}.
+  \]
+  Thus it suffices to show the properties for the stacks $\stack X_1 \times \cs{G} \times \dotsb \times \cs{G} \times \stack X_2$, where they follow form Lemmas~\ref{lem:product} and~\ref{lem:smooth_or_proper}\ref{lem:smooth_or_proper:bg}.
 \end{proof}
@@
 \begin{proof}
-    By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions} and Lemma~\ref{lem:open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
+  By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions}\remark{exact reference?} and Lemma~\ref{lem:open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
   By Lemma~\ref{lem:lc_immersion} it further suffices to consider the case that $\stack X = \as{m}/T$ for some $n$.
-    By Lemma~\ref{lem:product}, we can further decompose $\as{m}$ into $T$-eigenspaces.
-    Each of those splits into copies of $\as{1}/T \cong \as{1}/\Gm \times BT'$.
-
-    By Lemma~\ref{lem:smooth_or_proper} it remains to consider the stack $\as{1}/\Gm$, where $\Gm$ acts nontrivially.
+  By Lemma~\ref{lem:product_quotient}, we can further decompose $\as{m}$ into $T$-eigenspaces.
+  Each of those splits into copies of $\as{1}/T$, which in turn can be written as $\as{1}/\Gm \times BT'$ for some subtorus $T'$ of $T$.
+
+  By Lemma~\ref{lem:smooth_or_proper}\ref{lem:smooth_or_proper:bg} it remains to consider the stack $\as{1}/\Gm$, where $\Gm$ acts nontrivially.
   If the $\Gm$ action is contractive this case follows immediately from Proposition~\ref{prop:contractive} and Lemma~\ref{lem:smooth_or_proper}.

### 2017-10-10 rewrite.tex
Fiber products, part 2

@@
 \begin{Cor}\label{cor:properties_imply_monads}
-  \remark{This needs to be fixed as we don't have endofunctors anymore.}
   If $\stack X$ has properties \bc\ and \hbc, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
@@
 \begin{proof}
-  This is just a restatement of Lemma~\ref{lem:pre:groupoid_monad_hol} applied to the construction in Section~\ref{sec:HH}.
+  Since $\Hom(k_{\stack X},\, \Delta^!\Delta_!k_{\stack x}) = \Hom(\Delta_!k_{\stack X},\, \Delta_!k_{\stack X}) \ne 0$, we see that $\Delta^!\Delta_!$ restricts to a monad on $\catKHol{\stack X}$.
+  Thus by the assumption $p_{1,!} p_2^!$ is also an endofunctor of $\catKHol{\stack X}$.
+  The statement now follows from a restriction of Lemma~\ref{lem:pre:groupoid_monad_hol} applied to the construction in Section~\ref{sec:HH}.
 \end{proof}

### 2017-10-10 rewrite.tex
Example.

@@
     Let $X$ be a normal variety with an action of a torus $T$.
-    Then $\stack X = X/T$ has properties \bc\ and \hbc.
+    Then the quotient stack $\stack X = X/T$ has properties \bc\ and \hbc.
 \end{Thm}
@@
 
-[Put an example here.]
+\begin{Ex}
+  To illustrate let us compute $\HCoh(\catDMod{\as1/\Gm})$ where $\Gm$ acts in the usual way.
+  Let $i\colon \stack Z \to \ls\stack X$ be the inclusion of the fiber $\stack Z = \Gm \times \cs{\Gm}$ over the origin and $j\colon \stack U \to \ls\stack X$ the inclusion of the open complement $\stack U = \Gm/\Gm = \pt$.
+  Let $p\colon \stack X \to \pt$ be the structure map.
+  We have to compute $p_*p_{1,!}p_2^!k_{\stack X}$.
+
+  First we note that $p_2^!k_{\stack X} = \omega_{\ls \stack X}$.
+  Consider now the distinguished triangle
+  \[
+    p_*p_{1,!}p_2^!i_!i^!\omega_{\ls \stack X} \to
+    p_*p_{1,!}p_2^!\omega_{\ls \stack X} \to
+    p_*p_{1,!}p_2^!j_*j^!\omega_{\ls \stack X}.
+  \]
+  The right term is just the cohomology of a point, i.e.~$k$.
+  The left term evaluates to
+  \[
+    \Gamma_c(\Gm, k_{\Gm}) \otimes \GammadR(\cs{\Gm},k_{\Gm}) \cong \bigl(k[-1] \oplus k[-2]\bigr) \otimes k[u]
+  \]
+  with $u$ in degree $2$.
+  As the zeroth Hochschild cohomology cannot vanish (it must contain the identity functor), the connecting morphism is zero.
+  Hence
+  \[
+    \HCoh(\catDMod{\as1/\Gm}) \cong k[x]
+  \]
+  with $x$ in degree $1$.
+  More generally
+  \[
+    \HCoh(\catDMod{\as n/\Gm^n}) \cong k[x_1,\dotsc,x_n].
+  \]
+  In a future note we plan to give explicit computations for general toric varieties.
+\end{Ex}
 

### 2017-10-10 rewrite.tex
Base change and compactification.

@@
 
+\newcommand\sls[1]{L#1}
+\newcommand\slsY[2][\stack Y]{L_{#1}#2}
+\newcommand\scls[1]{\overline{L}#1}
+\newcommand\sclsY[2][\stack Y]{\overline{L}_{#1}#2}
+\newcommand\slsc[1]{L^c #1}
+\newcommand\slscY[2][\stack Y]{L^c_{#1}#2}
+
 \newcommand\goodness{property \textbf{(!)}}
@@
 \newcommand\goodX[1]{#1 with property \textbf{(!)}}
-\newcommand\goodnessb{property \textbf{(!')}}
-\newcommand\goodnessbshort{\textbf{(!')}}
-\newcommand\isgoodb{has property \textbf{(!')}}
-\newcommand\aregoodb{have property \textbf{(!')}}
-\newcommand\goodbX[1]{#1 with property \textbf{(!')}}
 
@@
 
-Consider a Cartesian diagram of stacks
+As was noted above, for a general stack there is no reason to expect that the base change morphism is an isomorphism.
+In such cases it is then interesting to understand the cone of the morphism, describing how badly base change fails.
+
+\subsection{The general situation}
+
+Let us for the moment return to an arbitrary Cartesian diagram of stacks
 \begin{equation}
-    \label{eq:base-change:square}
     \begin{tikzcd}
@@
 with $f$ and $g$ schematic.
-We have a morphism of functors $\catDModHol{\stack X₁} → \catDModHol{\stack X₂}$,
+As discussed above, in this situation we have a morphism of functors $\catDModHol{\stack X₁} → \catDModHol{\stack X₂}$,
 \begin{equation}
-    \label{eq:base-change-morphism}
+    \label{eq:c:base-change-morphism}
      p_! q^! → g^! f_!
@@
 \end{equation}
-If $f$ is proper, then \eqref{eq:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
+If $f$ is proper, then \eqref{eq:c:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
 To understand the behavior for non-proper $f$, we will approximate it by a proper morphism.
@@
 
-\subsection{The !-base-change property}
+\subsection{Base-change of the diagonal}
+
+We will now formulate a criterion analogous to properties \bc\ and \hbc, but using Lemma~\ref{lem:base-change-criterion}.
 
@@
 
-\begin{Def}\label{def:good}
-    We say that a quotient stack $\stack X = X/G$ \emph{\isgood} if the following two conditions hold.
-    \begin{enumerate}
-        \item $!$-base-change holds along the Cartesian square
-            \[
-                \begin{tikzcd}
-                    \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
-                    \stack X \arrow[r, "Δ"] & \stack X × \stack X
-                \end{tikzcd}
-            \]
-            i.e.~the canonical morphism $p_{1,!}p₂^! → Δ^!Δ_!$ is an isomorphism on holonomic D-modules.
-        \item For any schematic morphism $f\colon \stack Y₂ = Y₂/G → \stack Y₁ = Y₁/G$ of $G$-quotient stacks over $\stack X$, $!$-base-change holds along the Cartesian diagram
-            \[
-                \begin{tikzcd}
-                    \lsY[\stack Y₂]{\stack X} \arrow[r, "\ls f"] \arrow[d, "π₂"] & \lsY[\stack Y₁]{\stack X} \arrow[d, "π₁"]\\
-                    \stack Y₂ \arrow[r, "f"] & \stack Y₁
-                \end{tikzcd}
-            \]
-            i.e.~the canonical morphism $π_{2,!}(\ls f)^! → f^! π_{1,!}$ is an isomorphism on holonomic D-modules.
-    \end{enumerate}
-\end{Def}
-
-We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ \isgood.
-Theorem~\ref{thm:main} then immediately follows from the following observation which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodX{quotient stacks}.
-
-\begin{Prop}\label{prop:good-is-good}
-    If $\stack X = X/G$ \isgood, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
-    In particular there is an isomorphism of algebras
-    \[
-        \HCoh\bigl(\catDMod{\stack X}\bigr)
-        \cong
-        \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
-    \]
-\end{Prop}
-
-\begin{proof}
-    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid induced by $Δ\colon \stack X → \stack X × \stack X$.
-    Thus we let $\stack G_\cx$ be the simplicial stack with
-    \[
-        \stack G_i = \underbrace{\stack X \mathop{×}\limits_{\stack X × \stack X} \dotsb \mathop{×}\limits_{\stack X × \stack X} \stack X}_{\text{$i+1$ factors}}.
-    \]
-    The second base change condition of Lemma~\ref{lem:pre:groupoid_monad_hol} holds by definition.
-    Let $F\colon [n] → [m]$ be a morphism in $\cat{Δ}^{\mathrm{op}}$ and consider the induced diagram
-    \[
-        \begin{tikzcd}
-            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
-            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
-        \end{tikzcd}
-    \]
-    We note that $\stack G_{m+1} = \stack G_m ×_{\stack X × \stack X} \stack X$ and similarly for $\stack G_n$.
-    Thus setting $\stack Y₂ = \stack G_n$ and $\stack Y₁ = \stack G_m$ in the definition of \goodness, we see that all the required base changes holds.
-\end{proof}
-
-\begin{Rem}
-    We expect that most quotient stacks \arenotgood.
-    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it \isnotgood.
-\end{Rem}
-
-We will use Lemma~\ref{lem:base-change-criterion} in order to check the base change criteria in Definition~\ref{def:good}.
-In order to do so we unfortunately have to introduce some additional notation.
-Let us fix a compactification $\bar G$ of $G$ and a relative compactification $\stack X \xrightarrow{j} \bar{\stack X} \xrightarrow{\bar Δ} \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
+We will use Lemma~\ref{lem:base-change-criterion} in order to reformulate the base change criteria in properties \bc and \hbc.
+To do so we unfortunately have to introduce some additional notation.
+Let us fix a compactification $\bar G$ of $G$ and a relative compactification $\stack X \xrightarrow{j} \bar{\stack X} \xrightarrow{\bar Δ} \stack X × \stack X$ as in Section~\ref{sec:compactification:quotient}.
 For any $\stack Y → \stack X$ this induces a relative compactification $\clsY{\stack X} = \stack Y \XXtimes \bar{\stack X}$.
@@
 \end{equation}
+For the second let $\stack Y₂ → \stack Y₁$ be a morphism of stacks over $\stack X$:
+\begin{equation}\label{eq:diag:central2}
+    \begin{tikzcd}
+        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] \arrow[d, "\ls f"] & \clsY[\stack Y₂]{\stack X} \arrow[d, "{\cls f}"] & \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']  \arrow[d] \\
+        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}"] & \clsY[\stack Y₁]{\stack X} & \lscY[\stack Y₁]{\stack X} \arrow[l, hook']
+    \end{tikzcd}
+\end{equation}
+With this setup we make the following definition.
+
+\begin{Def}\label{def:good}
+    We say that a quotient stack $\stack X = X/G$ \emph{\isgood} if the following two conditions hold.
+    \begin{enumerate}
+        \item $i_{\stack X}^* \bar p₂^! j_!$ vanishes on $\catDModHol{\stack X}$.
+        \item For any schematic morphism $f\colon \stack Y₂ → \stack Y₁$ of $G$-quotient stacks over $\stack X$ the composition $i_{\stack Y₂}^* (\bar{\ls f})^!
+j_{\stack Y₁,!}$ vanishes on $\catDModHol{\lsY[\stack Y₁]{\stack X}}$.
+    \end{enumerate}
+\end{Def}
+
+\begin{Prop}\label{prop:good-is-good}
+    If $\stack X = X/G$ \isgood, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
+    In particular there is an isomorphism of algebras
+    \[
+        \HCoh\bigl(\catDMod{\stack X}\bigr)
+        \cong
+        \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
+    \]
+\end{Prop}
+
+\begin{proof}
+  By Lemma~\ref{lem:base-change-criterion}, \isgood\ implies properties \bc\ and \hbc.
+\end{proof}
+
+\subsection{Some reductions}
+
+\begin{Lem}
+    Let $U$ be a $G$-equivariant open subset of $X$.
+    If $X/G$ \isgood\ then $U/G$ \isgood.
+\end{Lem}
+
+\begin{proof}
+    Set $\stack U = U/G$.
+    We will only show the second condition of Definition~\ref{def:good}, the first one is similar.
+    Thus let $f\colon \stack Y₂ → \stack Y₁$ be a map of quotient stacks over $\stack U$ (and hence also over $U$).
+    We note that since $\stack U$ is an open subset we have isomorphisms $\lsY[\stack Y_i]{\stack U} \cong \stack Y_i \XXtimes \stack U$.
+    Consider the diagram
+    \begin{equation}
+        \label{eq:lem:cover:diagram}
+        \begin{tikzcd}
+            \lsY[\stack Y₁]{\stack U} \arrow[r, hook, "j_{\stack Y₁}^{\stack U}"] \arrow[d, hook, "α"] &
+            \clsY[\stack Y₁]{\stack U} \arrow[d, hook, "β"] &
+            \clsY[\stack Y₂]{\stack U} \arrow[l, "{\cls f}^{\stack U}"'] \arrow[d, hook, "γ"] &
+            \lscY[\stack Y₂]{\stack U} \arrow[l, hook', "i^{\stack U}_{\stack Y₂}"'] \arrow[d, hook, "δ"] \\
+            %
+            \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}^{\stack X}"] &
+            \clsY[\stack Y₁]{\stack X} &
+            \clsY[\stack Y₂]{\stack X} \arrow[l, "{\cls f}^{\stack X}"'] &
+            \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i^{\stack X}_{\stack Y₂}"']
+        \end{tikzcd}
+    \end{equation}
+    The vertical arrows are open embeddings and all squares are Cartesian (where we use the same compactification of $G$ for $\bar{\stack X}$ and $\bar{\stack U}$).
+    Thus
+    \begin{equation*}
+        i^{\stack U,*}_{\stack Y₂} {\cls f}^{\stack U,!} j_{\stack Y₁,!}^{\stack U} =
+        i^{\stack U,*}_{\stack Y₂} {\cls f}^{\stack U,!} j_{\stack Y₁,!}^{\stack U} α^* α_*=
+        δ^* i^{\stack X,*}_{\stack Y₂} {\cls f}^{\stack U,!} j_{\stack Y₁,!}^{\stack X} α_*=
+        0.
+        \qedhere
+    \end{equation*}
+\end{proof}
+
+A similar can be used to reduce the computation to a smooth cover.
+In particular we will want to reduce to computations on a schematic cover.
+On such a cover we will use primes to indicate maps on schemes and will use $\sls{}$ instead of $\ls{}$ for the covers of the loop spaces.
+If we start with the cover $\bar Γ → \bar{\stack X}$, the pullbacks to the part of diagram \eqref{eq:diag:central1} of interest are
+\begin{equation}
+    \label{eq:diag:scheme-cover1}
+    \begin{tikzcd}
+        Γ \arrow[r, hook, "j'"] \arrow[d] &
+        \bar Γ \arrow[d] &
+        \scls \stack X \arrow[l, "\bar p₂'"'] \arrow[d] &
+        \slsc \stack X \arrow[l, hook', "i_{\stack X}'"'] \arrow[d]\\
+        %
+        \stack X \arrow[r, hook, "j"] &
+        \bar{\stack X} &
+        \cls \stack X \arrow[l, "\bar p₂"'] &
+        \lsc \stack X \arrow[l, hook', "i_{\stack X}"']
+    \end{tikzcd}
+\end{equation}
+Similarly, the interesting parts of diagram \eqref{eq:diag:central2} become
+\begin{equation}
+    \label{eq:diag:scheme-cover2}
+    \begin{tikzcd}
+        \slsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}'"] \arrow[d] &
+        \sclsY[\stack Y₁]{\stack X} \arrow[d] &
+        \sclsY[\stack Y₂]{\stack X} \arrow[l, "\scls f"'] \arrow[d] &
+        \slscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₂}'"'] \arrow[d]\\
+        %
+        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}"] &
+        \clsY[\stack Y₁]{\stack X} &
+        \clsY[\stack Y₂]{\stack X} \arrow[l, "\cls f"'] &
+        \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₂}"']
+    \end{tikzcd}
+\end{equation}
+In both diagrams all vertical morphisms are smooth and the spaces in the top row are schemes.
+Explicitly, if $h'\colon Y → X$ is a $G$-equivariant morphism of schemes inducing the structure map $\stack Y → \stack X$, then
+\[
+    \sclsY \stack X =
+    \biggl\{
+        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y × \bar G : \bigl(g₂,\, h'(y),\, g₁h'(y)\bigr) ∈ \bar Γ
+    \biggr\}.
+\]
+
+\begin{Lem}\label{lem:base-change:scheme-cover}
+    A stack $X/G$ \isgood\ if the following two conditions hold:
+    \begin{enumerate}
+        \item The composition $(i_{\stack X}')^*(\bar p₂')^! j'_!$ vanishes on $\catDModHol{Γ/G×G}$.
+        \item For each equivariant morphism $f'\colon Y₂ → Y₁$ of $G$-schemes the composition $(i_{\stack Y₂}')^*(\scls f)^!
+j'_{\stack Y₁,!}$ vanishes on $\catDModHol{\slsY[\stack Y₁]{\stack X}/G×G}$.
+    \end{enumerate}
+\end{Lem}
+
+\begin{proof}
+    This follows from the fact that pullback along the smooth vertical morphisms in \eqref{eq:diag:scheme-cover1} and \eqref{eq:diag:scheme-cover2} is conservative \cite[Lemma~5.1.6]{DrinfeldGaitsgory:2013:FinitenessQuestions} and commutes with the other morphisms up to a shift.
+\end{proof}
+
+\begin{Lem}
+    \label{lem:base-change:cover}%
+    If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ \aregood, then $X/G$ \isgood.
+\end{Lem}
+
+\begin{proof}
+    Let $\stack U_i = U_i/G$ be the corresponding quotient stacks.
+    We will again only show the second condition, the first being simpler.
+
+    Let us first show that for any $\stack Y → \stack X$ the stacks $\lscY{\stack U_i}$ form an open cover of $\lscY{\stack X}$\footnote{
+        This is not completely obvious, since the $\bar{\stack U}_i$ do not necessarily form a cover of $\bar{\stack X}$.
+        For example, consider $\ps1$ with the usual linear $\Gm$-action and the usual affine cover.
+    }.
+    For this it suffices to show that the open subschemes $\sclsY \stack U_i$ cover $\sclsY \stack X$.
+    Let $(g₁, y, g₂)$ be a point of $\sclsY \stack X$.
+    Then there exists some $U_i$ with $h'(y) ∈ U_i$.
+    But then $g₁h'(y)$ is also in $U_i$ and hence $(h'(y), g₂, g₁h'(y)) ∈ \bar{\stack U}_i$.
+    Thus $(g₁, y, g₂)$ is in $\sclsY \stack U_i$.
+
+    It now suffices to show that the restrictions of $i_{\stack Y₂}^*\cls{f}^!j_{\stack Y₁,!} \sheaf F$ to $\lscY[\stack Y₂]{\stack U_i}$ vanish for every $\sheaf F ∈ \catDModHol{\lsY[\stack Y₁]{\stack X}}$.
+    But this follows from the diagram~\eqref{eq:lem:cover:diagram} (for $\stack U_i$ instead of $\stack U$) and the assumption on $\stack U_i$.
+\end{proof}
+
+Finally, can be useful to consider only partial compactifications.
+That is, in the constructions of Section~\ref{sec:compactification:quotient}, instead of going all the way to $\bar G$ we only use some subvariety of it.
+Thus let $H$ be a $G×G$-stable subvariety of $\bar G$ containing $G$, and let $^H\bar{Γ}$ be the closure of $Γ$ in $H × X × X$.
+We set
+\[
+    ^H\bar{\stack X} = \rquot{^H\bar{Γ}}{G×G}.
+\]
+Clearly, if $\left\{H_i\right\}$ is an open cover of $\bar G$ by $G×G$-stable subvarieties (each containing $G$), then $\left\{{}^{H_i}\bar{\stack X}\right\}$ is an open cover of $\bar{\stack X}$.
+
+Let us fix such an open cover.
+For any $\stack Y$ over $\stack X$ we obtain corresponding open covers $\left\{ {}^{H_i}\cls_{\stack Y} \stack X\right\}$ and $\left\{{}^{H_i}\lsc_{\stack Y} \stack X\right\}$ of $\clsY{\stack X}$ and $\lscY{\stack X}$ respectively.
+We get our usual diagrams for these partial compactifications:
+\[
+    \begin{tikzcd}
+        \stack X \arrow[r, hook, "{}^{H_i}j"] &
+        {}^{H_i}\bar{\stack X} &
+        {}^{H_i}\clsY[\stack X]{\stack X} \arrow[l, "{}^{H_i}p_{2}"'] &
+        {}^{H_i}\lscY[\stack X]{\stack X} \arrow[l, hook', "{}^{H_i}i_{\stack X}"']
+    \end{tikzcd}
+\]
+and
+\[
+    \begin{tikzcd}
+        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "{}^{H_i}j_{\stack Y₁}"] &
+        {}^{H_i}\clsY[\stack Y₁]{\stack X} &
+        {}^{H_i}\clsY[\stack Y₂]{\stack X} \arrow[l, "{}^{H_i}\cls f"'] &
+        {}^{H_i}\lscY[\stack Y₂]{\stack X}. \arrow[l, hook', "{}^{H_i}i_{\stack Y₂}"']
+    \end{tikzcd}.
+\]
+
+\begin{Lem}\label{lem:base-change:cover-by-relative-compactifications}
+    Let $H_i$ be an open cover of $\bar G$ by $G×G$-stable subvarieties, each containing $G$.
+    Then $\stack X = X/G$ \isgood\ if and only if the following two conditions hold for each $i$:
+    \begin{enumerate}
+        \item The composition $({}^{H_i}i_{\stack X})^*({}^{H_i}\bar p₂)^! ({}^{H_i}j)_!$ vanishes on $\catDModHol{\stack X}$.
+        \item For each schematic morphism of $G$-quotient stacks $f\colon \stack Y₂ → \stack Y₁$ the composition $({}^{H_i}i_{\stack Y₂})^*({}^{H_i}\cls f)^!
+({}^{H_i}j_{\stack Y₁})_!$ vanishes on $\catDModHol{\lsY[\stack Y₁]{\stack X}}$.
+    \end{enumerate}
+\end{Lem}
+
+\begin{proof}
+    Similar to the proof of Lemma~\ref{lem:base-change:cover}.
+\end{proof}
 

### 2017-10-10 rewrite.tex
Various small improvements and fixes.

@@
 
-This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced by Arinkin and Gaitsgory \cite{ArinkinGaitsgory:2015:SingularSupport}.
-More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
+This construction, applied to the category of (ind-)coherent sheaves on a (quasi-smooth, dg-) scheme, yields the singular support of coherent sheaves introduced by Arinkin and Gaitsgory \cite{ArinkinGaitsgory:2015:SingularSupport}.
+The authors use this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
 By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.
@@
 A first step to this -- and also a problem of independent interest -- is to understand the Hochschild cohomology of the category $\catDMod{\stack X}$ of D-modules on a stack $\stack X$.
+Thanks to the theory of integral kernels, this question can be approached geometrically.
 Representing the identity functor by its kernel, we obtain an isomorphism of dg algebras
@@
 \begin{Thm}\label{thm:main}
-    Let $G \cong \Gm^n$ be a torus acting on a normal scheme $X$ of finite type over $k$.
+    Let $G \cong \Gm^n$ be a torus acting on a normal quasi-projective variety $X$ over an algebraically closed field $k$ of characteristic $0$.
     Then there is a canonical isomorphism of algebras
@@
 In Section~\ref{sec:base-change} we give criteria for morphism~\eqref{eq:intro:central_cone} to be an isomorphism.
-In particular, we will use the contraction principle of Drinfeld--Gaitsgory \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}\remark{Better reference?}\ to understand the case of so-called contractive stacks.
+In particular, we will use the contraction principle of Drinfeld--Gaitsgory \cite[Section~5.1]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} to understand the case of so-called contractive stacks.
 Using the theory developed in Section~\ref{sec:base-change}, the proof of Theorem~\ref{thm:main} is given in Section~\ref{sec:torus}.
@@
 
-For any morphism $f\colon \stack X → \stack Y$ we obtain a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
+For any morphism $f\colon \stack X → \stack Y$ we have a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
 If $p\colon \stack X → \pt$ is the structure map, we set
@@
 \]
-The identities~\ref{eq:pre:monad-identities} ensure that the algebra is associative and unital.
-
-The most common source of monads is from a pair of adjoint functors $F\colon \cat C \rightleftarrows \cat D \cocolon G$.
+The identities~\eqref{eq:pre:monad-identities} ensure that the algebra is associative and unital.
+
+The most common source of monads is a pair of adjoint functors $F\colon \cat C \rightleftarrows \cat D \cocolon G$.
 One simply sets $T = G ∘ F$ and $η$ and $μ$ are given by the adjunction morphisms
@@
 
-Let us for the moment assume that $s$ (and hence $t$) is proper and schematic.
+Let us for the moment assume that $s$ (and hence $p_2$) is proper and schematic.
 In this case the maps $e$ and $m$ are also proper, since $s ∘ e = \id_{\stack G₀}$ and $s ∘ m = s ∘ p₂$ are proper.
@@
 
-The Beck--Chevalley condition us formulated using the \emph{nerve} of the groupoid $\stack G_\cx$.
+The Beck--Chevalley condition is formulated using the \emph{nerve} of the groupoid $\stack G_\cx$.
 Intuitively, this is the simplicial stack, usually also denoted $\stack{G}_\cx$, with
@@
 \begin{Thm}\label{thm:torus_quotient}
-    Let $X$ be a normal variety with an action of a torus $T$.
+    Let $X$ be a normal quasi-projective variety $X$ over an algebraically closed field $k$ of characteristic $0$ with an action of a torus $T$.
     Then the quotient stack $\stack X = X/T$ has properties \bc\ and \hbc.
@@
 \begin{proof}
-  By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions}\remark{exact reference?} and Lemma~\ref{lem:open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
+  By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions} and Lemma~\ref{lem:open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
   By Lemma~\ref{lem:lc_immersion} it further suffices to consider the case that $\stack X = \as{m}/T$ for some $n$.
@@
 Similarly, we denote by $\bar{\stack Z} = \stack X₂ ×_{\stack Y} \bar{\stack X}₁$ and $\stack Z^c = \stack X₂ ×_{\stack Y} \stack X₁^c$ the corresponding fiber products.
-The corresponding inclusion and projection maps are denoted as is indicated in the following Cartesian diagrams.
+The inclusion and projection maps are denoted as is indicated in the following Cartesian diagrams.
 \[
@@
     \]
-    In particular, if $i^* \bar{q}^! j_! = 0$, then $p_! q^! \cong g^! f_!$ is an isomorphism of functors.
+    In particular, if $i^* \bar{q}^! j_! = 0$, then $p_! q^! \to g^! f_!$ is an isomorphism of functors.
 \end{Lem}
@@
 
-In the preceding section we simply assumed that a relative compactification of the given map exists.
+In the preceding section we simply assumed that a relative compactification of the given map $f$ exists.
 We will now construct such a compactification for the diagonal map of a quotient stack.

### 2017-10-10 rewrite.tex
Lots of fixes.

@@
 
-\title{Hochschild cohomology of torus equivariant D-modules: New approach}
+\title{Hochschild cohomology of torus equivariant D-modules}
 \author{Clemens Koppensteiner}
@@
 \newcommand\cs{\stack{B}}
-\newcommand\catCoSimplicial{\cat{\Delta}^{\mathrm{op}}}
+\newcommand\catCoSimplicial{\Delta^{\mathrm{op}}}
 \newcommand\dR{\mathrm{dR}}
@@
 \begin{abstract}
-  We discuss the Hochschild cohomology of the category of D-modules associated to an algebraic.
+  We discuss the Hochschild cohomology of the category of D-modules associated to an algebraic stack.
   In particular we describe the Hochschild cohomology of the category of torus-equivariant D-modules as the cohomology of a D-module on the loop space of the quotient stack.
@@
 For co-complete compactly generated triangulated categories one answer is provided by Benson, Iyengar and Krause \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
-To each map from a graded-commutative ring $R$ to the center of $\cat C$ the authors associate the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
+To each map from a graded-commutative ring $R$ to the center of $\cat C$ one associates the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
 This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves mentioned above).
@@
 
-In this paper we investigate how the morphism
+In this paper we investigate the morphism
 \begin{equation}\label{eq:intro:central_cone}
@@
 
-In Section~\ref{sec:base-change} we give criteria for morphism~\eqref{eq:intro:central_cone} to be an isomorphism.
+In Section~\ref{sec:base-change} we give a criterion for morphism~\eqref{eq:intro:central_cone} to be an isomorphism.
 In particular, we will use the contraction principle of Drinfeld--Gaitsgory \cite[Section~5.1]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} to understand the case of so-called contractive stacks.
@@
 I would like to thank David Nadler for the original motivation for this project and many discussions concerning it.
+This work has been partially supported by the National Science Foundation under Grant No.~1638352, as well as the Giorgio and Elena Petronio Fellowship Fund.
 
@@
 \]
-As $\GammadR(\stack X,\, {-})$ is usually not continuous and the object $k_{\stack X}$ is usually not a compact object of $\catDMod{\stack X}$.
+As $\GammadR(\stack X,\, {-})$ is usually not continuous the object $k_{\stack X}$ is usually not a compact object of $\catDMod{\stack X}$.
 
@@
 \]
-Of course, if $X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
+Of course, if $\stack X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
 Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{1,!} p₂^!$.
@@
 Consider a Cartesian diagram of stacks
-\begin{equation}
-    \label{eq:base-change:square}
+\begin{equation*}
+    %\label{eq:base-change:square}
     \begin{tikzcd}
@@
     \end{tikzcd}
-\end{equation}
+\end{equation*}
 with $f$ and $g$ schematic.
@@
 induced by adjunctions
-\begin{equation}
-    \label{eq:base-change-adjunctions}
+\begin{equation*}
+    %\label{eq:base-change-adjunctions}
     p_! q^! →
@@
     g^! f_!.
-\end{equation}
+\end{equation*}
 If $f$ is proper, then \eqref{eq:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
@@
 
-With this we can write down the two properties that we need to check in order to get a good
+With this we can write down the two properties that we need to check in order for the naive expectation to hold.
 
@@
     \]
-    We say that $\stack X$ has property \bc\ if the canonical morphism
+    We say that $\stack X$ has \emph{property \bc} if the canonical morphism
     \[
@@
 \[
-    \stack G_m(\stack X) = \underbrace{\stack X \times_{\stack X \times \stack X} \dotsb \times_{\stack X \times \stack X} \stack X}_{m+1\text{ times}}.
+    \stack G_m(\stack X) = \underbrace{\stack X \XXtimes \dotsb \XXtimes \stack X}_{m+1\text{ times}}.
 \]
@@
 \begin{Def}
-    Let $\stack X$ be a QCA stack and consider the cartesian square
+    Let $\stack X$ be a QCA stack and consider the Cartesian square
     \[
@@
     where the horizontal maps are induced by a map $F\colon [n] \to [m]$ in $\catCoSimplicial$.
-    We say that $\stack X$ has property \hbc\ if for each such $F$ the canonical morphism
+    We say that $\stack X$ has \emph{property \hbc} if for each such $F$ the canonical morphism
     \[
@@
 \begin{Lem}\label{lem:smooth_or_proper}
-    Let $\stack X$ be a QCA stack with diagonal morphism $\Delta\colon \stack X \to \stack X \times \stack X$. Then,
+    Let $\stack X$ be a QCA stack with diagonal morphism $\Delta\colon \stack X \to \stack X \times \stack X$.
     \begin{enumerate}
@@
 
-    The diagonal morphism of $\cs{G}$ is smooth, so that property \hbc\ follows from \ref{lem:smooth_or_proper:bc}.
+    The diagonal morphism of $\cs{G}$ is smooth, so that property \bc\ follows from \ref{lem:smooth_or_proper:bc}.
     Note that $\stack G_m(\cs{G}) \cong G^m \times \cs{G}$.
@@
 We have $\ls \stack Y \cong \stack Y \times_{\stack X \times \stack X} \stack Y$ and it follows that there is a canonical open (resp.~closed) immersion of loop stacks $\ls i\colon \ls \stack Y \to \ls \stack X$.
-
 More generally, each $\stack G_m(\stack Y)$ is an open (resp.~closed) substack of $\stack G_m(\stack X)$.
-Abusing notation, we will sometimes continue to denote this inclusion by $i$.
-%In the special case $m=1$, we will also write $\ls i\colon \ls \stack Y \to \ls \stack X$.
 
@@
     Let us first assume that $i$ is open.
-    Now, using the assumption on $\stack X$ and the fact that $i^! = i^*$ we get
+    Using the assumption on $\stack X$ and the fact that $i^! = i^*$ we get
     \begin{multline*}
@@
     As above, it suffices to show that $i_!p_{\stack Y,1,!}p_{\stack Y,2}^!i^! \to i_!\Delta_{\stack Y}^!\Delta_{\stack Y,!}i^!$ is an equivalence.
-    Now, using the assumption on $\stack X$ and the fact that $i_! = i_*$ we get
+    Using the assumption on $\stack X$ and the fact that $i_! = i_*$ we get
     \begin{multline*}
@@
 We would like to have an extension of Lemma~\ref{lem:product} to fiber products.
-Unfortunately, as the discussion on \cite[Section~1.2]{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup} shows, the category of D-modules on a fiber product $\stack X_1 \times_{\stack Y} \stack X_2$ is rather badly behaved unless $\stack Y$ is a scheme.
+Unfortunately, as the discussion in \cite[Section~1.2]{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup} shows, the category of D-modules on a fiber product $\stack X_1 \times_{\stack Y} \stack X_2$ is rather badly behaved unless $\stack Y$ is a scheme.
 Thus we have to restrict ourselves to the following partial result which is sufficient for our applications.
@@
     on $\catDModHol{\stack X}$.
-    It suffices to show that the canonical maps on the outside terms to $i_!i^! p_{1,!}p_2^!$ and $j_*j^* p_{1,!}p_2^!$ are isomorphisms.
+    It suffices to show that the canonical maps on the outside terms to $i_!i^! p_{1,!}p_2^!$ and $j_*j^* p_{1,!}p_2^!$ respectively are isomorphisms.
 
@@
     \end{equation}
-    Write $\ls i \colon \ls\stack X^0 \hookrightarrow \ls\stack X$ for the corresponding closed inclusion of loop stacks.
+    Write $\ls i \colon \ls\stack X^0 \hookrightarrow \ls\stack X$ for the closed inclusion of loop stacks.
     We note that $\ls\stack X$ inherits a contractive $\Gm$ action form $\stack X$.
     Let $\ls \pi\colon \ls\stack X \to \ls\stack X^0$ be the corresponding contraction map.
-    Then by assumption and the contraction principle (Theorem~\ref{thm:contraction_principle}), \eqref{eq:lem:bc_contractive} is equivalent to
+    Then by assumption and the contraction principle, \eqref{eq:lem:bc_contractive} is equivalent to
     \[
@@
   By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions} and Lemma~\ref{lem:open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
-  By Lemma~\ref{lem:lc_immersion} it further suffices to consider the case that $\stack X = \as{m}/T$ for some $n$.
+  By Lemma~\ref{lem:lc_immersion} it further suffices to consider the case that $\stack X = \as{m}/T$ for some $m$.
   By Lemma~\ref{lem:product_quotient}, we can further decompose $\as{m}$ into $T$-eigenspaces.
@@
   If the $\Gm$ action is contractive this case follows immediately from Proposition~\ref{prop:contractive} and Lemma~\ref{lem:smooth_or_proper}.
-  Otherwise the inverse of the $\Gm$-action on $\as1$ is contractive and we can use the contraction principle (and hence Proposition~\ref{prop:contractive}) with the monoid $\as1 = \Gm \cup \{\infty\}$ instead of $\Gm \cup \{0\}$.
+  Otherwise the inverse of the $\Gm$-action on $\as1$ is contractive and we can use the contraction principle (and hence Proposition~\ref{prop:contractive}) with the monoid $\as[\infty]{1} = \Gm \cup \{\infty\}$ instead of $\Gm \cup \{0\}$.
 \end{proof}
@@
   \[
-    \Gamma_c(\Gm, k_{\Gm}) \otimes \GammadR(\cs{\Gm},k_{\Gm}) \cong \bigl(k[-1] \oplus k[-2]\bigr) \otimes k[u]
+    \Gamma_c(\Gm, k_{\Gm}) \otimes \GammadR(\cs{\Gm},k_{\cs{\Gm}}) \cong \bigl(k[-1] \oplus k[-2]\bigr) \otimes k[u]
   \]
@@
 \begin{equation}
+  \label{eq:c:base-change:square}
     \begin{tikzcd}
@@
 \begin{equation}
-    \label{eq:base-change-adjunctions}
+    \label{eq:c:base-change-adjunctions}
     p_! q^! →
@@
 
-Let us now assume that in the situation of diagram \eqref{eq:base-change:square} there exists a relative compactification of $f\colon \stack X₁ → \stack Y$.
+Let us now assume that in the situation of diagram \eqref{eq:c:base-change:square} there exists a relative compactification of $f\colon \stack X₁ → \stack Y$.
 Let $\stack X₁^c$ be the closed complement of the open inclusion $j\colon \stack X₁ \hookrightarrow \bar{\stack X}₁$.
@@
     \label{lem:base-change-criterion}%
-    In the situation of the Cartesian square \eqref{eq:base-change:square}, the cone of the base change morphism $p_! q^! → g^! f_!$ is given by
+    In the situation of the Cartesian square \eqref{eq:c:base-change:square}, the cone of the base change morphism $p_! q^! → g^! f_!$ is given by
     \[
@@
     Let $\tilde\jmath\colon \stack Z \hookrightarrow \bar{\stack Z}$ be the open inclusion complement to $i$.
-    We split the adjunctions in \eqref{eq:base-change-adjunctions} in two by using the compositions
+    We split the adjunctions in \eqref{eq:c:base-change-adjunctions} in two by using the compositions
     \[
@@
     It is possible to extend the methods of \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden} to quotients by higher dimensional tori.
-    The resulting constructions are useful for doing explicit computations.
+    The resulting constructions are useful for explicit computations.
 \end{Rem}
@@
 \[
-    \lsY = \stack Y \XXtimes \stack X,
+  \lsY{\stack X} = \stack Y \XXtimes \stack X,
 \]
@@
 
-We will use Lemma~\ref{lem:base-change-criterion} in order to reformulate the base change criteria in properties \bc and \hbc.
+We will use Lemma~\ref{lem:base-change-criterion} in order to reformulate the base change criteria in properties \bc\ and \hbc.
 To do so we unfortunately have to introduce some additional notation.
@@
 \begin{proof}
-  By Lemma~\ref{lem:base-change-criterion}, \isgood\ implies properties \bc\ and \hbc.
+  By Lemma~\ref{lem:base-change-criterion}, \goodness\ implies properties \bc\ and \hbc.
 \end{proof}
@@
 
-A similar can be used to reduce the computation to a smooth cover.
-In particular we will want to reduce to computations on a schematic cover.
+A similar argument can be used to reduce the computation to a smooth cover.
+In particular we will want to reduce to computations on a cover by schemes.
 On such a cover we will use primes to indicate maps on schemes and will use $\sls{}$ instead of $\ls{}$ for the covers of the loop spaces.
@@
 \begin{Lem}\label{lem:base-change:scheme-cover}
-    A stack $X/G$ \isgood\ if the following two conditions hold:
+    A quotient stack $X/G$ \isgood\ if the following two conditions hold:
     \begin{enumerate}
@@
 
-    Let us first show that for any $\stack Y → \stack X$ the stacks $\lscY{\stack U_i}$ form an open cover of $\lscY{\stack X}$\footnote{
+    Let us first show\footnote{
         This is not completely obvious, since the $\bar{\stack U}_i$ do not necessarily form a cover of $\bar{\stack X}$.
         For example, consider $\ps1$ with the usual linear $\Gm$-action and the usual affine cover.
-    }.
+    } that for any $\stack Y → \stack X$ the stacks $\lscY{\stack U_i}$ form an open cover of $\lscY{\stack X}$.
     For this it suffices to show that the open subschemes $\sclsY \stack U_i$ cover $\sclsY \stack X$.

### 2017-10-10 paper.tex
Put all macros into the file.
Acknowledgements

@@
 
-\title{Hochschild cohomology of torus-equivariant D-modules}
+\title{Hochschild cohomology of torus equivariant D-modules}
 \author{Clemens Koppensteiner}
 
-\usepackage{math-gl}
+%\usepackage{math-ag}
 
@@
 
-\let\stack\mathbf
+% overrides
 \let\shortbar\bar
@@
 
-%\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}
-\newcommand\catDModMon[2]{\catDMod{#1}^{#2-\mathup{mon}}}
-\newcommand\catDModHolMon[2]{\catDModHol{#1}^{#2-\mathup{mon}}}
-
+% spaces
+\newcommand\as[2][]{\mathbb A^{#2}_{#1}}    % affine space
+\newcommand\ps[2][]{\mathbb P^{#2}_{#1}}    % projective space
+\newcommand\pt{\mathrm{pt}}                 % a point
+\newcommand\Ga{\mathbb{G}_{\mathrm{a}}}     % G_a
+\newcommand\Gm{\mathbb{G}_{\mathrm{m}}}     % G_m
+\DeclareMathOperator\Spec{Spec}
+
+% stacks
+\let\stack\mathbf                           % basic formatting for stacks
+\newcommand\cs{\stack{B}}                   % classifying stack
+\newcommand\LocSys{\operatorname{LocSys}}   % local systems
+\newcommand\Bun{\operatorname{Bun}}         % bundles
+
+% category theory and homological algebra
+\newcommand\cat{\mathbf}                    % formatting for categories
+\newcommand\catCoSimplicial{\Delta^{\mathrm{op}}}
+\DeclareMathOperator\Hom{Hom}
+\newcommand\id[1][]{{\mathrm{Id}_{#1}}}     % identity map
+\newcommand\catVect[1][]{\cat{Vect}_{#1}}   % vector spaces
+\newcommand\catModules[1]{\cat{Mod}(#1)}    % modules over a ring, etc.
+\newcommand\cx\bullet                       % dot for complexes
+\newcommand\dual{∨}
+\newcommand\cocolon{%                       % mirrored \colon (for an adjunction)
+    \nobreak \mskip 6muplus1mu \mathpunct {}\nonscript \mkern -\thinmuskip{:}\mskip 2mu\relax%
+}
+\newcommand\rquot[2]{%                      % quotient on the right
+    \mathchoice%
+        {\left.#1\kern-0.2ex\middle/\kern-0.3ex\lower0.7ex\hbox{$\displaystyle #2$}\right.}%
+        {\left.#1\middle/#2\right.}%
+        {\left.#1\middle/#2\right.}%
+        {\left.#1\middle/#2\right.}%
+}
+\newcommand\isoto\similarrightarrow         % isomorphisms
+\newcommand\proj[1]{\operatorname{pr}_{#1}} % projection on a factor
+\newcommand{\HCoh}{\operatorname{HH}^\cx}   % Hochschild cohomology
+
+% Sheaves and D-modules
+\newcommand\sheaf\mathscr
+\DeclareMathOperator\supp{supp}     % support
+\newcommand\catDMod[2][]{\cat{DMod}_{#1}(#2)}   % category of D-modules
+\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}   % holonomic D-modules
 \newcommand\dR{\mathrm{dR}}
+\newcommand\GammadR{Γ_{\mkern-4mu\dR}}
 \newcommand{\renstar}{\blacktriangle}
-
-\newcommand{\HCoh}{\operatorname{HH}^\cx}
-\newcommand\GammadR{Γ_{\mkern-4mu\dR}}
+\newcommand\dualize{\mathbb D}
+\newcommand\catIndCoh[2][]{\cat{IndCoh}_{#1}(#2)} % category of ind-coherent sheaves
 
 \newcommand\opalg[1]{#1^{\mathrm{op}}}
-
-\renewcommand\B{\stack{B}}
-\newcommand\mappingstack{\mathbfup{Maps}}
-\newcommand\X{\mathbb{X}}
-
 \newcommand\Gammasub[1]{\Gamma_{\mkern-3mu#1}}
@@
     }
-\renewcommand\ls[1]{\mathbfcal{L} #1}
+
+\newcommand\bc{\textbf{($\mathbf{*}$)}}
+\newcommand\hbc{\textbf{($\mathbf{**}$)}}
+
+\newcommand\catK[2][]{\cat{K}_{#1}(#2)}
+\newcommand\catKHol[1]{\catK[\mathrm{hol}]{#1}}
+
+\newcommand\ls[1]{\mathbfcal{L} #1}
 \newcommand\lsY[2][\stack Y]{\mathbfcal{L}_{#1} #2}
@@
 \newcommand\slscY[2][\stack Y]{L^c_{#1}#2}
-
-\newcommand\stabls[2]{L^{#1}#2}
-\newcommand\stabcls[2]{\overline{L}^{#1}#2}
-\newcommand\stablsc[2]{L^{#1,c}#2}
-\newcommand\stablsY[3][\stack Y]{L_{#1}^{#2}#3}
-\newcommand\stabclsY[3][\stack Y]{\overline{L}_{#1}^{#2}#3}
-\newcommand\stablscY[3][\stack Y]{L_{#1}^{#2,c}#3}
-
-\newcommand\Stab{\operatorname{Stab}}
 
@@
 \newcommand\goodX[1]{#1 with property \textbf{(!)}}
-\newcommand\goodnessb{property \textbf{(!')}}
-\newcommand\goodnessbshort{\textbf{(!')}}
-\newcommand\isgoodb{has property \textbf{(!')}}
-\newcommand\aregoodb{have property \textbf{(!')}}
-\newcommand\goodbX[1]{#1 with property \textbf{(!')}}
-
-\newcommand\dualize{\mathbb D}
 
@@
 \begin{document}
-
 \maketitle
 
-[macros]
-
 \begin{abstract}
-    We discuss how to compute the Hochschild cohomology of the category of D-modules on a quotient stack via a relative compactification of the diagonal morphism.
-    We then apply this construction to the case of torus-equivariant D-modules and describe the Hochschild cohomology as the cohomology of a D-module on the loop space of the quotient stack.
+  We discuss the Hochschild cohomology of the category of D-modules associated to an algebraic stack.
+  In particular we describe the Hochschild cohomology of the category of torus-equivariant D-modules as the cohomology of a D-module on the loop space of the quotient stack.
+  Finally, we give an approach for understanding the Hochschild cohomology of D-modules on general stacks via a relative compactification of the diagonal.
   This work is motivated by a desire to understand the support theory (in the sense of \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}) of D-modules on stacks.
@@
 Even more generally one can ask the following question: Given a $k$-linear category $\cat C$, can one find a space over which $\cat C$ localizes?
-For co-complete compactly generated triangulated categories one answer is provided by \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
-To each map from a graded-commutative ring $R$ to the center of $\cat C$ the authors associate the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
-This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves).
+For co-complete compactly generated triangulated categories one answer is provided by Benson, Iyengar and Krause \cite{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}:
+To each map from a graded-commutative ring $R$ to the center of $\cat C$ one associates the \emph{triangulated support} functor $\supp_R$, assigning to each object $A ∈ \cat C$ a subset $\supp_R A \subseteq \Spec R$.
+This construction can be used to unify various theories of support in different areas of mathematics (though it does not yield the microlocal support of constructible sheaves mentioned above).
 
@@
 
-This construction, applied to the category of (ind-)coherent sheaves on a (quasismooth, dg-) scheme, yields the singular support of coherent sheaves introduced in \cite{ArinkinGaitsgory:2015:SingularSupport}.
-More concretely, the authors used this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
+This construction, applied to the category of (ind-)coherent sheaves on a (quasi-smooth, dg-) scheme, yields the singular support of coherent sheaves introduced by Arinkin and Gaitsgory \cite{ArinkinGaitsgory:2015:SingularSupport}.
+The authors use this notion of singular support for the category $\catIndCoh{\LocSys_G}$ in their formulation of the geometric Langlands conjecture.
 By Langlands duality, one should then have a matching support theory for the category $\catDMod{\Bun_G}$ and the question arises whether it is possible to formulate this theory in a way that is intrinsic to D-modules.
@@
 
-In this paper we investigate how to quantify the cone of the morphism
+In this paper we investigate the morphism
 \begin{equation}\label{eq:intro:central_cone}
@@
 \begin{Thm}\label{thm:main}
-    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
+    Let $G \cong \Gm^n$ be a torus acting on a normal quasi-projective variety $X$ over an algebraically closed field $k$ of characteristic $0$.
     Then there is a canonical isomorphism of algebras
@@
 In Section~\ref{sec:HH} we explain how morphism~\eqref{eq:intro:central_cone} arises as a morphism of monads and make precise its relationship with Hochschild cohomology of $\catDMod{\stack X}$.
-
-In Section~\ref{sec:base-change} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.
-Finally, in Section~\ref{sec:torus} we deduce Theorem~\ref{thm:main} from this description, using geometric considerations and the contraction principle of Drinfeld--Gaitsgory \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
+As a simple application of this formalism, we also show that $\HCoh{\catDMod{\stack X}}$ always has a subalgebra isomorphic to $\opalg{\GammadR(\stack X,\ k_{\stack X})}$.
+
+In Section~\ref{sec:base-change} we give a criterion for morphism~\eqref{eq:intro:central_cone} to be an isomorphism.
+In particular, we will use the contraction principle of Drinfeld--Gaitsgory \cite[Section~5.1]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} to understand the case of so-called contractive stacks.
+Using the theory developed in Section~\ref{sec:base-change}, the proof of Theorem~\ref{thm:main} is given in Section~\ref{sec:torus}.
+
+Finally, in Section~\ref{sec:compactification} we describe the cone of morphism~\eqref{eq:intro:central_cone} as sections of a sheaf on a \enquote{compactified} loop space of $\stack X$ and consider some of its properties.
+
+\subsection*{Future directions}
 
@@
 I would like to thank David Nadler for the original motivation for this project and many discussions concerning it.
-
-\section{D-modules on stacks}
-\label{sec:d-mods}
+I would also like to thank David Ben-Zvi, Dennis Gaitsgory and Nathan Ilten for discussions concerning this project.
+This work has been partially supported by the National Science Foundation under Grant No.~1638352, as well as the Giorgio and Elena Petronio Fellowship Fund.
+
+\section{D-modules on stacks}\label{sec:d-mods}
 
@@
 While the first construction is more \enquote{hands on}, the second construction is often more useful from a theoretical point of view.
-It is explained in detail in the upcoming book \cite{GaitsgoryRozenblyum:prelim:StudyInDAG} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
+It is explained in detail in the book \cite{GaitsgoryRozenblyum:2017:StudyInDAG:2} (see also \cite{FrancisGaitsgory:2012:ChiralKoszulDuality} for an overview).
 Many basic properties of the category $\catDMod{\stack X}$ are explored in \cite{DrinfeldGaitsgory:2013:FinitenessQuestions} and unless stated otherwise proofs for the assertions in this section can be found there.
 
-For any morphism $f\colon \stack X → \stack Y$ we obtain a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
+For any morphism $f\colon \stack X → \stack Y$ we have a continuous functor $f^!\colon \catDMod{\stack Y} → \catDMod{\stack X}$ and a (not necessarily continuous) functor $f_*\colon \catDMod{\stack X} → \catDMod{\stack Y}$.
 If $p\colon \stack X → \pt$ is the structure map, we set
@@
     induced by $(f_*,\,f^!)$ and $(p_*,\, p^!)$ adjunctions.
+    Similarly, if $f$ is an open immersion, then the base change isomorphism coincides with the natural transformation resulting from the adjunctions $(f^!,f_*)$ and $(p^!, p_*)$.
 \end{Prop}
@@
 
-It is often useful to consider the pullback of a D-module on $\stack X$ to a smooth cover.
-For quotient stacks we give the resulting subcategory a special name.
-
-\begin{Def}
-    \label{def:pre:monodromic}%
-    Let $X$ be a scheme with an action of an algebraic group $G$ and let $p\colon X → X/G$ be the quotient map.
-    The \emph{monodromic} subcategory $\catDModMon{X}{G} ⊆ \catDMod{X}$ is the full subcategory generated by the essential image of $p^!\colon \catDMod{X/G} → \catDMod{X}$ (or equivalently by the essential image of $p^*$).
-\end{Def}
-
-In Section~\ref{sec:torus} we will be concerned with $\Gm^n$-monodromic D-modules.
-For the case of $n = 1$ one has the following powerful theorem, known as the \emph{contraction principle}.
-It will be a crucial ingredient for our proof of Theorem~\ref{thm:main}.
-
-\begin{Thm}[{\cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}}]
-    \label{thm:pre:contraction_principle}%
-    Let $X$ be a scheme with an action by $\Gm$ that extends to an action of the monoid $\as 1$.
-    Let $i\colon X^0 \hookrightarrow X$ be the closed subscheme of $\Gm$-fixed points and let $π\colon X → X^0$ be the contraction morphism induced by the $\Gm$-equivariant morphism $\as 1 → \{0\}$.
-    Then there is a canonical isomorphism of functors
-    \[
-        π_* \cong i^* \colon \catDModMon{X}{\Gm} → \catDMod{X^0}
-    \]
-    given by adjunction
-    \[
-        π_* → π_* i_* i^* = (π ∘ i)_* i^* = i^*.
-    \]
-\end{Thm}
-
-\section{Monads}
-\label{sec:monads}
+\section{Monads}\label{sec:monads}
 
@@
 We refer to \cite[Section~6.1.2]{Lurie:2009:HigherToposTheory} for the correct $∞$-categorical setup.
-The following lemma is now an immediate corollary of \cite[Lemma~\RomanNum{II}.1.7.1.4]{GaitsgoryRozenblyum:prelim:StudyInDAG} or \cite[Theorem~4.7.6.2]{Lurie:2014-draft:HigherAlgebra}.
+The following lemma is now an immediate corollary of \cite[Lemma~4.7.1.4]{GaitsgoryRozenblyum:2017:StudyInDAG:2} or \cite[Theorem~4.7.5.2]{Lurie:2017-draft:HigherAlgebra}.
 
@@
 Let us assume for the moment that $Δ$ (and hence $p_i$) is proper.
-Then $Δ_* = Δ_!$ and $p_{1,*} = p_{1,!}$ and by Section~\ref{sec:monads} we have an isomorphism of monads
+Then $Δ_* = Δ_!$ and $p_{1,*} = p_{1,!}$ and by Section~\ref{sec:monads} we have an isomorphism of monads on $\catDModHol{\stack X}$
 \begin{equation}
@@
     The base change morphism \eqref{eq:central_iso} is also an isomorphism if $Δ$ is smooth.
-    In particular this implies that the \enquote{naive expectation} holds for $\stack X = \B G$ for any algebraic group $G$, i.e.~we have
-    \[
-        \HCoh(\catDMod{\B G}) = \opalg{\GammadR\bigl(\B G,\, p_{1,!} p₂^! k_{\B G}\bigr)}.
+    In particular this implies that the \enquote{naive expectation} holds for $\stack X = \cs{G}$ for any algebraic group $G$, i.e.~we have
+    \[
+        \HCoh(\catDMod{\cs G}) = \opalg{\GammadR\bigl(\cs G,\, p_{1,!} p₂^! k_{\cs G}\bigr)}.
     \]
     An argument similar to \cite{BenZvi:mathoverflow:CohomologyOfGmodG} shows that there is a further isomorphism
-    \[
-        \GammadR\bigl(\B G,\, p_{1,!} p₂^! k_{\stack X}\bigr) \cong
-        \GammadR(G, k_G)^\dual \otimes \GammadR(\B G, k_{\B G}).
-    \]
+    \begin{equation}\label{eq:HH_BG_decomp}
+        \GammadR\bigl(\cs G,\, p_{1,!} p₂^! k_{\stack X}\bigr) \cong
+        \GammadR(G, k_G)^\dual \otimes \GammadR(\cs G, k_{\cs G}).
+    \end{equation}
     Alternatively, we can use the identification
     \[
-        \catDMod{\B G} \cong \catModules{\GammadR(G, k_{G})^\dual},
+        \catDMod{\cs G} \cong \catModules{\GammadR(G, k_{G})^\dual},
     \]
@@
 
-\section{Base change along the diagonal}
-\label{sec:base-change}
-
-\subsection{The cone of the base-change map}\label{sec:base-change:cone}
+From \eqref{eq:HH_BG_decomp} we see that $\HCoh(\catDMod{\cs G})$ contains a copy of $\opalg{\GammadR(\cs G, k_{\cs G})}$.
+Indeed this is a general phenomenon.
+
+\begin{Prop}
+    \label{prop:mono-from-cohomology}%
+    There is a canonical monomorphism 
+    \[
+      \opalg{\GammadR\bigl(\stack X,\, k_{\stack X}\bigr)}
+        \hookrightarrow
+        \HCoh\bigl(\catDMod{\stack X}\bigr).
+    \]
+\end{Prop}
+
+\begin{proof}
+    Consider the sequence of maps
+    \[
+        \stack X \xrightarrow{Δ} \stack X × \stack X \xrightarrow{\proj{1}} \stack X.
+    \]
+    Since the composition is the identity, the functor $(\proj{1})_! ∘ Δ_!$ is faithful.
+    Hence $Δ_!$ is faithful too.
+    Thus the adjunction map
+    \[
+        \eta\colon \id[\catDModHol{\stack X}] → Δ^!Δ_!
+    \]
+    is a monomorphism.
+    Completing to a distinguished triangle
+    \[
+        k_{\stack X} \xrightarrow{\eta} Δ^!Δ_! k_{\stack X} → \sheaf F \xrightarrow{δ}
+    \]
+    for some $\sheaf F \in \catDModHol{\stack X}$, we see that the connection morphism $δ$ is the zero morphism (indeed $\eta \circ \delta[1] = 0$ and $\eta$ is mono).
+    This in turn implies that the induced map
+    \[
+        \GammadR\bigl(\stack X,\, k_{\stack X}\bigr)
+        →
+        \GammadR\bigl(\stack X,\, Δ^!Δ_! k_{\stack X}\bigr)
+        \cong
+        \opalg{\HCoh\bigl(\catDMod{\stack X}\bigr)}
+    \]
+    on cohomology is a monomorphism as well.
+\end{proof}
+
+\section{Base change along the diagonal}\label{sec:base-change}
 
 Consider a Cartesian diagram of stacks
-\begin{equation}
-    \label{eq:base-change:square}
+\begin{equation*}
+    %\label{eq:base-change:square}
     \begin{tikzcd}
@@
     g^! f_!.
-\end{equation}
+\end{equation*}
 If $f$ is proper, then \eqref{eq:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
+
+\subsection{The required base changes}
+
+In order for the isomorphism \eqref{eq:intro:naive} to hold, we only need know that the base change morphism is an isomorphism on $k_{\stack X}$.
+However, it is often useful to pass to substacks, so that we need to prove the isomorphism of a slightly larger class of D-modules.
+Thus we introduce the following subcategories.
+
+\begin{Def}
+  Let $\catK{\stack X}$ be the full subcategory of $\catDMod{\stack X}$ generated by $k_{\stack X}$ and let $\catKHol{\stack X}$ be its full subcategory consisting of holonomic objects.
+\end{Def}
+
+With this we can write down the two properties that we need to check in order for the naive expectation to hold.
+
+\begin{Def}
+    Let $\stack X$ be any QCA stack.
+    Consider the Cartesian diagram
+    \[
+        \begin{tikzcd}
+            \ls \stack X \arrow[d, "p_1"] \arrow[r, "p_2"] & \stack X \arrow[d, "\Delta"] \\
+            \stack X \arrow[r, "\Delta"] & \stack X \times \stack X
+        \end{tikzcd}
+    \]
+    We say that $\stack X$ has \emph{property \bc} if the canonical morphism
+    \[
+        p_{1,!}p_2^! \to \Delta^!\Delta_!
+    \]
+    of functors $\catKHol{\stack X} \to \catDModHol{\stack X}$ is an equivalence.
+\end{Def}
+
+Let us write $\stack G_\bullet = \stack G_\bullet(\stack X)$ for the nerve of the groupoid associated to $\ls\stack X \rightrightarrows \stack X$.
+Thus
+\[
+    \stack G_m(\stack X) = \underbrace{\stack X \XXtimes \dotsb \XXtimes \stack X}_{m+1\text{ times}}.
+\]
+
+\begin{Def}
+    Let $\stack X$ be a QCA stack and consider the Cartesian square
+    \[
+        \begin{tikzcd}
+            \stack G_{n+1} \arrow[r, "p_{s}"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
+            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
+        \end{tikzcd}
+    \]
+    where the horizontal maps are induced by a map $F\colon [n] \to [m]$ in $\catCoSimplicial$.
+    We say that $\stack X$ has \emph{property \hbc} if for each such $F$ the canonical morphism
+    \[
+        p_{F+1,!}p_s^! \to p_s^!p_{F,!}
+    \]
+    of functors $\catKHol{\stack G_n} \to \catDModHol{\stack G_{m+1}}$ is an equivalence.
+\end{Def}
+
+\begin{Cor}\label{cor:properties_imply_monads}
+  If $\stack X$ has properties \bc\ and \hbc, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
+  In particular there is an isomorphism of algebras
+  \[
+      \HCoh\bigl(\catDMod{\stack X}\bigr)
+      \cong
+      \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
+  \]
+\end{Cor}
+
+\begin{proof}
+  Since $\Hom(k_{\stack X},\, \Delta^!\Delta_!k_{\stack x}) = \Hom(\Delta_!k_{\stack X},\, \Delta_!k_{\stack X}) \ne 0$, we see that $\Delta^!\Delta_!$ restricts to a monad on $\catKHol{\stack X}$.
+  Thus by the assumption $p_{1,!} p_2^!$ is also an endofunctor of $\catKHol{\stack X}$.
+  The statement now follows from a restriction of Lemma~\ref{lem:pre:groupoid_monad_hol} applied to the construction in Section~\ref{sec:HH}.
+\end{proof}
+
+\begin{Rem}
+    We expect that most quotient stacks do not have property \bc.
+    For example, a direct computation shows that the transformation of property \bc\ is not an isomorphism for the D-module $k$ on the stack $\ps1/\Ga$.
+\end{Rem}
+
+\begin{Lem}\label{lem:smooth_or_proper}
+    Let $\stack X$ be a QCA stack with diagonal morphism $\Delta\colon \stack X \to \stack X \times \stack X$.
+    \begin{enumerate}
+        \item\label{lem:smooth_or_proper:bc} If $\Delta$ is either proper of smooth, then $\stack X$ has property \bc.
+        \item\label{lem:smooth_or_proper:hbc} If $\Delta$ is proper, then $\stack X$ has property \hbc.
+        \item\label{lem:smooth_or_proper:scheme} If $\stack X$ is a (separated) scheme, then $\stack X$ has both properties \bc\ and \hbc.
+        \item\label{lem:smooth_or_proper:bg} Let $G$ be an affine algebraic group. Then the classifying stack $\cs{G}$ has both properties \bc\ and \hbc.
+    \end{enumerate}
+\end{Lem}
+
+\begin{proof}
+    Statement \ref{lem:smooth_or_proper:bc} is a direct consequence of the base change theorem, Proposition~\ref{prop:pre:base-change}.
+    To be more explicit, the smooth version follows from Proposition~\ref{prop:pre:base-change} by duality and the fact that $f^!$ agrees with $f^*$ up to shift.
+
+    We only need to show \ref{lem:smooth_or_proper:hbc} under the additional assumption that $F$ is a face or degeneracy map.
+    In either case it follows immediately that $p_{F}$ is proper and we can again apply base change.
+
+    Statement \ref{lem:smooth_or_proper:scheme} is just a special case of \ref{lem:smooth_or_proper:bc} and \ref{lem:smooth_or_proper:hbc}.
+
+    The diagonal morphism of $\cs{G}$ is smooth, so that property \bc\ follows from \ref{lem:smooth_or_proper:bc}.
+    Note that $\stack G_m(\cs{G}) \cong G^m \times \cs{G}$.
+    Thus one sees that the maps $\stack G_m(\cs{G}) \to \stack G_{m-1}(\cs{G})$ are smooth, while the maps $\stack G_m(\cs{G}) \to \stack G_{m+1}(\cs{G})$ are closed immersions (and hence proper).
+    Thus property \hbc\ follows from smooth and proper base change.
+\end{proof}
+
+\subsection{Some reduction steps}
+
+Let $i\colon\stack Y \to \stack X$ be an open (or closed) immersion.
+We have $\ls \stack Y \cong \stack Y \times_{\stack X \times \stack X} \stack Y$ and it follows that there is a canonical open (resp.~closed) immersion of loop stacks $\ls i\colon \ls \stack Y \to \ls \stack X$.
+More generally, each $\stack G_m(\stack Y)$ is an open (resp.~closed) substack of $\stack G_m(\stack X)$.
+
+\begin{Lem}\label{lem:lc_immersion}
+    Let $i\colon\stack Y \hookrightarrow \stack X$ is a locally closed immersion of QCA stacks.
+    If $\stack X$ has property \bc\ or property \hbc, then so does $\stack Y$.
+\end{Lem}
+
+\begin{proof}
+    We will show the statement for property \bc.
+    The proof for \hbc\ is essentially the same.
+    First we note that if $\sheaf F \in \catKHol{\stack Y}$, then $i_*\sheaf F \in \catKHol{\stack X}$ since
+    \[
+      \Hom_{\catDMod{\stack X}}(k_{\stack X}, i_*\sheaf F) \cong
+      \Hom_{\catDMod{\stack Y}}(i^*k_{\stack X}, \sheaf F) \cong
+      \Hom_{\catDMod{\stack Y}}(k_{\stack Y}, \sheaf F) \ncong 0.
+    \]
+    Thus it suffices to show that $p_{\stack Y,1,!}p_{\stack Y,2}^!i^! \to \Delta_{\stack Y}^!\Delta_{\stack Y,!}i^!$ is an isomorphism of $\catKHol{\stack X}$.
+    We split $i$ into a closed immersion followed by an open one and prove the two cases separately.
+
+    Let us first assume that $i$ is open.
+    Using the assumption on $\stack X$ and the fact that $i^! = i^*$ we get
+    \begin{multline*}
+        p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
+        p_{\stack Y,1,!} (\ls i)^! p_{\stack X,2}^! \cong
+        i^! p_{\stack X,1,!} p_{\stack X,2}^! \isoto \\
+        i^! \Delta_{\stack X}^! \Delta_{\stack X,!} =
+        \Delta_{\stack Y}^! (i\times i)^! \Delta_{\stack X,!} \cong
+        \Delta_{\stack Y}^! \Delta_{\stack X,!} i^!.
+    \end{multline*}
+    Now let $i$ be a closed immersion.
+    As above, it suffices to show that $i_!p_{\stack Y,1,!}p_{\stack Y,2}^!i^! \to i_!\Delta_{\stack Y}^!\Delta_{\stack Y,!}i^!$ is an equivalence.
+    Using the assumption on $\stack X$ and the fact that $i_! = i_*$ we get
+    \begin{multline*}
+        i_! p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
+        p_{\stack X,1,!} (\ls i)_! p_{\stack Y,2}^!i^! \cong
+        p_{\stack X,1,!} p_{\stack X,2}^! i_!i^! \isoto \\
+        \Delta_{\stack X}^! \Delta_{\stack X,!} i_!i^! \cong
+        \Delta_{\stack Y}^! (i\times i)_! \Delta_{\stack X,!}i^! =
+        i_! \Delta_{\stack Y}^! \Delta_{\stack X,!} i^!.
+        \qedhere
+    \end{multline*}
+\end{proof}
+
+Since all operations are local we can check the properties on open covers.
+
+\begin{Lem}\label{lem:open_cover}
+    If $\stack X$ has an cover by open substacks $\stack U_i$ with property \bc\ (resp.~with property \hbc), then $\stack X$ has property \bc\ (resp.~property \hbc).
+    \qed
+\end{Lem}
+
+\begin{Lem}\label{lem:product}
+    If $\stack{X_1}$ and $\stack{X_2}$ both have property \bc\ (resp.~property \hbc), then so does $\stack{X_1} \times \stack{X_2}$.
+\end{Lem}
+
+\begin{proof}
+    The category $\catDMod{\stack X_1 \times \stack X_2}$ is generated by elements of the form $\sheaf F_1 \boxtimes \sheaf F_2$ with $\sheaf F_i \in \catDModHol{\stack X_i}$.
+    For any schematic morphism $f\colon \stack Y \to \stack Z$ of QCA stacks the functor $f^!$ is continuous on $\catDMod{\stack Z}$ and $f_!$ is preservers colimits in $\catDModHol{\stack Y}$, since it has a right adjoint.
+    Since the inclusion of a full subcategory reflects all colimits it is thus sufficient to check that the properties holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catKHol{\stack X_1 \times \stack X_2}$.
+
+    Note that $\ls(\stack X_1 \times \stack X_2) \cong \ls \stack X_1 \times \ls \stack X_2$ and more generally $\stack G_m(\stack X_1 \times \stack X_2) \cong \stack G_m(\stack X_1) \times \stack G_m(\stack X_2)$.
+    The statement now follows because all functors respect $\boxtimes$.
+\end{proof}
+
+We would like to have an extension of Lemma~\ref{lem:product} to fiber products.
+Unfortunately, as the discussion in \cite[Section~1.2]{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup} shows, the category of D-modules on a fiber product $\stack X_1 \times_{\stack Y} \stack X_2$ is rather badly behaved unless $\stack Y$ is a scheme.
+Thus we have to restrict ourselves to the following partial result which is sufficient for our applications.
+
+\begin{Lem}\label{lem:product_quotient}
+  Let $G$ be an affine algebraic group acting on schemes $X_1$ and $X_2$.
+  Suppose the quotient stacks $\stack X_1 = X_1/G$ and $\stack X_2 = X_2/G$ both have property \bc\ (resp.~property \hbc).
+  Then so does $(X_1 \times X_2)/G$.
+\end{Lem}
+
+\begin{proof}
+  The stack $(X_1 \times X_2)/G$ can be rewritten as $\stack X_1 \times_{\cs{G}} \stack X_2$.
+  Thus the results of \cite[Section~5.2]{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup} show that $!$-pullback exhibits the category $\catDMod{\stack X_1} \otimes_{\catDMod{\cs{G}}} \catDMod{\stack X_2}$ as a full subcategory of $\catDMod{\stack X_1 \times_{\cs{G}} \stack X_2}$ containing $\catK{\stack X_1 \times_{\cs{G}} \stack X_2}$.
+  This category can be described as the limit of the cosimplicial category with cosimplices
+  \[
+    \catDMod{\stack X_1 \times \cs{G} \times \dotsb \times \cs{G} \times \stack X_2}.
+  \]
+  Thus it suffices to show the properties for the stacks $\stack X_1 \times \cs{G} \times \dotsb \times \cs{G} \times \stack X_2$, where they follow form Lemmas~\ref{lem:product} and~\ref{lem:smooth_or_proper}\ref{lem:smooth_or_proper:bg}.
+\end{proof}
+
+\subsection{Contractive \texorpdfstring{$\Gm$}{Gm}-actions}
+
+Let $\stack X$ be a QCA stack with an action of $\Gm$.
+We call the action \emph{(globally) contractive} if it can be extended to an action of the monoid $\as 1$.
+Following the convention of \cite[Appendix~C]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} we denote by $\stack X^0$ the stack of $\{0,1\}$-equivariant maps $\{0\} \to \stack X$.
+The map $\{0\} \to \{0,1\}$ induces a \emph{contraction morphism} $\pi\colon \stack X \to \stack X^0$.
+
+We then have the following \emph{contraction principle} (cf.~also \cite[Proposition~3.2.2]{DrinfeldGaitsgory:2014:OnATheoremOfBraden}).
+
+\begin{Thm}[{\cite[Corollary~C.5.4]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}}]
+    \label{thm:contraction_principle}%
+    Let $\stack X$ be a contractive stack with a trivial $\Gm$-action.
+    Then there is a canonical isomorphism of functors
+    \[
+        π_! \cong i^! \colon \catDModHol{\stack X} → \catDModHol{\stack X^0}
+    \]
+    given by adjunction
+    \[
+        π_! → i^! i_! π_!  = i^! (π ∘ i)_! = i^!.
+    \]
+\end{Thm}
+
+\begin{Rem}
+  For our intended application in the proof of Theorem~\ref{thm:torus_quotient}, the special case of this statement for $\Gm$-quotient stacks is sufficient.
+  In this case the statement can be proved directly without having to show the full \enquote{stacky} version, cf.~\cite[Proposition~5.3.2]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}.
+\end{Rem}
+
+\begin{Prop}\label{prop:contractive}
+    Assume that $\stack X$ has a trivial contractive $\Gm$-action such that $i\colon \stack X^0 \to \stack X$ is a closed immersion and both $\stack X^0$ and $\stack U = \stack X\setminus \stack X^0$ have property \bc\ (respectively property \hbc).
+    Then so does $\stack X$.
+\end{Prop}
+
+\begin{proof}
+    Let us first prove the statement for property \bc.
+    Let $j\colon \stack U \hookrightarrow \stack X$ be the (open) complement of $i$.
+    Consider the distinguished triangle
+    \[
+        i_!i^! \Delta^!\Delta_! \to \Delta^!\Delta_! \to j_*j^*\Delta^!\Delta_!
+    \]
+    on $\catDModHol{\stack X}$.
+    It suffices to show that the canonical maps on the outside terms to $i_!i^! p_{1,!}p_2^!$ and $j_*j^* p_{1,!}p_2^!$ respectively are isomorphisms.
+
+    Using the fact that $j^* = j^!$, base change and the assumption we see that
+    \[
+        j_*j^*\Delta^!\Delta_! \cong
+        j_*\Delta^!\Delta_!j^* \isoto
+        j_*p_{\stack U,1,!}p_{\stack U,2}^! j^* \cong
+        j_*j^* p_{1,!}p_2^!
+    \]
+    is an equivalence.
+
+    Write $\pi\colon \stack X \to \stack X^0$ for the contraction map opposite to $i$.
+    Then by the contraction principle,
+    \begin{equation}\label{eq:lem:bc_contractive}
+        i_!i^! \Delta^!\Delta_! =
+        i_!\Delta_{\stack X_0}^!(i\times i)^! \Delta_! \cong
+        i_!\Delta_{\stack X_0}^!(\pi\times \pi)_! \Delta_! =
+        i_!\Delta_{\stack X_0}^!\Delta_{\stack X_0,!} \pi_! \cong
+        i_!\Delta_{\stack X_0}^!\Delta_{\stack X_0,!} i^!.
+    \end{equation}
+    Write $\ls i \colon \ls\stack X^0 \hookrightarrow \ls\stack X$ for the closed inclusion of loop stacks.
+    We note that $\ls\stack X$ inherits a contractive $\Gm$ action form $\stack X$.
+    Let $\ls \pi\colon \ls\stack X \to \ls\stack X^0$ be the corresponding contraction map.
+    Then by assumption and the contraction principle, \eqref{eq:lem:bc_contractive} is equivalent to
+    \[
+        i_!p_{\stack X_0,1,!}p_{\stack X_0,2}^! i^! =
+        i_!p_{\stack X_0,1,!} (\ls i)^! p_{2}^! \cong
+        i_!p_{\stack X_0,1,!} (\ls \pi)_! p_{2}^! =
+        i_! \pi_! p_{1,!} p_{2}^! =
+        i_! i^! p_{1,!} p_{2}^!.
+    \]
+    Finally, we note that the $\Gm$-action on $\stack X$ induces contractive $\Gm$-actions on each $\stack G_m(\stack X)$ with $(\stack G_m(\stack X))^0 = \stack G_m(\stack X^0)$.
+    Thus the statement for property \hbc\ follows in the same way as above.
+\end{proof}
+
+\section{Torus quotients}\label{sec:torus}
+
+\begin{Thm}\label{thm:torus_quotient}
+    Let $X$ be a normal quasi-projective variety $X$ over an algebraically closed field $k$ of characteristic $0$ with an action of a torus $T$.
+    Then the quotient stack $\stack X = X/T$ has properties \bc\ and \hbc.
+\end{Thm}
+
+\begin{proof}
+  By Sumihiro's theorem \cite{Sumihiro:1974:EquivariantCompletions} and Lemma~\ref{lem:open_cover} we can assume that $\stack X$ is affine with a linear action of $T$.
+  By Lemma~\ref{lem:lc_immersion} it further suffices to consider the case that $\stack X = \as{m}/T$ for some $m$.
+  By Lemma~\ref{lem:product_quotient}, we can further decompose $\as{m}$ into $T$-eigenspaces.
+  Each of those splits into copies of $\as{1}/T$, which in turn can be written as $\as{1}/\Gm \times BT'$ for some subtorus $T'$ of $T$.
+
+  By Lemma~\ref{lem:smooth_or_proper}\ref{lem:smooth_or_proper:bg} it remains to consider the stack $\as{1}/\Gm$, where $\Gm$ acts nontrivially.
+  If the $\Gm$ action is contractive this case follows immediately from Proposition~\ref{prop:contractive} and Lemma~\ref{lem:smooth_or_proper}.
+  Otherwise the inverse of the $\Gm$-action on $\as1$ is contractive and we can use the contraction principle (and hence Proposition~\ref{prop:contractive}) with the monoid $\as[\infty]{1} = \Gm \cup \{\infty\}$ instead of $\Gm \cup \{0\}$.
+\end{proof}
+
+Theorem~\ref{thm:main} is now an immediate consequence of Theorem~\ref{thm:torus_quotient} and Corollary~\ref{cor:properties_imply_monads}
+
+\begin{Ex}
+  To illustrate let us compute $\HCoh(\catDMod{\as1/\Gm})$ where $\Gm$ acts in the usual way.
+  Let $i\colon \stack Z \to \ls\stack X$ be the inclusion of the fiber $\stack Z = \Gm \times \cs{\Gm}$ over the origin and $j\colon \stack U \to \ls\stack X$ the inclusion of the open complement $\stack U = \Gm/\Gm = \pt$.
+  Let $p\colon \stack X \to \pt$ be the structure map.
+  We have to compute $p_*p_{1,!}p_2^!k_{\stack X}$.
+
+  First we note that $p_2^!k_{\stack X} = \omega_{\ls \stack X}$.
+  Consider now the distinguished triangle
+  \[
+    p_*p_{1,!}p_2^!i_!i^!\omega_{\ls \stack X} \to
+    p_*p_{1,!}p_2^!\omega_{\ls \stack X} \to
+    p_*p_{1,!}p_2^!j_*j^!\omega_{\ls \stack X}.
+  \]
+  The right term is just the cohomology of a point, i.e.~$k$.
+  The left term evaluates to
+  \[
+    \Gamma_c(\Gm, k_{\Gm}) \otimes \GammadR(\cs{\Gm},k_{\cs{\Gm}}) \cong \bigl(k[-1] \oplus k[-2]\bigr) \otimes k[u]
+  \]
+  with $u$ in degree $2$.
+  As the zeroth Hochschild cohomology cannot vanish (it must contain the identity functor), the connecting morphism is zero.
+  Hence
+  \[
+    \HCoh(\catDMod{\as1/\Gm}) \cong k[x]
+  \]
+  with $x$ in degree $1$.
+  More generally
+  \[
+    \HCoh(\catDMod{\as n/\Gm^n}) \cong k[x_1,\dotsc,x_n].
+  \]
+  In a future note we plan to give explicit computations for general toric varieties.
+\end{Ex}
+
+\section{Base change and compactification}\label{sec:compactification}
+
+As was noted above, for a general stack there is no reason to expect that the base change morphism is an isomorphism.
+In such cases it is then interesting to understand the cone of the morphism, describing how badly base change fails.
+
+\subsection{The general situation}
+
+Let us for the moment return to an arbitrary Cartesian diagram of stacks
+\begin{equation}
+  \label{eq:c:base-change:square}
+    \begin{tikzcd}
+        \stack Z \arrow[d, "p"] \arrow[r, "q"] & \stack X₁ \arrow[d, "f"] \\
+        \stack X₂ \arrow[r, "g"] & \stack Y
+    \end{tikzcd}
+\end{equation}
+with $f$ and $g$ schematic.
+As discussed above, in this situation we have a morphism of functors $\catDModHol{\stack X₁} → \catDModHol{\stack X₂}$,
+\begin{equation}
+    \label{eq:c:base-change-morphism}
+     p_! q^! → g^! f_!
+\end{equation}
+induced by adjunctions
+\begin{equation}
+    \label{eq:c:base-change-adjunctions}
+    p_! q^! →
+    p_! q^! f^! f_! =
+    p_! p^! g^! f_! →
+    g^! f_!.
+\end{equation}
+If $f$ is proper, then \eqref{eq:c:base-change-morphism} is an isomorphism by Proposition~\ref{prop:pre:base-change}.
 To understand the behavior for non-proper $f$, we will approximate it by a proper morphism.
@@
 
-Let us now assume that in the situation of diagram \eqref{eq:base-change:square} there exists a relative compactification of $f\colon \stack X₁ → \stack Y$.
+Let us now assume that in the situation of diagram \eqref{eq:c:base-change:square} there exists a relative compactification of $f\colon \stack X₁ → \stack Y$.
 Let $\stack X₁^c$ be the closed complement of the open inclusion $j\colon \stack X₁ \hookrightarrow \bar{\stack X}₁$.
 Similarly, we denote by $\bar{\stack Z} = \stack X₂ ×_{\stack Y} \bar{\stack X}₁$ and $\stack Z^c = \stack X₂ ×_{\stack Y} \stack X₁^c$ the corresponding fiber products.
-The corresponding inclusion and projection maps are denoted as is indicated in the following Cartesian diagrams.
+The inclusion and projection maps are denoted as is indicated in the following Cartesian diagrams.
 \[
@@
 
-\subsection{Relative compactifications for quotient stacks}
-\label{sec:base-change:compactification}%
-
-In the preceding section we simply assumed that a relative compactification of the given map exists.
+\subsection{Relative compactifications for quotient stacks}\label{sec:compactification:quotient}%
+
+In the preceding section we simply assumed that a relative compactification of the given map $f$ exists.
 We will now construct such a compactification for the diagonal map of a quotient stack.
@@
     It is possible to extend the methods of \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden} to quotients by higher dimensional tori.
-    The resulting constructions are useful for doing explicit computations.
+    The resulting constructions are useful for explicit computations.
 \end{Rem}
 
-\subsection{The !-base-change property}
+\subsection{Base-change of the diagonal}
+
+We will now formulate a criterion analogous to properties \bc\ and \hbc, but using Lemma~\ref{lem:base-change-criterion}.
 
@@
 
-\begin{Def}\label{def:good}
-    We say that a quotient stack $\stack X = X/G$ \emph{\isgood} if the following two conditions hold.
-    \begin{enumerate}
-        \item $!$-base-change holds along the Cartesian square
-            \[
-                \begin{tikzcd}
-                    \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
-                    \stack X \arrow[r, "Δ"] & \stack X × \stack X
-                \end{tikzcd}
-            \]
-            i.e.~the canonical morphism $p_{1,!}p₂^! → Δ^!Δ_!$ is an isomorphism on holonomic D-modules.
-        \item For any schematic morphism $f\colon \stack Y₂ = Y₂/G → \stack Y₁ = Y₁/G$ of $G$-quotient stacks over $\stack X$, $!$-base-change holds along the Cartesian diagram
-            \[
-                \begin{tikzcd}
-                    \lsY[\stack Y₂]{\stack X} \arrow[r, "\ls f"] \arrow[d, "π₂"] & \lsY[\stack Y₁]{\stack X} \arrow[d, "π₁"]\\
-                    \stack Y₂ \arrow[r, "f"] & \stack Y₁
-                \end{tikzcd}
-            \]
-            i.e.~the canonical morphism $π_{2,!}(\ls f)^! → f^! π_{1,!}$ is an isomorphism on holonomic D-modules.
-    \end{enumerate}
-\end{Def}
-
-We will show in Section~\ref{sec:torus} that any stack of the form $\rquot{X}{\Gm^n}$ \isgood.
-Theorem~\ref{thm:main} then immediately follows from the following observation which lets us compute the Hochschild cohomology of $\catDMod{\stack X}$ for \goodX{quotient stacks}.
-
-\begin{Prop}\label{prop:good-is-good}
-    If $\stack X = X/G$ \isgood, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
-    In particular there is an isomorphism of algebras
-    \[
-        \HCoh\bigl(\catDMod{\stack X}\bigr)
-        \cong
-        \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
-    \]
-\end{Prop}
-
-\begin{proof}
-    We apply Lemma~\ref{lem:pre:groupoid_monad_hol} to the groupoid induced by $Δ\colon \stack X → \stack X × \stack X$.
-    Thus we let $\stack G_\cx$ be the simplicial stack with
-    \[
-        \stack G_i = \underbrace{\stack X \mathop{×}\limits_{\stack X × \stack X} \dotsb \mathop{×}\limits_{\stack X × \stack X} \stack X}_{\text{$i+1$ factors}}.
-    \]
-    The second base change condition of Lemma~\ref{lem:pre:groupoid_monad_hol} holds by definition.
-    Let $F\colon [n] → [m]$ be a morphism in $\cat{Δ}^{\mathrm{op}}$ and consider the induced diagram
-    \[
-        \begin{tikzcd}
-            \stack G_{n+1} \arrow[d] \arrow[r] & \stack G_{m+1} \arrow[d] \arrow[r] & \stack X \arrow[d, "Δ"] \\
-            \stack G_{n} \arrow[r] & \stack G_m \arrow[r] & \stack X × \stack X
-        \end{tikzcd}
-    \]
-    We note that $\stack G_{m+1} = \stack G_m ×_{\stack X × \stack X} \stack X$ and similarly for $\stack G_n$.
-    Thus setting $\stack Y₂ = \stack G_n$ and $\stack Y₁ = \stack G_m$ in the definition of \goodness, we see that all the required base changes holds.
-\end{proof}
-
-\begin{Rem}
-    We expect that most quotient stacks \arenotgood.
-    For example, a direct computation shows that Theorem~\ref{thm:main} does not hold for the stack $\ps1/\Ga$, and hence it \isnotgood.
-\end{Rem}
-
-We will use Lemma~\ref{lem:base-change-criterion} in order to check the base change criteria in Definition~\ref{def:good}.
-In order to do so we unfortunately have to introduce some additional notation.
-Let us fix a compactification $\bar G$ of $G$ and a relative compactification $\stack X \xrightarrow{j} \bar{\stack X} \xrightarrow{\bar Δ} \stack X × \stack X$ as in Section~\ref{sec:base-change:compactification}.
+We will use Lemma~\ref{lem:base-change-criterion} in order to reformulate the base change criteria in properties \bc\ and \hbc.
+To do so we unfortunately have to introduce some additional notation.
+Let us fix a compactification $\bar G$ of $G$ and a relative compactification $\stack X \xrightarrow{j} \bar{\stack X} \xrightarrow{\bar Δ} \stack X × \stack X$ as in Section~\ref{sec:compactification:quotient}.
 For any $\stack Y → \stack X$ this induces a relative compactification $\clsY{\stack X} = \stack Y \XXtimes \bar{\stack X}$.
@@
 With this setup we make the following definition.
-\begin{Def}\label{def:good'}
-    We say that a quotient stack $\stack X = X/G$ \emph{\isgoodb} if the following two conditions hold.
+
+\begin{Def}\label{def:good}
+    We say that a quotient stack $\stack X = X/G$ \emph{\isgood} if the following two conditions hold.
     \begin{enumerate}
@@
 
-Lemma~\ref{lem:base-change-criterion} says that $\goodnessbshort$\ implies $\goodnessshort$.
-In the remainder of this section we will discuss several reduction steps for showing that a given stack \isgoodb.
-
-%\begin{Lem}
-%    If $\stack X₁ = X₁/G₁$ and $\stack X₂ = X₂/G₂$ are \goodstack, then $\stack X₁ × \stack X₂$ is \goodstack.
-%\end{Lem}
-%
-%\begin{proof}
-%    This follows from compatibility of $i_{\stack Y}^*\bar{q}_{\stack Y}^!j_!$ with $\boxtimes$ and coproducts.
-%    (Note that $\lscY{(\stack X₁ × \stack X₂)} = \lscY \stack{X₁} × \clsY \stack{X₂} ∪ \clsY{\stack X₁} × \lscY{\stack X₂}$.)
-%\end{proof}
+\begin{Prop}\label{prop:good-is-good}
+    If $\stack X = X/G$ \isgood, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
+    In particular there is an isomorphism of algebras
+    \[
+        \HCoh\bigl(\catDMod{\stack X}\bigr)
+        \cong
+        \opalg{\GammadR\bigl(\stack X,\, p_{1,!} p₂^! k_{\stack X}\bigr)}.
+    \]
+\end{Prop}
+
+\begin{proof}
+  By Lemma~\ref{lem:base-change-criterion}, \goodness\ implies properties \bc\ and \hbc.
+\end{proof}
+
+\subsection{Some reductions}
 
@@
     Let $U$ be a $G$-equivariant open subset of $X$.
-    If $X/G$ \isgoodb\ then $U/G$ \isgoodb.
+    If $X/G$ \isgood\ then $U/G$ \isgood.
 \end{Lem}
@@
     Set $\stack U = U/G$.
-    We will only show the second condition of Definition~\ref{def:good'}, the first one is similar.
+    We will only show the second condition of Definition~\ref{def:good}, the first one is similar.
     Thus let $f\colon \stack Y₂ → \stack Y₁$ be a map of quotient stacks over $\stack U$ (and hence also over $U$).
@@
 \begin{Lem}\label{lem:base-change:scheme-cover}
-    A stack $X/G$ \isgoodb\ if and only if the following two conditions hold:
+    A quotient stack $X/G$ \isgood\ if the following two conditions hold:
     \begin{enumerate}
-        \item The composition $(i_{\stack X}')^*(\bar p₂')^! j'_!$ vanishes on $\catDModHolMon{Γ}{G×G}$.
+        \item The composition $(i_{\stack X}')^*(\bar p₂')^! j'_!$ vanishes on $\catDModHol{Γ/G×G}$.
         \item For each equivariant morphism $f'\colon Y₂ → Y₁$ of $G$-schemes the composition $(i_{\stack Y₂}')^*(\scls f)^!
-j'_{\stack Y₁,!}$ vanishes on $\catDModHolMon{\slsY[\stack Y₁]{\stack X}}{G×G}$.
+j'_{\stack Y₁,!}$ vanishes on $\catDModHol{\slsY[\stack Y₁]{\stack X}/G×G}$.
     \end{enumerate}
@@
     \label{lem:base-change:cover}%
-    If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ \aregoodb, then $X/G$ \isgoodb.
+    If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ \aregood, then $X/G$ \isgood.
 \end{Lem}
@@
 
-Finally, it will be useful to consider only partial compactifications.
-That is, in the constructions of Section~\ref{sec:base-change:compactification}, instead of going all the way to $\bar G$ we only use some subvariety of it.
+Finally, can be useful to consider only partial compactifications.
+That is, in the constructions of Section~\ref{sec:compactification:quotient}, instead of going all the way to $\bar G$ we only use some subvariety of it.
 Thus let $H$ be a $G×G$-stable subvariety of $\bar G$ containing $G$, and let $^H\bar{Γ}$ be the closure of $Γ$ in $H × X × X$.
@@
     Let $H_i$ be an open cover of $\bar G$ by $G×G$-stable subvarieties, each containing $G$.
-    Then $\stack X = X/G$ \isgoodb\ if and only if the following two conditions hold for each $i$:
+    Then $\stack X = X/G$ \isgood\ if and only if the following two conditions hold for each $i$:
     \begin{enumerate}
@@
 
-\section{Torus quotients}
-\label{sec:torus}
-
-In this section we will apply the tools from the previous section to torus quotient stacks.
-Specifically, we will prove the following theorem.
-
-\begin{Thm}
-    \label{thm:torus:is-good}%
-    Let $G \cong \Gm^n$ be a torus acting locally linearly on a scheme $X$ of finite type over $k$.
-    Then the stack $\stack X = X/G$ \isgoodb.
-\end{Thm}
-
-Together with Lemma~\ref{lem:base-change-criterion} and Proposition~\ref{prop:good-is-good} this implies our main result, Theorem~\ref{thm:main}.
-Here by a \enquote{locally linear action} we mean that it is possible to cover $X$ by open $G$-stable subschemes $U_i$ such that each $U_i$ is $G$-equivariantly isomorphic to an open subscheme of some affine space $\as m$ with linear $G$-action.
-This assumption is actually stricter than needed, see Remark~\ref{rem:why_locally_linear} below.
-
-\begin{Rem}
-    Theorem~\ref{thm:torus:is-good} actually holds for $G$ the product of a torus and a finite Abelian group.
-    The argument is exactly the same as in our case, but for the sake of keeping notational complexity down we will not present it here.
-\end{Rem}
-
-By Lemma~\ref{lem:base-change:cover}, it suffices to prove Theorem~\ref{thm:torus:is-good} for stacks $X/G$ with $X$ affine.
-We fix an isomorphism $G \cong \Gm^n$ and compactify $G$ to $\bigl(\ps1\bigr)^n$.
-The variety $\bigl(\ps1\bigr)^n$ can be covered by $G$-equivariant open subvarieties of the form $\as n$.
-Thus by Lemma~\ref{lem:base-change:cover-by-relative-compactifications}, it suffices to check \goodnessb\ for the partial compactification $\Gm^n \subseteq \as n$.
-To simplify notation, we drop the superscript $\as n$ from the notation and set $\bar{\stack X} = {}^{\as n}\bar{\stack X}$ and similarly for all other spaces and the various maps.
-In other words, from now on all compactifications will implicitly be only with respect to $G \subseteq \as n$ (rather than $G \subseteq (\ps 1)^n$).
-
-We fix a morphisms of $G$-quotient stacks $f\colon \stack Y₂ → \stack Y₁$ over $\stack X$, induced by a $G$-equivariant morphism of schemes $f'\colon Y₂ → Y₁$.
-Further let $h_i'\colon Y_i → X$ be the structure maps.
-According to Lemma~\ref{lem:base-change:scheme-cover}, rather than working directly with the stacks, we can base change to schemes.
-We will use the notation of Lemma~\ref{lem:base-change:scheme-cover}, but for ease of notation we will drop the primes and the \enquote{$\stack Y$} from the maps.
-The following diagram summarizes all the spaces and maps that we need to consider.
-\[
-    \begin{tikzcd}
-        Γ \arrow[d, hook, "j"] & & \slsY[\stack Y₁]{\stack X} \arrow[d, hook, "j₁"] & \\
-        \bar Γ & \scls{\stack X} \arrow[l, "\bar p₂"'] & \sclsY[\stack Y₁]{\stack X} \arrow[l, gray, "\scls{h₁}"'] & \sclsY[\stack Y₂]{\stack X} \arrow[l, "\scls{f}"'] \\
-        & \slsc{\stack X} \arrow[u, hook, "i"] &  & \slscY[\stack Y₂]{\stack X} \arrow[u, hook, "i₂"]
-    \end{tikzcd}
-\]
-We want to show that our usual push-pull operations vanish along the two zig-zags (for $G×G$-mododromic holonomic D-modules).
-To unify notation, let us set $Y₀ = X$ and $h_0 = \id[X]$
-
-The general idea is now to introduce $\Gm$-actions that contracts $\sclsY[\stack Y_i] \stack X$ onto $\slscY[\stack Y_i] \stack X$.
-In order to do so, we will cut the schemes
-\[
-    \sclsY[\stack Y_i] \stack X =
-    \biggl\{
-        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ
-    \biggr\}
-\]
-into pieces according to the subgroups of $G$ that stabilize $h_i(y)$.
-For this let $\Stab\stack X$ be the set of all closed subgroups of $G$ that are stabilizers of points of $X$, i.e.
-\[
-    \Stab\stack X = \bigl\{ G_x : x ∈ X \bigr\}.
-\]
-
-\begin{Lem}
-    \label{lem:finitely_many_stabilizers}%
-    The set $\Stab\stack X$ is finite.
-\end{Lem}
-
-\begin{proof}
-    Since $X$ is affine, it can be embedded $G$-equivariantly into some $\as m$ with a linear $G$-action.
-    For $\as m/G$ the statement is easy to see.
-\end{proof}
-
-\begin{Rem}\label{rem:why_locally_linear}
-    We only use the assumption that the action is locally linear to prove Lemma~\ref{lem:finitely_many_stabilizers}, i.e.~that $\Stab\stack X$ is locally finite.
-    Thus it would suffice to assume in Theorem~\ref{thm:torus:is-good} that $X$ can be covered by open subschemes for which Lemma~\ref{lem:finitely_many_stabilizers} holds.
-\end{Rem}
-
-Let $S$ be closed subgroup of $G$ and let $X^S$ be the $S$-fixed points of $X$.
-Since $G$ is Abelian (and hence $S$ a normal subgroup), $X^S$ is a $G$-stable closed subscheme of $X$.
-Hence $X^S/G$ is a closed substack of $\stack X$.
-Let $\bar S$ be the closure of $S$ in $\bar G = \as n$ and consider the closed subspace
-\[
-    \stabclsY[\stack Y_i]{S}{\stack X} =
-    \biggl\{
-        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^S,\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S
-    \biggr\}
-    ⊆
-    \sclsY[\stack Y_i] \stack X.
-\]
-
-\begin{Lem}
-    \label{lem:stabilizers_cover}%
-    For $i \in \{0,1,2\}$, the subspaces $\stabclsY[\stack Y_i]{S}{\stack X}$ for $S ∈ \Stab\stack X$ cover $\sclsY[\stack Y_i]{\stack X}$.
-\end{Lem}
-
-\begin{proof}
-    Consider the spaces
-    \[
-        \stablsY[\stack Y_i]{S}{\stack X} =
-        \biggl\{
-            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × G : h_i(y) ∈ X^S,\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ Γ \text{ and } g₂ ∈ g₁S
-        \biggr\}
-        \subseteq \slsY[\stack Y_i] \stack X.
-    \]
-    The closure of $\stablsY[\stack Y_i]{S}{\stack X}$ in $\sclsY[\stack Y_i] \stack X$ is exactly $\stabclsY[\stack Y_i]{S}{\stack X}$.
-    It is easy to see that the subspaces $\stablsY[\stack Y_i]{S}{\stack X}$ for $S ∈ \Stab \stack X$ cover $\slsY[\stack Y_i] \stack X$.
-    Now the statement follows from the fact that the closure of a finite union is the union of the individual closures.
-\end{proof}
-
-The upshot of this is that we can check vanishing by restricting to all $\stabclsY[\stack Y_i]{S}{\stack X}$.
-However, since these spaces are closed we will need to make use of a Mayer--Vietoris argument.
-Thus we need to also consider intersections of these schemes.
-For this let $S₁ \subseteq S₂$ be two subgroups of $G$ contained in $\Stab\stack X$ and set
-\[
-    \stabclsY[\stack Y_i]{S₁,S₂} \stack X =
-    \biggl\{
-        \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁\bar S₁
-    \biggr\}.
-\]
-Clearly we have $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \subseteq \stabclsY[\stack Y_i]{S₁}{\stack X}$ and $\stabclsY[\stack Y_i]{S}{\stack X} = \stabclsY[\stack Y_i]{S,S}{\stack X}$.
-Similarly, we set
-\[
-    \bar Γ^{S₁,S₂} = \bigl\{ (g,x,y) ∈ \bar Γ : x ∈ X^{S₂} \text{ and there exists $g' ∈ G$ such that $g ∈ g'S₁$}  \bigr\}.
-\]
-As in Lemma~\ref{lem:stabilizers_cover} one sees that the closed subschemes $\bar Γ^{S,S}$ cover $\bar Γ$.
-Denote the inclusions by
-\[
-    α_i^{S₁,S₂}\colon \stabclsY[\stack Y_i]{S₁,S₂}{\stack X} \hookrightarrow \sclsY[\stack Y_i]{\stack X}
-    \qquad\text{and}\qquad
-    α_{-1}^{S₁,S₂}\colon \bar Γ^{S₁,S₂} \hookrightarrow \bar Γ.
-\]
-We are now ready to formulate the main technical lemma of this section.
-It will allow us to cut up our spaces into pieces on which we have control over the sheaves of interest.
-
-\begin{Lem}\label{lem:torus:key}
-    Fix any $S₁ ⊆ S₂$ in $\Stab\stack X$ and a component $H$ of $\bar G \setminus G$ (hence $H$ is a hyperplane of $\as n$).
-    Write $Z_i$ for the closed subschemes of $\slscY[\stack Y_i]\stack X$ with $g₂ ∈ H$, and similarly $Z_{-1} = \bar Γ ∩ H × X × X$.
-    Consider the Cartesian diagrams
-    \begin{equation}\label{eq:lem:torus:key:cartesian}
-        \begin{tikzcd}
-            Z₂ \arrow[r, hook, "i₂^H"] \arrow[d, "\scls f^H"] & \sclsY[\stack Y₂]{\stack X} \arrow[d, "\scls f"] \\
-            Z₁ \arrow[r, hook, "i₂^H"] & \sclsY[\stack Y₁]{\stack X}
-        \end{tikzcd}
-        \qquad\text{and}\qquad
-        \begin{tikzcd}
-            Z₀ \arrow[r, hook, "i₀^H"] \arrow[d, "\bar p₂^H"] & \scls{\stack X} \arrow[d, "\bar p₂"] \\
-            Z_{-1} \arrow[r, hook, "i_{-1}^H"] & \bar Γ
-        \end{tikzcd}. 
-    \end{equation}
-    Then the canonical morphisms [Write up the morphisms?]
-    \[
-        i^{H,*}_0 α_{0,*}^{S₁,S₂}α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F
-        →
-        \bar p₂^{H,!} i^{H,*}_{-1} α_{-1,*}^{S₁,S₂}α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
-    \]
-    and
-    \[
-        i^{H,*}_2 α_{2,*}^{S₁,S₂}α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G
-        →
-        {\scls f}^{H,!} i^{H,*}_1 α_{1,*}^{S₁,S₂}α₁^{S₁,S₂,!} j_{1,!} \sheaf G.
-    \]
-    are isomorphisms for any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ and $\sheaf G ∈ \catDModHolMon{\slsY[\stack Y₁]{\stack X}}{G×G}$.
-\end{Lem}
-
-Before proving the lemma, let us first finish the proof of Theorem~\ref{thm:torus:is-good}, assuming the Lemma.
-
-\begin{proof}[Proof of Theorem~\ref{thm:torus:is-good}]
-    We have to prove that 
-    \[
-        i₀^* \bar p₂^! j_{!} \sheaf F = 0
-        \qquad\text{and}\qquad
-        i₂^{*} {\scls f}^! j_{1,!} \sheaf G = 0
-    \]
-    for any $\sheaf F ∈ \catDModHolMon{Γ}{G×G}$ and $\sheaf G ∈ \catDModHolMon{\slsY[\stack Y₁]{\stack X}}{G×G}$.
-    Let $H$ be a component of $\bar G \setminus G$, i.e.~one of the coordinate hyperplanes of $\as n$.
-    It suffices to prove that 
-    \[
-        i₀^{H,*} \bar p₂^! j_{!} \sheaf F = 0
-        \qquad\text{and}\qquad
-        i₂^{H,*} {\scls f}^! j_{1,!} \sheaf G = 0
-    \]
-    for any such $H$.
-    We will prove the second of these statements.
-    The first follows in exactly the same way, using $\bar Γ$ and $\scls\stack X$ instead of $\sclsY[\stack Y₁]{\stack X}$ and $\sclsY[\stack Y₂]{\stack X}$.
-    The idea is to compare the above sheaves each with a sheaf that is evidently zero by cutting the space into pieces and using Mayer--Vietoris triangles.
-
-    By Lemma~\ref{lem:stabilizers_cover} the closed subschemes $\stabclsY[\stack Y_i]{S}\stack X$ for $S ∈ \Stab \stack X$ cover $\sclsY[\stack Y_i]{\stack X}$.
-    If $S₁,\, S₂ ∈ \Stab\stack X$, then
-    \[
-        \stabclsY[\stack Y_i]{S₁}{\stack X} ∩ \stabclsY[\stack Y_i]{S₂}{\stack X} =
-        \stabclsY[\stack Y_i]{S₁∩S₂,\, S₁S₂}\stack X.
-    \]
-    Thus, using the notation of diagram~\eqref{eq:lem:torus:key:cartesian}, we can use Mayer--Vietoris triangles to write $i₂^{H,*} {\scls f}^!
-j_{1,!} \sheaf G$ as an iterated extension of (direct sums of) sheaves of the form
-    \[
-        i^{H,*}_2 α_{2,*}^{S₁,S₂}α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G, \qquad S₁ ⊆ S₂ ∈ \Stab \stack X.
-    \]
-    Similarly we can write ${\scls f}^{H,!} i^{H,*}_1 j_{1,!}$ as an iterated extension of
-    \[
-        {\scls f}^{H,!} i^{H,*}_1 α_{1,*}^{S₁,S₂}α₁^{S₁,S₂,!} j_{1,!} \sheaf G, \qquad S₁ ⊆ S₂ ∈ \Stab \stack X.
-    \]
-    We have canonical maps between each of the sheaves in these triangles.
-    By Lemma~\ref{lem:torus:key} each of them, except possibly between the original sheaves, are isomorphisms.
-    But then also the canonical map
-    \[
-        i₂^{H,*} {\scls f}^! j_{1,!} \sheaf G → {\scls f}^{H,!} i^{H,*}_1 j_{1,!} \sheaf G
-    \]
-    is an isomorphism.
-    Finally, ${\scls f}^{H,!} i^{H,*}_1 j_{1,!} \sheaf G$ mush vanish, as $i^{H,*}$ can be factored through the $*$-restriction to $\slscY[\stack Y₁]{\stack X}$.
-\end{proof}
-
-\begin{proof}[Proof of Lemma~\ref{lem:torus:key}]
-    The schemes $\stablscY[\stack Y_i]{S₁,S₂}{\stack X} = \slscY[\stack Y_i]{\stack X} ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ are given by
-    \[
-        \biggl\{
-            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁(\bar S₁ \setminus S₁)
-        \biggr\}.
-    \]
-    Set $H' = H ∩ \bar S₁$ and $Z_i' = Z_i ∩ \stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$Z_{-1}' = Z_{-1} ∩ \bar Γ^{S₁,S₂}$).
-    These schemes can be described as
-    \[
-        Z_i' =
-        \biggl\{
-            \bigl(g₁,\, y,\, g₂\bigr) ∈ G × Y_i × \bar G : h_i(y) ∈ X^{S₂},\, \bigl(g₂,\, h_i(y),\, g₁h_i(y)\bigr) ∈ \bar Γ \text{ and } g₂ ∈ g₁H'
-        \biggr\}.
-    \]
-    and similarly for $Z_{-1}'$.
-    If $H' = \emptyset$ then the $Z_i'$ are empty and the statements of the lemma are trivially true.
-    Thus assume that $H'$ is not empty.
-    Let $i_i^{H'}$ be the inclusion of $Z_i'$ into $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ (resp.~$\bar Γ^{S₁,S₂}$).
-    We have to show that the canonical maps
-    \[
-        i^{H',*}_0 α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F
-        →
-        \bar p₂^{H',!} i^{H',*}_{-1} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
-    \]
-    and
-    \[
-        i^{H',*}_2 α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G
-        →
-        {\scls f}^{H',!} i^{H',*}_1 α₁^{S₁,S₂,!} j_{1,!} \sheaf G.
-    \]
-    are isomorphisms.
-
-    We will do so by using the contraction principle of Theorem~\ref{thm:pre:contraction_principle}.
-    For this we will introducing a contractive $\Gm$-action on $\bar Γ$ and all $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ such that the morphisms
-    \begin{equation}
-        \label{eq:torus:middle_row}
-        \begin{tikzcd}
-            \bar Γ^{S₁,S₂} &
-            \stabcls{S₁,S₂}{\stack X} \arrow[l, "\bar p₂"'] &
-            \stabclsY[\stack Y₁]{S₁,S₂}{\stack X} \arrow[l, "\scls{h₁}"'] &
-            \stabclsY[\stack Y₂]{S₁,S₂}{\stack X} \arrow[l, "\scls{f}"']
-        \end{tikzcd}
-    \end{equation}
-    are $\Gm$-equivariant (where we abuse notation to denote the restrictions of the morphisms with the same name).
-
-    We write $G \cong G₁ × S₁$ for some subgroup $G₁$ of $G$.
-    This gives a corresponding decomposition of the monoid $\bar G \cong \as n$ as $\bar G = \bar G₁ \bar S₁$.
-    Chose an action $μ$ of $\Gm$ on the identity component of $\bar S₁$ that contracts $\bar S₁$ onto $H'$ .
-    This induces an action of $\Gm$ on $\bar G = \bar G₁ \bar S₁$ by $u \cdot ts = tμ(u,s)$, contracting $\bar G$ to (a closed subset of) $H$.
-
-    In turn this action induces contractive actions on $\stabclsY[\stack Y_i]{S₁,S₂}{\stack X}$ and $\bar Γ^{S₁,S₂}$.
-    We write 
-    \[
-        π_i\colon \stabclsY[\stack Y_i]{S₁,S₂}{\stack X} → Z_i'
-        \qquad\text{and}\qquad
-        π_{-1}\colon \bar Γ^{S₁,S₂} → Z_{-1}'
-    \]
-    for the corresponding contraction morphisms.
-
-    We note that all D-modules are monodromic with respect to these $\Gm$-actions.
-    Thus we can apply the contraction principle and base change to obtain the canonical isomorphisms
-    \[
-        i^{H',*}_0 α₀^{S₁,S₂,!} \bar p₂^! j_{!} \sheaf F =
-        π_{0,*} \bar p₂^! α_{-1}^{S₁,S₂,!} j_{!} \sheaf F =
-        \bar p₂^{H',!} π_{-1,*} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F =
-        \bar p₂^{H',!} i^{H',*}_{-1} α_{-1}^{S₁,S₂,!} j_{!} \sheaf F
-    \]
-    and
-    \[
-        i^{H',*}_2 α₂^{S₁,S₂,!} {\scls f}^! j_{1,!} \sheaf G = 
-        π_{2,*} {\scls f}^! α₁^{S₁,S₂,!} j_{1,!} \sheaf G = 
-        {\scls f}^{H',!} π_{1,*} α₁^{S₁,S₂,!} j_{1,!} \sheaf G = 
-        {\scls f}^{H',!} i^{H',*}_1 α₁^{S₁,S₂,!} j_{1,!} \sheaf G
-    \]
-    as required.
-\end{proof}
-
 \printbibliography

### 2017-10-11 paper.tex
Parenthesis

@@
 We are led to consider the universal algebra acting on $\cat C$ by this construction, i.e.~the \emph{Hochschild cohomology} of $\cat C$.
-For a complete (pre-triangulated) dg category $\cat C$ the Hochschild cohomology is the dg algebra of derived endomorphisms of the identity functor of $\cat C$:
+For a complete pre-triangulated dg category $\cat C$ the Hochschild cohomology is the dg algebra of derived endomorphisms of the identity functor of $\cat C$:
 \[
@@
 where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
-In particular if $\stack X$ is a (separated) scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de~Rham cohomology of $\stack X$.
+In particular if $\stack X$ is a separated scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de~Rham cohomology of $\stack X$.
 However, if $\stack X$ is a general stack, then $Δ$ is not proper and the situation becomes more complicated.
@@
 In Section~\ref{sec:HH} we explain how morphism~\eqref{eq:intro:central_cone} arises as a morphism of monads and make precise its relationship with Hochschild cohomology of $\catDMod{\stack X}$.
-As a simple application of this formalism, we also show that $\HCoh{\catDMod{\stack X}}$ always has a subalgebra isomorphic to $\opalg{\GammadR(\stack X,\ k_{\stack X})}$.
+As a simple application of this formalism, we show that $\HCoh\bigl(\catDMod{\stack X}\bigr)$ always has a subalgebra isomorphic to $\opalg{\GammadR(\stack X,\ k_{\stack X})}$.
 
@@
 We refer to \cite{Keller:2006:OnDGCategories} for an introduction to dg categories.
-It is often convenient to regard (pretriangulated) dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2017-draft:HigherAlgebra}, which can be done via the nerve construction.
+It is often convenient to regard pretriangulated dg categories as $k$-linear stable $(∞,1)$-categories \cite{Lurie:2009:HigherToposTheory,Lurie:2017-draft:HigherAlgebra}, which can be done via the nerve construction.
 % \cite{Cohn:arXiv:DGCategoriesAreStableInfinityCategories,Faonte:arXiv:SimplicialNerveOfAnAinfinityCategory}.
@@
         \item\label{lem:smooth_or_proper:hbc} If $\Delta$ is proper, then $\stack X$ has property \hbc.
-        \item\label{lem:smooth_or_proper:scheme} If $\stack X$ is a (separated) scheme, then $\stack X$ has both properties \bc\ and \hbc.
+        \item\label{lem:smooth_or_proper:scheme} If $\stack X$ is a separated scheme, then $\stack X$ has both properties \bc\ and \hbc.
         \item\label{lem:smooth_or_proper:bg} Let $G$ be an affine algebraic group. Then the classifying stack $\cs{G}$ has both properties \bc\ and \hbc.

### 2018-04-09 paper.tex
date
Selecta submission
reviewer comments

@@
 We fix an algebraically closed base field $k$ of characteristic $0$.
-All stacks will be assumed to be algebraic over $k$ and quasi-compact with affine automorphism group (QCA).
+All stacks will be assumed to be algebraic over $k$ and quasi-compact with affine automorphism groups (QCA).
 Thus by definition for any stack $\stack X$ we have:
@@
 \]
-We note that the correct construction in more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2017-draft:HigherAlgebra}.
+We note that the correct construction is more complicated in the $∞$-categorical case and refer to \cite[Section~4.7]{Lurie:2017-draft:HigherAlgebra}.
 For any $X ∈ \cat C$ the algebra construction above gives an isomorphism of algebras
@@
     \item \emph{source} and \emph{target} maps $s,t\colon \stack G₁ \rightrightarrows \stack G₀$,
-    \item a \emph{unit} $e\colon G₀ → G₁$,
+    \item a \emph{unit} $e\colon \stack G₀ → \stack G₁$,
     \item a \emph{multiplication} (or \emph{composition}) map $m\colon \stack G₁ \mathop{×}\limits_{s,\stack G₀,t} \stack G₁ → \stack G₁$,
@@
 \[
-    ε\colon \cat C^\dual \otimes \cat C → \catVect
+    ε\colon \cat C \otimes \cat C^\dual → \catVect
 \]
@@
 Let $u = η(k)$.
-To each continuous endofunctor $F$ of $\cat C$ we can associate its kernel $\id[\cat C^\dual] \otimes F(u) ∈ \cat C^\dual \otimes \cat C$ and conversely to each kernel $Q ∈ \cat C^\dual \otimes \cat C$ we can associate the endofunctor
+To each continuous endofunctor $F$ of $\cat C$ we can associate its kernel $\bigl(\id[\cat C^\dual] \otimes F\bigr)(u) ∈ \cat C^\dual \otimes \cat C$ and conversely to each kernel $Q ∈ \cat C^\dual \otimes \cat C$ we can associate the endofunctor
 \[
@@
     \label{prop:mono-from-cohomology}%
-    There is a canonical monomorphism 
-    \[
-      \opalg{\GammadR\bigl(\stack X,\, k_{\stack X}\bigr)}
-        \hookrightarrow
-        \HCoh\bigl(\catDMod{\stack X}\bigr).
-    \]
+    The Hochschild cohomology $\HCoh\bigl(\catDMod{\stack X}\bigr)$ has $\opalg{\GammadR\bigl(\stack X,\, k_{\stack X}\bigr)}$ as a direct summand.
 \end{Prop}
@@
     for some $\sheaf F \in \catDModHol{\stack X}$, we see that the connection morphism $δ$ is the zero morphism (indeed $\eta \circ \delta[1] = 0$ and $\eta$ is mono).
-    This in turn implies that the induced map
+    Thus the same is true after applying $\Hom(k_{\stack X}, \{-\})$.
+    In particular, the induced map
     \[
@@
     \]
-    on cohomology is a monomorphism as well.
+    is a split monomorphism.
 \end{proof}

### 2018-04-10 paper.tex
imrn style

@@
-\documentclass[english]{ck-article}
-
-\title{Hochschild cohomology of torus equivariant D-modules}
-\author{Clemens Koppensteiner}
+\documentclass{oupau}
 
@@
 
-\addbibresource{math.bib}
+\usepackage[utf8]{inputenc}
+\usepackage[T1]{fontenc}
+
+\usepackage{amsmath,amsfonts,amssymb,amsthm}
+\usepackage{mathtools,extpfeil,xfrac}
+\usepackage{csquotes}
+\usepackage{microtype}
+\usepackage{tikz-cd}
+
+\setcitestyle{numbers}
+
+\RequirePackage{enumitem}
+\setlist[enumerate,1]{label=(\roman*)}
+\setlist[enumerate,2]{label=(\alph*)}
+\setlist[enumerate,3]{label=(\Alph*)}
+\setlist[enumerate,4]{label=\arabic*.}
+
+\usepackage[colorlinks=false,unicode=true]{hyperref}
+\usepackage{bookmark}
+
+\theoremstyle{remark}
+\newtheorem{remark}[theorem]{Remark}
 
@@
 }
-\newcommand\isoto\similarrightarrow         % isomorphisms
+\newcommand\isoto{\xrightarrow{\sim}}       % isomorphisms
 \newcommand\proj[1]{\operatorname{pr}_{#1}} % projection on a factor
@@
 % Sheaves and D-modules
-\newcommand\sheaf\mathscr
+\newcommand\sheaf\mathcal
 \DeclareMathOperator\supp{supp}     % support
 \newcommand\catDMod[2][]{\cat{DMod}_{#1}(#2)}   % category of D-modules
-\newcommand\catDModHol[1]{\catDMod[\mathup{hol}]{#1}}   % holonomic D-modules
+\newcommand\catDModHol[1]{\catDMod[\mathrm{hol}]{#1}}   % holonomic D-modules
 \newcommand\dR{\mathrm{dR}}
@@
 
-\newcommand\ls[1]{\mathbfcal{L} #1}
-\newcommand\lsY[2][\stack Y]{\mathbfcal{L}_{#1} #2}
-\newcommand\cls[1]{\overline{\mathbfcal{L}} #1}
-\newcommand\clsY[2][\stack Y]{\overline{\mathbfcal{L}}_{#1} #2}
-\newcommand\lsc[1]{\mathbfcal{L}^c #1}
-\newcommand\lscY[2][\stack Y]{\mathbfcal{L}_{#1}^c #2}
+\newcommand\ls[1]{\mathcal{L} #1}
+\newcommand\lsY[2][\stack Y]{\mathcal{L}_{#1} #2}
+\newcommand\cls[1]{\overline{\mathcal{L}} #1}
+\newcommand\clsY[2][\stack Y]{\overline{\mathcal{L}}_{#1} #2}
+\newcommand\lsc[1]{\mathcal{L}^c #1}
+\newcommand\lscY[2][\stack Y]{\mathcal{L}_{#1}^c #2}
 
@@
 \begin{document}
-\maketitle
-
-\begin{abstract}
+
+\title{Hochschild cohomology of torus equivariant D-modules}
+\shorttitle{Hochschild cohomology of torus equivariant D-modules}
+
+\author{Clemens Koppensteiner\affil{1}}
+\abbrevauthor{C. Koppensteiner}
+\headabbrevauthor{C. Koppensteiner}
+\address{%
+    \affilnum{1}Institute for Advanced Study, 1 Einstein Dr, Princeton, NJ 08540, USA
+}
+
+\received{}
+%\date{April 9, 2018}
+
+\begin{abstract}%
   We discuss the Hochschild cohomology of the category of D-modules associated to an algebraic stack.
@@
 \end{abstract}
+
+\maketitle
 
@@
 
-\begin{Thm}\label{thm:main}
+\begin{theorem}\label{thm:main}
     Let $G \cong \Gm^n$ be a torus acting on a normal quasi-projective variety $X$ over an algebraically closed field $k$ of characteristic $0$.
@@
     where the algebra structure on $\GammadR\bigl(X/G,\,p_{1,!} p₂^! k_{X/G}\bigr)$ is induced by the groupoid structure on $\ls(X/G)$.
-\end{Thm}
+\end{theorem}
 
@@
 We will be mainly concerned with the subcategory of holonomic D-modules since they enjoy extended functoriality.
-\begin{Def}
+\begin{definition}
     A $D$-module $\sheaf F ∈ \catDMod{\stack X}$ is called \emph{holonomic} if $f^!\sheaf F$ is holonomic for any smooth morphism $f\colon Z → \stack X$ from a scheme $Z$.
     The full subcategory of holonomic D-modules will be denoted $\catDModHol{\stack X}$.
-\end{Def}
+\end{definition}
 
@@
 
-\begin{Prop}
+\begin{proposition}
     Let $f\colon \stack X → \stack Y$ be a schematic morphism.
@@
     \]
-\end{Prop}
+\end{proposition}
 
@@
 
-\begin{Lem}
+\begin{lemma}
     For a smooth and schematic morphism $f$ the functor $f^!$ is conservative.
-\end{Lem}
-
-\begin{Prop}[{\cite[Section~4.2.1.3]{GaitsgoryRozenblyum:2017:StudyInDAG:2}}]
+\end{lemma}
+
+\begin{proposition}[{\cite[Section~4.2.1.3]{GaitsgoryRozenblyum:2017:StudyInDAG:2}}]
     \label{prop:pre:base-change}%
@@
     Similarly, if $f$ is an open immersion, then the base change isomorphism coincides with the natural transformation resulting from the adjunctions $(f^!,f_*)$ and $(p^!, p_*)$.
-\end{Prop}
-
-\begin{Prop}
+\end{proposition}
+
+\begin{proposition}
     \label{prop:pre:projection-formula}%
@@
     for $\sheaf F ∈ \catDMod{\stack Y}$ and $\sheaf G ∈ \catDMod{\stack X}$.
-\end{Prop}
-
-\begin{Rem}
+\end{proposition}
+
+\begin{remark}
     Propositions \ref{prop:pre:base-change} and \ref{prop:pre:projection-formula} hold more generally when $f$ is merely a \enquote{safe} morphism.
@@
     We fill not use either notion here and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
-\end{Rem}
+\end{remark}
 
@@
 
-\begin{Prop}[{\cite[Section~2.5]{GaitsgoryRozenblyum:2014:CrystalsAndDModules}}]
+\begin{proposition}[{\cite[Section~2.5]{GaitsgoryRozenblyum:2014:CrystalsAndDModules}}]
     \label{prop:recollement-std}%
@@
     are isomorphisms, the functors $j^!i_*$ and $i^!j_*$ vanish and $i_*$ and $j_*$ are full embeddings.
-\end{Prop}
+\end{proposition}
 
@@
 
-\begin{Ex}
+\begin{example}
     For our purpose the most important example is the following:
@@
     The source and target maps are given by $p₁$ and $p₂$, the unit by the diagonal $Δ\colon \stack X → \stack X×_\stack S\stack X$, the inverse by interchanging the factors and multiplication is $p₁₃\colon \stack X ×_\stack S \stack X ×_\stack S \stack X → \stack X×_\stack S\stack X$.
-\end{Ex}
+\end{example}
 
@@
 
-\begin{Lem}
+\begin{lemma}
     \label{lem:pre:groupoid_monad_hol}%
@@
     Then the endofunctor $p_{t,!} p_s^!$ of $\catDModHol{\stack X}$ has a canonical structure of a monad and as such is isomorphic to the adjunction monad $f^!f_!$.
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Lem}\label{lem:pre:hcoh}
+\begin{lemma}\label{lem:pre:hcoh}
     Let $\stack X$ be a stack.
@@
     \]
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Ex}
+\begin{example}
     The base change morphism \eqref{eq:central_iso} is also an isomorphism if $Δ$ is smooth.
@@
     If $G$ is reductive, then $\GammadR(G, k_G)^\dual$ is an exterior algebra and thus its Hochschild cohomology can be computed directly.
-\end{Ex}
+\end{example}
 
@@
 
-\begin{Prop}
+\begin{proposition}
     \label{prop:mono-from-cohomology}%
     The Hochschild cohomology $\HCoh\bigl(\catDMod{\stack X}\bigr)$ has $\opalg{\GammadR\bigl(\stack X,\, k_{\stack X}\bigr)}$ as a direct summand.
-\end{Prop}
+\end{proposition}
 
@@
 
-\begin{Def}
+\begin{definition}
   Let $\catK{\stack X}$ be the full subcategory of $\catDMod{\stack X}$ generated by $k_{\stack X}$ and let $\catKHol{\stack X}$ be its full subcategory consisting of holonomic objects.
-\end{Def}
+\end{definition}
 
@@
 
-\begin{Def}
+\begin{definition}
     Let $\stack X$ be any QCA stack.
@@
     of functors $\catKHol{\stack X} \to \catDModHol{\stack X}$ is an equivalence.
-\end{Def}
+\end{definition}
 
@@
 
-\begin{Def}
+\begin{definition}
     Let $\stack X$ be a QCA stack and consider the Cartesian square
@@
     of functors $\catKHol{\stack G_n} \to \catDModHol{\stack G_{m+1}}$ is an equivalence.
-\end{Def}
-
-\begin{Cor}\label{cor:properties_imply_monads}
+\end{definition}
+
+\begin{corollary}\label{cor:properties_imply_monads}
   If $\stack X$ has properties \bc\ and \hbc, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
@@
   \]
-\end{Cor}
+\end{corollary}
 
@@
 
-\begin{Rem}
+\begin{remark}
     We expect that most quotient stacks do not have property \bc.
     For example, a direct computation shows that the transformation of property \bc\ is not an isomorphism for the D-module $k$ on the stack $\ps1/\Ga$.
-\end{Rem}
-
-\begin{Lem}\label{lem:smooth_or_proper}
+\end{remark}
+
+\begin{lemma}\label{lem:smooth_or_proper}
     Let $\stack X$ be a QCA stack with diagonal morphism $\Delta\colon \stack X \to \stack X \times \stack X$.
@@
     \end{enumerate}
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Lem}\label{lem:lc_immersion}
+\begin{lemma}\label{lem:lc_immersion}
     Let $i\colon\stack Y \hookrightarrow \stack X$ is a locally closed immersion of QCA stacks.
     If $\stack X$ has property \bc\ or property \hbc, then so does $\stack Y$.
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Lem}\label{lem:open_cover}
+\begin{lemma}\label{lem:open_cover}
     If $\stack X$ has an cover by open substacks $\stack U_i$ with property \bc\ (resp.~with property \hbc), then $\stack X$ has property \bc\ (resp.~property \hbc).
-    \qed
-\end{Lem}
-
-\begin{Lem}\label{lem:product}
+    %\qed
+\end{lemma}
+
+\begin{lemma}\label{lem:product}
     If $\stack{X_1}$ and $\stack{X_2}$ both have property \bc\ (resp.~property \hbc), then so does $\stack{X_1} \times \stack{X_2}$.
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Lem}\label{lem:product_quotient}
+\begin{lemma}\label{lem:product_quotient}
   Let $G$ be an affine algebraic group acting on schemes $X_1$ and $X_2$.
@@
   Then so does $(X_1 \times X_2)/G$.
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Thm}[{\cite[Corollary~C.5.4]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}}]
+\begin{theorem}[{\cite[Corollary~C.5.4]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}}]
     \label{thm:contraction_principle}%
@@
     \]
-\end{Thm}
-
-\begin{Rem}
+\end{theorem}
+
+\begin{remark}
   For our intended application in the proof of Theorem~\ref{thm:torus_quotient}, the special case of this statement for $\Gm$-quotient stacks is sufficient.
   In this case the statement can be proved directly without having to show the full \enquote{stacky} version, cf.~\cite[Proposition~5.3.2]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}.
-\end{Rem}
-
-\begin{Prop}\label{prop:contractive}
+\end{remark}
+
+\begin{proposition}\label{prop:contractive}
     Assume that $\stack X$ has a trivial contractive $\Gm$-action such that $i\colon \stack X^0 \to \stack X$ is a closed immersion and both $\stack X^0$ and $\stack U = \stack X\setminus \stack X^0$ have property \bc\ (respectively property \hbc).
     Then so does $\stack X$.
-\end{Prop}
+\end{proposition}
 
@@
 
-\begin{Thm}\label{thm:torus_quotient}
+\begin{theorem}\label{thm:torus_quotient}
     Let $X$ be a normal quasi-projective variety $X$ over an algebraically closed field $k$ of characteristic $0$ with an action of a torus $T$.
     Then the quotient stack $\stack X = X/T$ has properties \bc\ and \hbc.
-\end{Thm}
+\end{theorem}
 
@@
 
-\begin{Ex}
+\begin{example}
   To illustrate let us compute $\HCoh(\catDMod{\as1/\Gm})$ where $\Gm$ acts in the usual way.
@@
   In a future note we plan to give explicit computations for general toric varieties.
-\end{Ex}
+\end{example}
 
@@
 
-\begin{Def}
+\begin{definition}
     A \emph{relative compactification} of a morphism $f\colon \stack X → \stack Y$ is a commutative diagram
@@
     where $j$ is an open embedding and $\bar f$ is proper.
-\end{Def}
+\end{definition}
 
@@
 
-\begin{Lem}
+\begin{lemma}
     \label{lem:base-change-criterion}%
@@
     In particular, if $i^* \bar{q}^! j_! = 0$, then $p_! q^! \to g^! f_!$ is an isomorphism of functors.
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Def}
+\begin{definition}
     Let $\stack X = X/G$.
@@
     We have an open embedding $j\colon X \hookrightarrow \bar{\stack X}$ and a proper morphism $\shortbar Δ\colon \bar{\stack X} → \stack X × \stack X$ induced by the map $f$ above, such that $Δ = \shortbar Δ ∘ j$.
-\end{Def}
-
-\begin{Rem}
+\end{definition}
+
+\begin{remark}
     In the case of $G = \Gm$ the compactification $\bar Γ$ is explicitly described in \cite{DrinfeldGaitsgory:2014:OnATheoremOfBraden}.
@@
     The resulting constructions are useful for explicit computations.
-\end{Rem}
+\end{remark}
 
@@
 
-\begin{Def}\label{def:good}
+\begin{definition}\label{def:good}
     We say that a quotient stack $\stack X = X/G$ \emph{\isgood} if the following two conditions hold.
@@
     \end{enumerate}
-\end{Def}
-
-\begin{Prop}\label{prop:good-is-good}
+\end{definition}
+
+\begin{proposition}\label{prop:good-is-good}
     If $\stack X = X/G$ \isgood, then there exists a canonical structure of monad on $p_{1,!}p₂^!$ and the morphism $p_{2,!}p₁^! → Δ^!Δ_!$ is an isomorphism of monads.
@@
 
-\begin{Lem}
+\begin{lemma}
     Let $U$ be a $G$-equivariant open subset of $X$.
     If $X/G$ \isgood\ then $U/G$ \isgood.
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Lem}\label{lem:base-change:scheme-cover}
+\begin{lemma}\label{lem:base-change:scheme-cover}
     A quotient stack $X/G$ \isgood\ if the following two conditions hold:
@@
 
-\begin{Lem}
+\begin{lemma}
     \label{lem:base-change:cover}%
     If there exists a $G$-stable open cover $U_i$ of $X$ such that all stacks $U_i/G$ \aregood, then $X/G$ \isgood.
-\end{Lem}
+\end{lemma}
 
@@
 
-\begin{Lem}\label{lem:base-change:cover-by-relative-compactifications}
+\begin{lemma}\label{lem:base-change:cover-by-relative-compactifications}
     Let $H_i$ be an open cover of $\bar G$ by $G×G$-stable subvarieties, each containing $G$.
@@
 
-\printbibliography
-
+\begin{thebibliography}{20}
+\providecommand{\url}[1]{\texttt{#1}}
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{doi: #1}\else
+  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi
+
+\bibitem{ArinkinGaitsgory:2015:SingularSupport}
+Dima Arinkin and Dennis Gaitsgory.
+\newblock Singular support of coherent sheaves and the geometric {L}anglands
+  conjecture.
+\newblock \emph{Selecta Mathematica. New Series}, 21\penalty0 (1):\penalty0
+  1--199, 2015.
+\newblock ISSN 1022-1824.
+\newblock \doi{10.1007/s00029-014-0167-5}.
+
+\bibitem{BeilinsonDrifeld:unpublished:Hitchin}
+Alexander Beilinson and Vladimir Drinfeld.
+\newblock Quantization of {H}itchin's integrable system and {H}ecke
+  eigensheaves.
+\newblock URL
+  \url{http://www.math.uchicago.edu/~mitya/langlands/hitchin/BD-hitchin.pdf}.
+
+\bibitem{BenZvi:mathoverflow:CohomologyOfGmodG}
+David Ben-Zvi.
+\newblock What is the equivariant cohomology of a group acting on itself by
+  conjugation?
+\newblock URL \url{http://mathoverflow.net/a/20849}.
+
+\bibitem{BenZviNadler:arXiv:CharacterTheoryOfAComplexGroup}
+David {Ben-Zvi} and David {Nadler}.
+\newblock {The Character Theory of a Complex Group}.
+\newblock \emph{ArXiv e-prints}, April 2009.
+
+\bibitem{BenZviNadler:arXiv:NonlinearTraces}
+David {Ben-Zvi} and David {Nadler}.
+\newblock {Nonlinear Traces}.
+\newblock \emph{ArXiv e-prints}, May 2013.
+
+\bibitem{BensonIyengarKrause:2008:LocalCohomologyAndSupportForTriangulatedCategories}
+Dave Benson, Srikanth~B. Iyengar, and Henning Krause.
+\newblock Local cohomology and support for triangulated categories.
+\newblock \emph{Annales Scientifiques de l'École Normale Supérieure},
+  41\penalty0 (4):\penalty0 573--619, 2008.
+\newblock ISSN 0012-9593.
+
+\bibitem{Braverman:LecturesOnAlgebraicDmodules}
+Alexander Braverman and Tatyana Chmutova.
+\newblock Lectures on algebraic $d$-modules.
+\newblock URL
+  \url{http://www.math.harvard.edu/~gaitsgde/grad_2009/Dmod_brav.pdf}.
+
+\bibitem{BravermanGaitsgory:2002:GeometricEisensteinSeries}
+Alexander Braverman and Dennis Gaitsgory.
+\newblock Geometric {E}isenstein series.
+\newblock \emph{Inventiones Mathematicae}, 150\penalty0 (2):\penalty0 287--384,
+  2002.
+\newblock ISSN 0020-9910.
+\newblock \doi{10.1007/s00222-002-0237-8}.
+
+\bibitem{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}
+V.~Drinfeld and D.~Gaitsgory.
+\newblock Compact generation of the category of {D}-modules on the stack of
+  {$G$}-bundles on a curve.
+\newblock \emph{Cambridge Journal of Mathematics}, 3\penalty0 (1-2):\penalty0
+  19--125, 2015.
+\newblock ISSN 2168-0930.
+\newblock \doi{10.4310/CJM.2015.v3.n1.a2}.
+
+\bibitem{DrinfeldGaitsgory:2013:FinitenessQuestions}
+Vladimir Drinfeld and Dennis Gaitsgory.
+\newblock On some finiteness questions for algebraic stacks.
+\newblock \emph{Geometric and Functional Analysis}, 23\penalty0 (1):\penalty0
+  149--294, 2013.
+\newblock ISSN 1016-443X.
+\newblock \doi{10.1007/s00039-012-0204-5}.
+
+\bibitem{DrinfeldGaitsgory:2014:OnATheoremOfBraden}
+Vladimir Drinfeld and Dennis Gaitsgory.
+\newblock On a theorem of {B}raden.
+\newblock \emph{Transformation Groups}, 19\penalty0 (2):\penalty0 313--358,
+  2014.
+\newblock ISSN 1083-4362.
+\newblock \doi{10.1007/s00031-014-9267-8}.
+
+\bibitem{FrancisGaitsgory:2012:ChiralKoszulDuality}
+John Francis and Dennis Gaitsgory.
+\newblock Chiral {K}oszul duality.
+\newblock \emph{Selecta Mathematica. New Series}, 18\penalty0 (1):\penalty0
+  27--87, 2012.
+\newblock ISSN 1022-1824.
+\newblock \doi{10.1007/s00029-011-0065-z}.
+
+\bibitem{GaitsgoryRozenblyum:2014:CrystalsAndDModules}
+Dennis Gaitsgory and Nick Rozenblyum.
+\newblock Crystals and {D}-modules.
+\newblock \emph{Pure and Applied Mathematics Quarterly}, 10\penalty0
+  (1):\penalty0 57--154, 2014.
+\newblock ISSN 1558-8599.
+\newblock \doi{10.4310/PAMQ.2014.v10.n1.a2}.
+
+\bibitem{GaitsgoryRozenblyum:2017:StudyInDAG:1}
+Dennis Gaitsgory and Nick Rozenblyum.
+\newblock \emph{Correspondences and Duality}, volume~1 of \emph{Mathematical
+  Surveys and Monographs}.
+\newblock American Mathematical Society, 2017{\natexlab{a}}.
+\newblock ISBN 978-1-4704-3569-1.
+
+\bibitem{GaitsgoryRozenblyum:2017:StudyInDAG:2}
+Dennis Gaitsgory and Nick Rozenblyum.
+\newblock \emph{Deformations, Lie Theory and Formal Geometry}, volume~2 of
+  \emph{Mathematical Surveys and Monographs}.
+\newblock American Mathematical Society, 2017{\natexlab{b}}.
+\newblock ISBN 978-1-4704-3570-7.
+
+\bibitem{KashiwaraSchapira:1994:SheavesOnManifolds}
+Masaki Kashiwara and Pierre Schapira.
+\newblock \emph{Sheaves on manifolds}.
+\newblock Number 292 in Grundlehren der Mathematischen Wissenschaften.
+  Springer-Verlag, Berlin, 1994.
+\newblock ISBN 3-540-51861-4.
+\newblock With a chapter in French by Christian Houzel, Corrected reprint of
+  the 1990 original.
+
+\bibitem{Keller:2006:OnDGCategories}
+Bernhard Keller.
+\newblock On differential graded categories.
+\newblock In \emph{International {C}ongress of {M}athematicians. {V}ol. {II}},
+  pages 151--190. Eur. Math. Soc., Zürich, 2006.
+
+\bibitem{Lurie:2017-draft:HigherAlgebra}
+Jacob Lurie.
+\newblock \emph{Higher Algebra}.
+\newblock URL \url{http://www.math.harvard.edu/~lurie/}.
+
+\bibitem{Lurie:2009:HigherToposTheory}
+Jacob Lurie.
+\newblock \emph{Higher topos theory}.
+\newblock Number 170 in Annals of Mathematics Studies. Princeton University
+  Press, Princeton, NJ, 2009.
+\newblock ISBN 978-0-691-14049-0; 0-691-14049-9.
+
+\bibitem{Sumihiro:1974:EquivariantCompletions}
+Hideyasu Sumihiro.
+\newblock Equivariant completion.
+\newblock \emph{Journal of Mathematics of Kyoto University}, 14:\penalty0
+  1--28, 1974.
+\newblock ISSN 0023-608X.
+\newblock \doi{10.1215/kjm/1250523277}.
+
+\end{thebibliography}
 \end{document}

### 2018-08-02 paper.tex
Referee comments, part 1

@@
 \end{equation}
-where $Δ\colon \stack X × \stack X → \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
+where $Δ\colon \stack X \to \stack X \times \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
 In particular if $\stack X$ is a separated scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de~Rham cohomology of $\stack X$.
@@
 Let $Δ\colon \stack X → \stack X × \stack X$ be the diagonal.
-The category $\catDMod{\stack X}$ has a monoidal structure given by the tensor product $\sheaf F \otimes \sheaf G \coloneq Δ^!\bigl( \sheaf F \boxtimes \sheaf G \bigr)$ with unit $ω_{\stack X} = p^!
+The category $\catDMod{\stack X}$ has a monoidal structure given by the tensor product $\sheaf F \otimes \sheaf G \coloneqq Δ^!\bigl( \sheaf F \boxtimes \sheaf G \bigr)$ with unit $ω_{\stack X} = p^!
 k$.
@@
     Alternatively they hold in full generality after replacing $f_*$ by the \enquote{renormalized de Rham pushforward}.
-    We fill not use either notion here and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
+    We will not use either notion here and refer the interested reader to \cite{DrinfeldGaitsgory:2013:FinitenessQuestions}.
 \end{remark}
@@
     Using the assumption on $\stack X$ and the fact that $i^! = i^*$ we get
-    \begin{multline*}
+    \[
         p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
         p_{\stack Y,1,!} (\ls i)^! p_{\stack X,2}^! \cong
-        i^! p_{\stack X,1,!} p_{\stack X,2}^! \isoto \\
+        i^! p_{\stack X,1,!} p_{\stack X,2}^! \isoto
         i^! \Delta_{\stack X}^! \Delta_{\stack X,!} =
@@
         \Delta_{\stack Y}^! \Delta_{\stack X,!} i^!.
-    \end{multline*}
+    \]
     Now let $i$ be a closed immersion.
@@
     Using the assumption on $\stack X$ and the fact that $i_! = i_*$ we get
-    \begin{multline*}
+    \[
         i_! p_{\stack Y,1,!} p_{\stack Y,2}^!i^! =
         p_{\stack X,1,!} (\ls i)_! p_{\stack Y,2}^!i^! \cong
-        p_{\stack X,1,!} p_{\stack X,2}^! i_!i^! \isoto \\
+        p_{\stack X,1,!} p_{\stack X,2}^! i_!i^! \isoto
         \Delta_{\stack X}^! \Delta_{\stack X,!} i_!i^! \cong
@@
         \qedhere
-    \end{multline*}
+    \]
 \end{proof}
@@
 \begin{lemma}\label{lem:open_cover}
-    If $\stack X$ has an cover by open substacks $\stack U_i$ with property \bc\ (resp.~with property \hbc), then $\stack X$ has property \bc\ (resp.~property \hbc).
+    If $\stack X$ has a cover by open substacks $\stack U_i$ with property \bc\ (resp.~with property \hbc), then $\stack X$ has property \bc\ (resp.~property \hbc).
     %\qed
@@
     The category $\catDMod{\stack X_1 \times \stack X_2}$ is generated by elements of the form $\sheaf F_1 \boxtimes \sheaf F_2$ with $\sheaf F_i \in \catDModHol{\stack X_i}$.
-    For any schematic morphism $f\colon \stack Y \to \stack Z$ of QCA stacks the functor $f^!$ is continuous on $\catDMod{\stack Z}$ and $f_!$ is preservers colimits in $\catDModHol{\stack Y}$, since it has a right adjoint.
-    Since the inclusion of a full subcategory reflects all colimits it is thus sufficient to check that the properties holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catKHol{\stack X_1 \times \stack X_2}$.
+    For any schematic morphism $f\colon \stack Y \to \stack Z$ of QCA stacks the functor $f^!$ is continuous on $\catDMod{\stack Z}$ and $f_!$ preserves colimits in $\catDModHol{\stack Y}$, since it has a right adjoint.
+    Since a full subcategory inclusion reflects all colimits it is thus sufficient to check that the properties holds on elements of the form $\sheaf F_1 \boxtimes \sheaf F_2 \in \catKHol{\stack X_1 \times \stack X_2}$.
 
@@
   \]
-  Thus it suffices to show the properties for the stacks $\stack X_1 \times \cs{G} \times \dotsb \times \cs{G} \times \stack X_2$, where they follow form Lemmas~\ref{lem:product} and~\ref{lem:smooth_or_proper}\ref{lem:smooth_or_proper:bg}.
+  Thus it suffices to show the properties for the stacks $\stack X_1 \times \cs{G} \times \dotsb \times \cs{G} \times \stack X_2$, where they follow from Lemmas~\ref{lem:product} and~\ref{lem:smooth_or_proper}\ref{lem:smooth_or_proper:bg}.
 \end{proof}
@@
     Write $\ls i \colon \ls\stack X^0 \hookrightarrow \ls\stack X$ for the closed inclusion of loop stacks.
-    We note that $\ls\stack X$ inherits a contractive $\Gm$ action form $\stack X$.
+    We note that $\ls\stack X$ inherits a contractive $\Gm$ action from $\stack X$.
     Let $\ls \pi\colon \ls\stack X \to \ls\stack X^0$ be the corresponding contraction map.
@@
 
-Theorem~\ref{thm:main} is now an immediate consequence of Theorem~\ref{thm:torus_quotient} and Corollary~\ref{cor:properties_imply_monads}
+Theorem~\ref{thm:main} is now an immediate consequence of Theorem~\ref{thm:torus_quotient} and Corollary~\ref{cor:properties_imply_monads}.
 
@@
   \[
-    p_*p_{1,!}p_2^!i_!i^!\omega_{\ls \stack X} \to
-    p_*p_{1,!}p_2^!\omega_{\ls \stack X} \to
-    p_*p_{1,!}p_2^!j_*j^!\omega_{\ls \stack X}.
+    p_*p_{1,!}i_!i^!\omega_{\ls \stack X} \to
+    p_*p_{1,!}\omega_{\ls \stack X} \to
+    p_*p_{1,!}j_*j^!\omega_{\ls \stack X}.
   \]
@@
 We pick a $G×G$-equivariant compactification $\bar G$ of $G$ and let $\bar Γ$ be the closure of $Γ$ in $\bar G × X × X × X$.
-We have an open embedding $j$ of $G × X \cong Γ$ into $\bar Γ$ and proper map $f\colon \bar Γ → X × X$ given by projection on the last two factors.
+We have an open embedding $j$ of $G × X \cong Γ$ into $\bar Γ$ and a map $f\colon \bar Γ → X × X$ given by projection on the last two factors.
 The composition $f ∘ j$ is equal to $(\proj2, a)$.
@@
 Thus for ease of notation we will from now on always set $Γ = \Gammasub a$ and $\bar Γ = \barGammasub{a}$.
+With this identification, it is clear that $f$ is proper.
 
@@
 
-Finally, can be useful to consider only partial compactifications.
+Finally, it can be useful to consider only partial compactifications.
 That is, in the constructions of Section~\ref{sec:compactification:quotient}, instead of going all the way to $\bar G$ we only use some subvariety of it.

### 2018-08-02 paper.tex
Potential confusions about the contraction principle.

@@
 We call the action \emph{(globally) contractive} if it can be extended to an action of the monoid $\as 1$.
+In this case we have in particular an action of the monoid $\{0,1\} \subset \as 1$ on $\stack X$.
 Following the convention of \cite[Appendix~C]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG} we denote by $\stack X^0$ the stack of $\{0,1\}$-equivariant maps $\{0\} \to \stack X$.
-The map $\{0\} \to \{0,1\}$ induces a \emph{contraction morphism} $\pi\colon \stack X \to \stack X^0$.
+The map $\{0\} \to \{0,1\}$ induces a \emph{contraction morphism} $\pi\colon \stack X \to \stack X^0$, while the map $\{0,1\} \to \{0\}$ induces an inclusion morphism $i\colon \stack X^0 \hookrightarrow \stack X$.
 
@@
 \begin{remark}
+    At first glance the requirement that the $\Gm$-action is trivial may seems paradoxical.
+    The example that the reader should keep in mind is the stack $\stack X = \as1/\Gm$, where the quotient is taken via the usual action of $\Gm$.
+    There is an action of $\Gm$ on $\stack X$ which comes from the action of $\Gm$ on $\as 1$.
+    This action is clearly trivial.
+    On the other hand it can be extended to an action of $\as 1$, again induced from the action on the cover.
+    This action is not trivial and is the one that defines $\stack X^0 = \cs{\Gm}$.
+\end{remark}
+
+\begin{remark}
   For our intended application in the proof of Theorem~\ref{thm:torus_quotient}, the special case of this statement for $\Gm$-quotient stacks is sufficient.
   In this case the statement can be proved directly without having to show the full \enquote{stacky} version, cf.~\cite[Proposition~5.3.2]{DrinfeldGaitsgory:2015:CompactGenerationOfDModOnBunG}.
+  We have elected to state the theorem as above in order to have a general version of the following proposition for future applications.
 \end{remark}

### 2018-08-02 paper.tex
Referee comments, part 3

@@
     Set $\stack U = U/G$.
+    Let us fix a compactification $\bar G$ of $G$ and let $\bar \Gamma \subset \bar G \times X \times X$ be as before.
     We will only show the second condition of Definition~\ref{def:good}, the first one is similar.
@@
     \end{equation}
-    The vertical arrows are open embeddings and all squares are Cartesian (where we use the same compactification of $G$ for $\bar{\stack X}$ and $\bar{\stack U}$).
+    The vertical arrows are open embeddings and all squares are Cartesian (where we use the same compactification of $G$ for $\bar{\stack X}$ and $\bar{\stack U}$, the latter being presented by $\bar \Gamma \cap \bar G \times U \times U$).
     Thus
@@
 On such a cover we will use primes to indicate maps on schemes and will use $\sls{}$ instead of $\ls{}$ for the covers of the loop spaces.
-If we start with the cover $\bar Γ → \bar{\stack X}$, the pullbacks to the part of diagram \eqref{eq:diag:central1} of interest are
+If we start with the cover $\bar Γ → \bar{\stack X}$ as in the Section~\ref{sec:compactification:quotient}, the pullbacks to the part of diagram \eqref{eq:diag:central1} of interest are
 \begin{equation}
@@
     Let $(g₁, y, g₂)$ be a point of $\sclsY \stack X$.
-    Then there exists some $U_i$ with $h'(y) ∈ U_i$.
+    Then there exists some $U_i$ with $h'(y) ∈ U_i$, where $h'\colon Y \to X$ induces the map $\stack Y \to \stack X$ as above.
     But then $g₁h'(y)$ is also in $U_i$ and hence $(h'(y), g₂, g₁h'(y)) ∈ \bar{\stack U}_i$.

### 2018-08-02 paper.tex
Correcting the bibliography

@@
   conjecture.
-\newblock \emph{Selecta Mathematica. New Series}, 21\penalty0 (1):\penalty0
+  \newblock \emph{Selecta Math. (N.S.)}, 21\penalty0 (1):\penalty0
   1--199, 2015.
@@
 \newblock \emph{ArXiv e-prints}, April 2009.
+\newblock \href{https://www.arxiv.org/abs/0904.1247}{arXiv:0904.1247}.
 
@@
 \newblock \emph{ArXiv e-prints}, May 2013.
+\newblock \href{https://www.arxiv.org/abs/1305.7175}{arXiv:1305.7175}.
 
@@
 \newblock Local cohomology and support for triangulated categories.
-\newblock \emph{Annales Scientifiques de l'École Normale Supérieure},
+\newblock \emph{Ann. Sci. \'Ec. Norm. Sup\'er. (4)},
   41\penalty0 (4):\penalty0 573--619, 2008.
@@
 Alexander Braverman and Tatyana Chmutova.
-\newblock Lectures on algebraic $d$-modules.
+\newblock Lectures on algebraic $D$-modules.
 \newblock URL
@@
 \newblock Geometric {E}isenstein series.
-\newblock \emph{Inventiones Mathematicae}, 150\penalty0 (2):\penalty0 287--384,
+\newblock \emph{Invent. Math.}, 150\penalty0 (2):\penalty0 287--384,
   2002.
@@
   {$G$}-bundles on a curve.
-\newblock \emph{Cambridge Journal of Mathematics}, 3\penalty0 (1-2):\penalty0
+\newblock \emph{Camb. J. Math.}, 3\penalty0 (1-2):\penalty0
   19--125, 2015.
@@
 \newblock On some finiteness questions for algebraic stacks.
-\newblock \emph{Geometric and Functional Analysis}, 23\penalty0 (1):\penalty0
+\newblock \emph{Geom. Funct. Anal.}, 23\penalty0 (1):\penalty0
   149--294, 2013.
@@
 \newblock On a theorem of {B}raden.
-\newblock \emph{Transformation Groups}, 19\penalty0 (2):\penalty0 313--358,
+\newblock \emph{Transform. Groups}, 19\penalty0 (2):\penalty0 313--358,
   2014.
@@
 \newblock Chiral {K}oszul duality.
-\newblock \emph{Selecta Mathematica. New Series}, 18\penalty0 (1):\penalty0
+\newblock \emph{Selecta Math. (N.S.)}, 18\penalty0 (1):\penalty0
   27--87, 2012.
@@
 \newblock Crystals and {D}-modules.
-\newblock \emph{Pure and Applied Mathematics Quarterly}, 10\penalty0
+\newblock \emph{Pure Appl. Math. Q.}, 10\penalty0
   (1):\penalty0 57--154, 2014.
@@
 \newblock Equivariant completion.
-\newblock \emph{Journal of Mathematics of Kyoto University}, 14:\penalty0
+\newblock \emph{J. Math. Kyoto Univ.}, 14:\penalty0
   1--28, 1974.

### 2018-08-04 paper.tex
Minor changes.

@@
 where $Δ\colon \stack X \to \stack X \times \stack X$ is the diagonal morphism and $ω_{\stack X}$ is the dualizing module.
-In particular if $\stack X$ is a separated scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\HCoh(\catDMod{\stack X})$ is isomorphic to the de~Rham cohomology of $\stack X$.
+In particular if $\stack X$ is a separated scheme, then $Δ$ is a closed embedding and $(Δ^*,Δ_*)$ adjunction combined with Kashiwara's Equivalence show that $\opalg{\HCoh(\catDMod{\stack X})}$ is isomorphic to the de~Rham cohomology of $\stack X$.
 However, if $\stack X$ is a general stack, then $Δ$ is not proper and the situation becomes more complicated.
@@
 \end{equation}
-and thus when the naive isomorphism \eqref{eq:intro:naive} holds.
+and thus whether the naive isomorphism \eqref{eq:intro:naive} holds.
 As an application, we prove the following theorem, giving a class of stacks where \eqref{eq:intro:naive} is indeed an isomorphism.
@@
 induces a groupoid with $\stack{G}₀ = \stack X$ and $\stack{G}₁ = \stack X ×_{\stack Y} \stack X$.
-The above constructions now give two monads on $\catDMod{\stack{X}}$: one by $(f_*,f^!)$ adjunction and one from the groupoid structure.
+The above constructions give two monads on $\catDMod{\stack{X}}$: one by $(f_*,f^!)$ adjunction and one from the groupoid structure.
 The base change isomorphism
@@
 \]
-Of course, if $\stack X$ is not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
+Of course, if $\stack X$ is QCA but not an algebraic space, then $Δ$ is not proper (nor is it in general smooth).
 Thus in general \eqref{eq:central_iso} is not an isomorphism and there is no canonical structure of monad on $p_{1,!} p₂^!$.
@@
 Dennis Gaitsgory and Nick Rozenblyum.
-\newblock \emph{Correspondences and Duality}, volume~1 of \emph{Mathematical
-  Surveys and Monographs}.
-\newblock American Mathematical Society, 2017{\natexlab{a}}.
+\newblock \emph{A Study in Derived Algebraic Geometry, Volume~1. Correspondences and Duality}.
+\newblock Number 221 in Mathematical Surveys and Monographs.
+  American Mathematical Society, 2017{\natexlab{a}}.
 \newblock ISBN 978-1-4704-3569-1.
@@
 Dennis Gaitsgory and Nick Rozenblyum.
-\newblock \emph{Deformations, Lie Theory and Formal Geometry}, volume~2 of
-  \emph{Mathematical Surveys and Monographs}.
-\newblock American Mathematical Society, 2017{\natexlab{b}}.
+\newblock \emph{A Study in Derived Algebraic Geometry, Volume~2. Deformations, Lie Theory and Formal Geometry}.
+\newblock Number 221 in Mathematical Surveys and Monographs.
+  American Mathematical Society, 2017{\natexlab{b}}.
 \newblock ISBN 978-1-4704-3570-7.
@@
 \newblock ISBN 3-540-51861-4.
-\newblock With a chapter in French by Christian Houzel, Corrected reprint of
-  the 1990 original.
+\newblock With a chapter in French by Christian Houzel.
+\newblock Corrected reprint of the 1990 original.
 

### 2018-08-05 paper.tex
OUP runs TL 2012...

@@
     \begin{tikzcd}
-        \ls \stack X \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
-        \stack X \arrow[r, "Δ"] & \stack X × \stack X
+        \ls \stack X \arrow{r}{p₂} \arrow{d}{p₁} & \stack X \arrow{d}{Δ} \\
+        \stack X \arrow{r}{Δ} & \stack X × \stack X
     \end{tikzcd}
@@
     \begin{tikzcd}
-        T \arrow[r, "Tη"] \arrow[d, "ηT"'] \arrow[dr, equal] & T² \arrow[d, "μ"] \\
-        T² \arrow[r, "μ"'] & T
+        T \arrow{r}{Tη} \arrow{d}[swap]{ηT} \arrow{dr}{\mathrm{id}} & T² \arrow{d}{μ} \\
+        T² \arrow{r}[swap]{μ} & T
     \end{tikzcd}
@@
             \begin{tikzcd}[column sep=small]
-                {} & & \stack G₁ \arrow[dddll, bend right, "s"] \arrow[dddrr, bend left, "t"] & & \\
-                & & \stack G₁ ×_{\stack G₀} \stack G₁ \arrow[u, "m"] \arrow[dl, "p₂"] \arrow[dr, "p₁"] & & \\
-                & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & & \stack G₁ \arrow[dl, "s"] \arrow[dr, "t"] & \\
+                {} & & \stack G₁ \arrow[bend right]{dddll}[swap]{s} \arrow[bend left]{dddrr}{t} & & \\
+                   & & \stack G₁ ×_{\stack G₀} \stack G₁ \arrow{u}{m} \arrow{dl}{p₂} \arrow{dr}{p₁} & & \\
+                   & \stack G₁ \arrow{dl}{s} \arrow{dr}{t} & & \stack G₁ \arrow{dl}{s} \arrow{dr}{t} & \\
                 \stack G₀ & & \stack G₀ & & \stack G₀
@@
         \begin{tikzcd}
-            \stack G₁ \arrow[r, "p_s"] \arrow[d, "p_t"] & \stack G₀ \arrow[d, "f"] \\
-            \stack G₀ \arrow[r, "f"] & \stack Y
+            \stack G₁ \arrow{r}{p_s} \arrow{d}{p_t} & \stack G₀ \arrow{d}{f} \\
+            \stack G₀ \arrow{r}{f} & \stack Y
         \end{tikzcd}
@@
     \begin{tikzcd}
-        \ls{\stack X} \arrow[r, "p₂"] \arrow[d, "p₁"] & \stack X \arrow[d, "Δ"] \\
-        \stack X \arrow[r, "Δ"] & \stack X × \stack X
+        \ls{\stack X} \arrow{r}{p₂} \arrow{d}{p₁} & \stack X \arrow{d}{Δ} \\
+        \stack X \arrow{r}{Δ} & \stack X × \stack X
     \end{tikzcd}
@@
         \begin{tikzcd}
-            \ls \stack X \arrow[d, "p_1"] \arrow[r, "p_2"] & \stack X \arrow[d, "\Delta"] \\
-            \stack X \arrow[r, "\Delta"] & \stack X \times \stack X
+            \ls \stack X \arrow{d}{p_1} \arrow{r}{p_2} & \stack X \arrow{d}{\Delta} \\
+            \stack X \arrow{r}{\Delta} & \stack X \times \stack X
         \end{tikzcd}
@@
         \begin{tikzcd}
-            \stack G_{n+1} \arrow[r, "p_{s}"] \arrow[d, "p_{F+1}"] & \stack G_n \arrow[d, "p_F"] \\
-            \stack G_{m+1} \arrow[r, "p_s"] & \stack G_m
+            \stack G_{n+1} \arrow{r}{p_{s}} \arrow{d}{p_{F+1}} & \stack G_n \arrow{d}{p_F} \\
+            \stack G_{m+1} \arrow{r}{p_s} & \stack G_m
         \end{tikzcd}
@@
     \begin{tikzcd}
-        \ls\stack X \arrow[r, "j_{\stack X}", hook] \arrow[d, "p₂"] & \cls\stack X \arrow[d, "\bar p₂"] & \lsc\stack X \arrow[l, hook', "i_{\stack X}"']  \arrow[d] \\
-        \stack X \arrow[r, hook, "j"] & \bar{\stack X} & \stack X^c \arrow[l, hook']
+        \ls\stack X \arrow[hook]{r}{j_{\stack X}} \arrow{d}{p₂} & \cls\stack X \arrow{d}{\bar p₂} & \lsc\stack X \arrow[cm left hook->]{l}[swap]{i_{\stack X}}  \arrow{d} \\
+        \stack X \arrow[hook]{r}{j} & \bar{\stack X} & \stack X^c \arrow[cm left hook->]{l}
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \lsY[\stack Y₂]{\stack X} \arrow[r, hook, "j_{\stack Y₂}"] \arrow[d, "\ls f"] & \clsY[\stack Y₂]{\stack X} \arrow[d, "{\cls f}"] & \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₁}"']  \arrow[d] \\
-        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}"] & \clsY[\stack Y₁]{\stack X} & \lscY[\stack Y₁]{\stack X} \arrow[l, hook']
+        \lsY[\stack Y₂]{\stack X} \arrow[hook]{r}{j_{\stack Y₂}} \arrow{d}{\ls f} & \clsY[\stack Y₂]{\stack X} \arrow{d}{{\cls f}} & \lscY[\stack Y₂]{\stack X} \arrow[cm left hook->]{l}[swap]{i_{\stack Y₁}}  \arrow{d} \\
+        \lsY[\stack Y₁]{\stack X} \arrow[hook]{r}{j_{\stack Y₁}} & \clsY[\stack Y₁]{\stack X} & \lscY[\stack Y₁]{\stack X} \arrow[cm left hook->]{l}
     \end{tikzcd}
@@
         \begin{tikzcd}
-            \lsY[\stack Y₁]{\stack U} \arrow[r, hook, "j_{\stack Y₁}^{\stack U}"] \arrow[d, hook, "α"] &
-            \clsY[\stack Y₁]{\stack U} \arrow[d, hook, "β"] &
-            \clsY[\stack Y₂]{\stack U} \arrow[l, "{\cls f}^{\stack U}"'] \arrow[d, hook, "γ"] &
-            \lscY[\stack Y₂]{\stack U} \arrow[l, hook', "i^{\stack U}_{\stack Y₂}"'] \arrow[d, hook, "δ"] \\
+            \lsY[\stack Y₁]{\stack U} \arrow[hook]{r}{j_{\stack Y₁}^{\stack U}} \arrow[hook]{d}{α} &
+            \clsY[\stack Y₁]{\stack U} \arrow[hook]{d}{β} &
+            \clsY[\stack Y₂]{\stack U} \arrow{l}[swap]{{\cls f}^{\stack U}} \arrow[hook]{d}{γ} &
+            \lscY[\stack Y₂]{\stack U} \arrow[cm left hook->]{l}[swap]{i^{\stack U}_{\stack Y₂}} \arrow[hook]{d}{δ} \\
             %
-            \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}^{\stack X}"] &
+            \lsY[\stack Y₁]{\stack X} \arrow[hook]{r}{j_{\stack Y₁}^{\stack X}} &
             \clsY[\stack Y₁]{\stack X} &
-            \clsY[\stack Y₂]{\stack X} \arrow[l, "{\cls f}^{\stack X}"'] &
-            \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i^{\stack X}_{\stack Y₂}"']
+            \clsY[\stack Y₂]{\stack X} \arrow{l}[swap]{{\cls f}^{\stack X}} &
+            \lscY[\stack Y₂]{\stack X} \arrow[cm left hook->]{l}[swap]{i^{\stack X}_{\stack Y₂}}
         \end{tikzcd}
@@
     \begin{tikzcd}
-        Γ \arrow[r, hook, "j'"] \arrow[d] &
-        \bar Γ \arrow[d] &
-        \scls \stack X \arrow[l, "\bar p₂'"'] \arrow[d] &
-        \slsc \stack X \arrow[l, hook', "i_{\stack X}'"'] \arrow[d]\\
+        Γ \arrow[hook]{r}{j'} \arrow{d} &
+        \bar Γ \arrow{d} &
+        \scls \stack X \arrow{l}[swap]{\bar p₂'} \arrow{d} &
+        \slsc \stack X \arrow[cm left hook->]{l}[swap]{i_{\stack X}'} \arrow{d}\\
         %
-        \stack X \arrow[r, hook, "j"] &
+        \stack X \arrow[hook]{r}{j} &
         \bar{\stack X} &
-        \cls \stack X \arrow[l, "\bar p₂"'] &
-        \lsc \stack X \arrow[l, hook', "i_{\stack X}"']
+        \cls \stack X \arrow{l}[swap]{\bar p₂} &
+        \lsc \stack X \arrow[cm left hook->]{l}[swap]{i_{\stack X}}
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \slsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}'"] \arrow[d] &
-        \sclsY[\stack Y₁]{\stack X} \arrow[d] &
-        \sclsY[\stack Y₂]{\stack X} \arrow[l, "\scls f"'] \arrow[d] &
-        \slscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₂}'"'] \arrow[d]\\
+        \slsY[\stack Y₁]{\stack X} \arrow[hook]{r}{j_{\stack Y₁}'} \arrow{d} &
+        \sclsY[\stack Y₁]{\stack X} \arrow{d} &
+        \sclsY[\stack Y₂]{\stack X} \arrow{l}[swap]{\scls f} \arrow{d} &
+        \slscY[\stack Y₂]{\stack X} \arrow[cm left hook->]{l}[swap]{i_{\stack Y₂}'} \arrow{d}\\
         %
-        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "j_{\stack Y₁}"] &
+        \lsY[\stack Y₁]{\stack X} \arrow[hook]{r}{j_{\stack Y₁}} &
         \clsY[\stack Y₁]{\stack X} &
-        \clsY[\stack Y₂]{\stack X} \arrow[l, "\cls f"'] &
-        \lscY[\stack Y₂]{\stack X} \arrow[l, hook', "i_{\stack Y₂}"']
+        \clsY[\stack Y₂]{\stack X} \arrow{l}[swap]{\cls f} &
+        \lscY[\stack Y₂]{\stack X} \arrow[cm left hook->]{l}[swap]{i_{\stack Y₂}}
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \stack X \arrow[r, hook, "{}^{H_i}j"] &
+        \stack X \arrow[hook]{r}{{}^{H_i}j} &
         {}^{H_i}\bar{\stack X} &
-        {}^{H_i}\clsY[\stack X]{\stack X} \arrow[l, "{}^{H_i}p_{2}"'] &
-        {}^{H_i}\lscY[\stack X]{\stack X} \arrow[l, hook', "{}^{H_i}i_{\stack X}"']
+        {}^{H_i}\clsY[\stack X]{\stack X} \arrow{l}[swap]{{}^{H_i}p_{2}} &
+        {}^{H_i}\lscY[\stack X]{\stack X} \arrow[cm left hook->]{l}[swap]{{}^{H_i}i_{\stack X}}
     \end{tikzcd}
@@
     \begin{tikzcd}
-        \lsY[\stack Y₁]{\stack X} \arrow[r, hook, "{}^{H_i}j_{\stack Y₁}"] &
+        \lsY[\stack Y₁]{\stack X} \arrow[hook]{r}{{}^{H_i}j_{\stack Y₁}} &
         {}^{H_i}\clsY[\stack Y₁]{\stack X} &
-        {}^{H_i}\clsY[\stack Y₂]{\stack X} \arrow[l, "{}^{H_i}\cls f"'] &
-        {}^{H_i}\lscY[\stack Y₂]{\stack X}. \arrow[l, hook', "{}^{H_i}i_{\stack Y₂}"']
+        {}^{H_i}\clsY[\stack Y₂]{\stack X} \arrow{l}[swap]{{}^{H_i}\cls f} &
+        {}^{H_i}\lscY[\stack Y₂]{\stack X}. \arrow[cm left hook->]{l}[swap]{{}^{H_i}i_{\stack Y₂}}
     \end{tikzcd}.
